### 2021-09-11 draft.tex
Deploy to GitHub Pages

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\thispagestyle{empty}
{\Large\bfseries\sffamily Food web reconstruction through phylogenetic
transfer of low-rank network representation}
\vskip 5em

%
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
%
\,\textsuperscript{1,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{1,3,2}\quad %
\href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{5,2}\quad %
\href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
%
\,\textsuperscript{6}\quad %
\href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
%
\,\textsuperscript{4}\quad %
\href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
%
\,\textsuperscript{7}\quad %
\href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
%
\,\textsuperscript{8}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,Département de Sciences Biologiques, Université de
Montréal, Montréal, Canada\quad \textsuperscript{2}\,Québec Centre for
Biodiversity Sciences, Montréal,
Canada\quad \textsuperscript{3}\,Université de Sherbrooke, Sherbrooke,
Canada\quad \textsuperscript{4}\,Department of Forest Resources
Management, University of British Columbia, Vancouver,
Canada\quad \textsuperscript{5}\,Department of Biology, McGill
University, Montréal, Canada\quad \textsuperscript{6}\,Department of
Ecology \& Evolutionary Biology, University of Toronto, Toronto,
Canada\quad \textsuperscript{7}\,Centre for Integrative Ecology, School
of Biological Sciences, University of Canterbury, Canterbury, New
Zealand\quad \textsuperscript{8}\,School of Mathematics and Statistics,
University of Canterbury, Canterbury, New Zealand

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill
\textbf{\sffamily Abstract: }Despite their importance in many ecological
processes, collecting data and information on ecological interactions,
and therefore species interaction networks, is an exceedingly
challenging task. For this reason, large parts of the world have a
deficit of data of which species interact, and what we can expect the
network structure of these interactions to be. As data collection alone
is unlikely to be sufficient at filling these global gaps, community
ecologists must adopt predictive methods. In this contribution we
develop such a method, relying on graph embedding (the extraction of
explanatory latent variables from known graph structures) and transfer
learning (the application of previous solution to novel problems with
limited predictors overlap) in order to assemble a predicted list of
trophic interactions between mammals of Canada. This interaction list is
derived from extensive knowledge of the mammalian food web of Europe,
despite the fact that there are fewer than 5\% of common species between
the two locations. We provide guidance on how this method can be adapted
by substituting some approaches or predictors in order to make it more
generally applicable to a broad family of ecological problems.
\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

There are two core challenges we are faced with in furthering our
understanding of ecological networks across space, particularly at
macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard and Olesen
2016). First, networks within a location are difficult to sample
properly (Jordano 2016a, 2016b), resulting in a widespread ``Eltonian
shortfall'' (Hortal et al. 2015). This first challenge (local
incompleteness) has been, in large part, addressed by the recent
multiplication of methods aiming to predict interactions \emph{within}
an \emph{existing} network, a lot of which are reviewed in Strydom et
al. (2021). Second, recent analyses based on collected data (Poisot,
Bergeron, et al. 2021) or metadata (Cameron et al. 2019) highlight that
ecological networks are currently studied in a biased subset of space
and bioclimates, which impedes our ability to generalize any local
understanding of network structure. Meaning that although the framework
to address incompleteness \emph{within} a network exists there would
still be regions that, due to a \emph{lack} of local interaction data,
we are unable to infer potential species interactions. Having a general
solution for the issue of metaweb inference (Morales-Castilla et al.
2015) that, despite situations where minimal knowledge about
interactions within a species pool is known, is capable of producing a
plausible metaweb could be the catalyst for significant breakthroughs in
our ability to start thinking about species interactions networks over
large spatial scales.

Here, we present a general method for the transfer learning of network
representations, relying on the similarities of species in a
biologically/ecologically relevant proxy space (\emph{e.g.} shared
morphology or ancestry). Transfer learning is a machine learning
methodology that uses the knowledge gained from solving one problem and
applying it to a related (destination) problem (Torrey and Shavlik 2010;
Pan and Yang 2010). In this instance, we solve the problem of predicting
trophic interactions between species, based on knowledge extracted from
another species pool for which interactions are known, using
phylogenetic structure as a medium for transfer. This allows us to
construct a \emph{probabilistic} metaweb for a community for which we
have \emph{no} prior interaction data for the desired species pool. Our
methodology is outlined in fig.~\ref{fig:concept}, where we provide an
illustration based on learning an embedding of a metaweb of trophic
interactions for European mammals (known interactions; Maiorano et al.
2020b, 2020a), and based on phylogenetic relationships between mammals
globally (Upham, Esselstyn, and Jetz 2019), infer a metaweb for the
Canadian mammalian species pool (interactions are treated as unknown in
this instance).

\begin{figure}
\hypertarget{fig:concept}{%
\centering
\includegraphics{figures/figure-concept.png}
\caption{Overview of the phylogenetic transfer learning (and prediction)
of species interactions networks. Starting from an initial, known,
network, we learn its representation through a graph embedding step
(here, a truncated Singular Value Decomposition; Step 1), yielding a
series of latent traits (vulnerability traits representing species at
the lower trophic-level and generality traits representing species at
higher trophic-levels; \emph{sensu} Schoener (1989)); second, for the
destination species pool, we perform ancestral character estimation
using a phylogeny (here, using a Brownian model for the latent traits;
Step 2); we then sample from the reconstructed distribution of latent
traits (Step 3) to generate a probabilistic metaweb at the destination
(here, assuming a uniform distribution of traits), and threshold it to
yield the final list of interactions (Step 4).}\label{fig:concept}
}
\end{figure}

There is a plurality of measures of species similarities that can be
used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla et al.
2015); however, phylogenetic proximity has several desirable properties
when working at large scales. Gerhold et al. (2015) made the point that
phylogenetic signal captures diversification of characters (large
macro-evolutionary process), but not necessarily community assembly
(fine ecological process); Dormann et al. (2010) previously found very
similar conclusions. Interactions tend to conserve a phylogenetic signal
that encompasses a wide range of ecological and evolutionary mechanisms
(Mouquet et al. 2012; Cavender-Bares et al. 2009), and - most
importantly - retain this signal even when it is not detectable at the
community scale (Poisot and Stouffer 2018; Hutchinson, Cagua, and
Stouffer 2017). Finally, species interactions at macro-ecological scales
seem to respond mostly to macro-evolutionary processes (Price 2003);
which is evidenced by the presence of conserved backbones in food webs
(Dalla Riva and Stouffer 2016), strong evolutionary signature on prey
choice (Stouffer et al. 2012), and strong phylogenetic signature in food
web intervality (Eklöf and Stouffer 2016). Phylogenetic reconstruction
has also previously been used to understand ancestral plant-insect
interaction networks (Braga et al. 2021). Taken together, these
considerations suggest that phylogenies can reliably be used to transfer
knowledge on species interactions.

Our case study shows that phylogenetic transfer learning is indeed an
effective approach to predict the Canadian mammalian metaweb. This
showcases that although the components (species) that make up the
Canadian and European communities may not be \emph{perfectly} shared, if
the medium (proxy space) selected in the transfer step is biologically
plausible, we can still effectively learn from the known network and
make biologically relevant predictions of interactions. It should be
reiterated that the framework presented in fig.~\ref{fig:concept} is
amenable to changes; notably, the measure of similarity may not be
phylogeny, and can be replaced by information on foraging (Beckerman,
Petchey, and Warren 2006), cell-level mechanisms (Boeckaerts et al.
2021), or a combination of traits and phylogenetic structure (Stock
2021).

\hypertarget{data-used-for-the-case-study}{%
\section{Data used for the case
study}\label{data-used-for-the-case-study}}

We use data on the European metaweb assembled by Maiorano et al.
(2020b), following the definition of the metaweb first introduced by
Dunne (2006), \emph{i.e.} an inventory of all possible interactions
within species from a spatially delimited pool. Notably the metaweb is
not a prediction of the food web at any specific locale within the
frontiers of the species pool -- in fact, these local food webs are
expected to have a subset of both the species and the interactions of
their metaweb (Poisot et al. 2012). This being said, as the metaweb
represents the total of functional, phylogenetic, and macroecological
processes (Morales-Castilla et al. 2015), it is thus still worthy of
ecological attention. We induced the subgraph corresponding to all
mammals by matching species names in the original network first to the
GBIF taxonomic backbone (GBIF Secretariat 2021) and retaining all those
who matched to mammals; all nodes had valid matches to GBIF at this
step, and so this backbone is used for all name reconciliation steps as
outlined below.

The European metaweb represents the knowledge we want to learn and
transfer; the phylogenetic similarity of mammals here represents the
support for transfer. We used the mammalian consensus supertree by
Upham, Esselstyn, and Jetz (2019), for which all approximatively 6000
names have been similarly matched to their GBIF valid names. This step
allows us to place each node of the mammalian European metaweb in the
phylogeny.

The destination problem to which we want to transfer knowledge is the
trophic interactions between mammals in Canada. We obtained the list of
extant species from the IUCN checklist, and selected the terrestrial and
semi-aquatic species (this corresponds to the same selection that was
applied by Maiorano et al. (2020b) in the European metaweb). The IUCN
names were, as previously, reconciled against GBIF to have an exact
match to the taxonomy.

After taxonomic cleaning and reconciliation as outlined in the following
sections, the mammalian European metaweb had 260 species, and the
Canadian species pool has 163; of these, 17 (about 4\% of the total) are
shared, and 89 species from Canada (54\%) had at least one congeneric
species in Europe. The similarity for both species pool predictably
increases with higher taxonomic order, with 19\% of shared genera, 47\%
of shared families, and 75\% of shared orders; for the last point,
Canada and Europe each had a single unique order (\emph{Didelphimorphia}
for Canada, \emph{Erinaceomorpha} for Europe).

In the following sections, we describe the representational learning
step applied to European data, the transfer step through phylogenetic
similarity, and the generation of a probabilistic metaweb for the
destination species pool.

\hypertarget{method-description}{%
\section{Method description}\label{method-description}}

The crux of the method is the transfer of knowledge of a known network,
in order to predict interactions between species from another location.
In fig.~\ref{fig:concept}, we give a high-level overview of the
approach; in the example around which this manuscript is built
(leveraging detailed knowledge about binary trophic interactions between
Mammalia in Europe to predict the less known trophic interactions
between closely phylogenetically related Mammalia in Canada), we use a
series of specific steps for network embedding, trait inference, network
prediction and thresholding.

Specifically, our approach can be summarized as follows: from the known
network in Europe, we use a truncated Singular Value Decomposition
(t-SVD; Halko, Martinsson, and Tropp 2011) to generate latent traits
representing a low-dimensional embedding of the network; these traits
give an unbiased estimate of the node's position in the latent feature
spaces. Then, we map these latent traits onto a reference phylogeny
(other distance-based measures of species proximity that allow for the
inference of features in the latent space can be used, for example the
dissimilarity in functional traits). Based on the reconstructed latent
traits for species in the destination species pool, a Random Dot Product
Graph model (hereafter RDPG; S. J. Young and Scheinerman 2007) predicts
the interaction between species through a function of the nodes'
features through matrix multiplication. Thus, from latent traits and
nodes position, we can infer interactions.

\hypertarget{implementation-and-code-availability}{%
\subsection{Implementation and code
availability}\label{implementation-and-code-availability}}

The entire pipeline is implemented in \emph{Julia} 1.6 (Bezanson et al.
2017) and is available under the permissive MIT License at
\href{https://osf.io/2zwqm/}{\texttt{https://osf.io/2zwqm/}}. The
taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau and
Poisot 2021). The network embedding and analysis is done using
\texttt{EcologicalNetworks.jl} (Banville, Vissault, and Poisot 2021;
Poisot et al. 2019). The phylogenetic simulations are done using
\texttt{PhyloNetworks.jl} (Solís-Lemus, Bastide, and Ané 2017) and
\texttt{Phylo.jl} (Reeve et al. 2016). A complete \texttt{Project.toml}
file specifying the full tree of dependencies is available alongside the
code. This material also includes a fully annotated copy of the entire
code required to run this project (describing both the intent of the
code and discussing some technical implementation details), a vignette
for every step of the process, and a series of Jupyter notebooks with
the text and code. The pipeline can be executed on a laptop in a matter
of minutes, and therefore does not require extensive computational
power.

\hypertarget{step-1-learning-the-origin-network-representation}{%
\subsection{Step 1: Learning the origin network
representation}\label{step-1-learning-the-origin-network-representation}}

The first step in transfer learning is to learn the structure of the
original dataset. In order to do so, we rely on an approach inspired
from representational learning, where we learn a \emph{representation}
of the metaweb (in the form of the latent subspaces), rather than a list
of interactions (species \emph{a} eats \emph{b}). This approach is
conceptually different from other metaweb-scale predictions
(\emph{.e.g.} Albouy et al. 2019), in that the metaweb representation is
easily transferable. Specifically, we use RDPG to create a number of
latent variables that can be combined into an approximation of the
network adjacency matrix. RDPG results are known to have strong
phylogenetic signal, and to capture the evolutionary backbone of food
webs (Dalla Riva and Stouffer 2016). In addition, recent advances show
that the latent variables produced this way can be used to predict
\emph{de novo} network edges (Runghen, Stouffer, and Dalla Riva 2021).

The latent variables are created by performing a truncated Singular
Value Decomposition (t-SVD) on the adjacency matrix. SVD is an
appropriate embedding of ecological networks, which has recently been
shown to both capture their complex, emerging properties (Strydom, Dalla
Riva, and Poisot 2021) and to allow highly accurate prediction of the
interactions within a single network (Poisot, Ouellet, et al. 2021).
Under SVD, an adjacency matrix \(\mathbf{A}\) (where
\(\mathbf{A}_{m,n}\in\mathbb{B}\) where 1 indicates predation and 0 an
absence thereof) is decomposed into three components resulting in
\(\mathbf{A} = \mathbf{L}\mathbf{\Sigma}\mathbf{R}.\) Here,
\(\mathbf{\Sigma}\) is a \(m \times n\) diagonal matrix and contains
only singular (\(\sigma\)) values along its diagonal, \(\mathbf{L}\) is
a \(m \times m\) unitary matrix, and \(\mathbf{R}'\) a \(n \times n\)
unitary matrix. Truncating the SVD removes additional noise in the
dataset by omitting non-zero and/or smaller \(\sigma\) values from
\(\mathbf{\Sigma}\) using the rank of the matrix. Under a t-SVD
\(\mathbf{A}_{m,n}\) is decomposed so that \(\mathbf{\Sigma}\) is a
square \(r \times r\) diagonal matrix (where \(r\) is the rank of
\(\mathbf{A}\)) containing only non-zero \(\sigma\) values.
Additionally, \(\mathbf{L}\) is now a \(m \times r\) semi unitary matrix
and \(\mathbf{R}'\) a \(n \times r\) semi-unitary matrix.

The specific rank at which the SVD ought to be truncated is a difficult
question. The purpose of SVD is to remove the noise (expressed at high
dimensions) and to focus on the signal, (expressed at low dimensions).
In datasets with a clear signal/noise demarcation, a scree plot of
\(\mathbf{\Sigma}\) can show a sharp drop at the rank where noise starts
(Zhu and Ghodsi 2006). Because the European metaweb is almost entirely
known, the amount of noise is low; this is reflected in
fig.~\ref{fig:scree} (left), where the scree plot shows no important
drop, and in fig.~\ref{fig:scree} (right) where the proportion of
variance explained increases smoothly at higher dimensions. For this
reason, we default back to an arbitrary threshold that explains 60\% of
the variance in the underlying data, corresponding to 12 dimensions.

A RDPG estimates the probability of observing interactions between nodes
(species) as a function of the nodes' latent variables. The latent
variables used for the RDPG, called the left and right subspaces, are
defined as \(\mathcal{L} = \mathbf{L}\sqrt{\mathbf{\Sigma}}\), and
\(\mathcal{R} = \sqrt{\mathbf{\Sigma}}\mathbf{R}\) -- using the full
rank of \(\mathbf{A}\), \(\mathcal{L}\mathcal{R}' = \mathbf{A}\), and
using any smaller rank results in
\(\mathcal{L}\mathcal{R}' \approx \mathbf{A}\). Using a rank of 1 for
the t-SVD provides a first-order approximation of the network.

\begin{figure}
\hypertarget{fig:scree}{%
\centering
\includegraphics{figures/figure-screeplot.png}
\caption{Left: representation of the screeplot of the singular values
from the t-SVD on the European metaweb. The screeplot shows no obvious
drop in the singular values that may be leveraged to automatically
detect a minimal dimension for embedding, after \emph{e.g.} Zhu and
Ghodsi (2006). Right: cumulative fraction of variance explained by each
dimension up to the rank of the European metaweb. The grey lines
represent cutoffs at 50, 60\ldots{} 90\% of variance explained. For the
rest of the analysis, we reverted to an arbitrary threshold of 60\% of
variance explained, which represented a good tradeoff between accuracy
and reduced number of features.}\label{fig:scree}
}
\end{figure}

Because RDPG relies on matrix multiplication, the higher dimensions
essentially serve to make specific interactions converge towards 0 or 1;
therefore, for reasonably low ranks, there is no guarantee that the
values in the reconstructed network will be within the unit range. In
order to determine what constitutes an appropriate threshold for
probability, we performed the RDPG approach on the European metaweb, and
evaluated the probability threshold by treating this as a binary
classification problem, specifically assuming that both 0 and 1 in the
European metaweb are all true. Given the methodological details given in
Maiorano et al. (2020b) and O'Connor et al. (2020), this seems like a
reasonable assumption, although one that does not hold for all metawebs.
We used the thresholding approach presented in Poisot, Ouellet, et al.
(2021), and picked a cutoff that maximized Youden's \(J\) statistic
(Youden (1950); a measure of the informedness (trust) of predictions);
the resulting cutoff was 0.22, and gave an accuracy above 0.99.

The left and right subspaces for the European metaweb, accompanied by
the threshold for prediction, represent the knowledge we seek to
transfer. In the next section, we explain how we rely on phylogenetic
similarity to do so.

\hypertarget{steps-2-and-3-transfer-learning-through-phylogenetic-relatedness}{%
\subsection{Steps 2 and 3: Transfer learning through phylogenetic
relatedness}\label{steps-2-and-3-transfer-learning-through-phylogenetic-relatedness}}

In order to transfer the knowledge from the European metaweb to the
Canadian species pool, we performed ancestral character estimation using
a Brownian motion model, which is a conservative approach in the absence
of strong hypotheses about the nature of phylogenetic signal in the
network decomposition (Litsios and Salamin 2012). This uses the
estimated feature vectors for the European mammals to create a state
reconstruction for all species (conceptually something akin to a
trait-based mammalian phylogeny using generality and vulnerability
traits) and allows us to impute the missing (latent) trait data for the
Canadian species that are not already in the European network; as we are
focused on predicting contemporary interactions, we only retained the
values for the tips of the three. We assumed that all traits
(\emph{i.e.} the feature vectors for the left and right subspaces) were
independent, which is a reasonable assumption as every trait/dimension
added to the t-SVD has an \emph{additive} effect to the one before it.
Note that the Upham, Esselstyn, and Jetz (2019) tree itself has some
uncertainty associated to inner nodes of the phylogeny. In this case
study, we have decided to not propagate this uncertainty, as it would
complexify the process. The Brownian motion algorithm returns the
\emph{average} value of the trait, and its upper and lower bounds.
Because we do not estimate other parameters of the traits'
distributions, we considered that every species trait is represented as
a uniform distribution between these bounds; in a situation where the
algorithm would return point values for all simulations, one could in
theory either estimate the parameters of a distribution for each tip, or
draw randomly from the outputs. In all cases, the inferred left and
right sub-spaces for the Canadian species pool (\(\hat{\mathcal{L}}\)
and \(\hat{\mathcal{R}}\)) have entries that are distributions,
representing the range of values for a given species at a given
dimension.

These objects represent the transferred knowledge, which we can use for
prediction of the Canadian metaweb.

\hypertarget{step-4-probabilistic-prediction-of-the-destination-network}{%
\subsection{Step 4: Probabilistic prediction of the destination
network}\label{step-4-probabilistic-prediction-of-the-destination-network}}

The phylogenetic reconstruction of \(\hat{\mathcal{L}}\) and
\(\hat{\mathcal{R}}\) has an associated uncertainty, represented by the
breadth of the uniform distribution associated to each of their entries.
Therefore, we can use this information to assemble a
\emph{probabilistic} metaweb in the sense of Poisot et al. (2016),
\emph{i.e.} in which every interaction is represented as a single,
independent, Bernoulli event of probability \(p\).

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple) and right
(green/brown) subspaces, alongside the adjacency matrix of the food web
they encode (greyscale). The European metaweb is on the left, and the
imputed Canadian metaweb (before data inflation) on the right. This
figure illustrates how much structure the left sub-space captures. As we
show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
subspace are species without any prey.}\label{fig:subspaces}
}
\end{figure}

Specifically, we have adopted the following approach. For every entry in
\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\), we draw a value from
its distribution. This results in one instance of the possible left
(\(\hat{\mathcal{l}}\)) and right (\(\hat{\mathcal{r}}\)) subspaces for
the Canadian metaweb. These can be multiplied, to produce one matrix of
real values. Because the entries in \(\hat{\mathcal{l}}\) and
\(\hat{\mathcal{r}}\) are in the same space where \(\mathcal{L}\) and
\(\mathcal{R}\) were originally predicted, it follows that the threshold
\(\rho\) estimated for the European metaweb also applies. We use this
information to produce one random Canadian metaweb,
\(N = \hat{\mathcal{L}}\)\(\hat{\mathcal{R}}' \ge \rho\). As we can see
in (fig.~\ref{fig:subspaces}) the European and Canadian metawebs are
structurally similar (as would be expected given the biogeographic
similarities) and that the two (left and right) subspaces are distinct
\emph{i.e.} capturing predation (generality) and prey (vulnerability)
traits.

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
Garland, Midford, and Ives 1999), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws, etc..

\hypertarget{data-cleanup-discovery-validation-and-thresholding}{%
\subsection{Data cleanup, discovery, validation, and
thresholding}\label{data-cleanup-discovery-validation-and-thresholding}}

Once the probabilistic metaweb for Canada has been produced, we followed
a number of data inflation steps to finalize it.

\begin{figure}
\hypertarget{fig:inflation}{%
\centering
\includegraphics{figures/figure-validation.png}
\caption{Left, comparison of the probabilities of interactions assigned
by the model to all interactions (grey curve), the subset of
interactions found in GLOBI (red), and in the Strong and Leroux (2014)
Newfoundland dataset (blue). The model recovers more interaction with a
low probability compared to data mining, which can suggest that
collected datasets are biased towards more common or easy to identify
interactions. Right, distribution of the in-degree and out-degree of the
mammals from Canada in the reconstructed metaweb. This figure describes
a flat, relatively short food web, in which there are few predators but
a large number of preys.}\label{fig:inflation}
}
\end{figure}

First, we extracted the subgraph corresponding to the 17 species shared
between the European and Canadian pools and replaced these interactions
with a probability of 0 (non-interaction) or 1 (interaction). This
represents a minute modification of the inferred network (about 0.8\% of
all species pairs from the Canadian web), but ensures that we are
directly re-using knowledge from Europe.

Second, we looked for all species in the Canadian pool known to the
Global Biotic Interactions (GLoBI) database (Poelen, Simons, and Mungall
2014), and extracted their known interactions. Because GLOBI aggregates
observed interactions, it is not a \emph{networks} data source, and
therefore the only information we can reliably extract from it is that a
species pair \emph{was reported to interact at least once}. This last
statement should yet be taken with caution, as some sources in GLOBI
(\emph{e.g.} Thessen and Parr 2014) are produced though text analysis,
and therefore may not document direct evidence of the interaction.
Nevertheless, should the predictive model work, we would expect that a
majority of interactions known to GLOBI would also be predicted. After
performing this check, we set the probability of all interactions known
to GLOBI (366 in total, 33 of which were not predicted by the model, for
a success rate of 91\%) to 1.

Finally, we downloaded the data from Strong and Leroux (2014), who mined
various literature sources to identify trophic interactions in
Newfoundland. This dataset documented 25 interactions between mammals,
only two of which were not part of our (Canada-level) predictions,
resulting in a success rate of 92\%. These two interactions were added
to our predicted metaweb with a probability of 1.

\begin{figure}
\hypertarget{fig:thresholds}{%
\centering
\includegraphics{figures/figure-cutoffs.png}
\caption{Left: effect of varying the cutoff for probabilities to be
considered non-zero on the number of unique links and on \(\hat{L}\),
the probabilistic estimate of the number of links assuming that all
interactions are independent. Right: effect of varying the cutoff on the
number of disconnected species, and on network connectance. In both
panels, the grey line indicates the cutoff
\(P(i\rightarrow j) \approx 0.08\) that resulted in the first species
losing all of its interactions.}\label{fig:thresholds}
}
\end{figure}

Because the confidence intervals on the inferred trait space are
probably over-estimates, we decided to apply a thresholding step to the
interactions after the data inflation (fig.~\ref{fig:thresholds}).
Cirtwill and Hambäck (2021) proposed a number of strategies to threshold
probabilistic networks. Their methods assume the underlying data to be
tag-based sequencing, which represents interactions as co-occurrences of
predator and prey within the same tags; this is conceptually identical
to our Bernoulli-trial based reconstruction of a probabilistic network.
We performed a full analysis of the effect of various cutoffs, and as
they either resulted in removing too few interactions, or removing
enough interactions that species started to be disconnected from the
network, we set this threshold for a probability equivalent to 0 to the
largest possible value that still allowed all species to have at least
one interaction with a non-zero probability. The need for this slight
deviation from the Cirtwill and Hambäck (2021) method highlights the
need for additional development on network thresholding.

\hypertarget{results-and-discussion-of-the-case-study}{%
\section{Results and discussion of the case
study}\label{results-and-discussion-of-the-case-study}}

In fig.~\ref{fig:thresholds}, we examine the effect of varying the
cutoff on \(P(i \rightarrow j)\) on the number of links, species, and
connectance. Determining a cutoff using the maximum curvature, or
central difference approximation of the second order partial derivative,
as suggested by \emph{e.g.} Cirtwill and Hambäck (2021), results in
respectively species being lost, or almost all links being kept. We
therefore settled on the value that allowed all species to remain with
at least one interaction. This result, in and of itself, suggests that
additional methodological developments for the thresholding of
probabilistic networks are required.

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/figure-degree.png}
\caption{Top: biological significance of the first dimension. Left:
there is a linear relationship between the values on the first dimension
of the left subspace and the generality, \emph{i.e.} the relative number
of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
this subspace are at the bottom-most trophic level. Right: there is,
similarly, a linear relationship between the position of a species on
the first dimension of the right subspace and its vulnerability,
\emph{i.e.} the relative number of predators. Taken together, these two
figures show that the first-order representation of this network would
capture its degree distribution. Bottom: topological consequences of the
first dimension. Left: differences in the \(z\)-score of the actual
configuration model for the reconstructed network, and the prediction
based only on the first dimension. Right: distribution of the
differences in the left panel.}\label{fig:degree}
}
\end{figure}

The t-SVD embedding is able to learn relevant ecological features for
the network. fig.~\ref{fig:degree} shows that the first rank correlates
linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
the number of preys and predators. Importantly, this implies that a rank
1 approximation represents the configuration model for the metaweb,
\emph{i.e.} a set of random networks generated from a given degree
sequence (Park and Newman 2004). Accounting for the probabilistic nature
of the degrees, the rank 1 approximation also represents the \emph{soft}
configuration model (van der Hoorn, Lippner, and Krioukov 2018). Both
models are maximum entropy graph models (Garlaschelli, Hollander, and
Roccaverde 2018), with sharp (all network realizations satisfy the
specified degree sequence) and soft (network realizations satisfy the
degree sequence on average) local constraints, respectively. The (soft)
configuration model is an unbiased random graph model widely used by
ecologists in the context of null hypothesis significance testing of
network structure (\emph{e.g.} Bascompte et al. 2003) and can provide
informative priors for Bayesian inference of network structure
(\emph{e.g.} J.-G. Young, Cantwell, and Newman 2021). It is noteworthy
that for this metaweb, the relevant information was extracted at the
first rank. Because the first rank corresponds to the leading singular
value of the system, the results of fig.~\ref{fig:degree} have a
straightforward interpretation: degree-based processes are the most
important in structuring the mammalian food web.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

One important aspect in which Europe and Canada differ (despite their
comparable bioclimatic conditions) is the legacy of human impacts, which
have been much longer in Europe. Nenzén, Montoya, and Varela (2014)
showed that even at small scales (the Iberian peninsula), mammal food
webs retain the signal of both climate change and human activity, even
when this human activity was orders of magnitude less important than it
is now. Similarly, Yeakel et al. (2014) showed that changes in human
occupation over several centuries can lead to food web collapse.
Megafauna in particular seems to be very sensitive to human arrival
(Pires et al. 2015). In short, there is well-substantiated support for
the idea that human footprint affects more than the risk of species
extinction (Marco et al. 2018), and can lead to changes in interaction
structure. Yet, owing to the inherent plasticity of interactions, there
have been documented instances of food webs undergoing rapid
collapse/recovery cycles over short periods of time (Pedersen et al.
2017). The embedding of a network, in a sense, embeds its
macro-evolutionary history, especially as RDPG captures ecological
signal (Dalla Riva and Stouffer 2016); at this point, it is important to
recall that a metaweb is intended as a catalogue of all possible
interactions, which should then be filtered (Morales-Castilla et al.
2015). In practice (and in this instance) the reconstructed metaweb will
predict interactions that are plausible based on the species'
evolutionary history, however some interactions would not be realized
due to human impact.

Cirtwill et al. (2019) previously made the point that network inference
techniques based on Bayesian approaches would perform far better in the
presence of an interaction-level informative prior; the desirable
properties of such a prior would be that it is expressed as a
probability, preferably representing a Bernoulli event, the value of
which would be representative of relevant biological processes. We argue
that the probability returned at the very last step of our framework may
serve as this informative prior; indeed, the output of our analysis can
be used in subsequent steps, also possibly involving expert elicitation
to validate some of the most strongly recommended interactions. One
important \emph{caveat} to keep in mind when working with interaction
inference is that interactions can never really be true negatives (in
the current state of our methodological framework and data collection
limitations); this renders the task of validating a model through the
usual application of binary classification statistics very difficult
(although see Strydom et al. 2021 for a discussion of alternative
suggestions).

As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
lines around planet-wide problems''; in this regard, our approach must
contend with two interesting problems. The first is the limit of the
metaweb to embed and transfer. If the initial metaweb is too narrow in
scope, notably from a taxonomic point of view, the chances of finding
another area with enough related species to make a reliable inference
decrease. This is notably true if the metaweb is assembled in an area
with mostly endemic species. Conversely, the metaweb should be reliably
filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
species have been examined, either through literature surveys or expert
elicitation. The second problem is to determine which area should be
used to infer the new metaweb in, as this determines the species pool
that must be used. In our application, we focused on the mammals of
Canada. The upside of this approach is that information at the country
level is likely to be required by policy makers and stakeholders for
their biodiversity assessment, as each country tends to set goals at the
national level (Buxton et al. 2021) for which quantitative instruments
are designed (Turak et al. 2017), with specific strategies often enacted
at smaller scales (Ray, Grimm, and Olive 2021). Yet these national
divisions, in large parts of the world, reflect nothing except for the
legacy of settler colonialism, and operating under them must be done
under the clear realization that they contributed to the ongoing
biodiversity crisis (Adam 2014), can reinforce environmental injustice
(Choudry 2013; Domínguez and Luoma 2020), and on Turtle Island
especially, will probably end up being replaced by Indigenous principles
of land management (Eichhorn, Baker, and Griffiths 2019; No'kmaq et al.
2021).

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. TP, TS, DC, and LP received funding from the Canadian Institue
for Ecology \& Evolution. FB is funded by the Institut de Valorisation
des Données. TS, SB, and TP are funded by a donation from the Courtois
Foundation. CB was awarded a Mitacs Elevate Fellowship no. IT12391, in
partnership with fRI Research, and also acknowledges funding from
Alberta Innovates and the Forest Resources Improvement Association of
Alberta. M-JF acknowledges funding from NSERC Discovery Grant and NSERC
CRC RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
Iho National Science Challenge, administered by New Zealand Ministry of
Business, Innovation, and Employment. BM is funded by the NSERC
Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's
scholarshipTP acknowledges financial support from NSERC through the
Discovery Grants and Discovery Accelerator Supplement programs.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
Adam, Rachelle. 2014. \emph{Elephant Treaties: The Colonial Legacy of
the Biodiversity Crisis}. UPNE.

\leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
Albouy, Camille, Philippe Archambault, Ward Appeltans, Miguel B. Araújo,
David Beauchesne, Kevin Cazelles, Alyssa R. Cirtwill, et al. 2019.
{``The Marine Fish Food Web Is Globally Connected.''} \emph{Nature
Ecology \& Evolution} 3 (8): 1153--61.
\url{https://doi.org/10.1038/s41559-019-0950-y}.

\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
Banville, Francis, Steve Vissault, and Timothée Poisot. 2021.
{``Mangal.jl and EcologicalNetworks.jl: Two Complementary Packages for
Analyzing Ecological Networks in Julia.''} \emph{Journal of Open Source
Software} 6 (61): 2721. \url{https://doi.org/10.21105/joss.02721}.

\leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
Bascompte, J., P. Jordano, C. J. Melian, and J. M. Olesen. 2003. {``The
Nested Assembly of Plant-Animal Mutualistic Networks.''}
\emph{Proceedings of the National Academy of Sciences} 100 (16):
9383--87. \url{https://doi.org/10.1073/pnas.1633576100}.

\leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
Beckerman, Andrew P., Owen L. Petchey, and Philip H. Warren. 2006.
{``Foraging Biology Predicts Food Web Complexity.''} \emph{Proceedings
of the National Academy of Sciences} 103 (37): 13745--49.
\url{https://doi.org/10.1073/pnas.0603039103}.

\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J., A. Edelman, S. Karpinski, and V. Shah. 2017. {``Julia: A
Fresh Approach to Numerical Computing.''} \emph{SIAM Review} 59 (1):
65--98. \url{https://doi.org/10.1137/141000671}.

\leavevmode\hypertarget{ref-Boeckaerts2021PreBac}{}%
Boeckaerts, Dimitri, Michiel Stock, Bjorn Criel, Hans Gerstmans, Bernard
De Baets, and Yves Briers. 2021. {``Predicting Bacteriophage Hosts Based
on Sequences of Annotated Receptor-Binding Proteins.''} \emph{Scientific
Reports} 11 (1): 1467. \url{https://doi.org/10.1038/s41598-021-81063-4}.

\leavevmode\hypertarget{ref-Braga2021PhyRec}{}%
Braga, Mariana P., Niklas Janz, Sören Nylin, Fredrik Ronquist, and
Michael J. Landis. 2021. {``Phylogenetic Reconstruction of Ancestral
Ecological Networks Through Time for Pierid Butterflies and Their Host
Plants.''} \emph{Ecology Letters} n/a (n/a).
\url{https://doi.org/10.1111/ele.13842}.

\leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
Buxton, Rachel T., Joseph R. Bennett, Andrea J. Reid, Charles Shulman,
Steven J. Cooke, Charles M. Francis, Elizabeth A. Nyboer, et al. 2021.
{``Key Information Needs to Move from Knowledge to Action for
Biodiversity Conservation in Canada.''} \emph{Biological Conservation}
256: 108983. \url{https://doi.org/10.1016/j.biocon.2021.108983}.

\leavevmode\hypertarget{ref-Cameron2019UneGlo}{}%
Cameron, Erin K., Maja K. Sundqvist, Sally A. Keith, Paul J. CaraDonna,
Erik A. Mousing, Karin A. Nilsson, Daniel B. Metcalfe, and Aimée T.
Classen. 2019. {``Uneven Global Distribution of Food Web Studies Under
Climate Change.''} \emph{Ecosphere} 10 (3): e02645.
\url{https://doi.org/10.1002/ecs2.2645}.

\leavevmode\hypertarget{ref-Cavender-Bares2009MerCom}{}%
Cavender-Bares, Jeannine, Kenneth H. Kozak, Paul V. A. Fine, and Steven
W. Kembel. 2009. {``The Merging of Community Ecology and Phylogenetic
Biology.''} \emph{Ecology Letters} 12 (7): 693--715.
\url{https://doi.org/10.1111/j.1461-0248.2009.01314.x}.

\leavevmode\hypertarget{ref-Choudry2013SavBio}{}%
Choudry, Aziz. 2013. {``Saving Biodiversity, for Whom and for What?
Conservation NGOs, Complicity, Colonialism and Conquest in an Era of
Capitalist Globalization.''} In \emph{NGOization: Complicity,
Contradictions and Prospects}, 24--44. Bloomsbury Publishing.

\leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
Cirtwill, Alyssa R., Anna Eklf, Tomas Roslin, Kate Wootton, and
Dominique Gravel. 2019. {``A Quantitative Framework for Investigating
the Reliability of Empirical Network Construction.''} \emph{Methods in
Ecology and Evolution} 0 (ja).
\url{https://doi.org/10.1111/2041-210X.13180}.

\leavevmode\hypertarget{ref-Cirtwill2021BuiFoo}{}%
Cirtwill, Alyssa R., and Peter Hambäck. 2021. {``Building Food Networks
from Molecular Data: Bayesian or Fixed-Number Thresholds for Including
Links.''} \emph{Basic and Applied Ecology} 50: 67--76.
\url{https://doi.org/10.1016/j.baae.2020.11.007}.

\leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
Dalla Riva, Giulio V., and Daniel B. Stouffer. 2016. {``Exploring the
Evolutionary Signature of Food Webs' Backbones Using Functional
Traits.''} \emph{Oikos} 125 (4): 446--56.
\url{https://doi.org/10.1111/oik.02305}.

\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
Dansereau, Gabriel, and Timothée Poisot. 2021. {``SimpleSDMLayers.jl and
GBIF.jl: A Framework for Species Distribution Modeling in Julia.''}
\emph{Journal of Open Source Software} 6 (57): 2872.
\url{https://doi.org/10.21105/joss.02872}.

\leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
Domínguez, Lara, and Colin Luoma. 2020. {``Decolonising Conservation
Policy: How Colonial Land and Conservation Ideologies Persist and
Perpetuate Indigenous Injustices at the Expense of the Environment.''}
\emph{Land} 9 (3): 65. \url{https://doi.org/10.3390/land9030065}.

\leavevmode\hypertarget{ref-Dormann2010EvoCli}{}%
Dormann, Carsten F., Bernd Gruber, Marten Winter, and Dirk Herrmann.
2010. {``Evolution of Climate Niches in European Mammals?''}
\emph{Biology Letters} 6 (2): 229--32.
\url{https://doi.org/10.1098/rsbl.2009.0688}.

\leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
Dunne, Jennifer A. 2006. {``The Network Structure of Food Webs.''} In
\emph{Ecological Networks: Linking Structure and Dynamics}, edited by
Jennifer A Dunne and Mercedes Pascual, 27--86. Oxford University Press.

\leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
Eichhorn, Markus P., Kate Baker, and Mark Griffiths. 2019. {``Steps
Towards Decolonising Biogeography.''} \emph{Frontiers of Biogeography}
12 (1): 1--7. \url{https://doi.org/10.21425/F5FBG44795}.

\leavevmode\hypertarget{ref-Eklof2016PhyCom}{}%
Eklöf, Anna, and Daniel B. Stouffer. 2016. {``The Phylogenetic Component
of Food Web Structure and Intervality.''} \emph{Theoretical Ecology} 9
(1): 107--15. \url{https://doi.org/10.1007/s12080-015-0273-9}.

\leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
Garland, THEODORE, JR., PETER E. Midford, and ANTHONY R. Ives. 1999.
{``An Introduction to Phylogenetically Based Statistical Methods, with a
New Method for Confidence Intervals on Ancestral Values1.''}
\emph{American Zoologist} 39 (2): 374--88.
\url{https://doi.org/10.1093/icb/39.2.374}.

\leavevmode\hypertarget{ref-Garlaschelli2018CovStr}{}%
Garlaschelli, Diego, Frank den Hollander, and Andrea Roccaverde. 2018.
{``Covariance Structure Behind Breaking of Ensemble Equivalence in
Random Graphs.''} \emph{Journal of Statistical Physics} 173 (3-4):
644--62. \url{https://doi.org/10.1007/s10955-018-2114-x}.

\leavevmode\hypertarget{ref-GBIFSecretariat2021GbiBac}{}%
GBIF Secretariat. 2021. {``GBIF Backbone Taxonomy.''}
\url{https://doi.org/10.15468/39omei}.

\leavevmode\hypertarget{ref-Gerhold2015PhyPat}{}%
Gerhold, Pille, James F. Cahill, Marten Winter, Igor V. Bartish, and
Andreas Prinzing. 2015. {``Phylogenetic Patterns Are Not Proxies of
Community Assembly Mechanisms (they Are Far Better).''} \emph{Functional
Ecology} 29 (5): 600--614.
\url{https://doi.org/10.1111/1365-2435.12425}.

\leavevmode\hypertarget{ref-Halko2011FinStr}{}%
Halko, N., P. G. Martinsson, and J. A. Tropp. 2011. {``Finding Structure
with Randomness: Probabilistic Algorithms for Constructing Approximate
Matrix Decompositions.''} \emph{SIAM Review} 53 (2): 217--88.
\url{https://doi.org/10.1137/090771806}.

\leavevmode\hypertarget{ref-Herbert1965Dun}{}%
Herbert, Frank. 1965. \emph{Dune}. First. Philadelphia: Chilton Book
Company.

\leavevmode\hypertarget{ref-vanderHoorn2018SpaMax}{}%
Hoorn, Pim van der, Gabor Lippner, and Dmitri Krioukov. 2018. {``Sparse
Maximum-Entropy Random Graphs with a Given Power-Law Degree
Distribution.''} \emph{Journal of Statistical Physics} 173 (3-4):
806--44. \url{https://doi.org/10.1007/s10955-017-1887-7}.

\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
Hortal, Joaquín, Francesco de Bello, José Alexandre F. Diniz-Filho,
Thomas M. Lewinsohn, Jorge M. Lobo, and Richard J. Ladle. 2015. {``Seven
Shortfalls That Beset Large-Scale Knowledge of Biodiversity.''}
\emph{Annual Review of Ecology, Evolution, and Systematics} 46 (1):
523--49. \url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}.

\leavevmode\hypertarget{ref-Hutchinson2017CopSig}{}%
Hutchinson, Matthew C., Edgar Fernando Cagua, and Daniel B. Stouffer.
2017. {``Cophylogenetic Signal Is Detectable in Pollination Interactions
Across Ecological Scales.''} \emph{Ecology}, n/a--.
\url{https://doi.org/10.1002/ecy.1955}.

\leavevmode\hypertarget{ref-Jordano2016ChaEco}{}%
Jordano, Pedro. 2016a. {``Chasing Ecological Interactions.''} \emph{PLOS
Biol} 14 (9): e1002559.
\url{https://doi.org/10.1371/journal.pbio.1002559}.

\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
---------. 2016b. {``Sampling Networks of Ecological Interactions.''}
Edited by Daniel Stouffer. \emph{Functional Ecology} 30 (12): 1883--93.
\url{https://doi.org/10.1111/1365-2435.12763}.

\leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
Litsios, Glenn, and Nicolas Salamin. 2012. {``Effects of Phylogenetic
Signal on Ancestral State Reconstruction.''} \emph{Systematic Biology}
61 (3): 533--38. \url{https://doi.org/10.1093/sysbio/syr124}.

\leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
Maiorano, Luigi, Alessandro Montemaggiori, Gentile Francesco Ficetola,
Louise O'Connor, and Wilfried Thuiller. 2020a. {``Data from: Tetra-EU
1.0: A Species-Level Trophic Meta-Web of European Tetrapods.''} Dryad.
\url{https://doi.org/10.5061/DRYAD.JM63XSJ7B}.

\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
---------. 2020b. {``TETRA-EU 1.0: A Species-Level Trophic Metaweb of
European Tetrapods.''} Edited by Allen Hurlbert. \emph{Global Ecology
and Biogeography} 29 (9): 1452--57.
\url{https://doi.org/10.1111/geb.13138}.

\leavevmode\hypertarget{ref-Marco2018ChaHum}{}%
Marco, Moreno Di, Oscar Venter, Hugh P. Possingham, and James E. M.
Watson. 2018. {``Changes in Human Footprint Drive Changes in Species
Extinction Risk.''} \emph{Nature Communications} 9 (1): 4621.
\url{https://doi.org/10.1038/s41467-018-07049-5}.

\leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
Morales-Castilla, Ignacio, Miguel G. Matias, Dominique Gravel, and
Miguel B. Araújo. 2015. {``Inferring Biotic Interactions from
Proxies.''} \emph{Trends in Ecology \& Evolution} 30 (6): 347--56.
\url{https://doi.org/10.1016/j.tree.2015.03.014}.

\leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
Mouquet, Nicolas, Vincent Devictor, Christine N. Meynard, Francois
Munoz, Louis-Félix Bersier, Jérôme Chave, Pierre Couteron, et al. 2012.
{``Ecophylogenetics: Advances and Perspectives.''} \emph{Biological
Reviews} 87 (4): 769--85.
\url{https://doi.org/10.1111/j.1469-185X.2012.00224.x}.

\leavevmode\hypertarget{ref-Nenzen2014Imp850}{}%
Nenzén, Hedvig K., Daniel Montoya, and Sara Varela. 2014. {``The Impact
of 850,000 Years of Climate Changes on the Structure and Dynamics of
Mammal Food Webs.''} \emph{PLOS ONE} 9 (9): e106651.
\url{https://doi.org/10.1371/journal.pone.0106651}.

\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
No'kmaq, M'sit, Albert Marshall, Karen F. Beazley, Jessica Hum, shalan
joudry, Anastasia Papadopoulos, Sherry Pictou, Janet Rabesca, Lisa
Young, and Melanie Zurba. 2021. {``{`Awakening the Sleeping Giant'}:
Re-Indigenization Principles for Transforming Biodiversity Conservation
in Canada and Beyond.''} \emph{FACETS} 6 (1): 839--69.

\leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
O'Connor, Louise M. J., Laura J. Pollock, João Braga, Gentile Francesco
Ficetola, Luigi Maiorano, Camille Martinez-Almoyna, Alessandro
Montemaggiori, Marc Ohlmann, and Wilfried Thuiller. 2020. {``Unveiling
the Food Webs of Tetrapods Across Europe Through the Prism of the
Eltonian Niche.''} \emph{Journal of Biogeography} 47 (1): 181--92.
\url{https://doi.org/10.1111/jbi.13773}.

\leavevmode\hypertarget{ref-Pan2010SurTra}{}%
Pan, Sinno Jialin, and Qiang Yang. 2010. {``A Survey on Transfer
Learning.''} \emph{IEEE Transactions on Knowledge and Data Engineering}
22 (10): 1345--59. \url{https://doi.org/10.1109/TKDE.2009.191}.

\leavevmode\hypertarget{ref-Park2004StaMec}{}%
Park, Juyong, and M. E. J. Newman. 2004. {``Statistical Mechanics of
Networks.''} \emph{Physical Review E} 70 (6): 066117.
\url{https://doi.org/10.1103/PhysRevE.70.066117}.

\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
Pedersen, Eric J., Patrick L. Thompson, R. Aaron Ball, Marie-Josée
Fortin, Tarik C. Gouhier, Heike Link, Charlotte Moritz, et al. 2017.
{``Signatures of the Collapse and Incipient Recovery of an Overexploited
Marine Ecosystem.''} \emph{Royal Society Open Science} 4 (7): 170215.
\url{https://doi.org/10.1098/rsos.170215}.

\leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
Pires, Mathias M., Paul L. Koch, Richard A. Fariña, Marcus A. M. de
Aguiar, Sérgio F. dos Reis, and Paulo R. Guimarães. 2015. {``Pleistocene
Megafaunal Interaction Networks Became More Vulnerable After Human
Arrival.''} \emph{Proceedings of the Royal Society B: Biological
Sciences} 282 (1814): 20151367.
\url{https://doi.org/10.1098/rspb.2015.1367}.

\leavevmode\hypertarget{ref-Poelen2014GloBio}{}%
Poelen, Jorrit H., James D. Simons, and Chris J. Mungall. 2014.
{``Global Biotic Interactions: An Open Infrastructure to Share and
Analyze Species-Interaction Datasets.''} \emph{Ecological Informatics}
24: 148--59. \url{https://doi.org/10.1016/j.ecoinf.2014.08.005}.

\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
Poisot, Timothée, Zacharie Belisle, Laura Hoebeke, Michiel Stock, and
Piotr Szefer. 2019. {``EcologicalNetworks.jl - Analysing Ecological
Networks.''} \emph{Ecography}. \url{https://doi.org/10.1111/ecog.04310}.

\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew MacDonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2021. {``Global Knowledge Gaps in Species
Interaction Networks Data.''} \emph{Journal of Biogeography} n/a (n/a).
\url{https://doi.org/10.1111/jbi.14127}.

\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
Poisot, Timothée, Elsa Canard, David Mouillot, Nicolas Mouquet, and
Dominique Gravel. 2012. {``The Dissimilarity of Species Interaction
Networks.''} \emph{Ecology Letters} 15 (12): 1353--61.
\url{https://doi.org/10.1111/ele.12002}.

\leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
Poisot, Timothée, Alyssa R. Cirtwill, Kévin Cazelles, Dominique Gravel,
Marie-Josée Fortin, and Daniel B. Stouffer. 2016. {``The Structure of
Probabilistic Networks.''} Edited by Jana Vamosi. \emph{Methods in
Ecology and Evolution} 7 (3): 303--12.
\url{https://doi.org/10.1111/2041-210X.12468}.

\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
Poisot, Timothée, Marie-Andrée Ouellet, Nardus Mollentze, Maxwell J.
Farrell, Daniel J. Becker, Gregory F. Albery, Rory J. Gibb, Stephanie N.
Seifert, and Colin J. Carlson. 2021. {``Imputing the Mammalian Virome
with Linear Filtering and Singular Value Decomposition.''}
\emph{arXiv:2105.14973 {[}q-Bio{]}}.
\url{http://arxiv.org/abs/2105.14973}.

\leavevmode\hypertarget{ref-Poisot2018IntRet}{}%
Poisot, Timothée, and Daniel B. Stouffer. 2018. {``Interactions Retain
the Co-Phylogenetic Matching That Communities Lost.''} \emph{Oikos} 127
(2): 230--38. \url{https://doi.org/10.1111/oik.03788}.

\leavevmode\hypertarget{ref-Price2003MacThe}{}%
Price, Peter W. 2003. \emph{Macroevolutionary Theory on Macroecological
Patterns}. Cambridge University Press.

\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
Ray, Justina C., Jaime Grimm, and Andrea Olive. 2021. {``The
Biodiversity Crisis in Canada: Failures and Challenges of Federal and
Sub-National Strategic and Legal Frameworks.''} \emph{FACETS} 6:
1044--68. \url{https://doi.org/10.1139/facets-2020-0075}.

\leavevmode\hypertarget{ref-Reeve2016HowPar}{}%
Reeve, Richard, Tom Leinster, Christina A. Cobbold, Jill Thompson, Neil
Brummitt, Sonia N. Mitchell, and Louise Matthews. 2016. {``How to
Partition Diversity.''} \emph{arXiv:1404.6520 {[}q-Bio{]}}.
\url{http://arxiv.org/abs/1404.6520}.

\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
Runghen, Rogini, Daniel B Stouffer, and Giulio V Dalla Riva. 2021.
{``Exploiting Node Metadata to Predict Interactions in Large Networks
Using Graph Embedding and Neural Networks.''}
\url{https://doi.org/10.1101/2021.06.10.447991}.

\leavevmode\hypertarget{ref-Schoener1989FooWeb}{}%
Schoener, Thomas W. 1989. {``Food Webs from the Small to the Large.''}
\emph{Ecology} 70 (6): 1559--89.

\leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
Solís-Lemus, Claudia, Paul Bastide, and Cécile Ané. 2017.
{``PhyloNetworks: A Package for Phylogenetic Networks.''}
\emph{Molecular Biology and Evolution} 34 (12): 3292--98.
\url{https://doi.org/10.1093/molbev/msx235}.

\leavevmode\hypertarget{ref-Stock2021PaiLea}{}%
Stock, Michiel. 2021. {``Pairwise Learning for Predicting Pollination
Interactions Based on Traits and Phylogeny.''} \emph{Ecological
Modelling}, 14.

\leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
Stouffer, D. B., M. Sales-Pardo, M. I. Sirer, and J. Bascompte. 2012.
{``Evolutionary Conservation of Species' Roles in Food Webs.''}
\emph{Science} 335 (6075): 1489--92.
\url{https://doi.org/10.1126/science.1216556}.

\leavevmode\hypertarget{ref-Strong2014ImpNon}{}%
Strong, Justin S., and Shawn J. Leroux. 2014. {``Impact of Non-Native
Terrestrial Mammals on the Structure of the Terrestrial Mammal Food Web
of Newfoundland, Canada.''} \emph{PLOS ONE} 9 (8): e106264.
\url{https://doi.org/10.1371/journal.pone.0106264}.

\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, Tanya, Michael David Catchen, Francis Banville, Dominique
Caron, Gabriel Dansereau, Philippe Desjardins-Proulx, Norma Forero, et
al. 2021. {``A Roadmap Toward Predicting Species Interaction Networks
(Across Space and Time).''} Preprint. EcoEvoRxiv.
\url{https://doi.org/10.32942/osf.io/eu7k3}.

\leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
Strydom, Tanya, Giulio V. Dalla Riva, and Timothée Poisot. 2021. {``SVD
Entropy Reveals the High Complexity of Ecological Networks.''}
\emph{Frontiers in Ecology and Evolution} 9.
\url{https://doi.org/10.3389/fevo.2021.623141}.

\leavevmode\hypertarget{ref-Thessen2014KnoExt}{}%
Thessen, Anne E., and Cynthia Sims Parr. 2014. {``Knowledge Extraction
and Semantic Annotation of Text from the Encyclopedia of Life.''}
\emph{PloS One} 9 (3): e89550.

\leavevmode\hypertarget{ref-Torrey2010TraLea}{}%
Torrey, Lisa, and Jude Shavlik. 2010. {``Transfer Learning.''} In
\emph{Handbook of Research on Machine Learning Applications and Trends:
Algorithms, Methods, and Techniques}, 242--64. IGI global.

\leavevmode\hypertarget{ref-Trojelsgaard2016EcoNet}{}%
Trøjelsgaard, Kristian, and Jens M. Olesen. 2016. {``Ecological Networks
in Motion: Micro- and Macroscopic Variability Across Scales.''}
\emph{Functional Ecology} 30 (12): 1926--35.
\url{https://doi.org/10.1111/1365-2435.12710}.

\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
Turak, Eren, James Brazill-Boast, Tim Cooney, Michael Drielsma, Jocelyn
DelaCruz, Gillian Dunkerley, Miguel Fernandez, et al. 2017. {``Using the
Essential Biodiversity Variables Framework to Measure Biodiversity
Change at National Scale.''} \emph{Biological Conservation}, SI:Measures
of biodiversity, 213: 264--71.
\url{https://doi.org/10.1016/j.biocon.2016.08.019}.

\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
Upham, Nathan S., Jacob A. Esselstyn, and Walter Jetz. 2019.
{``Inferring the Mammal Tree: Species-Level Sets of Phylogenies for
Questions in Ecology, Evolution, and Conservation.''} \emph{PLOS
Biology} 17 (12): e3000494.
\url{https://doi.org/10.1371/journal.pbio.3000494}.

\leavevmode\hypertarget{ref-Yeakel2014ColEco}{}%
Yeakel, Justin D., Mathias M. Pires, Lars Rudolf, Nathaniel J. Dominy,
Paul L. Koch, Paulo R. Guimarães, and Thilo Gross. 2014. {``Collapse of
an Ecological Network in Ancient Egypt.''} \emph{PNAS} 111 (40):
14472--77. \url{https://doi.org/10.1073/pnas.1408471111}.

\leavevmode\hypertarget{ref-Youden1950IndRat}{}%
Youden, W. J. 1950. {``Index for Rating Diagnostic Tests.''}
\emph{Cancer} 3 (1): 32--35.
\url{https://doi.org/10.1002/1097-0142(1950)3:1\%3C32::AID-CNCR2820030106\%3E3.0.CO;2-3}.

\leavevmode\hypertarget{ref-Young2021BayInf}{}%
Young, Jean-Gabriel, George T Cantwell, and M E J Newman. 2021.
{``Bayesian Inference of Network Structure from Unreliable Data.''}
\emph{Journal of Complex Networks} 8 (6).
\url{https://doi.org/10.1093/comnet/cnaa046}.

\leavevmode\hypertarget{ref-Young2007RanDot}{}%
Young, Stephen J., and Edward R. Scheinerman. 2007. {``Random Dot
Product Graph Models for Social Networks.''} In \emph{Algorithms and
Models for the Web-Graph}, edited by Anthony Bonato and Fan R. K. Chung,
138--49. Lecture Notes in Computer Science. Berlin, Heidelberg:
Springer. \url{https://doi.org/10.1007/978-3-540-77004-6_11}.

\leavevmode\hypertarget{ref-Zhu2006AutDim}{}%
Zhu, Mu, and Ali Ghodsi. 2006. {``Automatic Dimensionality Selection
from the Scree Plot via the Use of Profile Likelihood.''}
\emph{Computational Statistics \& Data Analysis} 51 (2): 918--30.
\url{https://doi.org/10.1016/j.csda.2005.09.010}.

\end{CSLReferences}

\end{document}

### 2021-09-11 preprint.tex
Deploy to GitHub Pages

--- 2021-09-11 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}
-
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
+
+\geometry{includemp,
+            letterpaper,
+            top=1.2in,
+            bottom=2.510cm,
+            inner=0.5in,
+            outer=0.4in,
+            marginparwidth=1.95in,
+            marginparsep=0.4in}
+
+\usepackage[singlelinecheck=off]{caption}
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+\usepackage{floatrow}
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+\floatsetup[table]{margins=hangoutside,
+             facing=yes,
+             capposition=beside,
+             capbesideposition={center,outside},
+             floatwidth=\textwidth}
 
@@
 
-\doublespacing
+\setcounter{secnumdepth}{5}
+
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Food web reconstruction through phylogenetic
-transfer of low-rank network representation}
-\vskip 5em
-
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
+
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Food web reconstruction through
+phylogenetic transfer of low-rank network representation}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 \href{https://orcid.org/0000-0003-0193-5441}{Salomé\,Bouskila}%
 %
-\,\textsuperscript{1,‡}\quad %
+\,\textsuperscript{1,‡}, %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
 %
-\,\textsuperscript{1,3,2}\quad %
+\,\textsuperscript{1,3,2}, %
 \href{https://orcid.org/0000-0003-4036-977X}{Ceres\,Barros}%
 %
-\,\textsuperscript{4}\quad %
+\,\textsuperscript{4}, %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
 %
-\,\textsuperscript{5,2}\quad %
+\,\textsuperscript{5,2}, %
 \href{https://orcid.org/0000-0003-0452-6993}{Maxwell J\,Farrell}%
 %
-\,\textsuperscript{6}\quad %
+\,\textsuperscript{6}, %
 \href{https://orcid.org/0000-0002-9935-1366}{Marie-Josée\,Fortin}%
 %
-\,\textsuperscript{6}\quad %
+\,\textsuperscript{6}, %
 \href{https://orcid.org/0000-0003-3220-6161}{Victoria\,Hemming}%
 %
-\,\textsuperscript{4}\quad %
+\,\textsuperscript{4}, %
 \href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{3,2}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
 %
-\,\textsuperscript{5}\quad %
+\,\textsuperscript{5}, %
 \href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
 %
-\,\textsuperscript{7}\quad %
+\,\textsuperscript{7}, %
 \href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
 %
-\,\textsuperscript{8}\quad %
+\,\textsuperscript{8}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 \,\textsuperscript{1,2}
-
+\vskip 1em
 \textsuperscript{1}\,Département de Sciences Biologiques, Université de
-Montréal, Montréal, Canada\quad \textsuperscript{2}\,Québec Centre for
-Biodiversity Sciences, Montréal,
-Canada\quad \textsuperscript{3}\,Université de Sherbrooke, Sherbrooke,
-Canada\quad \textsuperscript{4}\,Department of Forest Resources
-Management, University of British Columbia, Vancouver,
-Canada\quad \textsuperscript{5}\,Department of Biology, McGill
-University, Montréal, Canada\quad \textsuperscript{6}\,Department of
-Ecology \& Evolutionary Biology, University of Toronto, Toronto,
-Canada\quad \textsuperscript{7}\,Centre for Integrative Ecology, School
-of Biological Sciences, University of Canterbury, Canterbury, New
-Zealand\quad \textsuperscript{8}\,School of Mathematics and Statistics,
-University of Canterbury, Canterbury, New Zealand
-
+Montréal, Montréal, Canada; \textsuperscript{2}\,Québec Centre for
+Biodiversity Sciences, Montréal, Canada; \textsuperscript{3}\,Université
+de Sherbrooke, Sherbrooke, Canada; \textsuperscript{4}\,Department of
+Forest Resources Management, University of British Columbia, Vancouver,
+Canada; \textsuperscript{5}\,Department of Biology, McGill University,
+Montréal, Canada; \textsuperscript{6}\,Department of Ecology \&
+Evolutionary Biology, University of Toronto, Toronto,
+Canada; \textsuperscript{7}\,Centre for Integrative Ecology, School of
+Biological Sciences, University of Canterbury, Canterbury, New
+Zealand; \textsuperscript{8}\,School of Mathematics and Statistics,
+University of Canterbury, Canterbury, New Zealand\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
-
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
-\textbf{\sffamily Abstract: }Despite their importance in many ecological
+}
+\end{flushleft}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
+
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+ecological networks\\network embedding\\transfer learning\\ancestral
+character estimation\\biogeography\\}
+}
+
+\textbf{Abstract}:\,Despite their importance in many ecological
 processes, collecting data and information on ecological interactions,
@@
 generally applicable to a broad family of ecological problems.
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2021-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@7e1fb30781c47bd0a86a8dcf9e9ef05c54084b9a 🚀

@@
 \usepackage[T1]{fontenc}
-\usepackage{stix}
+\usepackage{stix2}
 \usepackage[scaled]{helvet}
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=4.5cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
 
@@
 \pagestyle{plain}
+
+\tolerance=1
+\emergencystretch=\maxdimen
+\hyphenpenalty=10000
+\hbadness=10000
 
@@
 \begin{document}
+\raggedright
 \thispagestyle{empty}
@@
 %
-\,\textsuperscript{5}\quad %
+\,\textsuperscript{5,2}\quad %
 \href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
@@
 \vfill
-\textbf{\sffamily Abstract: }Despite their importance in many ecological
-processes, collecting data and information on ecological interactions,
-and therefore species interaction networks, is an exceedingly
-challenging task. For this reason, large parts of the world have a
-deficit of data of which species interact, and what we can expect the
-network structure of these interactions to be. As data collection alone
-is unlikely to be sufficient at filling these global gaps, community
-ecologists must adopt predictive methods. In this contribution we
-develop such a method, relying on graph embedding (the extraction of
-explanatory latent variables from known graph structures) and transfer
-learning (the application of previous solution to novel problems with
-limited predictors overlap) in order to assemble a predicted list of
-trophic interactions between mammals of Canada. This interaction list is
-derived from extensive knowledge of the mammalian food web of Europe,
-despite the fact that there are fewer than 5\% of common species between
-the two locations. We provide guidance on how this method can be adapted
-by substituting some approaches or predictors in order to make it more
-generally applicable to a broad family of ecological problems.
+Despite their importance in many ecological processes, collecting data
+and information on ecological interactions, and therefore species
+interaction networks, is an exceedingly challenging task. For this
+reason, large parts of the world have a data deficit when it comes to
+species interactions, and how the resulting networks are structured. As
+data collection alone is unlikely to be sufficient at filling these
+global gaps, community ecologists must adopt predictive methods. In this
+contribution, we develop such a method, relying on graph embedding (the
+extraction of explanatory latent variables from known graph structures)
+and transfer learning (the application of previous solutions to novel
+problems with limited predictors overlap) in order to assemble a
+predicted list of trophic interactions between mammals of Canada. This
+interaction list is derived from extensive knowledge of the mammalian
+food web of Europe, despite the fact that there are fewer than 5\% of
+common species between the two locations. The results of the predictive
+model are compared against databases of recorded pairwise interactions,
+showing that we correctly recover over 95\% of known interactions. We
+provide guidance on how this method can be adapted by substituting some
+approaches or predictors in order to make it more generally applicable.
+
 \vfill
@@
 understanding of ecological networks across space, particularly at
-macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard and Olesen
+macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
 2016). First, networks within a location are difficult to sample
-properly (Jordano 2016a, 2016b), resulting in a widespread ``Eltonian
-shortfall'' (Hortal et al. 2015). This first challenge (local
-incompleteness) has been, in large part, addressed by the recent
-multiplication of methods aiming to predict interactions \emph{within}
-an \emph{existing} network, a lot of which are reviewed in Strydom et
-al. (2021). Second, recent analyses based on collected data (Poisot,
-Bergeron, et al. 2021) or metadata (Cameron et al. 2019) highlight that
-ecological networks are currently studied in a biased subset of space
-and bioclimates, which impedes our ability to generalize any local
-understanding of network structure. Meaning that although the framework
-to address incompleteness \emph{within} a network exists there would
-still be regions that, due to a \emph{lack} of local interaction data,
-we are unable to infer potential species interactions. Having a general
-solution for the issue of metaweb inference (Morales-Castilla et al.
-2015) that, despite situations where minimal knowledge about
-interactions within a species pool is known, is capable of producing a
-plausible metaweb could be the catalyst for significant breakthroughs in
-our ability to start thinking about species interactions networks over
-large spatial scales.
+properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
+shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
+about inter and intra specific relationships. This first challenge has
+been, in large part, addressed by the recent emergence of a suite of
+methods aiming to predict interactions within \emph{existing} networks,
+many of which are reviewed in Strydom \emph{et al.} (2021a). Second,
+recent analyses based on collected data (Poisot \emph{et al.} 2021a) or
+metadata (Cameron \emph{et al.} 2019) highlight that ecological networks
+are currently studied in a biased subset of space and bioclimates, which
+impedes our ability to generalize any local understanding of network
+structure. Meaning that, although the framework to address
+incompleteness \emph{within} networks exists, there would still be
+regions for which, due to a \emph{lack} of local interaction data, we
+are unable to infer potential species interactions. Having a general
+solution for inferring a \emph{plausible} metaweb (despite the
+unavailability of interaction data) could be the catalyst for
+significant breakthroughs in our ability to start thinking about species
+interactions networks over large spatial scales.
 
@@
 methodology that uses the knowledge gained from solving one problem and
-applying it to a related (destination) problem (Torrey and Shavlik 2010;
-Pan and Yang 2010). In this instance, we solve the problem of predicting
+applying it to a related (destination) problem (Pan \& Yang 2010; Torrey
+\& Shavlik 2010). In this instance, we solve the problem of predicting
 trophic interactions between species, based on knowledge extracted from
-another species pool for which interactions are known, using
+another species pool for which interactions are known by using
 phylogenetic structure as a medium for transfer. This allows us to
 construct a \emph{probabilistic} metaweb for a community for which we
-have \emph{no} prior interaction data for the desired species pool. Our
-methodology is outlined in fig.~\ref{fig:concept}, where we provide an
-illustration based on learning an embedding of a metaweb of trophic
-interactions for European mammals (known interactions; Maiorano et al.
-2020b, 2020a), and based on phylogenetic relationships between mammals
-globally (Upham, Esselstyn, and Jetz 2019), infer a metaweb for the
-Canadian mammalian species pool (interactions are treated as unknown in
-this instance).
+have \emph{no} prior trophic interaction data for the desired species
+pool. Our methodology is outlined in fig.~\ref{fig:concept}, where we
+provide an illustration based on learning the embedding of a metaweb of
+trophic interactions for European mammals (known interactions; Maiorano
+\emph{et al.} 2020b, a) and, based on phylogenetic relationships between
+mammals globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.}
+2019), infer a metaweb for the Canadian mammalian species pool
+(interactions are treated as unknown in this instance).
 
@@
 There is a plurality of measures of species similarities that can be
-used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla et al.
-2015); however, phylogenetic proximity has several desirable properties
-when working at large scales. Gerhold et al. (2015) made the point that
-phylogenetic signal captures diversification of characters (large
-macro-evolutionary process), but not necessarily community assembly
-(fine ecological process); Dormann et al. (2010) previously found very
-similar conclusions. Interactions tend to conserve a phylogenetic signal
-that encompasses a wide range of ecological and evolutionary mechanisms
-(Mouquet et al. 2012; Cavender-Bares et al. 2009), and - most
-importantly - retain this signal even when it is not detectable at the
-community scale (Poisot and Stouffer 2018; Hutchinson, Cagua, and
-Stouffer 2017). Finally, species interactions at macro-ecological scales
-seem to respond mostly to macro-evolutionary processes (Price 2003);
-which is evidenced by the presence of conserved backbones in food webs
-(Dalla Riva and Stouffer 2016), strong evolutionary signature on prey
-choice (Stouffer et al. 2012), and strong phylogenetic signature in food
-web intervality (Eklöf and Stouffer 2016). Phylogenetic reconstruction
-has also previously been used to understand ancestral plant-insect
-interaction networks (Braga et al. 2021). Taken together, these
-considerations suggest that phylogenies can reliably be used to transfer
-knowledge on species interactions.
+used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla
+\emph{et al.} 2015); however, phylogenetic proximity has several
+desirable properties when working at large scales. Gerhold \emph{et al.}
+(2015) made the point that phylogenetic signal captures diversification
+of characters (large macro-evolutionary process), but not necessarily
+community assembly (fine ecological process); Dormann \emph{et al.}
+(2010) previously found very similar conclusions. Interactions tend
+reflect a phylogenetic signal because they have a conserved pattern of
+evolutionary convergence that encompasses a wide range of ecological and
+evolutionary mechanisms (Cavender-Bares \emph{et al.} 2009; Mouquet
+\emph{et al.} 2012), and - most importantly - retain this signal even
+when it is not detectable at the community scale (Hutchinson \emph{et
+al.} 2017; Poisot \& Stouffer 2018). Finally, species interactions at
+macro-ecological scales seem to respond mostly to macro-evolutionary
+processes (Price 2003); which is evidenced by the presence of conserved
+backbones in food webs (Dalla Riva \& Stouffer 2016), strong
+evolutionary signature on prey choice (Stouffer \emph{et al.} 2012), and
+strong phylogenetic signature in food web intervality (Eklöf \& Stouffer
+2016). Phylogenetic reconstruction has also previously been used within
+the context of ecological networks, namely understanding ancestral
+plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
+these considerations suggest that phylogenies can reliably be used to
+transfer knowledge on species interactions.
 
@@
 showcases that although the components (species) that make up the
-Canadian and European communities may not be \emph{perfectly} shared, if
-the medium (proxy space) selected in the transfer step is biologically
+Canadian and European communities may be \emph{minimally} shared, if the
+medium (proxy space) selected in the transfer step is biologically
 plausible, we can still effectively learn from the known network and
@@
 amenable to changes; notably, the measure of similarity may not be
-phylogeny, and can be replaced by information on foraging (Beckerman,
-Petchey, and Warren 2006), cell-level mechanisms (Boeckaerts et al.
+phylogeny, and can be replaced by information on foraging (Beckerman
+\emph{et al.} 2006), cell-level mechanisms (Boeckaerts \emph{et al.}
 2021), or a combination of traits and phylogenetic structure (Stock
@@
 
-We use data on the European metaweb assembled by Maiorano et al.
-(2020b), following the definition of the metaweb first introduced by
-Dunne (2006), \emph{i.e.} an inventory of all possible interactions
+We use data from the European metaweb assembled by Maiorano \emph{et
+al.} (2020b), following the definition of the metaweb first introduced
+by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
 within species from a spatially delimited pool. Notably the metaweb is
@@
 expected to have a subset of both the species and the interactions of
-their metaweb (Poisot et al. 2012). This being said, as the metaweb
-represents the total of functional, phylogenetic, and macroecological
-processes (Morales-Castilla et al. 2015), it is thus still worthy of
-ecological attention. We induced the subgraph corresponding to all
-mammals by matching species names in the original network first to the
-GBIF taxonomic backbone (GBIF Secretariat 2021) and retaining all those
-who matched to mammals; all nodes had valid matches to GBIF at this
-step, and so this backbone is used for all name reconciliation steps as
-outlined below.
+their metaweb (Poisot \emph{et al.} 2012). This being said, as the
+metaweb represents the total of functional, phylogenetic, and
+macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
+thus still worthy of ecological attention. We deduced the subgraph
+corresponding to all mammals by matching species names in the original
+network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
+retaining all those who matched to mammals. This serves a dual purpose
+1) to extract only mammals from the European network and 2) to match and
+standardize species names when aggregating the different data sources
+further downstream (which is an important consideration when combining
+datasets Grenié \emph{et al.} (2021)). All nodes had valid matches to
+GBIF at this step, and so this backbone is used for all name
+reconciliation steps as outlined below.
 
@@
 transfer; the phylogenetic similarity of mammals here represents the
-support for transfer. We used the mammalian consensus supertree by
-Upham, Esselstyn, and Jetz (2019), for which all approximatively 6000
-names have been similarly matched to their GBIF valid names. This step
-allows us to place each node of the mammalian European metaweb in the
+information for transfer. We used the mammalian consensus supertree by
+Upham \emph{et al.} (2019), for which all approximatively 6000 names
+have been similarly matched to their GBIF valid names. This step allows
+us to place each node of the mammalian European metaweb in the
 phylogeny.
@@
 semi-aquatic species (this corresponds to the same selection that was
-applied by Maiorano et al. (2020b) in the European metaweb). The IUCN
-names were, as previously, reconciled against GBIF to have an exact
+applied by Maiorano \emph{et al.} (2020b) in the European metaweb). The
+IUCN names were, as previously, reconciled against GBIF to have an exact
 match to the taxonomy.
@@
 After taxonomic cleaning and reconciliation as outlined in the following
-sections, the mammalian European metaweb had 260 species, and the
+sections, the mammalian European metaweb has 260 species, and the
 Canadian species pool has 163; of these, 17 (about 4\% of the total) are
 shared, and 89 species from Canada (54\%) had at least one congeneric
-species in Europe. The similarity for both species pool predictably
+species in Europe. The similarity for both species pools predictably
 increases with higher taxonomic order, with 19\% of shared genera, 47\%
@@
 network in Europe, we use a truncated Singular Value Decomposition
-(t-SVD; Halko, Martinsson, and Tropp 2011) to generate latent traits
-representing a low-dimensional embedding of the network; these traits
-give an unbiased estimate of the node's position in the latent feature
-spaces. Then, we map these latent traits onto a reference phylogeny
-(other distance-based measures of species proximity that allow for the
+(t-SVD; Halko \emph{et al.} 2011) to generate latent traits representing
+a low-dimensional embedding of the network; these traits give an
+unbiased estimate of the node's position in the latent feature spaces.
+Then, we map these latent traits onto a reference phylogeny (other
+distance-based measures of species proximity that allow for the
 inference of features in the latent space can be used, for example the
@@
 traits for species in the destination species pool, a Random Dot Product
-Graph model (hereafter RDPG; S. J. Young and Scheinerman 2007) predicts
-the interaction between species through a function of the nodes'
-features through matrix multiplication. Thus, from latent traits and
-nodes position, we can infer interactions.
+Graph model (hereafter RDPG; Young \& Scheinerman 2007) predicts the
+interaction between species through a function of the nodes' features
+through matrix multiplication. Thus, from latent traits and node
+position, we can infer interactions.
 
@@
 
-The entire pipeline is implemented in \emph{Julia} 1.6 (Bezanson et al.
-2017) and is available under the permissive MIT License at
+The entire pipeline is implemented in \emph{Julia} 1.6 (Bezanson
+\emph{et al.} 2017) and is available under the permissive MIT License at
 \href{https://osf.io/2zwqm/}{\texttt{https://osf.io/2zwqm/}}. The
-taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau and
+taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau \&
 Poisot 2021). The network embedding and analysis is done using
-\texttt{EcologicalNetworks.jl} (Banville, Vissault, and Poisot 2021;
-Poisot et al. 2019). The phylogenetic simulations are done using
-\texttt{PhyloNetworks.jl} (Solís-Lemus, Bastide, and Ané 2017) and
-\texttt{Phylo.jl} (Reeve et al. 2016). A complete \texttt{Project.toml}
-file specifying the full tree of dependencies is available alongside the
-code. This material also includes a fully annotated copy of the entire
-code required to run this project (describing both the intent of the
-code and discussing some technical implementation details), a vignette
-for every step of the process, and a series of Jupyter notebooks with
-the text and code. The pipeline can be executed on a laptop in a matter
-of minutes, and therefore does not require extensive computational
-power.
+\texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019; Banville
+\emph{et al.} 2021). The phylogenetic simulations are done using
+\texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
+\texttt{Phylo.jl} (Reeve \emph{et al.} 2016). A complete
+\texttt{Project.toml} file specifying the full tree of dependencies is
+available alongside the code. This material also includes a fully
+annotated copy of the entire code required to run this project
+(describing both the intent of the code and discussing some technical
+implementation details), a vignette for every step of the process, and a
+series of Jupyter notebooks with the text and code. The pipeline can be
+executed on a laptop in a matter of minutes, and therefore does not
+require extensive computational power.
 
@@
 of interactions (species \emph{a} eats \emph{b}). This approach is
-conceptually different from other metaweb-scale predictions
-(\emph{.e.g.} Albouy et al. 2019), in that the metaweb representation is
-easily transferable. Specifically, we use RDPG to create a number of
-latent variables that can be combined into an approximation of the
-network adjacency matrix. RDPG results are known to have strong
-phylogenetic signal, and to capture the evolutionary backbone of food
-webs (Dalla Riva and Stouffer 2016). In addition, recent advances show
-that the latent variables produced this way can be used to predict
-\emph{de novo} network edges (Runghen, Stouffer, and Dalla Riva 2021).
+conceptually different from other metaweb-scale predictions (\emph{e.g.}
+Albouy \emph{et al.} 2019), in that the metaweb representation is easily
+transferable. Specifically, we use RDPG to create a number of latent
+variables that can be combined into an approximation of the network
+adjacency matrix. RDPG results are known to have strong phylogenetic
+signal, and to capture the evolutionary backbone of food webs (Dalla
+Riva \& Stouffer 2016). In addition, recent advances show that the
+latent variables produced this way can be used to predict \emph{de novo}
+network edges (\emph{i.e.} interactions; Runghen \emph{et al.} 2021).
 
@@
 appropriate embedding of ecological networks, which has recently been
-shown to both capture their complex, emerging properties (Strydom, Dalla
-Riva, and Poisot 2021) and to allow highly accurate prediction of the
-interactions within a single network (Poisot, Ouellet, et al. 2021).
-Under SVD, an adjacency matrix \(\mathbf{A}\) (where
+shown to both capture their complex, emerging properties (Strydom
+\emph{et al.} 2021b) and to allow highly accurate prediction of the
+interactions within a single network (Poisot \emph{et al.} 2021b). Under
+SVD, an adjacency matrix \(\mathbf{A}\) (where
 \(\mathbf{A}_{m,n}\in\mathbb{B}\) where 1 indicates predation and 0 an
 absence thereof) is decomposed into three components resulting in
-\(\mathbf{A} = \mathbf{L}\mathbf{\Sigma}\mathbf{R}.\) Here,
+\(\mathbf{A} = \mathbf{L}\mathbf{\Sigma}\mathbf{R'}.\) Here,
 \(\mathbf{\Sigma}\) is a \(m \times n\) diagonal matrix and contains
@@
 \(\mathbf{A}_{m,n}\) is decomposed so that \(\mathbf{\Sigma}\) is a
-square \(r \times r\) diagonal matrix (where \(r\) is the rank of
-\(\mathbf{A}\)) containing only non-zero \(\sigma\) values.
-Additionally, \(\mathbf{L}\) is now a \(m \times r\) semi unitary matrix
-and \(\mathbf{R}'\) a \(n \times r\) semi-unitary matrix.
+square \(r \times r\) diagonal matrix (whith \(1 \le r \le r_{full}\)
+where \(r_{full}\) is the full rank of \(\mathbf{A}\) and \(r\) the rank
+at which we truncate the matrix) containing only non-zero \(\sigma\)
+values. Additionally, \(\mathbf{L}\) is now a \(m \times r\) semi
+unitary matrix and \(\mathbf{R}'\) a \(n \times r\) semi-unitary matrix.
 
@@
 \(\mathbf{\Sigma}\) can show a sharp drop at the rank where noise starts
-(Zhu and Ghodsi 2006). Because the European metaweb is almost entirely
-known, the amount of noise is low; this is reflected in
+(Zhu \& Ghodsi 2006). Because the European metaweb is almost entirely
+known, the amount of noise (uncertainty) is low; this is reflected in
 fig.~\ref{fig:scree} (left), where the scree plot shows no important
@@
 variance explained increases smoothly at higher dimensions. For this
-reason, we default back to an arbitrary threshold that explains 60\% of
-the variance in the underlying data, corresponding to 12 dimensions.
+reason, we default back to a threshold that explains 60\% of the
+variance in the underlying data, corresponding to 12 dimensions -
+\emph{i.e.} a tradeoff between accuracy and a reduced number of
+features.
 
@@
 drop in the singular values that may be leveraged to automatically
-detect a minimal dimension for embedding, after \emph{e.g.} Zhu and
+detect a minimal dimension for embedding, after \emph{e.g.} Zhu \&
 Ghodsi (2006). Right: cumulative fraction of variance explained by each
@@
 European metaweb are all true. Given the methodological details given in
-Maiorano et al. (2020b) and O'Connor et al. (2020), this seems like a
-reasonable assumption, although one that does not hold for all metawebs.
-We used the thresholding approach presented in Poisot, Ouellet, et al.
-(2021), and picked a cutoff that maximized Youden's \(J\) statistic
-(Youden (1950); a measure of the informedness (trust) of predictions);
-the resulting cutoff was 0.22, and gave an accuracy above 0.99.
+Maiorano \emph{et al.} (2020b) and O'Connor \emph{et al.} (2020), this
+seems like a reasonable assumption, although one that does not hold for
+all metawebs. We used the thresholding approach presented in Poisot
+\emph{et al.} (2021b), and picked a cutoff that maximized Youden's \(J\)
+statistic (a measure of the informedness (trust) of predictions; Youden
+(1950)); the resulting cutoff was 0.22, and gave an accuracy above 0.99.
 
@@
 of strong hypotheses about the nature of phylogenetic signal in the
-network decomposition (Litsios and Salamin 2012). This uses the
-estimated feature vectors for the European mammals to create a state
+network decomposition (Litsios \& Salamin 2012). This uses the estimated
+feature vectors for the European mammals to create a state
 reconstruction for all species (conceptually something akin to a
@@
 focused on predicting contemporary interactions, we only retained the
-values for the tips of the three. We assumed that all traits
-(\emph{i.e.} the feature vectors for the left and right subspaces) were
-independent, which is a reasonable assumption as every trait/dimension
-added to the t-SVD has an \emph{additive} effect to the one before it.
-Note that the Upham, Esselstyn, and Jetz (2019) tree itself has some
-uncertainty associated to inner nodes of the phylogeny. In this case
-study, we have decided to not propagate this uncertainty, as it would
-complexify the process. The Brownian motion algorithm returns the
-\emph{average} value of the trait, and its upper and lower bounds.
-Because we do not estimate other parameters of the traits'
-distributions, we considered that every species trait is represented as
-a uniform distribution between these bounds; in a situation where the
-algorithm would return point values for all simulations, one could in
-theory either estimate the parameters of a distribution for each tip, or
-draw randomly from the outputs. In all cases, the inferred left and
-right sub-spaces for the Canadian species pool (\(\hat{\mathcal{L}}\)
-and \(\hat{\mathcal{R}}\)) have entries that are distributions,
-representing the range of values for a given species at a given
-dimension.
+values for the tips of the tree. We assumed that all traits (\emph{i.e.}
+the feature vectors for the left and right subspaces) were independent,
+which is a reasonable assumption as every trait/dimension added to the
+t-SVD has an \emph{additive} effect to the one before it. Note that the
+Upham \emph{et al.} (2019) tree itself has some uncertainty associated
+to inner nodes of the phylogeny. In this case study, we have decided to
+not propagate this uncertainty, as it would complexify the process. The
+Brownian motion algorithm returns the \emph{average} value of the trait,
+and its upper and lower bounds. Because we do not estimate other
+parameters of the traits' distributions, we considered that every
+species trait is represented as a uniform distribution between these
+bounds; in a situation where the algorithm would return point values for
+all simulations, one could in theory either estimate the parameters of a
+distribution for each tip, or draw randomly from the outputs. In all
+cases, the inferred left and right sub-spaces for the Canadian species
+pool (\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\)) have entries that
+are distributions, representing the range of values for a given species
+at a given dimension.
 
@@
 Therefore, we can use this information to assemble a
-\emph{probabilistic} metaweb in the sense of Poisot et al. (2016),
-\emph{i.e.} in which every interaction is represented as a single,
-independent, Bernoulli event of probability \(p\).
+\emph{probabilistic} metaweb in the sense of Poisot \emph{et al.}
+(2016), \emph{i.e.} in which every interaction is represented as a
+single, independent, Bernoulli event of probability \(p\).
 
@@
 structurally similar (as would be expected given the biogeographic
-similarities) and that the two (left and right) subspaces are distinct
+similarities) and the two (left and right) subspaces are distinct
 \emph{i.e.} capturing predation (generality) and prey (vulnerability)
@@
 probably broader than what they would actually be, see \emph{e.g.}
-Garland, Midford, and Ives 1999), we repeat the above process
+Garland \emph{et al.} 1999), we repeat the above process
 \(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
@@
 means that these two species were predicted to interact in all
-\(2\times 10^5\) random draws, etc..
+\(2\times 10^5\) random draws.
 
@@
 Once the probabilistic metaweb for Canada has been produced, we followed
-a number of data inflation steps to finalize it.
+a number of data inflation steps to finalize it. This step is external
+to the actual transfer learning framework but rather serves as a way to
+augment and validate the predicted metaweb.
 
@@
 by the model to all interactions (grey curve), the subset of
-interactions found in GLOBI (red), and in the Strong and Leroux (2014)
+interactions found in GLOBI (red), and in the Strong \& Leroux (2014)
 Newfoundland dataset (blue). The model recovers more interaction with a
@@
 between the European and Canadian pools and replaced these interactions
-with a probability of 0 (non-interaction) or 1 (interaction). This
-represents a minute modification of the inferred network (about 0.8\% of
-all species pairs from the Canadian web), but ensures that we are
-directly re-using knowledge from Europe.
+with a probability of 0 (non-interaction) or 1 (interaction), according
+to their value in the European metaweb. This represents a minute
+modification of the inferred network (about 0.8\% of all species pairs
+from the Canadian web), but ensures that we are directly re-using
+knowledge from Europe.
 
 Second, we looked for all species in the Canadian pool known to the
-Global Biotic Interactions (GLoBI) database (Poelen, Simons, and Mungall
-2014), and extracted their known interactions. Because GLOBI aggregates
+Global Biotic Interactions (GLoBI) database (Poelen \emph{et al.} 2014),
+and extracted their known interactions. Because GLOBI aggregates
 observed interactions, it is not a \emph{networks} data source, and
@@
 statement should yet be taken with caution, as some sources in GLOBI
-(\emph{e.g.} Thessen and Parr 2014) are produced though text analysis,
+(\emph{e.g.} Thessen \& Parr 2014) are produced through text analysis,
 and therefore may not document direct evidence of the interaction.
@@
 
-Finally, we downloaded the data from Strong and Leroux (2014), who mined
+Finally, we downloaded the data from Strong \& Leroux (2014), who mined
 various literature sources to identify trophic interactions in
@@
 interactions after the data inflation (fig.~\ref{fig:thresholds}).
-Cirtwill and Hambäck (2021) proposed a number of strategies to threshold
+Cirtwill \& Hambäck (2021) proposed a number of strategies to threshold
 probabilistic networks. Their methods assume the underlying data to be
@@
 one interaction with a non-zero probability. The need for this slight
-deviation from the Cirtwill and Hambäck (2021) method highlights the
-need for additional development on network thresholding.
+deviation from the Cirtwill \& Hambäck (2021) method highlights the need
+for additional development on network thresholding.
 
@@
 central difference approximation of the second order partial derivative,
-as suggested by \emph{e.g.} Cirtwill and Hambäck (2021), results in
-respectively species being lost, or almost all links being kept. We
-therefore settled on the value that allowed all species to remain with
-at least one interaction. This result, in and of itself, suggests that
-additional methodological developments for the thresholding of
-probabilistic networks are required.
+as suggested by \emph{e.g.} Cirtwill \& Hambäck (2021), results in
+species being lost, or almost all links being kept. We therefore settled
+on the value that allowed all species to remain with at least one
+interaction. This result, in and of itself, suggests that additional
+methodological developments for the thresholding of probabilistic
+networks are required.
 
@@
 \emph{i.e.} a set of random networks generated from a given degree
-sequence (Park and Newman 2004). Accounting for the probabilistic nature
+sequence (Park \& Newman 2004). Accounting for the probabilistic nature
 of the degrees, the rank 1 approximation also represents the \emph{soft}
-configuration model (van der Hoorn, Lippner, and Krioukov 2018). Both
-models are maximum entropy graph models (Garlaschelli, Hollander, and
-Roccaverde 2018), with sharp (all network realizations satisfy the
-specified degree sequence) and soft (network realizations satisfy the
-degree sequence on average) local constraints, respectively. The (soft)
-configuration model is an unbiased random graph model widely used by
-ecologists in the context of null hypothesis significance testing of
-network structure (\emph{e.g.} Bascompte et al. 2003) and can provide
-informative priors for Bayesian inference of network structure
-(\emph{e.g.} J.-G. Young, Cantwell, and Newman 2021). It is noteworthy
-that for this metaweb, the relevant information was extracted at the
-first rank. Because the first rank corresponds to the leading singular
-value of the system, the results of fig.~\ref{fig:degree} have a
-straightforward interpretation: degree-based processes are the most
-important in structuring the mammalian food web.
+configuration model (van der Hoorn \emph{et al.} 2018). Both models are
+maximum entropy graph models (Garlaschelli \emph{et al.} 2018), with
+sharp (all network realizations satisfy the specified degree sequence)
+and soft (network realizations satisfy the degree sequence on average)
+local constraints, respectively. The (soft) configuration model is an
+unbiased random graph model widely used by ecologists in the context of
+null hypothesis significance testing of network structure (\emph{e.g.}
+Bascompte \emph{et al.} 2003) and can provide informative priors for
+Bayesian inference of network structure (\emph{e.g.} Young \emph{et al.}
+2021). It is noteworthy that for this metaweb, the relevant information
+was extracted at the first rank. Because the first rank corresponds to
+the leading singular value of the system, the results of
+fig.~\ref{fig:degree} have a straightforward interpretation:
+degree-based processes are the most important in structuring the
+mammalian food web.
 
@@
 One important aspect in which Europe and Canada differ (despite their
-comparable bioclimatic conditions) is the legacy of human impacts, which
-have been much longer in Europe. Nenzén, Montoya, and Varela (2014)
-showed that even at small scales (the Iberian peninsula), mammal food
-webs retain the signal of both climate change and human activity, even
-when this human activity was orders of magnitude less important than it
-is now. Similarly, Yeakel et al. (2014) showed that changes in human
-occupation over several centuries can lead to food web collapse.
-Megafauna in particular seems to be very sensitive to human arrival
-(Pires et al. 2015). In short, there is well-substantiated support for
-the idea that human footprint affects more than the risk of species
-extinction (Marco et al. 2018), and can lead to changes in interaction
-structure. Yet, owing to the inherent plasticity of interactions, there
-have been documented instances of food webs undergoing rapid
-collapse/recovery cycles over short periods of time (Pedersen et al.
-2017). The embedding of a network, in a sense, embeds its
-macro-evolutionary history, especially as RDPG captures ecological
-signal (Dalla Riva and Stouffer 2016); at this point, it is important to
-recall that a metaweb is intended as a catalogue of all possible
-interactions, which should then be filtered (Morales-Castilla et al.
-2015). In practice (and in this instance) the reconstructed metaweb will
-predict interactions that are plausible based on the species'
-evolutionary history, however some interactions would not be realized
-due to human impact.
-
-Cirtwill et al. (2019) previously made the point that network inference
-techniques based on Bayesian approaches would perform far better in the
-presence of an interaction-level informative prior; the desirable
-properties of such a prior would be that it is expressed as a
+comparable bioclimatic conditions) is the degree of the legacy of human
+impacts, which have been much longer in Europe. Nenzén \emph{et al.}
+(2014) showed that even at small scales (the Iberian peninsula), mammal
+food webs retain the signal of both climate change and human activity,
+even when this human activity was orders of magnitude less important
+than it is now. Similarly, Yeakel \emph{et al.} (2014) showed that
+changes in human occupation over several centuries can lead to food web
+collapse. Megafauna in particular seems to be very sensitive to human
+arrival (Pires \emph{et al.} 2015). In short, there is
+well-substantiated support for the idea that human footprint affects
+more than the risk of species extinction (Marco \emph{et al.} 2018), and
+can lead to changes in interaction structure. Yet, owing to the inherent
+plasticity of interactions, there have been documented instances of food
+webs undergoing rapid collapse/recovery cycles over short periods of
+time (Pedersen \emph{et al.} 2017). The embedding of a network, in a
+sense, embeds its macro-evolutionary history, especially as RDPG
+captures ecological signal (Dalla Riva \& Stouffer 2016); at this point,
+it is important to recall that a metaweb is intended as a catalogue of
+all possible interactions, which should then be filtered
+(Morales-Castilla \emph{et al.} 2015). In practice (and in this
+instance) the reconstructed metaweb will predict interactions that are
+plausible based on the species' evolutionary history, however some
+interactions would not be realized due to human impact.
+
+Cirtwill \emph{et al.} (2019) previously made the point that network
+inference techniques based on Bayesian approaches would perform far
+better in the presence of an interaction-level informative prior; the
+desirable properties of such a prior would be that it is expressed as a
 probability, preferably representing a Bernoulli event, the value of
-which would be representative of relevant biological processes. We argue
-that the probability returned at the very last step of our framework may
-serve as this informative prior; indeed, the output of our analysis can
-be used in subsequent steps, also possibly involving expert elicitation
-to validate some of the most strongly recommended interactions. One
-important \emph{caveat} to keep in mind when working with interaction
-inference is that interactions can never really be true negatives (in
-the current state of our methodological framework and data collection
-limitations); this renders the task of validating a model through the
-usual application of binary classification statistics very difficult
-(although see Strydom et al. 2021 for a discussion of alternative
-suggestions).
+which would be representative of relevant biological processes
+(probability of predation in this case). We argue that the probability
+returned at the very last step of our framework may serve as this
+informative prior; indeed, the output of our analysis can be used in
+subsequent steps, also possibly involving expert elicitation to validate
+some of the most strongly recommended interactions. One important
+\emph{caveat} to keep in mind when working with interaction inference is
+that interactions can never really be true negatives (in the current
+state of our methodological framework and data collection limitations);
+this renders the task of validating a model through the usual
+application of binary classification statistics very difficult (although
+see Strydom \emph{et al.} 2021a for a discussion of alternative
+suggestions). The other way through which our framework can be improved
+is by substituting the predictors that are used for transfer. For
+example, in the presence of information on species traits that are known
+to be predictive of species interactions, one might want to rely on
+functional rather than phylogenetic distances -- in food webs, body size
+(and allometrically related variables) has been established as such a
+variable (Brose \emph{et al.} 2006); the identification of relevant
+functional traits is facilitated by recent methodological developments
+(Rosado \emph{et al.} 2013). It should be noted that Xing \& Fayle
+(2021) highlight phylogenetic relatedness as one of the core components
+of network comparison at the global scale. In this case study, we have
+embedded the original metaweb using t-SVD, because it lends itself to a
+RDPG reconstruction, which is known to capture the consequences of
+evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
+there are others ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
+Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
+alternatives.
 
@@
 their biodiversity assessment, as each country tends to set goals at the
-national level (Buxton et al. 2021) for which quantitative instruments
-are designed (Turak et al. 2017), with specific strategies often enacted
-at smaller scales (Ray, Grimm, and Olive 2021). Yet these national
-divisions, in large parts of the world, reflect nothing except for the
-legacy of settler colonialism, and operating under them must be done
-under the clear realization that they contributed to the ongoing
-biodiversity crisis (Adam 2014), can reinforce environmental injustice
-(Choudry 2013; Domínguez and Luoma 2020), and on Turtle Island
+national level (Buxton \emph{et al.} 2021) for which quantitative
+instruments are designed (Turak \emph{et al.} 2017), with specific
+strategies often enacted at smaller scales (Ray \emph{et al.} 2021). Yet
+these national divisions, in large parts of the world, reflect nothing
+except for the legacy of settler colonialism, and operating under them
+must be done under the clear realization that they contributed to the
+ongoing biodiversity crisis (Adam 2014), can reinforce environmental
+injustice (Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
 especially, will probably end up being replaced by Indigenous principles
-of land management (Eichhorn, Baker, and Griffiths 2019; No'kmaq et al.
+of land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
 2021).
@@
 Alberta. M-JF acknowledges funding from NSERC Discovery Grant and NSERC
-CRC RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
+CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
 Iho National Science Challenge, administered by New Zealand Ministry of
@@
 Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's
-scholarshipTP acknowledges financial support from NSERC through the
-Discovery Grants and Discovery Accelerator Supplement programs.
+scholarship. LP acknowledges funding from NSERC Discovery Grant (NSERC
+RGPIN-2019-05771). TP acknowledges financial support from NSERC through
+the Discovery Grants and Discovery Accelerator Supplement programs.
 
@@
 \leavevmode\hypertarget{ref-Adam2014EleTre}{}%
-Adam, Rachelle. 2014. \emph{Elephant Treaties: The Colonial Legacy of
-the Biodiversity Crisis}. UPNE.
+Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
+biodiversity crisis}. UPNE.
 
 \leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
-Albouy, Camille, Philippe Archambault, Ward Appeltans, Miguel B. Araújo,
-David Beauchesne, Kevin Cazelles, Alyssa R. Cirtwill, et al. 2019.
-{``The Marine Fish Food Web Is Globally Connected.''} \emph{Nature
-Ecology \& Evolution} 3 (8): 1153--61.
-\url{https://doi.org/10.1038/s41559-019-0950-y}.
+Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
+D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
+globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.
+
+\leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
+Arsov, N. \& Mirceva, G. (2019). Network Embedding: An Overview.
+\emph{arXiv:1911.11726 {[}cs, stat{]}}.
 
 \leavevmode\hypertarget{ref-Banville2021ManJl}{}%
-Banville, Francis, Steve Vissault, and Timothée Poisot. 2021.
-{``Mangal.jl and EcologicalNetworks.jl: Two Complementary Packages for
-Analyzing Ecological Networks in Julia.''} \emph{Journal of Open Source
-Software} 6 (61): 2721. \url{https://doi.org/10.21105/joss.02721}.
+Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
+EcologicalNetworks.jl: Two complementary packages for analyzing
+ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
+2721.
 
 \leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
-Bascompte, J., P. Jordano, C. J. Melian, and J. M. Olesen. 2003. {``The
-Nested Assembly of Plant-Animal Mutualistic Networks.''}
-\emph{Proceedings of the National Academy of Sciences} 100 (16):
-9383--87. \url{https://doi.org/10.1073/pnas.1633576100}.
+Bascompte, J., Jordano, P., Melian, C.J. \& Olesen, J.M. (2003). The
+nested assembly of plant-animal mutualistic networks. \emph{Proceedings
+of the National Academy of Sciences}, 100, 9383--9387.
 
 \leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
-Beckerman, Andrew P., Owen L. Petchey, and Philip H. Warren. 2006.
-{``Foraging Biology Predicts Food Web Complexity.''} \emph{Proceedings
-of the National Academy of Sciences} 103 (37): 13745--49.
-\url{https://doi.org/10.1073/pnas.0603039103}.
+Beckerman, A.P., Petchey, O.L. \& Warren, P.H. (2006). Foraging biology
+predicts food web complexity. \emph{Proceedings of the National Academy
+of Sciences}, 103, 13745--13749.
 
 \leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
-Bezanson, J., A. Edelman, S. Karpinski, and V. Shah. 2017. {``Julia: A
-Fresh Approach to Numerical Computing.''} \emph{SIAM Review} 59 (1):
-65--98. \url{https://doi.org/10.1137/141000671}.
+Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V. (2017). Julia: A
+Fresh Approach to Numerical Computing. \emph{SIAM Review}, 59, 65--98.
 
 \leavevmode\hypertarget{ref-Boeckaerts2021PreBac}{}%
-Boeckaerts, Dimitri, Michiel Stock, Bjorn Criel, Hans Gerstmans, Bernard
-De Baets, and Yves Briers. 2021. {``Predicting Bacteriophage Hosts Based
-on Sequences of Annotated Receptor-Binding Proteins.''} \emph{Scientific
-Reports} 11 (1): 1467. \url{https://doi.org/10.1038/s41598-021-81063-4}.
+Boeckaerts, D., Stock, M., Criel, B., Gerstmans, H., De Baets, B. \&
+Briers, Y. (2021). Predicting bacteriophage hosts based on sequences of
+annotated receptor-binding proteins. \emph{Scientific Reports}, 11,
+1467.
 
 \leavevmode\hypertarget{ref-Braga2021PhyRec}{}%
-Braga, Mariana P., Niklas Janz, Sören Nylin, Fredrik Ronquist, and
-Michael J. Landis. 2021. {``Phylogenetic Reconstruction of Ancestral
-Ecological Networks Through Time for Pierid Butterflies and Their Host
-Plants.''} \emph{Ecology Letters} n/a (n/a).
-\url{https://doi.org/10.1111/ele.13842}.
+Braga, M.P., Janz, N., Nylin, S., Ronquist, F. \& Landis, M.J. (2021).
+Phylogenetic reconstruction of ancestral ecological networks through
+time for pierid butterflies and their host plants. \emph{Ecology
+Letters}, n/a.
+
+\leavevmode\hypertarget{ref-Brose2006ConRes}{}%
+Brose, U., Jonsson, T., Berlow, E.L., Warren, P., Banasek-Richter, C.,
+Bersier, L.-F., \emph{et al.} (2006). ConsumerResource Body-Size
+Relationships in Natural Food Webs. \emph{Ecology}, 87, 2411--2417.
 
 \leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
-Buxton, Rachel T., Joseph R. Bennett, Andrea J. Reid, Charles Shulman,
-Steven J. Cooke, Charles M. Francis, Elizabeth A. Nyboer, et al. 2021.
-{``Key Information Needs to Move from Knowledge to Action for
-Biodiversity Conservation in Canada.''} \emph{Biological Conservation}
-256: 108983. \url{https://doi.org/10.1016/j.biocon.2021.108983}.
+Buxton, R.T., Bennett, J.R., Reid, A.J., Shulman, C., Cooke, S.J.,
+Francis, C.M., \emph{et al.} (2021). Key information needs to move from
+knowledge to action for biodiversity conservation in Canada.
+\emph{Biological Conservation}, 256, 108983.
+
+\leavevmode\hypertarget{ref-Cai2017ComSur}{}%
+Cai, H., Zheng, V.W. \& Chang, K.C.-C. (2017). A Comprehensive Survey of
+Graph Embedding: Problems, Techniques and Applications. \emph{arXiv
+preprint arXiv:1709.07604}.
 
 \leavevmode\hypertarget{ref-Cameron2019UneGlo}{}%
-Cameron, Erin K., Maja K. Sundqvist, Sally A. Keith, Paul J. CaraDonna,
-Erik A. Mousing, Karin A. Nilsson, Daniel B. Metcalfe, and Aimée T.
-Classen. 2019. {``Uneven Global Distribution of Food Web Studies Under
-Climate Change.''} \emph{Ecosphere} 10 (3): e02645.
-\url{https://doi.org/10.1002/ecs2.2645}.
+Cameron, E.K., Sundqvist, M.K., Keith, S.A., CaraDonna, P.J., Mousing,
+E.A., Nilsson, K.A., \emph{et al.} (2019). Uneven global distribution of
+food web studies under climate change. \emph{Ecosphere}, 10, e02645.
+
+\leavevmode\hypertarget{ref-Cao2019NetEmb}{}%
+Cao, R.-M., Liu, S.-Y. \& Xu, X.-K. (2019). Network embedding for link
+prediction: The pitfall and improvement. \emph{Chaos: An
+Interdisciplinary Journal of Nonlinear Science}, 29, 103102.
 
 \leavevmode\hypertarget{ref-Cavender-Bares2009MerCom}{}%
-Cavender-Bares, Jeannine, Kenneth H. Kozak, Paul V. A. Fine, and Steven
-W. Kembel. 2009. {``The Merging of Community Ecology and Phylogenetic
-Biology.''} \emph{Ecology Letters} 12 (7): 693--715.
-\url{https://doi.org/10.1111/j.1461-0248.2009.01314.x}.
+Cavender-Bares, J., Kozak, K.H., Fine, P.V.A. \& Kembel, S.W. (2009).
+The merging of community ecology and phylogenetic biology. \emph{Ecology
+Letters}, 12, 693--715.
 
 \leavevmode\hypertarget{ref-Choudry2013SavBio}{}%
-Choudry, Aziz. 2013. {``Saving Biodiversity, for Whom and for What?
-Conservation NGOs, Complicity, Colonialism and Conquest in an Era of
-Capitalist Globalization.''} In \emph{NGOization: Complicity,
-Contradictions and Prospects}, 24--44. Bloomsbury Publishing.
+Choudry, A. (2013). Saving biodiversity, for whom and for what?
+Conservation NGOs, complicity, colonialism and conquest in an era of
+capitalist globalization. In: \emph{NGOization: Complicity,
+contradictions and prospects}. Bloomsbury Publishing, pp. 24--44.
 
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, Alyssa R., Anna Eklf, Tomas Roslin, Kate Wootton, and
-Dominique Gravel. 2019. {``A Quantitative Framework for Investigating
-the Reliability of Empirical Network Construction.''} \emph{Methods in
-Ecology and Evolution} 0 (ja).
-\url{https://doi.org/10.1111/2041-210X.13180}.
+Cirtwill, A.R., Eklf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
+A quantitative framework for investigating the reliability of empirical
+network construction. \emph{Methods in Ecology and Evolution}, 0.
 
 \leavevmode\hypertarget{ref-Cirtwill2021BuiFoo}{}%
-Cirtwill, Alyssa R., and Peter Hambäck. 2021. {``Building Food Networks
-from Molecular Data: Bayesian or Fixed-Number Thresholds for Including
-Links.''} \emph{Basic and Applied Ecology} 50: 67--76.
-\url{https://doi.org/10.1016/j.baae.2020.11.007}.
+Cirtwill, A.R. \& Hambäck, P. (2021). Building food networks from
+molecular data: Bayesian or fixed-number thresholds for including links.
+\emph{Basic and Applied Ecology}, 50, 67--76.
 
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
-Dalla Riva, Giulio V., and Daniel B. Stouffer. 2016. {``Exploring the
-Evolutionary Signature of Food Webs' Backbones Using Functional
-Traits.''} \emph{Oikos} 125 (4): 446--56.
-\url{https://doi.org/10.1111/oik.02305}.
+Dalla Riva, G.V. \& Stouffer, D.B. (2016). Exploring the evolutionary
+signature of food webs' backbones using functional traits. \emph{Oikos},
+125, 446--456.
 
 \leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
-Dansereau, Gabriel, and Timothée Poisot. 2021. {``SimpleSDMLayers.jl and
-GBIF.jl: A Framework for Species Distribution Modeling in Julia.''}
-\emph{Journal of Open Source Software} 6 (57): 2872.
-\url{https://doi.org/10.21105/joss.02872}.
+Dansereau, G. \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
+Framework for Species Distribution Modeling in Julia. \emph{Journal of
+Open Source Software}, 6, 2872.
 
 \leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
-Domínguez, Lara, and Colin Luoma. 2020. {``Decolonising Conservation
-Policy: How Colonial Land and Conservation Ideologies Persist and
-Perpetuate Indigenous Injustices at the Expense of the Environment.''}
-\emph{Land} 9 (3): 65. \url{https://doi.org/10.3390/land9030065}.
+Domínguez, L. \& Luoma, C. (2020). Decolonising Conservation Policy: How
+Colonial Land and Conservation Ideologies Persist and Perpetuate
+Indigenous Injustices at the Expense of the Environment. \emph{Land}, 9,
+65.
 
 \leavevmode\hypertarget{ref-Dormann2010EvoCli}{}%
-Dormann, Carsten F., Bernd Gruber, Marten Winter, and Dirk Herrmann.
-2010. {``Evolution of Climate Niches in European Mammals?''}
-\emph{Biology Letters} 6 (2): 229--32.
-\url{https://doi.org/10.1098/rsbl.2009.0688}.
+Dormann, C.F., Gruber, B., Winter, M. \& Herrmann, D. (2010). Evolution
+of climate niches in European mammals? \emph{Biology Letters}, 6,
+229--232.
 
 \leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
-Dunne, Jennifer A. 2006. {``The Network Structure of Food Webs.''} In
-\emph{Ecological Networks: Linking Structure and Dynamics}, edited by
-Jennifer A Dunne and Mercedes Pascual, 27--86. Oxford University Press.
+Dunne, J.A. (2006). The Network Structure of Food Webs. In:
+\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
+J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
 
 \leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
-Eichhorn, Markus P., Kate Baker, and Mark Griffiths. 2019. {``Steps
-Towards Decolonising Biogeography.''} \emph{Frontiers of Biogeography}
-12 (1): 1--7. \url{https://doi.org/10.21425/F5FBG44795}.
+Eichhorn, M.P., Baker, K. \& Griffiths, M. (2019). Steps towards
+decolonising biogeography. \emph{Frontiers of Biogeography}, 12, 1--7.
 
 \leavevmode\hypertarget{ref-Eklof2016PhyCom}{}%
-Eklöf, Anna, and Daniel B. Stouffer. 2016. {``The Phylogenetic Component
-of Food Web Structure and Intervality.''} \emph{Theoretical Ecology} 9
-(1): 107--15. \url{https://doi.org/10.1007/s12080-015-0273-9}.
+Eklöf, A. \& Stouffer, D.B. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theoretical Ecology}, 9, 107--115.
 
 \leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
-Garland, THEODORE, JR., PETER E. Midford, and ANTHONY R. Ives. 1999.
-{``An Introduction to Phylogenetically Based Statistical Methods, with a
-New Method for Confidence Intervals on Ancestral Values1.''}
-\emph{American Zoologist} 39 (2): 374--88.
-\url{https://doi.org/10.1093/icb/39.2.374}.
+Garland, T., JR., Midford, P.E. \& Ives, A.R. (1999). An Introduction to
+Phylogenetically Based Statistical Methods, with a New Method for
+Confidence Intervals on Ancestral Values1. \emph{American Zoologist},
+39, 374--388.
 
 \leavevmode\hypertarget{ref-Garlaschelli2018CovStr}{}%
-Garlaschelli, Diego, Frank den Hollander, and Andrea Roccaverde. 2018.
-{``Covariance Structure Behind Breaking of Ensemble Equivalence in
-Random Graphs.''} \emph{Journal of Statistical Physics} 173 (3-4):
-644--62. \url{https://doi.org/10.1007/s10955-018-2114-x}.
+Garlaschelli, D., Hollander, F. den \& Roccaverde, A. (2018). Covariance
+structure behind breaking of ensemble equivalence in random graphs.
+\emph{Journal of Statistical Physics}, 173, 644--662.
 
 \leavevmode\hypertarget{ref-GBIFSecretariat2021GbiBac}{}%
-GBIF Secretariat. 2021. {``GBIF Backbone Taxonomy.''}
-\url{https://doi.org/10.15468/39omei}.
+GBIF Secretariat. (2021). GBIF Backbone Taxonomy.
 
 \leavevmode\hypertarget{ref-Gerhold2015PhyPat}{}%
-Gerhold, Pille, James F. Cahill, Marten Winter, Igor V. Bartish, and
-Andreas Prinzing. 2015. {``Phylogenetic Patterns Are Not Proxies of
-Community Assembly Mechanisms (they Are Far Better).''} \emph{Functional
-Ecology} 29 (5): 600--614.
-\url{https://doi.org/10.1111/1365-2435.12425}.
+Gerhold, P., Cahill, J.F., Winter, M., Bartish, I.V. \& Prinzing, A.
+(2015). Phylogenetic patterns are not proxies of community assembly
+mechanisms (they are far better). \emph{Functional Ecology}, 29,
+600--614.
+
+\leavevmode\hypertarget{ref-Grenie2021HarTax}{}%
+Grenié, M., Berti, E., Carvajal-Quintero, J.D., Winter, M. \& Sagouis,
+A. (2021). Harmonizing taxon names in biodiversity data: A review of
+tools, databases, and best practices.
 
 \leavevmode\hypertarget{ref-Halko2011FinStr}{}%
-Halko, N., P. G. Martinsson, and J. A. Tropp. 2011. {``Finding Structure
+Halko, N., Martinsson, P.G. \& Tropp, J.A. (2011). Finding Structure
 with Randomness: Probabilistic Algorithms for Constructing Approximate
-Matrix Decompositions.''} \emph{SIAM Review} 53 (2): 217--88.
-\url{https://doi.org/10.1137/090771806}.
+Matrix Decompositions. \emph{SIAM Review}, 53, 217--288.
 
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, Frank. 1965. \emph{Dune}. First. Philadelphia: Chilton Book
-Company.
+Herbert, F. (1965). \emph{Dune}. First. Chilton Book Company,
+Philadelphia.
+
+\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
+Hortal, J., de Bello, F., Diniz-Filho, J.A.F., Lewinsohn, T.M., Lobo,
+J.M. \& Ladle, R.J. (2015). Seven Shortfalls that Beset Large-Scale
+Knowledge of Biodiversity. \emph{Annual Review of Ecology, Evolution,
+and Systematics}, 46, 523--549.
+
+\leavevmode\hypertarget{ref-Hutchinson2017CopSig}{}%
+Hutchinson, M.C., Cagua, E.F. \& Stouffer, D.B. (2017). Cophylogenetic
+signal is detectable in pollination interactions across ecological
+scales. \emph{Ecology}, n/a--n/a.
+
+\leavevmode\hypertarget{ref-Jordano2016ChaEco}{}%
+Jordano, P. (2016a). Chasing Ecological Interactions. \emph{PLOS Biol},
+14, e1002559.
+
+\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
+Jordano, P. (2016b). Sampling networks of ecological interactions.
+\emph{Functional Ecology}, 30, 1883--1893.
+
+\leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
+Litsios, G. \& Salamin, N. (2012). Effects of Phylogenetic Signal on
+Ancestral State Reconstruction. \emph{Systematic Biology}, 61, 533--538.
+
+\leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
+Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
+Thuiller, W. (2020a). Data from: Tetra-EU 1.0: A species-level trophic
+meta-web of European tetrapods.
+
+\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
+Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
+Thuiller, W. (2020b). TETRA-EU 1.0: A species-level trophic metaweb of
+European tetrapods. \emph{Global Ecology and Biogeography}, 29,
+1452--1457.
+
+\leavevmode\hypertarget{ref-Marco2018ChaHum}{}%
+Marco, M.D., Venter, O., Possingham, H.P. \& Watson, J.E.M. (2018).
+Changes in human footprint drive changes in species extinction risk.
+\emph{Nature Communications}, 9, 4621.
+
+\leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
+Morales-Castilla, I., Matias, M.G., Gravel, D. \& Araújo, M.B. (2015).
+Inferring biotic interactions from proxies. \emph{Trends in Ecology \&
+Evolution}, 30, 347--356.
+
+\leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
+Mouquet, N., Devictor, V., Meynard, C.N., Munoz, F., Bersier, L.-F.,
+Chave, J., \emph{et al.} (2012). Ecophylogenetics: Advances and
+perspectives. \emph{Biological Reviews}, 87, 769--785.
+
+\leavevmode\hypertarget{ref-Nenzen2014Imp850}{}%
+Nenzén, H.K., Montoya, D. \& Varela, S. (2014). The Impact of 850,000
+Years of Climate Changes on the Structure and Dynamics of Mammal Food
+Webs. \emph{PLOS ONE}, 9, e106651.
+
+\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
+No'kmaq, M., Marshall, A., Beazley, K.F., Hum, J., joudry, shalan,
+Papadopoulos, A., \emph{et al.} (2021). {``Awakening the sleeping
+giant''}: Re-Indigenization principles for transforming biodiversity
+conservation in Canada and beyond. \emph{FACETS}, 6, 839--869.
+
+\leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
+O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
+L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
+of tetrapods across Europe through the prism of the Eltonian niche.
+\emph{Journal of Biogeography}, 47, 181--192.
+
+\leavevmode\hypertarget{ref-Pan2010SurTra}{}%
+Pan, S.J. \& Yang, Q. (2010). A Survey on Transfer Learning. \emph{IEEE
+Transactions on Knowledge and Data Engineering}, 22, 1345--1359.
+
+\leavevmode\hypertarget{ref-Park2004StaMec}{}%
+Park, J. \& Newman, M.E.J. (2004). Statistical mechanics of networks.
+\emph{Physical Review E}, 70, 066117.
+
+\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
+Pedersen, E.J., Thompson, P.L., Ball, R.A., Fortin, M.-J., Gouhier,
+T.C., Link, H., \emph{et al.} (2017). Signatures of the collapse and
+incipient recovery of an overexploited marine ecosystem. \emph{Royal
+Society Open Science}, 4, 170215.
+
+\leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
+Pires, M.M., Koch, P.L., Fariña, R.A., de Aguiar, M.A.M., dos Reis, S.F.
+\& Guimarães, P.R. (2015). Pleistocene megafaunal interaction networks
+became more vulnerable after human arrival. \emph{Proceedings of the
+Royal Society B: Biological Sciences}, 282, 20151367.
+
+\leavevmode\hypertarget{ref-Poelen2014GloBio}{}%
+Poelen, J.H., Simons, J.D. \& Mungall, C.J. (2014). Global biotic
+interactions: An open infrastructure to share and analyze
+species-interaction datasets. \emph{Ecological Informatics}, 24,
+148--159.
+
+\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
+Poisot, T., Belisle, Z., Hoebeke, L., Stock, M. \& Szefer, P. (2019).
+EcologicalNetworks.jl - analysing ecological networks. \emph{Ecography}.
+
+\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
+Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
+MacDonald, A., \emph{et al.} (2021a). Global knowledge gaps in species
+interaction networks data. \emph{Journal of Biogeography}, n/a.
+
+\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
+Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
+The dissimilarity of species interaction networks. \emph{Ecology
+Letters}, 15, 1353--1361.
+
+\leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
+Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
+Stouffer, D.B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, 7, 303--312.
+
+\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
+Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
+Albery, G.F., \emph{et al.} (2021b). Imputing the mammalian virome with
+linear filtering and singular value decomposition.
+\emph{arXiv:2105.14973 {[}q-bio{]}}.
+
+\leavevmode\hypertarget{ref-Poisot2018IntRet}{}%
+Poisot, T. \& Stouffer, D.B. (2018). Interactions retain the
+co-phylogenetic matching that communities lost. \emph{Oikos}, 127,
+230--238.
+
+\leavevmode\hypertarget{ref-Price2003MacThe}{}%
+Price, P.W. (2003). \emph{Macroevolutionary theory on macroecological
+patterns}. Cambridge University Press.
+
+\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
+Ray, J.C., Grimm, J. \& Olive, A. (2021). The biodiversity crisis in
+Canada: Failures and challenges of federal and sub-national strategic
+and legal frameworks. \emph{FACETS}, 6, 1044--1068.
+
+\leavevmode\hypertarget{ref-Reeve2016HowPar}{}%
+Reeve, R., Leinster, T., Cobbold, C.A., Thompson, J., Brummitt, N.,
+Mitchell, S.N., \emph{et al.} (2016). How to partition diversity.
+\emph{arXiv:1404.6520 {[}q-bio{]}}.
+
+\leavevmode\hypertarget{ref-Rosado2013GoiBac}{}%
+Rosado, B.H.P., Dias, A. \& de Mattos, E. (2013). Going Back to Basics:
+Importance of Ecophysiology when Choosing Functional Traits for Studying
+Communities and Ecosystems. \emph{Natureza \&
+conservaç\textasciitilde ao revista brasileira de
+conservaç\textasciitilde ao da natureza}, 11, 15--22.
+
+\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
+Runghen, R., Stouffer, D.B. \& Dalla Riva, G.V. (2021). Exploiting node
+metadata to predict interactions in large networks using graph embedding
+and neural networks.
+
+\leavevmode\hypertarget{ref-Schoener1989FooWeb}{}%
+Schoener, T.W. (1989). Food webs from the small to the large.
+\emph{Ecology}, 70, 1559--1589.
+
+\leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
+Solís-Lemus, C., Bastide, P. \& Ané, C. (2017). PhyloNetworks: A Package
+for Phylogenetic Networks. \emph{Molecular Biology and Evolution}, 34,
+3292--3298.
+
+\leavevmode\hypertarget{ref-Stock2021PaiLea}{}%
+Stock, M. (2021). Pairwise learning for predicting pollination
+interactions based on traits and phylogeny. \emph{Ecological Modelling},
+14.
+
+\leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
+Stouffer, D.B., Sales-Pardo, M., Sirer, M.I. \& Bascompte, J. (2012).
+Evolutionary Conservation of Species' Roles in Food Webs.
+\emph{Science}, 335, 1489--1492.
+
+\leavevmode\hypertarget{ref-Strong2014ImpNon}{}%
+Strong, J.S. \& Leroux, S.J. (2014). Impact of Non-Native Terrestrial
+Mammals on the Structure of the Terrestrial Mammal Food Web of
+Newfoundland, Canada. \emph{PLOS ONE}, 9, e106264.
+
+\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
+Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., \emph{et al.} (2021a). \emph{A Roadmap Toward
+Predicting Species Interaction Networks (Across Space and Time)}
+(Preprint). EcoEvoRxiv.
+
+\leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
+Strydom, T., Dalla Riva, G.V. \& Poisot, T. (2021b). SVD Entropy Reveals
+the High Complexity of Ecological Networks. \emph{Frontiers in Ecology
+and Evolution}, 9.
+
+\leavevmode\hypertarget{ref-Thessen2014KnoExt}{}%
+Thessen, A.E. \& Parr, C.S. (2014). Knowledge extraction and semantic
+annotation of text from the encyclopedia of life. \emph{PloS one}, 9,
+e89550.
+
+\leavevmode\hypertarget{ref-Torrey2010TraLea}{}%
+Torrey, L. \& Shavlik, J. (2010). Transfer learning. In: \emph{Handbook
+of research on machine learning applications and trends: Algorithms,
+methods, and techniques}. IGI global, pp. 242--264.
+
+\leavevmode\hypertarget{ref-Trojelsgaard2016EcoNet}{}%
+Trøjelsgaard, K. \& Olesen, J.M. (2016). Ecological networks in motion:
+Micro- and macroscopic variability across scales. \emph{Functional
+Ecology}, 30, 1926--1935.
+
+\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
+Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
+Dunkerley, G., \emph{et al.} (2017). Using the essential biodiversity
+variables framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, SI:Measures of biodiversity, 213,
+264--271.
+
+\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
+Upham, N.S., Esselstyn, J.A. \& Jetz, W. (2019). Inferring the mammal
+tree: Species-level sets of phylogenies for questions in ecology,
+evolution, and conservation. \emph{PLOS Biology}, 17, e3000494.
 
 \leavevmode\hypertarget{ref-vanderHoorn2018SpaMax}{}%
-Hoorn, Pim van der, Gabor Lippner, and Dmitri Krioukov. 2018. {``Sparse
+van der Hoorn, P., Lippner, G. \& Krioukov, D. (2018). Sparse
 Maximum-Entropy Random Graphs with a Given Power-Law Degree
-Distribution.''} \emph{Journal of Statistical Physics} 173 (3-4):
-806--44. \url{https://doi.org/10.1007/s10955-017-1887-7}.
-
-\leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
-Hortal, Joaquín, Francesco de Bello, José Alexandre F. Diniz-Filho,
-Thomas M. Lewinsohn, Jorge M. Lobo, and Richard J. Ladle. 2015. {``Seven
-Shortfalls That Beset Large-Scale Knowledge of Biodiversity.''}
-\emph{Annual Review of Ecology, Evolution, and Systematics} 46 (1):
-523--49. \url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}.
-
-\leavevmode\hypertarget{ref-Hutchinson2017CopSig}{}%
-Hutchinson, Matthew C., Edgar Fernando Cagua, and Daniel B. Stouffer.
-2017. {``Cophylogenetic Signal Is Detectable in Pollination Interactions
-Across Ecological Scales.''} \emph{Ecology}, n/a--.
-\url{https://doi.org/10.1002/ecy.1955}.
-
-\leavevmode\hypertarget{ref-Jordano2016ChaEco}{}%
-Jordano, Pedro. 2016a. {``Chasing Ecological Interactions.''} \emph{PLOS
-Biol} 14 (9): e1002559.
-\url{https://doi.org/10.1371/journal.pbio.1002559}.
-
-\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
----------. 2016b. {``Sampling Networks of Ecological Interactions.''}
-Edited by Daniel Stouffer. \emph{Functional Ecology} 30 (12): 1883--93.
-\url{https://doi.org/10.1111/1365-2435.12763}.
-
-\leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
-Litsios, Glenn, and Nicolas Salamin. 2012. {``Effects of Phylogenetic
-Signal on Ancestral State Reconstruction.''} \emph{Systematic Biology}
-61 (3): 533--38. \url{https://doi.org/10.1093/sysbio/syr124}.
-
-\leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
-Maiorano, Luigi, Alessandro Montemaggiori, Gentile Francesco Ficetola,
-Louise O'Connor, and Wilfried Thuiller. 2020a. {``Data from: Tetra-EU
-1.0: A Species-Level Trophic Meta-Web of European Tetrapods.''} Dryad.
-\url{https://doi.org/10.5061/DRYAD.JM63XSJ7B}.
-
-\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
----------. 2020b. {``TETRA-EU 1.0: A Species-Level Trophic Metaweb of
-European Tetrapods.''} Edited by Allen Hurlbert. \emph{Global Ecology
-and Biogeography} 29 (9): 1452--57.
-\url{https://doi.org/10.1111/geb.13138}.
-
-\leavevmode\hypertarget{ref-Marco2018ChaHum}{}%
-Marco, Moreno Di, Oscar Venter, Hugh P. Possingham, and James E. M.
-Watson. 2018. {``Changes in Human Footprint Drive Changes in Species
-Extinction Risk.''} \emph{Nature Communications} 9 (1): 4621.
-\url{https://doi.org/10.1038/s41467-018-07049-5}.
-
-\leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
-Morales-Castilla, Ignacio, Miguel G. Matias, Dominique Gravel, and
-Miguel B. Araújo. 2015. {``Inferring Biotic Interactions from
-Proxies.''} \emph{Trends in Ecology \& Evolution} 30 (6): 347--56.
-\url{https://doi.org/10.1016/j.tree.2015.03.014}.
-
-\leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
-Mouquet, Nicolas, Vincent Devictor, Christine N. Meynard, Francois
-Munoz, Louis-Félix Bersier, Jérôme Chave, Pierre Couteron, et al. 2012.
-{``Ecophylogenetics: Advances and Perspectives.''} \emph{Biological
-Reviews} 87 (4): 769--85.
-\url{https://doi.org/10.1111/j.1469-185X.2012.00224.x}.
-
-\leavevmode\hypertarget{ref-Nenzen2014Imp850}{}%
-Nenzén, Hedvig K., Daniel Montoya, and Sara Varela. 2014. {``The Impact
-of 850,000 Years of Climate Changes on the Structure and Dynamics of
-Mammal Food Webs.''} \emph{PLOS ONE} 9 (9): e106651.
-\url{https://doi.org/10.1371/journal.pone.0106651}.
-
-\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
-No'kmaq, M'sit, Albert Marshall, Karen F. Beazley, Jessica Hum, shalan
-joudry, Anastasia Papadopoulos, Sherry Pictou, Janet Rabesca, Lisa
-Young, and Melanie Zurba. 2021. {``{`Awakening the Sleeping Giant'}:
-Re-Indigenization Principles for Transforming Biodiversity Conservation
-in Canada and Beyond.''} \emph{FACETS} 6 (1): 839--69.
-
-\leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
-O'Connor, Louise M. J., Laura J. Pollock, João Braga, Gentile Francesco
-Ficetola, Luigi Maiorano, Camille Martinez-Almoyna, Alessandro
-Montemaggiori, Marc Ohlmann, and Wilfried Thuiller. 2020. {``Unveiling
-the Food Webs of Tetrapods Across Europe Through the Prism of the
-Eltonian Niche.''} \emph{Journal of Biogeography} 47 (1): 181--92.
-\url{https://doi.org/10.1111/jbi.13773}.
-
-\leavevmode\hypertarget{ref-Pan2010SurTra}{}%
-Pan, Sinno Jialin, and Qiang Yang. 2010. {``A Survey on Transfer
-Learning.''} \emph{IEEE Transactions on Knowledge and Data Engineering}
-22 (10): 1345--59. \url{https://doi.org/10.1109/TKDE.2009.191}.
-
-\leavevmode\hypertarget{ref-Park2004StaMec}{}%
-Park, Juyong, and M. E. J. Newman. 2004. {``Statistical Mechanics of
-Networks.''} \emph{Physical Review E} 70 (6): 066117.
-\url{https://doi.org/10.1103/PhysRevE.70.066117}.
-
-\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
-Pedersen, Eric J., Patrick L. Thompson, R. Aaron Ball, Marie-Josée
-Fortin, Tarik C. Gouhier, Heike Link, Charlotte Moritz, et al. 2017.
-{``Signatures of the Collapse and Incipient Recovery of an Overexploited
-Marine Ecosystem.''} \emph{Royal Society Open Science} 4 (7): 170215.
-\url{https://doi.org/10.1098/rsos.170215}.
-
-\leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
-Pires, Mathias M., Paul L. Koch, Richard A. Fariña, Marcus A. M. de
-Aguiar, Sérgio F. dos Reis, and Paulo R. Guimarães. 2015. {``Pleistocene
-Megafaunal Interaction Networks Became More Vulnerable After Human
-Arrival.''} \emph{Proceedings of the Royal Society B: Biological
-Sciences} 282 (1814): 20151367.
-\url{https://doi.org/10.1098/rspb.2015.1367}.
-
-\leavevmode\hypertarget{ref-Poelen2014GloBio}{}%
-Poelen, Jorrit H., James D. Simons, and Chris J. Mungall. 2014.
-{``Global Biotic Interactions: An Open Infrastructure to Share and
-Analyze Species-Interaction Datasets.''} \emph{Ecological Informatics}
-24: 148--59. \url{https://doi.org/10.1016/j.ecoinf.2014.08.005}.
-
-\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
-Poisot, Timothée, Zacharie Belisle, Laura Hoebeke, Michiel Stock, and
-Piotr Szefer. 2019. {``EcologicalNetworks.jl - Analysing Ecological
-Networks.''} \emph{Ecography}. \url{https://doi.org/10.1111/ecog.04310}.
-
-\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
-Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
-Dominique Gravel, Andrew MacDonald, Benjamin Mercier, Clément Violet,
-and Steve Vissault. 2021. {``Global Knowledge Gaps in Species
-Interaction Networks Data.''} \emph{Journal of Biogeography} n/a (n/a).
-\url{https://doi.org/10.1111/jbi.14127}.
-
-\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
-Poisot, Timothée, Elsa Canard, David Mouillot, Nicolas Mouquet, and
-Dominique Gravel. 2012. {``The Dissimilarity of Species Interaction
-Networks.''} \emph{Ecology Letters} 15 (12): 1353--61.
-\url{https://doi.org/10.1111/ele.12002}.
-
-\leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
-Poisot, Timothée, Alyssa R. Cirtwill, Kévin Cazelles, Dominique Gravel,
-Marie-Josée Fortin, and Daniel B. Stouffer. 2016. {``The Structure of
-Probabilistic Networks.''} Edited by Jana Vamosi. \emph{Methods in
-Ecology and Evolution} 7 (3): 303--12.
-\url{https://doi.org/10.1111/2041-210X.12468}.
-
-\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
-Poisot, Timothée, Marie-Andrée Ouellet, Nardus Mollentze, Maxwell J.
-Farrell, Daniel J. Becker, Gregory F. Albery, Rory J. Gibb, Stephanie N.
-Seifert, and Colin J. Carlson. 2021. {``Imputing the Mammalian Virome
-with Linear Filtering and Singular Value Decomposition.''}
-\emph{arXiv:2105.14973 {[}q-Bio{]}}.
-\url{http://arxiv.org/abs/2105.14973}.
-
-\leavevmode\hypertarget{ref-Poisot2018IntRet}{}%
-Poisot, Timothée, and Daniel B. Stouffer. 2018. {``Interactions Retain
-the Co-Phylogenetic Matching That Communities Lost.''} \emph{Oikos} 127
-(2): 230--38. \url{https://doi.org/10.1111/oik.03788}.
-
-\leavevmode\hypertarget{ref-Price2003MacThe}{}%
-Price, Peter W. 2003. \emph{Macroevolutionary Theory on Macroecological
-Patterns}. Cambridge University Press.
-
-\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
-Ray, Justina C., Jaime Grimm, and Andrea Olive. 2021. {``The
-Biodiversity Crisis in Canada: Failures and Challenges of Federal and
-Sub-National Strategic and Legal Frameworks.''} \emph{FACETS} 6:
-1044--68. \url{https://doi.org/10.1139/facets-2020-0075}.
-
-\leavevmode\hypertarget{ref-Reeve2016HowPar}{}%
-Reeve, Richard, Tom Leinster, Christina A. Cobbold, Jill Thompson, Neil
-Brummitt, Sonia N. Mitchell, and Louise Matthews. 2016. {``How to
-Partition Diversity.''} \emph{arXiv:1404.6520 {[}q-Bio{]}}.
-\url{http://arxiv.org/abs/1404.6520}.
-
-\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
-Runghen, Rogini, Daniel B Stouffer, and Giulio V Dalla Riva. 2021.
-{``Exploiting Node Metadata to Predict Interactions in Large Networks
-Using Graph Embedding and Neural Networks.''}
-\url{https://doi.org/10.1101/2021.06.10.447991}.
-
-\leavevmode\hypertarget{ref-Schoener1989FooWeb}{}%
-Schoener, Thomas W. 1989. {``Food Webs from the Small to the Large.''}
-\emph{Ecology} 70 (6): 1559--89.
-
-\leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
-Solís-Lemus, Claudia, Paul Bastide, and Cécile Ané. 2017.
-{``PhyloNetworks: A Package for Phylogenetic Networks.''}
-\emph{Molecular Biology and Evolution} 34 (12): 3292--98.
-\url{https://doi.org/10.1093/molbev/msx235}.
-
-\leavevmode\hypertarget{ref-Stock2021PaiLea}{}%
-Stock, Michiel. 2021. {``Pairwise Learning for Predicting Pollination
-Interactions Based on Traits and Phylogeny.''} \emph{Ecological
-Modelling}, 14.
-
-\leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
-Stouffer, D. B., M. Sales-Pardo, M. I. Sirer, and J. Bascompte. 2012.
-{``Evolutionary Conservation of Species' Roles in Food Webs.''}
-\emph{Science} 335 (6075): 1489--92.
-\url{https://doi.org/10.1126/science.1216556}.
-
-\leavevmode\hypertarget{ref-Strong2014ImpNon}{}%
-Strong, Justin S., and Shawn J. Leroux. 2014. {``Impact of Non-Native
-Terrestrial Mammals on the Structure of the Terrestrial Mammal Food Web
-of Newfoundland, Canada.''} \emph{PLOS ONE} 9 (8): e106264.
-\url{https://doi.org/10.1371/journal.pone.0106264}.
-
-\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
-Strydom, Tanya, Michael David Catchen, Francis Banville, Dominique
-Caron, Gabriel Dansereau, Philippe Desjardins-Proulx, Norma Forero, et
-al. 2021. {``A Roadmap Toward Predicting Species Interaction Networks
-(Across Space and Time).''} Preprint. EcoEvoRxiv.
-\url{https://doi.org/10.32942/osf.io/eu7k3}.
-
-\leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
-Strydom, Tanya, Giulio V. Dalla Riva, and Timothée Poisot. 2021. {``SVD
-Entropy Reveals the High Complexity of Ecological Networks.''}
-\emph{Frontiers in Ecology and Evolution} 9.
-\url{https://doi.org/10.3389/fevo.2021.623141}.
-
-\leavevmode\hypertarget{ref-Thessen2014KnoExt}{}%
-Thessen, Anne E., and Cynthia Sims Parr. 2014. {``Knowledge Extraction
-and Semantic Annotation of Text from the Encyclopedia of Life.''}
-\emph{PloS One} 9 (3): e89550.
-
-\leavevmode\hypertarget{ref-Torrey2010TraLea}{}%
-Torrey, Lisa, and Jude Shavlik. 2010. {``Transfer Learning.''} In
-\emph{Handbook of Research on Machine Learning Applications and Trends:
-Algorithms, Methods, and Techniques}, 242--64. IGI global.
-
-\leavevmode\hypertarget{ref-Trojelsgaard2016EcoNet}{}%
-Trøjelsgaard, Kristian, and Jens M. Olesen. 2016. {``Ecological Networks
-in Motion: Micro- and Macroscopic Variability Across Scales.''}
-\emph{Functional Ecology} 30 (12): 1926--35.
-\url{https://doi.org/10.1111/1365-2435.12710}.
-
-\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
-Turak, Eren, James Brazill-Boast, Tim Cooney, Michael Drielsma, Jocelyn
-DelaCruz, Gillian Dunkerley, Miguel Fernandez, et al. 2017. {``Using the
-Essential Biodiversity Variables Framework to Measure Biodiversity
-Change at National Scale.''} \emph{Biological Conservation}, SI:Measures
-of biodiversity, 213: 264--71.
-\url{https://doi.org/10.1016/j.biocon.2016.08.019}.
-
-\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
-Upham, Nathan S., Jacob A. Esselstyn, and Walter Jetz. 2019.
-{``Inferring the Mammal Tree: Species-Level Sets of Phylogenies for
-Questions in Ecology, Evolution, and Conservation.''} \emph{PLOS
-Biology} 17 (12): e3000494.
-\url{https://doi.org/10.1371/journal.pbio.3000494}.
+Distribution. \emph{Journal of Statistical Physics}, 173, 806--844.
+
+\leavevmode\hypertarget{ref-Xing2021RisEco}{}%
+Xing, S. \& Fayle, T.M. (2021). The rise of ecological network
+meta-analyses: Problems and prospects. \emph{Global Ecology and
+Conservation}, 30, e01805.
 
 \leavevmode\hypertarget{ref-Yeakel2014ColEco}{}%
-Yeakel, Justin D., Mathias M. Pires, Lars Rudolf, Nathaniel J. Dominy,
-Paul L. Koch, Paulo R. Guimarães, and Thilo Gross. 2014. {``Collapse of
-an Ecological Network in Ancient Egypt.''} \emph{PNAS} 111 (40):
-14472--77. \url{https://doi.org/10.1073/pnas.1408471111}.
+Yeakel, J.D., Pires, M.M., Rudolf, L., Dominy, N.J., Koch, P.L.,
+Guimarães, P.R., \emph{et al.} (2014). Collapse of an ecological network
+in Ancient Egypt. \emph{PNAS}, 111, 14472--14477.
 
 \leavevmode\hypertarget{ref-Youden1950IndRat}{}%
-Youden, W. J. 1950. {``Index for Rating Diagnostic Tests.''}
-\emph{Cancer} 3 (1): 32--35.
-\url{https://doi.org/10.1002/1097-0142(1950)3:1\%3C32::AID-CNCR2820030106\%3E3.0.CO;2-3}.
+Youden, W.J. (1950). Index for rating diagnostic tests. \emph{Cancer},
+3, 32--35.
 
 \leavevmode\hypertarget{ref-Young2021BayInf}{}%
-Young, Jean-Gabriel, George T Cantwell, and M E J Newman. 2021.
-{``Bayesian Inference of Network Structure from Unreliable Data.''}
-\emph{Journal of Complex Networks} 8 (6).
-\url{https://doi.org/10.1093/comnet/cnaa046}.
+Young, J.-G., Cantwell, G.T. \& Newman, M.E.J. (2021). Bayesian
+inference of network structure from unreliable data. \emph{Journal of
+Complex Networks}, 8.
 
 \leavevmode\hypertarget{ref-Young2007RanDot}{}%
-Young, Stephen J., and Edward R. Scheinerman. 2007. {``Random Dot
-Product Graph Models for Social Networks.''} In \emph{Algorithms and
-Models for the Web-Graph}, edited by Anthony Bonato and Fan R. K. Chung,
-138--49. Lecture Notes in Computer Science. Berlin, Heidelberg:
-Springer. \url{https://doi.org/10.1007/978-3-540-77004-6_11}.
+Young, S.J. \& Scheinerman, E.R. (2007). Random Dot Product Graph Models
+for Social Networks. In: \emph{Algorithms and Models for the Web-Graph},
+Lecture Notes in Computer Science (eds. Bonato, A. \& Chung, F.R.K.).
+Springer, Berlin, Heidelberg, pp. 138--149.
 
 \leavevmode\hypertarget{ref-Zhu2006AutDim}{}%
-Zhu, Mu, and Ali Ghodsi. 2006. {``Automatic Dimensionality Selection
-from the Scree Plot via the Use of Profile Likelihood.''}
-\emph{Computational Statistics \& Data Analysis} 51 (2): 918--30.
-\url{https://doi.org/10.1016/j.csda.2005.09.010}.
+Zhu, M. \& Ghodsi, A. (2006). Automatic dimensionality selection from
+the scree plot via the use of profile likelihood. \emph{Computational
+Statistics \& Data Analysis}, 51, 918--930.
 

### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@7e1fb30781c47bd0a86a8dcf9e9ef05c54084b9a 🚀

@@
 \documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
             letterpaper,
-            top=1.2in,
+            top=1.0in,
             bottom=2.510cm,
-            inner=0.5in,
-            outer=0.4in,
-            marginparwidth=1.95in,
-            marginparsep=0.4in}
+            left=0.35in,
+            right=0.35in,
+            marginparwidth=2.0in,
+            marginparsep=0.35in}
 
@@
 }
+
 \usepackage{floatrow}
+
 \floatsetup[figure]{margins=hangright,
@@
               floatwidth=\textwidth}
-\floatsetup[table]{margins=hangoutside,
-             facing=yes,
-             capposition=beside,
-             capbesideposition={center,outside},
-             floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 %
-\,\textsuperscript{5}, %
+\,\textsuperscript{5,2}, %
 \href{https://orcid.org/0000-0001-5785-8321}{Rogini\,Runghen}%
@@
 
-\textbf{Abstract}:\,Despite their importance in many ecological
-processes, collecting data and information on ecological interactions,
-and therefore species interaction networks, is an exceedingly
-challenging task. For this reason, large parts of the world have a
-deficit of data of which species interact, and what we can expect the
-network structure of these interactions to be. As data collection alone
-is unlikely to be sufficient at filling these global gaps, community
-ecologists must adopt predictive methods. In this contribution we
-develop such a method, relying on graph embedding (the extraction of
-explanatory latent variables from known graph structures) and transfer
-learning (the application of previous solution to novel problems with
-limited predictors overlap) in order to assemble a predicted list of
-trophic interactions between mammals of Canada. This interaction list is
-derived from extensive knowledge of the mammalian food web of Europe,
-despite the fact that there are fewer than 5\% of common species between
-the two locations. We provide guidance on how this method can be adapted
-by substituting some approaches or predictors in order to make it more
-generally applicable to a broad family of ecological problems.
+Despite their importance in many ecological processes, collecting data
+and information on ecological interactions, and therefore species
+interaction networks, is an exceedingly challenging task. For this
+reason, large parts of the world have a data deficit when it comes to
+species interactions, and how the resulting networks are structured. As
+data collection alone is unlikely to be sufficient at filling these
+global gaps, community ecologists must adopt predictive methods. In this
+contribution, we develop such a method, relying on graph embedding (the
+extraction of explanatory latent variables from known graph structures)
+and transfer learning (the application of previous solutions to novel
+problems with limited predictors overlap) in order to assemble a
+predicted list of trophic interactions between mammals of Canada. This
+interaction list is derived from extensive knowledge of the mammalian
+food web of Europe, despite the fact that there are fewer than 5\% of
+common species between the two locations. The results of the predictive
+model are compared against databases of recorded pairwise interactions,
+showing that we correctly recover over 95\% of known interactions. We
+provide guidance on how this method can be adapted by substituting some
+approaches or predictors in order to make it more generally applicable.
 

### 2021-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@e71b02cf58bd95e46d2f4268b1ae53f7f072f07c 🚀

@@
 variables used for the RDPG, called the left and right subspaces, are
-defined as \(\mathcal{L} = \mathbf{L}\sqrt{\mathbf{\Sigma}}\), and
-\(\mathcal{R} = \sqrt{\mathbf{\Sigma}}\mathbf{R}\) -- using the full
-rank of \(\mathbf{A}\), \(\mathcal{L}\mathcal{R}' = \mathbf{A}\), and
+defined as \(\mathscr{L} = \mathbf{L}\sqrt{\mathbf{\Sigma}}\), and
+\(\mathscr{R} = \sqrt{\mathbf{\Sigma}}\mathbf{R}\) -- using the full
+rank of \(\mathbf{A}\), \(\mathscr{L}\mathscr{R}' = \mathbf{A}\), and
 using any smaller rank results in
-\(\mathcal{L}\mathcal{R}' \approx \mathbf{A}\). Using a rank of 1 for
+\(\mathscr{L}\mathscr{R}' \approx \mathbf{A}\). Using a rank of 1 for
 the t-SVD provides a first-order approximation of the network.
@@
 cases, the inferred left and right sub-spaces for the Canadian species
-pool (\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\)) have entries that
+pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have entries that
 are distributions, representing the range of values for a given species
@@
 
-The phylogenetic reconstruction of \(\hat{\mathcal{L}}\) and
-\(\hat{\mathcal{R}}\) has an associated uncertainty, represented by the
+The phylogenetic reconstruction of \(\hat{\mathscr{L}}\) and
+\(\hat{\mathscr{R}}\) has an associated uncertainty, represented by the
 breadth of the uniform distribution associated to each of their entries.
@@
 Specifically, we have adopted the following approach. For every entry in
-\(\hat{\mathcal{L}}\) and \(\hat{\mathcal{R}}\), we draw a value from
+\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\), we draw a value from
 its distribution. This results in one instance of the possible left
-(\(\hat{\mathcal{l}}\)) and right (\(\hat{\mathcal{r}}\)) subspaces for
+(\(\hat{\mathscr{l}}\)) and right (\(\hat{\mathscr{r}}\)) subspaces for
 the Canadian metaweb. These can be multiplied, to produce one matrix of
-real values. Because the entries in \(\hat{\mathcal{l}}\) and
-\(\hat{\mathcal{r}}\) are in the same space where \(\mathcal{L}\) and
-\(\mathcal{R}\) were originally predicted, it follows that the threshold
+real values. Because the entries in \(\hat{\mathscr{l}}\) and
+\(\hat{\mathscr{r}}\) are in the same space where \(\mathscr{L}\) and
+\(\mathscr{R}\) were originally predicted, it follows that the threshold
 \(\rho\) estimated for the European metaweb also applies. We use this
 information to produce one random Canadian metaweb,
-\(N = \hat{\mathcal{L}}\)\(\hat{\mathcal{R}}' \ge \rho\). As we can see
+\(N = \hat{\mathscr{L}}\)\(\hat{\mathscr{R}}' \ge \rho\). As we can see
 in (fig.~\ref{fig:subspaces}) the European and Canadian metawebs are

### 2021-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@de45ae8d78139046c161efbf0490595013cc49eb 🚀

@@
 further downstream (which is an important consideration when combining
-datasets Grenié \emph{et al.} (2021)). All nodes had valid matches to
+datasets (Grenié \emph{et al.} 2021)). All nodes had valid matches to
 GBIF at this step, and so this backbone is used for all name

### 2021-09-15 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@d132640e15855776d2d8d7e9febd6db8ab493aa0 🚀

@@
 significant breakthroughs in our ability to start thinking about species
-interactions networks over large spatial scales.
+interaction networks over large spatial scales.
 

### 2021-09-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@97749228c7ffc006fb4863d4e501d0fcd761ae2c 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@fc74eeb831ab79a23c1728874edc8c81ff99994b 🚀

@@
 Despite their importance in many ecological processes, collecting data
-and information on ecological interactions, and therefore species
-interaction networks, is an exceedingly challenging task. For this
-reason, large parts of the world have a data deficit when it comes to
-species interactions, and how the resulting networks are structured. As
-data collection alone is unlikely to be sufficient at filling these
-global gaps, community ecologists must adopt predictive methods. In this
-contribution, we develop such a method, relying on graph embedding (the
-extraction of explanatory latent variables from known graph structures)
-and transfer learning (the application of previous solutions to novel
-problems with limited predictors overlap) in order to assemble a
-predicted list of trophic interactions between mammals of Canada. This
-interaction list is derived from extensive knowledge of the mammalian
-food web of Europe, despite the fact that there are fewer than 5\% of
-common species between the two locations. The results of the predictive
+and information on ecological interactions is an exceedingly challenging
+task. For this reason, large parts of the world have a data deficit when
+it comes to species interactions, and how the resulting networks are
+structured. As data collection alone is unlikely to be sufficient,
+community ecologists must adopt predictive methods. Here we develop such
+a method, relying on graph embedding and transfer learning to assemble a
+predicted list of trophic interactions between Canadian mammals. This
+interaction list is derived from the European food web, despite sharing
+only 5\% of common species with Canada. The results of the predictive
 model are compared against databases of recorded pairwise interactions,
@@
 resulting in a success rate of 92\%. These two interactions were added
-to our predicted metaweb with a probability of 1.
+to our predicted metaweb with a probability of 1. A table listing all
+interactions in the predicted Canadian metaweb can be found in the
+supplementary material.
 

### 2021-10-21 reviews/01_ELE/01_draft_revised.tex
🚮 add the diff file

--- 2021-09-20 draft.tex
@@
 are unable to infer potential species interactions. Having a general
-solution for inferring a \emph{plausible} metaweb (despite the
+solution for inferring \emph{plausible} interactions (despite the
 unavailability of interaction data) could be the catalyst for
 significant breakthroughs in our ability to start thinking about species
-interaction networks over large spatial scales.
-
-Here, we present a general method for the transfer learning of network
-representations, relying on the similarities of species in a
+interaction networks over large spatial scales. In a recent overview of
+the field of ecological network prediction, Strydom \emph{et al.}
+(2021a) identified two challenges of interest to the prediction of
+interactions at large scales. First, there is a relative scarcity of
+relevant data in most places globally -- paradoxically, this restricts
+our ability to infer interactions to locations where inference is
+perhaps the least required; second, accurate predictions often demand
+accurate predictors, and the lack of methods that can leverage small
+amount of data is a serious impediment to our predictive ability
+globally.
+
+Here, we present a general method to recommend possible trophic
+interactions, relying on the transfer learning of network
+representations, specifically by using similarities of species in a
 biologically/ecologically relevant proxy space (\emph{e.g.} shared
@@
 another species pool for which interactions are known by using
-phylogenetic structure as a medium for transfer. This allows us to
-construct a \emph{probabilistic} metaweb for a community for which we
-have \emph{no} prior trophic interaction data for the desired species
-pool. Our methodology is outlined in fig.~\ref{fig:concept}, where we
-provide an illustration based on learning the embedding of a metaweb of
-trophic interactions for European mammals (known interactions; Maiorano
-\emph{et al.} 2020b, a) and, based on phylogenetic relationships between
-mammals globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.}
-2019), infer a metaweb for the Canadian mammalian species pool
-(interactions are treated as unknown in this instance).
+phylogenetic structure as a medium for transfer. There is a plurality of
+measures of species similarities that can be used for metaweb
+reconstruction (see \emph{e.g.} Morales-Castilla \emph{et al.} 2015);
+however, phylogenetic proximity has several desirable properties when
+working at large scales. Gerhold \emph{et al.} (2015) made the point
+that phylogenetic signal captures diversification of characters (large
+macro-evolutionary process), but not necessarily community assembly
+(fine ecological process); Dormann \emph{et al.} (2010) previously found
+very similar conclusions. Interactions tend reflect a phylogenetic
+signal because they have a conserved pattern of evolutionary convergence
+that encompasses a wide range of ecological and evolutionary mechanisms
+(Cavender-Bares \emph{et al.} 2009; Mouquet \emph{et al.} 2012), and -
+most importantly - retain this signal even when it is not detectable at
+the community scale (Hutchinson \emph{et al.} 2017; Poisot \& Stouffer
+2018). Finally, species interactions at macro-ecological scales seem to
+respond mostly to macro-evolutionary processes (Price 2003); which is
+evidenced by the presence of conserved backbones in food webs (Dalla
+Riva \& Stouffer 2016), strong evolutionary signature on prey choice
+(Stouffer \emph{et al.} 2012), and strong phylogenetic signature in food
+web intervality (Eklöf \& Stouffer 2016). Phylogenetic reconstruction
+has also previously been used within the context of ecological networks,
+namely understanding ancestral plant-insect interactions (Braga \emph{et
+al.} 2021). Taken together, these considerations suggest that
+phylogenies can reliably be used to transfer knowledge on species
+interactions.
 
@@
 
-There is a plurality of measures of species similarities that can be
-used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla
-\emph{et al.} 2015); however, phylogenetic proximity has several
-desirable properties when working at large scales. Gerhold \emph{et al.}
-(2015) made the point that phylogenetic signal captures diversification
-of characters (large macro-evolutionary process), but not necessarily
-community assembly (fine ecological process); Dormann \emph{et al.}
-(2010) previously found very similar conclusions. Interactions tend
-reflect a phylogenetic signal because they have a conserved pattern of
-evolutionary convergence that encompasses a wide range of ecological and
-evolutionary mechanisms (Cavender-Bares \emph{et al.} 2009; Mouquet
-\emph{et al.} 2012), and - most importantly - retain this signal even
-when it is not detectable at the community scale (Hutchinson \emph{et
-al.} 2017; Poisot \& Stouffer 2018). Finally, species interactions at
-macro-ecological scales seem to respond mostly to macro-evolutionary
-processes (Price 2003); which is evidenced by the presence of conserved
-backbones in food webs (Dalla Riva \& Stouffer 2016), strong
-evolutionary signature on prey choice (Stouffer \emph{et al.} 2012), and
-strong phylogenetic signature in food web intervality (Eklöf \& Stouffer
-2016). Phylogenetic reconstruction has also previously been used within
-the context of ecological networks, namely understanding ancestral
-plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
-these considerations suggest that phylogenies can reliably be used to
-transfer knowledge on species interactions.
-
-Our case study shows that phylogenetic transfer learning is indeed an
-effective approach to predict the Canadian mammalian metaweb. This
-showcases that although the components (species) that make up the
-Canadian and European communities may be \emph{minimally} shared, if the
-medium (proxy space) selected in the transfer step is biologically
-plausible, we can still effectively learn from the known network and
-make biologically relevant predictions of interactions. It should be
-reiterated that the framework presented in fig.~\ref{fig:concept} is
-amenable to changes; notably, the measure of similarity may not be
-phylogeny, and can be replaced by information on foraging (Beckerman
-\emph{et al.} 2006), cell-level mechanisms (Boeckaerts \emph{et al.}
-2021), or a combination of traits and phylogenetic structure (Stock
-2021).
+Our methodology is outlined in fig.~\ref{fig:concept}, where we provide
+an illustration based on learning the embedding of a metaweb of trophic
+interactions for European mammals (Maiorano \emph{et al.} 2020; known
+interactions; \textbf{Maiorano2020TetEu?}) and, based on phylogenetic
+relationships between mammals globally (\emph{i.e.}, phylogenetic tree
+Upham \emph{et al.} 2019), infer a metaweb for the Canadian mammalian
+species pool (interactions are treated as unknown in this instance).
+Following the definition of Dunne (2006), a metaweb is a network
+analogue to the concept of a regional species pool. Specifically, a
+metaweb is an inventory of all \emph{possible} interactions within
+species likely to occurr within a spatially delimited area (the network
+\(\gamma\)-diversity, in a sense). The metaweb is, therefore, \emph{not}
+a prediction of the food web at any specific locale within the frontiers
+of the spatial area it recovers, and will in fact have a different
+structure (notably by having a larger connectance; see \emph{e.g.}
+\textbf{Wood2015EffSpa?}). These local food webs are expected to be a
+subset of both the species and the interactions of their metaweb, and
+have been called ``metaweb realizations'' (Poisot \emph{et al.} 2015).
+The difference between a food web at a specific location and the metaweb
+has to do with a variety of mechanisms, including species co-occurrence,
+local environmental conditions, and local distribution of functional
+traits. Nevertheless, the metaweb represents the total of functional,
+phylogenetic, and macroecological processes (Morales-Castilla \emph{et
+al.} 2015), and therefore still holds valuable ecological information.
+Because the metaweb can be down-sampled given appropriate knowledge of
+local species composition (the network \(\alpha\)-diversity, in a
+sense), it is possible to infer what may drive the structure of food
+webs at finer spatial scales. This has been done for example for
+tree-gallers-parasitoid systems (\textbf{Gravel2018BriElt?}), fish
+trophic interactions (Albouy \emph{et al.} 2019), tetrapods trophic
+interactions (O'Connor \emph{et al.} 2020), and crop-pests networks
+(Grünig \emph{et al.} 2020). Whereas the original metaweb definition was
+based on presence/absence, we focus on \emph{probabilistic} metawebs;
+not only does our method recommed interactions that may exist, it gives
+each interaction a score that is mathematically equivalent to the chance
+of success of a Bernoulli trial (see \emph{e.g.} Poisot \emph{et al.}
+2016), which allows properly weigh interactions as a function of how
+likely they are.
+
+Our case study shows that phylogenetic transfer learning is an effective
+approach to the generation of probabilistic metawebs. This showcases
+that although the components (species) that make up the Canadian and
+European communities may be \emph{minimally} shared (the overall species
+overlap is less than 4\%), if the medium (proxy space) selected in the
+transfer step is biologically plausible, we can still effectively learn
+from the known network and make biologically relevant predictions of
+interactions. Indeed, as we detail in the result, when validated against
+known but fracational data of trophic interactions between Canadian
+mammals, our model achieves a predictive accuracy of approx. 91\%. It
+should be reiterated that the framework presented in
+fig.~\ref{fig:concept} is amenable to changes; notably, the measure of
+similarity may not be phylogeny, and can be replaced by information on
+foraging (Beckerman \emph{et al.} 2006), cell-level mechanisms
+(Boeckaerts \emph{et al.} 2021), or a combination of traits and
+phylogenetic structure (Stock 2021).
 
@@
 
-We use data from the European metaweb assembled by Maiorano \emph{et
-al.} (2020b), following the definition of the metaweb first introduced
-by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
-within species from a spatially delimited pool. Notably the metaweb is
-not a prediction of the food web at any specific locale within the
-frontiers of the species pool -- in fact, these local food webs are
-expected to have a subset of both the species and the interactions of
-their metaweb (Poisot \emph{et al.} 2012). This being said, as the
-metaweb represents the total of functional, phylogenetic, and
-macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
-thus still worthy of ecological attention. We deduced the subgraph
-corresponding to all mammals by matching species names in the original
-network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
-retaining all those who matched to mammals. This serves a dual purpose
-1) to extract only mammals from the European network and 2) to match and
-standardize species names when aggregating the different data sources
-further downstream (which is an important consideration when combining
-datasets (Grenié \emph{et al.} 2021)). All nodes had valid matches to
-GBIF at this step, and so this backbone is used for all name
-reconciliation steps as outlined below.
+We use data from the European metaweb assembled by
+(\textbf{Maiorano2020TetEu?}).
+
+\textbf{TANYA TODO} description of the data
+
+We induced the subgraph corresponding to all mammals by matching species
+names in the original network to the GBIF taxonomic backbone (GBIF
+Secretariat 2021) and retaining all those who matched to mammals. This
+serves a dual purpose 1) to extract only mammals from the European
+network and 2) to match and standardize species names when aggregating
+the different data sources further downstream (which is an important
+consideration when combining datasets (Grenié \emph{et al.} 2021)). All
+nodes had valid matches to GBIF at this step, and so this backbone is
+used for all name reconciliation steps as outlined below.
 
@@
 semi-aquatic species (this corresponds to the same selection that was
-applied by Maiorano \emph{et al.} (2020b) in the European metaweb). The
+applied by (\textbf{Maiorano2020TetEu?}) in the European metaweb). The
 IUCN names were, as previously, reconciled against GBIF to have an exact
@@
 
+The method we develop is, ecologically speaking, a ``black box,''
+\emph{i.e.} an algorithm that can be understood mathematically, but
+whose component parts are not always directly tied to ecological
+processes. There is a growing realization in machine learning that
+(unintentional) black box algorithms are not necessarily a bad thing
+Holm (2019), as long as their constituent parts can be examined (which
+is the case with our method). But more importantly, data hold more
+information that we may thought; as such, even algorithms that are
+disconnected from the model can make correct guesses most of the time
+(Halevy \emph{et al.} 2009); in fact, in an instance of ecological
+forecasting of spatio-temporal systems, model-free approaches
+(\emph{i.e.} drawing all of their information from the data)
+outperformed model-informed ones (Perretti \emph{et al.} 2013).
+
 \hypertarget{implementation-and-code-availability}{%
@@
 \href{https://osf.io/2zwqm/}{\texttt{https://osf.io/2zwqm/}}. The
-taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau \&
-Poisot 2021). The network embedding and analysis is done using
-\texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019; Banville
-\emph{et al.} 2021). The phylogenetic simulations are done using
-\texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
+taxonomic cleanup steps are done using \texttt{GBIF.jl}
+(\textbf{Dansereau2021SimJl?}). The network embedding and analysis is
+done using \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019;
+Banville \emph{et al.} 2021). The phylogenetic simulations are done
+using \texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
 \texttt{Phylo.jl} (Reeve \emph{et al.} 2016). A complete
@@
 latent variables produced this way can be used to predict \emph{de novo}
-network edges (\emph{i.e.} interactions; Runghen \emph{et al.} 2021).
+network edges. Interstingly, the latent variables do not need to be
+prouced by decomposing the network itself; in a recent contribution,
+Runghen \emph{et al.} (2021) show that deep artificial neural networks
+are able to reconstruct the left and right subspaces of a RDPG, in order
+to predict human movement networks from individual/location metadata.
+This is an exciting opportunity, as it opens up the possibility of using
+additional predictors.
 
@@
 European metaweb are all true. Given the methodological details given in
-Maiorano \emph{et al.} (2020b) and O'Connor \emph{et al.} (2020), this
+(\textbf{Maiorano2020TetEu?}) and O'Connor \emph{et al.} (2020), this
 seems like a reasonable assumption, although one that does not hold for
@@
 species trait is represented as a uniform distribution between these
-bounds; in a situation where the algorithm would return point values for
-all simulations, one could in theory either estimate the parameters of a
-distribution for each tip, or draw randomly from the outputs. In all
-cases, the inferred left and right sub-spaces for the Canadian species
-pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have entries that
-are distributions, representing the range of values for a given species
-at a given dimension.
+bounds. The choice of the uniform distribution was made because the
+algorithm returns a minimum and maximum point estimate for the value,
+and given this information, the uniform distribution is the one with
+maximum entropy. Had all mean parameters estimates been positive, the
+exponential distribution would have been an alternative, but this is not
+the case for the subspaces of an RDPG. In order to examine the
+consequences of the choice of distribution, we estimated the variance
+per latent variable per node to use a normal distribution; as we show in
+Supp. Mat. 2, this decision results in dramatically over-estimating the
+number and probability of interactions, and therefore we keep the
+discussions in the main text to the uniform case. The inferred left and
+right sub-spaces for the Canadian species pool (\(\hat{\mathscr{L}}\)
+and \(\hat{\mathscr{R}}\)) have entries that are distributions,
+representing the range of values for a given species at a given
+dimension.
 
@@
 interactions would not be realized due to human impact.
+
+Dallas \emph{et al.} (2017) suggest that most links in ecological
+networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
+observe. This argument essentially echoes Jordano (2016b): the sampling
+of ecological interactions is difficult because it requires first the
+joint observation of two species, and then the observation of their
+interaction. In addition, it is generally expected that weak or rare
+links would be more common in networks (Csermely 2004), compared to
+strong, persistent links; this is notably the case in food chains,
+wherein many weaker links are key to the stability of a system (Neutel
+\emph{et al.} 2002). In the light of these observations, the results in
+fig.~\ref{fig:inflation} are not particularly surprising: we expect to
+see a surge in these low-probability interactions under a model that has
+a good predictive accuracy. Because the predictions we generate are by
+design probabilistic, then one can weigh these rare links appropriately.
+In a sense, that most ecological interactions are elusive can call for a
+slightly different approach to sampling: once the common interactions
+are documented, the effort required in documenting each rare interaction
+may increase exponentially. Recent proposals suggest that machine
+learning algorithms, in these situations, can act as data generators
+(Hoffmann \emph{et al.} 2019): in this perspective, high quality
+observational data can be supplemented with synthetic data coming from
+predictive models, which increases the volume of information available
+for inference.
 
@@
 these national divisions, in large parts of the world, reflect nothing
-except for the legacy of settler colonialism, and operating under them
-must be done under the clear realization that they contributed to the
+except for the legacy of settler colonialism; indeed, the use of
+ecological data is not an apolitical act (Nost \& Goldstein 2021).
+Operating under the framework of national boundaries, and relying on
+data infrastructures designed to answer questions within them, must be
+done under the clear realization that this logic contributed to the
 ongoing biodiversity crisis (Adam 2014), can reinforce environmental
@@
 \leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
-Arsov, N. \& Mirceva, G. (2019). Network Embedding: An Overview.
-\emph{arXiv:1911.11726 {[}cs, stat{]}}.
+Arsov, N. \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
+Available at: \url{http://arxiv.org/abs/1911.11726}. Last accessed.
 
@@
 Brose, U., Jonsson, T., Berlow, E.L., Warren, P., Banasek-Richter, C.,
-Bersier, L.-F., \emph{et al.} (2006). ConsumerResource Body-Size
+Bersier, L.-F., \emph{et al.} (2006). Consumer--Resource Body-Size
 Relationships in Natural Food Webs. \emph{Ecology}, 87, 2411--2417.
@@
 \leavevmode\hypertarget{ref-Cai2017ComSur}{}%
-Cai, H., Zheng, V.W. \& Chang, K.C.-C. (2017). A Comprehensive Survey of
-Graph Embedding: Problems, Techniques and Applications. \emph{arXiv
-preprint arXiv:1709.07604}.
+Cai, H., Zheng, V.W. \& Chang, K.C.-C. (2017). \emph{A Comprehensive
+Survey of Graph Embedding: Problems, Techniques and Applications}.
+Available at: \url{http://arxiv.org/abs/1709.07604}. Last accessed.
 
@@
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, A.R., Eklf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
+Cirtwill, A.R., Eklӧf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
 A quantitative framework for investigating the reliability of empirical
@@
 
+\leavevmode\hypertarget{ref-Csermely2004StrLin}{}%
+Csermely, P. (2004). Strong links are important, but weak links
+stabilize them. \emph{Trends in Biochemical Sciences}, 29, 331--334.
+
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
@@
 
-\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
-Dansereau, G. \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
-Framework for Species Distribution Modeling in Julia. \emph{Journal of
-Open Source Software}, 6, 2872.
+\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
+Dallas, T., Park, A.W. \& Drake, J.M. (2017). Predicting cryptic links
+in host-parasite networks. \emph{PLOS Computational Biology}, 13,
+e1005557.
 
@@
 
+\leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
+Grünig, M., Mazzi, D., Calanca, P., Karger, D.N. \& Pellissier, L.
+(2020). Crop and forest pest metawebs shift towards increased linkage
+and suitability overlap under climate change. \emph{Communications
+Biology}, 3, 1--10.
+
+\leavevmode\hypertarget{ref-Halevy2009UnrEff}{}%
+Halevy, A., Norvig, P. \& Pereira, F. (2009). The Unreasonable
+Effectiveness of Data. \emph{IEEE Intelligent Systems}, 24, 8--12.
+
 \leavevmode\hypertarget{ref-Halko2011FinStr}{}%
@@
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, F. (1965). \emph{Dune}. First. Chilton Book Company,
+Herbert, F. (1965). \emph{Dune}. 1st edn. Chilton Book Company,
 Philadelphia.
+
+\leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
+Hoffmann, J., Bar-Sinai, Y., Lee, L.M., Andrejevic, J., Mishra, S.,
+Rubinstein, S.M., \emph{et al.} (2019). Machine learning in a
+data-limited regime: Augmenting experiments with synthetic data uncovers
+order in crumpled sheets. \emph{Science Advances}, 5, eaau6792.
+
+\leavevmode\hypertarget{ref-Holm2019DefBla}{}%
+Holm, E.A. (2019). In defense of the black box. \emph{Science}, 364,
+26--27.
 
@@
 Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020a). Data from: Tetra-EU 1.0: A species-level trophic
+Thuiller, W. (2020). Data from: Tetra-EU 1.0: A species-level trophic
 meta-web of European tetrapods.
-
-\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
-Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020b). TETRA-EU 1.0: A species-level trophic metaweb of
-European tetrapods. \emph{Global Ecology and Biogeography}, 29,
-1452--1457.
 
@@
 Webs. \emph{PLOS ONE}, 9, e106651.
+
+\leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
+Neutel, A.-M., Heesterbeek, J.A.P. \& de Ruiter, P.C. (2002). Stability
+in Real Food Webs: Weak Links in Long Loops. \emph{Science}, 296,
+1120--1123.
 
@@
 
+\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
+Nost, E. \& Goldstein, J.E. (2021). A political ecology of data.
+\emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
 O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
+L., Martinez‐Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
 of tetrapods across Europe through the prism of the Eltonian niche.
@@
 
+\leavevmode\hypertarget{ref-Perretti2013ModFor}{}%
+Perretti, C.T., Munch, S.B. \& Sugihara, G. (2013). Model-free
+forecasting outperforms the correct mechanistic model for simulated and
+experimental data. \emph{Proceedings of the National Academy of
+Sciences}, 110, 5253--5257.
+
 \leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
@@
 
-\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
-Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
-The dissimilarity of species interaction networks. \emph{Ecology
-Letters}, 15, 1353--1361.
-
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
@@
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
-Albery, G.F., \emph{et al.} (2021b). Imputing the mammalian virome with
-linear filtering and singular value decomposition.
-\emph{arXiv:2105.14973 {[}q-bio{]}}.
+Albery, G.F., \emph{et al.} (2021b). \emph{Imputing the mammalian virome
+with linear filtering and singular value decomposition}. Available at:
+\url{http://arxiv.org/abs/2105.14973}. Last accessed.
 
@@
 
+\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, 124, 243--251.
+
 \leavevmode\hypertarget{ref-Price2003MacThe}{}%
@@
 Reeve, R., Leinster, T., Cobbold, C.A., Thompson, J., Brummitt, N.,
-Mitchell, S.N., \emph{et al.} (2016). How to partition diversity.
-\emph{arXiv:1404.6520 {[}q-bio{]}}.
+Mitchell, S.N., \emph{et al.} (2016). \emph{How to partition diversity}.
+Available at: \url{http://arxiv.org/abs/1404.6520}. Last accessed.
 
@@
 Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021a). \emph{A Roadmap Toward
-Predicting Species Interaction Networks (Across Space and Time)}
-(Preprint). EcoEvoRxiv.
+Desjardins-Proulx, P., \emph{et al.} (2021a). A roadmap towards
+predicting species interaction networks (across space and time).
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, 376, 20210063.
 
@@
 variables framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, SI:Measures of biodiversity, 213,
+\emph{Biological Conservation}, SI:measures of biodiversity, 213,
 264--271.

### 2021-10-22 reviews/01_ELE/01_draft_revised.tex
diff files

@@
 evidenced by the presence of conserved backbones in food webs (Dalla
-Riva \& Stouffer 2016), strong evolutionary signature on prey choice
-(Stouffer \emph{et al.} 2012), and strong phylogenetic signature in food
-web intervality (Eklöf \& Stouffer 2016). Phylogenetic reconstruction
-has also previously been used within the context of ecological networks,
-namely understanding ancestral plant-insect interactions (Braga \emph{et
-al.} 2021). Taken together, these considerations suggest that
-phylogenies can reliably be used to transfer knowledge on species
-interactions.
+Riva \& Stouffer 2016; Mora \emph{et al.} 2018), strong evolutionary
+signature on prey choice (Stouffer \emph{et al.} 2012), and strong
+phylogenetic signature in food web intervality (Eklöf \& Stouffer 2016).
+Phylogenetic reconstruction has also previously been used within the
+context of ecological networks, namely understanding ancestral
+plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
+these considerations suggest that phylogenies can reliably be used to
+transfer knowledge on species interactions.
 
@@
 an illustration based on learning the embedding of a metaweb of trophic
-interactions for European mammals (Maiorano \emph{et al.} 2020; known
-interactions; \textbf{Maiorano2020TetEu?}) and, based on phylogenetic
-relationships between mammals globally (\emph{i.e.}, phylogenetic tree
-Upham \emph{et al.} 2019), infer a metaweb for the Canadian mammalian
-species pool (interactions are treated as unknown in this instance).
-Following the definition of Dunne (2006), a metaweb is a network
-analogue to the concept of a regional species pool. Specifically, a
-metaweb is an inventory of all \emph{possible} interactions within
-species likely to occurr within a spatially delimited area (the network
-\(\gamma\)-diversity, in a sense). The metaweb is, therefore, \emph{not}
-a prediction of the food web at any specific locale within the frontiers
-of the spatial area it recovers, and will in fact have a different
-structure (notably by having a larger connectance; see \emph{e.g.}
-\textbf{Wood2015EffSpa?}). These local food webs are expected to be a
-subset of both the species and the interactions of their metaweb, and
-have been called ``metaweb realizations'' (Poisot \emph{et al.} 2015).
-The difference between a food web at a specific location and the metaweb
-has to do with a variety of mechanisms, including species co-occurrence,
-local environmental conditions, and local distribution of functional
-traits. Nevertheless, the metaweb represents the total of functional,
-phylogenetic, and macroecological processes (Morales-Castilla \emph{et
-al.} 2015), and therefore still holds valuable ecological information.
-Because the metaweb can be down-sampled given appropriate knowledge of
-local species composition (the network \(\alpha\)-diversity, in a
-sense), it is possible to infer what may drive the structure of food
-webs at finer spatial scales. This has been done for example for
-tree-gallers-parasitoid systems (\textbf{Gravel2018BriElt?}), fish
+interactions for European mammals (known interactions; Maiorano \emph{et
+al.} 2020b, a) and, based on phylogenetic relationships between mammals
+globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.} 2019),
+infer a metaweb for the Canadian mammalian species pool (interactions
+are treated as unknown in this instance). Following the definition of
+Dunne (2006), a metaweb is a network analogue to the concept of a
+regional species pool. Specifically, a metaweb is an inventory of all
+\emph{possible} interactions within species likely to occurr within a
+spatially delimited area (the network \(\gamma\)-diversity, in a sense).
+The metaweb is, therefore, \emph{not} a prediction of the food web at
+any specific locale within the frontiers of the spatial area it
+recovers, and will in fact have a different structure (notably by having
+a larger connectance; see \emph{e.g.} Wood \emph{et al.} 2015). These
+local food webs are expected to be a subset of both the species and the
+interactions of their metaweb, and have been called ``metaweb
+realizations'' (Poisot \emph{et al.} 2015). The difference between a
+food web at a specific location and the metaweb has to do with a variety
+of mechanisms, including species co-occurrence, local environmental
+conditions, and local distribution of functional traits. Nevertheless,
+the metaweb represents the total of functional, phylogenetic, and
+macroecological processes (Morales-Castilla \emph{et al.} 2015), and
+therefore still holds valuable ecological information. Because the
+metaweb can be down-sampled given appropriate knowledge of local species
+composition (the network \(\alpha\)-diversity, in a sense), it is
+possible to infer what may drive the structure of food webs at finer
+spatial scales. This has been done for example for
+tree-gallers-parasitoid systems (Gravel \emph{et al.} 2018), fish
 trophic interactions (Albouy \emph{et al.} 2019), tetrapods trophic
@@
 (Boeckaerts \emph{et al.} 2021), or a combination of traits and
-phylogenetic structure (Stock 2021).
+phylogenetic structure (Stock 2021). Most importantly, although we focus
+on a trophic system, it is an established fact that different types of
+interactions do themselves interact (Kéfi \emph{et al.} 2012; see
+\emph{e.g.} Kawatsu \emph{et al.} 2021). Future development of metaweb
+inference techniques should cover the prediction of multiple interaction
+types.
 
@@
 
-We use data from the European metaweb assembled by
-(\textbf{Maiorano2020TetEu?}).
+We use data from the European metaweb assembled by Maiorano \emph{et
+al.} (2020b).
 
@@
 semi-aquatic species (this corresponds to the same selection that was
-applied by (\textbf{Maiorano2020TetEu?}) in the European metaweb). The
+applied by Maiorano \emph{et al.} (2020b) in the European metaweb). The
 IUCN names were, as previously, reconciled against GBIF to have an exact
@@
 
-The crux of the method is the transfer of knowledge of a known network,
-in order to predict interactions between species from another location.
-In fig.~\ref{fig:concept}, we give a high-level overview of the
+The core point of our method is the transfer of knowledge of a known
+ecological network, in order to predict interactions between species
+from another location at which the network is unknown (or partially
+known). In fig.~\ref{fig:concept}, we give a high-level overview of the
 approach; in the example around which this manuscript is built
@@
 \href{https://osf.io/2zwqm/}{\texttt{https://osf.io/2zwqm/}}. The
-taxonomic cleanup steps are done using \texttt{GBIF.jl}
-(\textbf{Dansereau2021SimJl?}). The network embedding and analysis is
-done using \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019;
-Banville \emph{et al.} 2021). The phylogenetic simulations are done
-using \texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
+taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau \&
+Poisot 2021). The network embedding and analysis is done using
+\texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019; Banville
+\emph{et al.} 2021). The phylogenetic simulations are done using
+\texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
 \texttt{Phylo.jl} (Reeve \emph{et al.} 2016). A complete
@@
 signal, and to capture the evolutionary backbone of food webs (Dalla
-Riva \& Stouffer 2016). In addition, recent advances show that the
-latent variables produced this way can be used to predict \emph{de novo}
-network edges. Interstingly, the latent variables do not need to be
-prouced by decomposing the network itself; in a recent contribution,
-Runghen \emph{et al.} (2021) show that deep artificial neural networks
-are able to reconstruct the left and right subspaces of a RDPG, in order
-to predict human movement networks from individual/location metadata.
-This is an exciting opportunity, as it opens up the possibility of using
-additional predictors.
+Riva \& Stouffer 2016); in other words, the latent variables of an RDPG
+can be mapped onto a phylogenetic tree, and phylogenetically close
+predators should share phylogenetically close preys. In addition, recent
+advances show that the latent variables produced this way can be used to
+predict \emph{de novo} network edges. Interstingly, the latent variables
+do not need to be prouced by decomposing the network itself; in a recent
+contribution, Runghen \emph{et al.} (2021) show that deep artificial
+neural networks are able to reconstruct the left and right subspaces of
+an RDPG, in order to predict human movement networks from
+individual/location metadata. This is an exciting opportunity, as it
+opens up the possibility of using additional predictors.
 
@@
 absence thereof) is decomposed into three components resulting in
-\(\mathbf{A} = \mathbf{L}\mathbf{\Sigma}\mathbf{R'}.\) Here,
+\(\mathbf{A} = \mathbf{U}\mathbf{\Sigma}\mathbf{V'}.\) Here,
 \(\mathbf{\Sigma}\) is a \(m \times n\) diagonal matrix and contains
-only singular (\(\sigma\)) values along its diagonal, \(\mathbf{L}\) is
-a \(m \times m\) unitary matrix, and \(\mathbf{R}'\) a \(n \times n\)
+only singular (\(\sigma\)) values along its diagonal, \(\mathbf{U}\) is
+a \(m \times m\) unitary matrix, and \(\mathbf{V}'\) a \(n \times n\)
 unitary matrix. Truncating the SVD removes additional noise in the
@@
 at which we truncate the matrix) containing only non-zero \(\sigma\)
-values. Additionally, \(\mathbf{L}\) is now a \(m \times r\) semi
-unitary matrix and \(\mathbf{R}'\) a \(n \times r\) semi-unitary matrix.
+values. Additionally, \(\mathbf{U}\) is now a \(m \times r\) semi
+unitary matrix and \(\mathbf{V}'\) a \(n \times r\) semi-unitary matrix.
+As an aside, most ecologists are indirectly familiar with SVD: Principal
+Component Analysis is a special case of SVD, which is more sensitive to
+numerical instabilities (see notably Shlens 2014).
 
@@
 
-A RDPG estimates the probability of observing interactions between nodes
-(species) as a function of the nodes' latent variables. The latent
-variables used for the RDPG, called the left and right subspaces, are
-defined as \(\mathscr{L} = \mathbf{L}\sqrt{\mathbf{\Sigma}}\), and
-\(\mathscr{R} = \sqrt{\mathbf{\Sigma}}\mathbf{R}\) -- using the full
-rank of \(\mathbf{A}\), \(\mathscr{L}\mathscr{R}' = \mathbf{A}\), and
+An RDPG estimates the probability of observing interactions between
+nodes (species) as a function of the nodes' latent variables, and is a
+way to turn a SVD (which decompose a matrix intro three) into two
+matrices that can be multiplied to provide an approximation of the
+network. The latent variables used for the RDPG, called the left and
+right subspaces, are defined as
+\(\mathscr{L} = \mathbf{U}\sqrt{\mathbf{\Sigma}}\), and
+\(\mathscr{R} = \sqrt{\mathbf{\Sigma}}\mathbf{V}'\) -- using the full
+rank of \(\mathbf{A}\), \(\mathscr{L}\mathscr{R} = \mathbf{A}\), and
 using any smaller rank results in
-\(\mathscr{L}\mathscr{R}' \approx \mathbf{A}\). Using a rank of 1 for
-the t-SVD provides a first-order approximation of the network.
+\(\mathscr{L}\mathscr{R} \approx \mathbf{A}\). Using a rank of 1 for the
+t-SVD provides a first-order approximation of the network. One advantage
+of using a RDPG rather than a SVD is that the number of components to
+estimate decreases; notably, one does not have to estimate the
+eigenvalues of the SVD. Furthermore, the two subspaces can be directly
+multiplied to yield a network.
 
@@
 European metaweb are all true. Given the methodological details given in
-(\textbf{Maiorano2020TetEu?}) and O'Connor \emph{et al.} (2020), this
+Maiorano \emph{et al.} (2020b) and O'Connor \emph{et al.} (2020), this
 seems like a reasonable assumption, although one that does not hold for
@@
 (1950)); the resulting cutoff was 0.22, and gave an accuracy above 0.99.
+In Supp. Mat. 1, we provide several lines of evidence that using the
+entire network to estimate the threshold does not lead to overfitting;
+that using a subset of species would yield the same threshold; that
+decreasing the quality of the original data by adding of removing
+interactions would minimally affect the predicive accuracy of RDPG
+applied to the European metaweb; and that the networks reconstructed
+from artifically modified data are reconstructured with the correct
+ecological properties.
 
@@
 
+It must be noted that despite bringing in a large amount of information
+from the European species pool and interactions, the Canadian metaweb
+has distinct structural properties. Following an approach similar to
+Vermaat \emph{et al.} (2009), we show in Supp. Mat. 3 that not only can
+we observed differences in a multivariate space between the European and
+Canadian metaweb, we can also observe differences in the same space
+between random subgraphs from these networks. These results line up with
+the studies spatializing metawebs that have been discussed in the
+introduction: changes in the species pool are driving local structural
+changes in the networks.
+
 \hypertarget{data-cleanup-discovery-validation-and-thresholding}{%
@@
 Nevertheless, should the predictive model work, we would expect that a
-majority of interactions known to GLOBI would also be predicted. After
-performing this check, we set the probability of all interactions known
-to GLOBI (366 in total, 33 of which were not predicted by the model, for
-a success rate of 91\%) to 1.
+majority of interactions known to GLOBI would also be predicted. We
+retrieved 366 interactions between mammals from the Canadian species
+pool from GLOBI, 33 of which were not predicted by the model; this
+results in a success rate of 91\%. After performing this check, we set
+the probability of all interactions known to GLOBI to 1.
 
@@
 predictive models, which increases the volume of information available
-for inference.
-
-Cirtwill \emph{et al.} (2019) previously made the point that network
-inference techniques based on Bayesian approaches would perform far
-better in the presence of an interaction-level informative prior; the
-desirable properties of such a prior would be that it is expressed as a
-probability, preferably representing a Bernoulli event, the value of
-which would be representative of relevant biological processes
+for inference. Indeed, Strydom \emph{et al.} (2021a) suggest that
+knowing the metaweb may render the prediction of local networks easier,
+because it fixes an ``upper bound'' on which interactions can exist;
+indeed, with a probabilistic metaweb, we can consider that the metaweb
+represents an aggregation of informative priors on the interactions.
+
+Related to the last point, Cirtwill \emph{et al.} (2019) show that
+network inference techniques based on Bayesian approaches would perform
+far better in the presence of an interaction-level informative prior;
+the desirable properties of such a prior would be that it is expressed
+as a probability, preferably representing a Bernoulli event, the value
+of which would be representative of relevant biological processes
 (probability of predation in this case). We argue that the probability
@@
 of network comparison at the global scale. In this case study, we have
-embedded the original metaweb using t-SVD, because it lends itself to a
+embedded the original metaweb using t-SVD, because it lends itself to an
 RDPG reconstruction, which is known to capture the consequences of
@@
 As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, our approach must
-contend with two interesting problems. The first is the limit of the
-metaweb to embed and transfer. If the initial metaweb is too narrow in
-scope, notably from a taxonomic point of view, the chances of finding
-another area with enough related species to make a reliable inference
-decrease. This is notably true if the metaweb is assembled in an area
-with mostly endemic species. Conversely, the metaweb should be reliably
-filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
-species have been examined, either through literature surveys or expert
-elicitation. The second problem is to determine which area should be
-used to infer the new metaweb in, as this determines the species pool
-that must be used. In our application, we focused on the mammals of
-Canada. The upside of this approach is that information at the country
-level is likely to be required by policy makers and stakeholders for
-their biodiversity assessment, as each country tends to set goals at the
+lines around planet-wide problems''; in this regard, our approach (and
+indeed, any inference of a metaweb at large scales) must contend with
+several interesting and interwoven families of problems. The first is
+the limit of the metaweb to embed and transfer. If the initial metaweb
+is too narrow in scope, notably from a taxonomic point of view, the
+chances of finding another area with enough related species to make a
+reliable inference decreases; this would likely be indicated by large
+confidence intervals during ancestral character estimation, but the lack
+of well documented metawebs is currently preventing from developing more
+concrete guidelines. The question of phylogenetic relatedness and
+dispersal is notably true if the metaweb is assembled in an area with
+mostly endemic species, and as with every predictive algorithm, there is
+room for the application of our best ecological judgement. Conversely,
+the metaweb should be reliably filled, which assumes that the \(S^2\)
+interactions in a pool of \(S\) species have been examined, either
+through literature surveys or expert elicitation. Supp. Mat. 1 provides
+some guidance as to the type of sampling effort that should be
+prioritized. Although RDPG was able to maintain very high predictive
+power when interactions where missing, the addition of false positive
+interactions was immediately detected; this suggests that it may be
+appropriate to err on the side of ``too many'' interactions when
+constructing the initial metaweb to be transfered. The second series of
+problems are related to determining which area should be used to infer
+the new metaweb in, as this determines the species pool that must be
+used. In our application, we focused on the mammals of Canada. The
+upside of this approach is that information at the country level is
+likely to be required by policy makers and stakeholders for their
+biodiversity assessment, as each country tends to set goals at the
 national level (Buxton \emph{et al.} 2021) for which quantitative
 instruments are designed (Turak \emph{et al.} 2017), with specific
-strategies often enacted at smaller scales (Ray \emph{et al.} 2021). Yet
-these national divisions, in large parts of the world, reflect nothing
-except for the legacy of settler colonialism; indeed, the use of
-ecological data is not an apolitical act (Nost \& Goldstein 2021).
-Operating under the framework of national boundaries, and relying on
-data infrastructures designed to answer questions within them, must be
-done under the clear realization that this logic contributed to the
-ongoing biodiversity crisis (Adam 2014), can reinforce environmental
-injustice (Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
-especially, will probably end up being replaced by Indigenous principles
-of land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
-2021).
+strategies often enacted at smaller scales (Ray \emph{et al.} 2021). And
+yet, we do not really have a satisfying answer to the question of
+``where does a food web stops?''; the current most satisfying solutions
+involve examining the spatial consistency of network area relationships
+(see \emph{e.g.} Galiana \emph{et al.} 2018; Galiana \emph{et al.} 2019,
+2021), which is of course impossible in the absence of enough
+information about the network itse;f.~This suggests that an \emph{a
+posteriori} refinement of the results may be required, based on a
+downscaling of the metaweb. The final family of problems relates less to
+the availability of data or quantitative tools, and more to the praxis
+of spatial ecology. Operating under the context of national divisions,
+in large parts of the world, reflects nothing more than the legacy of
+settler colonialism. Indeed, the use of ecological data is not an
+apolitical act (Nost \& Goldstein 2021), as data infrastructures tend to
+be designed to answer questions within national boundaries, and their
+use both draws upon and reinforces territorial statecraft; as per Machen
+\& Nost (2021), this is particularly true when the output of
+``algorithmic thinking'' (\emph{e.g.} relying on machine learning to
+generate knowledge) can be re-used for governance (\emph{e.g.} enacting
+conservation decisions at the national scale). We therefore recognize
+that methods such as we propose operate under the framework that
+contributed to the ongoing biodiversity crisis (Adam 2014), reinforced
+environmental injustice (Choudry 2013; Domínguez \& Luoma 2020), and on
+Turtle Island especially, should be replaced by Indigenous principles of
+land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
+2021). As we see AI/ML being increasingly mobilized to generate
+knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
+\emph{et al.} 2019; Mosebo Fernandes \emph{et al.} 2020), our discussion
+of these tools need to go beyond the technical, and into the governance
+consequences they can have.
 
@@
 Brose, U., Jonsson, T., Berlow, E.L., Warren, P., Banasek-Richter, C.,
-Bersier, L.-F., \emph{et al.} (2006). Consumer--Resource Body-Size
+Bersier, L.-F., \emph{et al.} (2006). ConsumerResource Body-Size
 Relationships in Natural Food Webs. \emph{Ecology}, 87, 2411--2417.
@@
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, A.R., Eklӧf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
-A quantitative framework for investigating the reliability of empirical
+Cirtwill, A.R., Ekl, A., Roslin, T., Wootton, K. \& Gravel, D. (2019). A
+quantitative framework for investigating the reliability of empirical
 network construction. \emph{Methods in Ecology and Evolution}, 0.
@@
 e1005557.
+
+\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
+Dansereau, G. \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
+Framework for Species Distribution Modeling in Julia. \emph{Journal of
+Open Source Software}, 6, 2872.
 
@@
 
+\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
+Galiana, N., Barros, C., Braga, J., Ficetola, G.F., Maiorano, L.,
+Thuiller, W., \emph{et al.} (2021). The spatial scaling of food web
+structure across European biogeographical regions. \emph{Ecography},
+n/a.
+
+\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
+Galiana, N., Hawkins, B.A. \& Montoya, J.M. (2019). The geographical
+variation of network structure is scale dependent: Understanding the
+biotic specialization of hostparasitoid networks. \emph{Ecography}, 42,
+1175--1187.
+
+\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
+Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
+Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
+interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.
+
 \leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
@@
 
+\leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
+Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
+Nyman, T., \emph{et al.} (2018). Bringing Elton and Grinnell together: A
+quantitative framework to represent the biogeography of ecological
+interaction networks. \emph{Ecography}, 0.
+
 \leavevmode\hypertarget{ref-Grenie2021HarTax}{}%
@@
 
+\leavevmode\hypertarget{ref-Kawatsu2021AreNet}{}%
+Kawatsu, K., Ushio, M., van Veen, F.J.F. \& Kondoh, M. (2021). Are
+networks of trophic interactions sufficient for understanding the
+dynamics of multi-trophic communities? Analysis of a tri-trophic insect
+food-web time-series. \emph{Ecology Letters}, 24, 543--552.
+
+\leavevmode\hypertarget{ref-Kefi2012MorMea}{}%
+Kéfi, S., Berlow, E.L., Wieters, E.A., Navarrete, S.A., Petchey, O.L.,
+Wood, S.A., \emph{et al.} (2012). More than a meal\ldots{} integrating
+non-feeding interactions into food webs: More than a meal \ldots.
+\emph{Ecology Letters}, 15, 291--300.
+
+\leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
+Lamba, A., Cassey, P., Segaran, R.R. \& Koh, L.P. (2019). Deep learning
+for environmental conservation. \emph{Current Biology}, 29, R977--R982.
+
 \leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
@@
 
+\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
+Machen, R. \& Nost, E. (2021). Thinking algorithmically: The making of
+hegemonic knowledge in climate governance. \emph{Transactions of the
+Institute of British Geographers}, 46, 555--569.
+
 \leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
 Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020). Data from: Tetra-EU 1.0: A species-level trophic
+Thuiller, W. (2020a). Data from: Tetra-EU 1.0: A species-level trophic
 meta-web of European tetrapods.
+
+\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
+Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
+Thuiller, W. (2020b). TETRA-EU 1.0: A species-level trophic metaweb of
+European tetrapods. \emph{Global Ecology and Biogeography}, 29,
+1452--1457.
 
@@
 
+\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
+Mora, B.B., Gravel, D., Gilarranz, L.J., Poisot, T. \& Stouffer, D.B.
+(2018). Identifying a common backbone of interactions underlying food
+webs from different ecosystems. \emph{Nature Communications}, 9, 2603.
+
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
@@
 Evolution}, 30, 347--356.
+
+\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
+Mosebo Fernandes, A.C., Quintero Gonzalez, R., Lenihan-Clarke, M.A.,
+Leslie Trotter, E.F. \& Jokar Arsanjani, J. (2020). Machine Learning for
+Conservation Planning in a Changing Climate. \emph{Sustainability}, 12,
+7657.
 
@@
 O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez‐Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
+L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
 of tetrapods across Europe through the prism of the Eltonian niche.
@@
 
+\leavevmode\hypertarget{ref-Shlens2014TutPri}{}%
+Shlens, J. (2014). \emph{A Tutorial on Principal Component Analysis}.
+Available at: \url{http://arxiv.org/abs/1404.1100}. Last accessed.
+
 \leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
@@
 
+\leavevmode\hypertarget{ref-Vermaat2009MajDim}{}%
+Vermaat, J.E., Dunne, J.A. \& Gilbert, A.J. (2009). Major dimensions in
+food-web structure properties. \emph{Ecology}, 90, 278--282.
+
+\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
+Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, 5, 3769--3782.
+
 \leavevmode\hypertarget{ref-Xing2021RisEco}{}%

### 2021-10-28 reviews/01_ELE/01_draft_revised.tex
materials

@@
 %
-\,\textsuperscript{4}\quad %
+\,\textsuperscript{7}\quad %
 \href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
@@
 %
-\,\textsuperscript{7}\quad %
+\,\textsuperscript{8}\quad %
 \href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
 %
-\,\textsuperscript{8}\quad %
+\,\textsuperscript{9}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 \textsuperscript{1}\,Département de Sciences Biologiques, Université de
-Montréal, Montréal, Canada\quad \textsuperscript{2}\,Québec Centre for
-Biodiversity Sciences, Montréal,
-Canada\quad \textsuperscript{3}\,Université de Sherbrooke, Sherbrooke,
-Canada\quad \textsuperscript{4}\,Department of Forest Resources
-Management, University of British Columbia, Vancouver,
-Canada\quad \textsuperscript{5}\,Department of Biology, McGill
+Montréal, Montréal, Canada\quad \textsuperscript{2}\,Quebec Centre for
+Biodiversity Science, Montréal,
+Canada\quad \textsuperscript{3}\,Département de Biologie, Université de
+Sherbrooke, Sherbrooke, Canada\quad \textsuperscript{4}\,Department of
+Forest Resources Management, University of British Columbia, Vancouver,
+B.C., Canada\quad \textsuperscript{5}\,Department of Biology, McGill
 University, Montréal, Canada\quad \textsuperscript{6}\,Department of
 Ecology \& Evolutionary Biology, University of Toronto, Toronto,
-Canada\quad \textsuperscript{7}\,Centre for Integrative Ecology, School
+Canada\quad \textsuperscript{7}\,Department of Forest and Conservation
+Sciences, University of British Columbia, Vancouver,
+Canada\quad \textsuperscript{8}\,Centre for Integrative Ecology, School
 of Biological Sciences, University of Canterbury, Canterbury, New
-Zealand\quad \textsuperscript{8}\,School of Mathematics and Statistics,
+Zealand\quad \textsuperscript{9}\,School of Mathematics and Statistics,
 University of Canterbury, Canterbury, New Zealand
@@
 structured. As data collection alone is unlikely to be sufficient,
-community ecologists must adopt predictive methods. Here we develop such
-a method, relying on graph embedding and transfer learning to assemble a
-predicted list of trophic interactions between Canadian mammals. This
-interaction list is derived from the European food web, despite sharing
-only 5\% of common species with Canada. The results of the predictive
-model are compared against databases of recorded pairwise interactions,
-showing that we correctly recover over 95\% of known interactions. We
-provide guidance on how this method can be adapted by substituting some
-approaches or predictors in order to make it more generally applicable.
+community ecologists must adopt predictive methods. Here, we develop
+such a method relying on graph embedding and transfer learning to
+assemble a predicted list of trophic interactions between Canadian
+mammals. This interaction list is derived from the European food web,
+despite sharing 4\% of common species with Canada. The results of the
+predictive model are compared against databases of recorded pairwise
+interactions, showing that we correctly recover 91\% of known
+interactions. We provide guidance on how this method can be adapted by
+substituting some approaches or predictors in order to make it more
+generally applicable.
 
@@
 macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
-2016). First, networks within a location are difficult to sample
-properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
+2016). First, ecological networks within a location are difficult to
+sample properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
 shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
-about inter and intra specific relationships. This first challenge has
+about inter- and intra- specific relationships. This first challenge has
 been, in large part, addressed by the recent emergence of a suite of
@@
 are unable to infer potential species interactions. Having a general
-solution for inferring \emph{plausible} interactions (despite the
+solution for inferring \emph{potential} interactions (despite the
 unavailability of interaction data) could be the catalyst for
@@
 
-Here, we present a general method to recommend possible trophic
+Here, we present a general method to recommend potential trophic
 interactions, relying on the transfer learning of network
@@
 phylogenetic structure as a medium for transfer. There is a plurality of
-measures of species similarities that can be used for metaweb
-reconstruction (see \emph{e.g.} Morales-Castilla \emph{et al.} 2015);
-however, phylogenetic proximity has several desirable properties when
-working at large scales. Gerhold \emph{et al.} (2015) made the point
-that phylogenetic signal captures diversification of characters (large
+measures of species similarities that can be used for inferring
+\emph{potential} species interactions \emph{i.e.} metaweb reconstruction
+(see \emph{e.g.} Morales-Castilla \emph{et al.} 2015); however,
+phylogenetic proximity has several desirable properties when working at
+large scales. Gerhold \emph{et al.} (2015) made the point that
+phylogenetic signal captures diversification of characters (large
 macro-evolutionary process), but not necessarily community assembly
 (fine ecological process); Dormann \emph{et al.} (2010) previously found
-very similar conclusions. Interactions tend reflect a phylogenetic
+very similar conclusions. Interactions tend to reflect a phylogenetic
 signal because they have a conserved pattern of evolutionary convergence
@@
 (here, a truncated Singular Value Decomposition; Step 1), yielding a
-series of latent traits (vulnerability traits representing species at
-the lower trophic-level and generality traits representing species at
-higher trophic-levels; \emph{sensu} Schoener (1989)); second, for the
+series of latent traits (latent vulnerability traits are more
+representative of species at the lower trophic-level and latent
+generality traits are more representative of species at higher
+trophic-levels; \emph{sensu} Schoener (1989)); second, for the
 destination species pool, we perform ancestral character estimation
@@
 are treated as unknown in this instance). Following the definition of
-Dunne (2006), a metaweb is a network analogue to the concept of a
-regional species pool. Specifically, a metaweb is an inventory of all
-\emph{possible} interactions within species likely to occurr within a
-spatially delimited area (the network \(\gamma\)-diversity, in a sense).
-The metaweb is, therefore, \emph{not} a prediction of the food web at
-any specific locale within the frontiers of the spatial area it
-recovers, and will in fact have a different structure (notably by having
-a larger connectance; see \emph{e.g.} Wood \emph{et al.} 2015). These
-local food webs are expected to be a subset of both the species and the
-interactions of their metaweb, and have been called ``metaweb
-realizations'' (Poisot \emph{et al.} 2015). The difference between a
-food web at a specific location and the metaweb has to do with a variety
-of mechanisms, including species co-occurrence, local environmental
-conditions, and local distribution of functional traits. Nevertheless,
-the metaweb represents the total of functional, phylogenetic, and
-macroecological processes (Morales-Castilla \emph{et al.} 2015), and
-therefore still holds valuable ecological information. Because the
-metaweb can be down-sampled given appropriate knowledge of local species
-composition (the network \(\alpha\)-diversity, in a sense), it is
-possible to infer what may drive the structure of food webs at finer
-spatial scales. This has been done for example for
-tree-gallers-parasitoid systems (Gravel \emph{et al.} 2018), fish
-trophic interactions (Albouy \emph{et al.} 2019), tetrapods trophic
-interactions (O'Connor \emph{et al.} 2020), and crop-pests networks
-(Grünig \emph{et al.} 2020). Whereas the original metaweb definition was
-based on presence/absence, we focus on \emph{probabilistic} metawebs;
-not only does our method recommed interactions that may exist, it gives
-each interaction a score that is mathematically equivalent to the chance
-of success of a Bernoulli trial (see \emph{e.g.} Poisot \emph{et al.}
-2016), which allows properly weigh interactions as a function of how
-likely they are.
+Dunne (2006), a metaweb is a network analogue to the regional species
+pool; specifically, it is an inventory of all \emph{potential}
+interactions between species from a spatially delimited area (and so
+captures the \(\gamma\) diversity of interactions). The metaweb is,
+therefore, \emph{not} a prediction of the food web at a specific locale
+within the spatial area it covers, and will have a different structure
+(notably by having a larger connectance; see \emph{e.g.} Wood \emph{et
+al.} 2015). These local food webs (which captures the \(\alpha\)
+diversity of interactions) are a subset of the metaweb's species and
+interactions, and have been called ``metaweb realizations'' (Poisot
+\emph{et al.} 2015). Differences between local food web and their
+metaweb are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others.
+
+Because the metaweb represents the joint effect of functional,
+phylogenetic, and macroecological processes (Morales-Castilla \emph{et
+al.} 2015), it holds valuable ecological information. Specifically, it
+is the ``upper bounds'' on what the composition of the local networks
+can be (see \emph{e.g.} McLeod \emph{et al.} 2021). These local
+networks, in turn, can be reconstructed given appropriate knowledge of
+local species composition, providing information on structure of food
+webs at finer spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel \emph{et al.} 2018), fish trophic
+interactions (Albouy \emph{et al.} 2019), tetrapod trophic interactions
+(O'Connor \emph{et al.} 2020), and crop-pest networks (Grünig \emph{et
+al.} 2020). Whereas the original metaweb definition, and indeed most
+past uses of metawebs, was based on the presence/absence of
+interactions, we focus on \emph{probabilistic} metawebs where
+interactions are represented as the chance of success of a Bernoulli
+trial (see \emph{e.g.} Poisot \emph{et al.} 2016); therefore, not only
+does our method recommend interactions that may exist, it gives each
+interaction a score, allowing us to properly weigh them.
 
@@
 from the known network and make biologically relevant predictions of
-interactions. Indeed, as we detail in the result, when validated against
-known but fracational data of trophic interactions between Canadian
-mammals, our model achieves a predictive accuracy of approx. 91\%. It
-should be reiterated that the framework presented in
-fig.~\ref{fig:concept} is amenable to changes; notably, the measure of
-similarity may not be phylogeny, and can be replaced by information on
-foraging (Beckerman \emph{et al.} 2006), cell-level mechanisms
+interactions. Indeed, as we detail in the results, when validated
+against known but fractional data of trophic interactions between
+Canadian mammals, our model achieves a predictive accuracy of
+approximately 91\%. It should be reiterated that the framework presented
+in fig.~\ref{fig:concept} is amenable to changes; notably, the measure
+of similarity may not be phylogeny, and can be replaced by information
+on foraging (Beckerman \emph{et al.} 2006), cell-level mechanisms
 (Boeckaerts \emph{et al.} 2021), or a combination of traits and
 phylogenetic structure (Stock 2021). Most importantly, although we focus
-on a trophic system, it is an established fact that different types of
-interactions do themselves interact (Kéfi \emph{et al.} 2012; see
+on a trophic system, it is an established fact that different
+(non-trophic) interactions do themselves interact with and influence the
+outcome of trophic interactions (Kéfi \emph{et al.} 2012; see
 \emph{e.g.} Kawatsu \emph{et al.} 2021). Future development of metaweb
@@
 We use data from the European metaweb assembled by Maiorano \emph{et
-al.} (2020b).
-
-\textbf{TANYA TODO} description of the data
-
-We induced the subgraph corresponding to all mammals by matching species
-names in the original network to the GBIF taxonomic backbone (GBIF
+al.} (2020b). This was assembled using data extracted from scientific
+literature (including published papers, books, and grey literature) from
+the last 50 years and includes all terrestrial tetrapods (mammals,
+breeding birds, reptiles and amphibians) occurring on the European
+sub-continent (and Turkey) - with the caveat that only species
+introduced in historical times and currently naturalized being included.
+This metaweb itself is a network of binary (\emph{i.e.}
+presence/absence), potential two-way interactions between species pairs.
+
+We filtered down the European metaweb to create a subgraph corresponding
+to all mammals by matching species names in the original network to the
+Global Biodiversity Information Facility (GBIF) taxonomic backbone (GBIF
 Secretariat 2021) and retaining all those who matched to mammals. This
@@
 transfer; the phylogenetic similarity of mammals here represents the
-information for transfer. We used the mammalian consensus supertree by
-Upham \emph{et al.} (2019), for which all approximatively 6000 names
-have been similarly matched to their GBIF valid names. This step allows
-us to place each node of the mammalian European metaweb in the
-phylogeny.
+information for transfer (\emph{i.e.} the transfer medium). We used the
+mammalian consensus supertree by Upham \emph{et al.} (2019), for which
+all approximatively 6000 names have been similarly matched to their GBIF
+valid names. This step allows us to place each node of the mammalian
+European metaweb in the phylogeny.
 
@@
 trophic interactions between mammals in Canada. We obtained the list of
-extant species from the IUCN checklist, and selected the terrestrial and
-semi-aquatic species (this corresponds to the same selection that was
-applied by Maiorano \emph{et al.} (2020b) in the European metaweb). The
-IUCN names were, as previously, reconciled against GBIF to have an exact
-match to the taxonomy.
+extant species from the International Union for Conservation of Nature
+(IUCN) checklist, and selected the terrestrial and semi-aquatic species
+(this corresponds to the same selection that was applied by Maiorano
+\emph{et al.} (2020b) in the European metaweb). The IUCN names were, as
+previously, reconciled against GBIF to have an exact match to the
+taxonomy.
 
@@
 (t-SVD; Halko \emph{et al.} 2011) to generate latent traits representing
-a low-dimensional embedding of the network; these traits give an
-unbiased estimate of the node's position in the latent feature spaces.
-Then, we map these latent traits onto a reference phylogeny (other
-distance-based measures of species proximity that allow for the
-inference of features in the latent space can be used, for example the
-dissimilarity in functional traits). Based on the reconstructed latent
-traits for species in the destination species pool, a Random Dot Product
-Graph model (hereafter RDPG; Young \& Scheinerman 2007) predicts the
-interaction between species through a function of the nodes' features
-through matrix multiplication. Thus, from latent traits and node
-position, we can infer interactions.
+a low-dimensional embedding of the network. As an aside, most ecologists
+are indirectly familiar with SVD: Principal Component Analysis is a
+special case of SVD, which is more sensitive to numerical instabilities
+(see notably Shlens 2014). The latent traits give an unbiased estimate
+of the node's position in the latent feature spaces and can be mapped
+onto a reference phylogeny (other distance-based measures of species
+proximity that allow for the inference of features in the latent space
+can be used, for example the dissimilarity in functional traits). Based
+on the reconstructed latent traits for species in the destination
+species pool, a Random Dot Product Graph model (hereafter RDPG; Young \&
+Scheinerman 2007) predicts the interaction between species through a
+function of the nodes' features through matrix multiplication. Thus,
+from latent traits and node position, we can infer interactions.
 
@@
 (unintentional) black box algorithms are not necessarily a bad thing
-Holm (2019), as long as their constituent parts can be examined (which
+(Holm 2019), as long as their constituent parts can be examined (which
 is the case with our method). But more importantly, data hold more
-information that we may thought; as such, even algorithms that are
+information than we might think; as such, even algorithms that are
 disconnected from the model can make correct guesses most of the time
@@
 Riva \& Stouffer 2016); in other words, the latent variables of an RDPG
-can be mapped onto a phylogenetic tree, and phylogenetically close
-predators should share phylogenetically close preys. In addition, recent
-advances show that the latent variables produced this way can be used to
-predict \emph{de novo} network edges. Interstingly, the latent variables
-do not need to be prouced by decomposing the network itself; in a recent
-contribution, Runghen \emph{et al.} (2021) show that deep artificial
-neural networks are able to reconstruct the left and right subspaces of
-an RDPG, in order to predict human movement networks from
+can be mapped onto a phylogenetic tree, and phylogenetically similar
+predators should share phylogenetically similar preys. In addition,
+recent advances show that the latent variables produced this way can be
+used to predict \emph{de novo} network edges. Interestingly, the latent
+variables do not need to be produced by decomposing the network itself;
+in a recent contribution, Runghen \emph{et al.} (2021) showed that deep
+artificial neural networks are able to reconstruct the left and right
+subspaces of an RDPG, in order to predict human movement networks from
 individual/location metadata. This is an exciting opportunity, as it
-opens up the possibility of using additional predictors.
+opens up the possibility of using additional metadata as predictors.
 
@@
 unitary matrix and \(\mathbf{V}'\) a \(n \times r\) semi-unitary matrix.
-As an aside, most ecologists are indirectly familiar with SVD: Principal
-Component Analysis is a special case of SVD, which is more sensitive to
-numerical instabilities (see notably Shlens 2014).
 
@@
 nodes (species) as a function of the nodes' latent variables, and is a
-way to turn a SVD (which decompose a matrix intro three) into two
+way to turn a SVD (which decompose one matrix into three) into two
 matrices that can be multiplied to provide an approximation of the
@@
 of using a RDPG rather than a SVD is that the number of components to
-estimate decreases; notably, one does not have to estimate the
-eigenvalues of the SVD. Furthermore, the two subspaces can be directly
+estimate decreases; notably, one does not have to estimate the singular
+values of the SVD. Furthermore, the two subspaces can be directly
 multiplied to yield a network.
@@
 \includegraphics{figures/figure-screeplot.png}
-\caption{Left: representation of the screeplot of the singular values
-from the t-SVD on the European metaweb. The screeplot shows no obvious
+\caption{Left: representation of the scree plot of the singular values
+from the t-SVD on the European metaweb. The scree plot shows no obvious
 drop in the singular values that may be leveraged to automatically
@@
 dimension up to the rank of the European metaweb. The grey lines
-represent cutoffs at 50, 60\ldots{} 90\% of variance explained. For the
+represent cutoffs at 50, 60, \ldots, 90\% of variance explained. For the
 rest of the analysis, we reverted to an arbitrary threshold of 60\% of
@@
 decreasing the quality of the original data by adding of removing
-interactions would minimally affect the predicive accuracy of RDPG
+interactions would minimally affect the predictive accuracy of RDPG
 applied to the European metaweb; and that the networks reconstructed
-from artifically modified data are reconstructured with the correct
+from artificially modified data are reconstructed with the correct
 ecological properties.
@@
 reconstruction for all species (conceptually something akin to a
-trait-based mammalian phylogeny using generality and vulnerability
-traits) and allows us to impute the missing (latent) trait data for the
-Canadian species that are not already in the European network; as we are
-focused on predicting contemporary interactions, we only retained the
-values for the tips of the tree. We assumed that all traits (\emph{i.e.}
-the feature vectors for the left and right subspaces) were independent,
-which is a reasonable assumption as every trait/dimension added to the
-t-SVD has an \emph{additive} effect to the one before it. Note that the
-Upham \emph{et al.} (2019) tree itself has some uncertainty associated
-to inner nodes of the phylogeny. In this case study, we have decided to
-not propagate this uncertainty, as it would complexify the process. The
-Brownian motion algorithm returns the \emph{average} value of the trait,
-and its upper and lower bounds. Because we do not estimate other
-parameters of the traits' distributions, we considered that every
-species trait is represented as a uniform distribution between these
-bounds. The choice of the uniform distribution was made because the
-algorithm returns a minimum and maximum point estimate for the value,
-and given this information, the uniform distribution is the one with
-maximum entropy. Had all mean parameters estimates been positive, the
-exponential distribution would have been an alternative, but this is not
-the case for the subspaces of an RDPG. In order to examine the
-consequences of the choice of distribution, we estimated the variance
-per latent variable per node to use a normal distribution; as we show in
-Supp. Mat. 2, this decision results in dramatically over-estimating the
-number and probability of interactions, and therefore we keep the
-discussions in the main text to the uniform case. The inferred left and
-right sub-spaces for the Canadian species pool (\(\hat{\mathscr{L}}\)
-and \(\hat{\mathscr{R}}\)) have entries that are distributions,
-representing the range of values for a given species at a given
-dimension.
+trait-based mammalian phylogeny using latent generality and
+vulnerability traits) and allows us to impute the missing (latent) trait
+data for the Canadian species that are not already in the European
+network; as we are focused on predicting contemporary interactions, we
+only retained the values for the tips of the tree. We assumed that all
+traits (\emph{i.e.} the feature vectors for the left and right
+subspaces) were independent, which is a reasonable assumption as every
+trait/dimension added to the t-SVD has an \emph{additive} effect to the
+one before it. Note that the Upham \emph{et al.} (2019) tree itself has
+some uncertainty associated to inner nodes of the phylogeny. In this
+case study, we have decided to not propagate this uncertainty, as it
+would complexify the process. The Brownian motion algorithm returns the
+\emph{average} value of the trait, and its upper and lower bounds.
+Because we do not estimate other parameters of the traits'
+distributions, we considered that every species trait is represented as
+a uniform distribution between these bounds. The choice of the uniform
+distribution was made because the algorithm returns a minimum and
+maximum point estimate for the value, and given this information, the
+uniform distribution is the one with maximum entropy. Had all mean
+parameters estimates been positive, the exponential distribution would
+have been an alternative, but this is not the case for the subspaces of
+an RDPG. In order to examine the consequences of the choice of
+distribution, we estimated the variance per latent variable per node to
+use a Normal distribution; as we show in Supp. Mat. 2, this decision
+results in dramatically over-estimating the number and probability of
+interactions, and therefore we keep the discussions in the main text to
+the uniform case. The inferred left and right subspaces for the Canadian
+species pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have
+entries that are distributions, representing the range of values for a
+given species at a given dimension.
 
@@
 imputed Canadian metaweb (before data inflation) on the right. This
-figure illustrates how much structure the left sub-space captures. As we
+figure illustrates how much structure the left subspace captures. As we
 show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
@@
 information to produce one random Canadian metaweb,
-\(N = \hat{\mathscr{L}}\)\(\hat{\mathscr{R}}' \ge \rho\). As we can see
-in (fig.~\ref{fig:subspaces}) the European and Canadian metawebs are
+\(N = \hat{\mathscr{L}}\hat{\mathscr{R}}' \ge \rho\). As we can see in
+(fig.~\ref{fig:subspaces}), the European and Canadian metawebs are
 structurally similar (as would be expected given the biogeographic
@@
 \emph{i.e.} capturing predation (generality) and prey (vulnerability)
-traits.
+latent traits.
 
@@
 Vermaat \emph{et al.} (2009), we show in Supp. Mat. 3 that not only can
-we observed differences in a multivariate space between the European and
+we observe differences in a multivariate space between the European and
 Canadian metaweb, we can also observe differences in the same space
@@
 interactions found in GLOBI (red), and in the Strong \& Leroux (2014)
-Newfoundland dataset (blue). The model recovers more interaction with a
+Newfoundland dataset (blue). The model recovers more interactions with a
 low probability compared to data mining, which can suggest that
@@
 Global Biotic Interactions (GLoBI) database (Poelen \emph{et al.} 2014),
-and extracted their known interactions. Because GLOBI aggregates
+and extracted their known interactions. Because GLoBI aggregates
 observed interactions, it is not a \emph{networks} data source, and
@@
 species pair \emph{was reported to interact at least once}. This last
-statement should yet be taken with caution, as some sources in GLOBI
+statement should yet be taken with caution, as some sources in GLoBI
 (\emph{e.g.} Thessen \& Parr 2014) are produced through text analysis,
@@
 Nevertheless, should the predictive model work, we would expect that a
-majority of interactions known to GLOBI would also be predicted. We
+majority of interactions known to GLoBI would also be predicted. We
 retrieved 366 interactions between mammals from the Canadian species
-pool from GLOBI, 33 of which were not predicted by the model; this
+pool from GLoBI, 33 of which were not predicted by the model; this
 results in a success rate of 91\%. After performing this check, we set
-the probability of all interactions known to GLOBI to 1.
+the probability of all interactions known to GLoBI to 1.
 
@@
 linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
-the number of preys and predators. Importantly, this implies that a rank
-1 approximation represents the configuration model for the metaweb,
-\emph{i.e.} a set of random networks generated from a given degree
-sequence (Park \& Newman 2004). Accounting for the probabilistic nature
-of the degrees, the rank 1 approximation also represents the \emph{soft}
-configuration model (van der Hoorn \emph{et al.} 2018). Both models are
-maximum entropy graph models (Garlaschelli \emph{et al.} 2018), with
-sharp (all network realizations satisfy the specified degree sequence)
-and soft (network realizations satisfy the degree sequence on average)
-local constraints, respectively. The (soft) configuration model is an
-unbiased random graph model widely used by ecologists in the context of
-null hypothesis significance testing of network structure (\emph{e.g.}
-Bascompte \emph{et al.} 2003) and can provide informative priors for
-Bayesian inference of network structure (\emph{e.g.} Young \emph{et al.}
-2021). It is noteworthy that for this metaweb, the relevant information
-was extracted at the first rank. Because the first rank corresponds to
-the leading singular value of the system, the results of
-fig.~\ref{fig:degree} have a straightforward interpretation:
-degree-based processes are the most important in structuring the
-mammalian food web.
+the number of preys and predators for each species. Importantly, this
+implies that a rank 1 approximation represents the configuration model
+for the metaweb, \emph{i.e.} a set of random networks generated from a
+given degree sequence (Park \& Newman 2004). Accounting for the
+probabilistic nature of the degrees, the rank 1 approximation also
+represents the \emph{soft} configuration model (van der Hoorn \emph{et
+al.} 2018). Both models are maximum entropy graph models (Garlaschelli
+\emph{et al.} 2018), with sharp (all network realizations satisfy the
+specified degree sequence) and soft (network realizations satisfy the
+degree sequence on average) local constraints, respectively. The (soft)
+configuration model is an unbiased random graph model widely used by
+ecologists in the context of null hypothesis significance testing of
+network structure (\emph{e.g.} Bascompte \emph{et al.} 2003) and can
+provide informative priors for Bayesian inference of network structure
+(\emph{e.g.} Young \emph{et al.} 2021). It is noteworthy that for this
+metaweb, the relevant information was extracted at the first rank.
+Because the first rank corresponds to the leading singular value of the
+system, the results of fig.~\ref{fig:degree} have a straightforward
+interpretation: degree-based processes are the most important in
+structuring the mammalian food web.
 
@@
 it is important to recall that a metaweb is intended as a catalogue of
-all possible interactions, which should then be filtered
+all potential interactions, which should then be filtered
 (Morales-Castilla \emph{et al.} 2015). In practice (and in this
@@
 plausible based on the species' evolutionary history, however some
-interactions would not be realized due to human impact.
-
-Dallas \emph{et al.} (2017) suggest that most links in ecological
+interactions would/would not be realized due to human impact.
+
+Dallas \emph{et al.} (2017) suggested that most links in ecological
 networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
@@
 predictive models, which increases the volume of information available
-for inference. Indeed, Strydom \emph{et al.} (2021a) suggest that
+for inference. Indeed, Strydom \emph{et al.} (2021a) suggested that
 knowing the metaweb may render the prediction of local networks easier,
@@
 
-Related to the last point, Cirtwill \emph{et al.} (2019) show that
+Related to the last point, Cirtwill \emph{et al.} (2019) showed that
 network inference techniques based on Bayesian approaches would perform
@@
 evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
-there are others ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
+there are other ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
 Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
@@
 confidence intervals during ancestral character estimation, but the lack
-of well documented metawebs is currently preventing from developing more
-concrete guidelines. The question of phylogenetic relatedness and
+of well documented metawebs is currently preventing the development of
+more concrete guidelines. The question of phylogenetic relatedness and
 dispersal is notably true if the metaweb is assembled in an area with
@@
 prioritized. Although RDPG was able to maintain very high predictive
-power when interactions where missing, the addition of false positive
+power when interactions were missing, the addition of false positive
 interactions was immediately detected; this suggests that it may be
 appropriate to err on the side of ``too many'' interactions when
-constructing the initial metaweb to be transfered. The second series of
+constructing the initial metaweb to be transferred. The second series of
 problems are related to determining which area should be used to infer
@@
 yet, we do not really have a satisfying answer to the question of
-``where does a food web stops?''; the current most satisfying solutions
+``where does a food web stop?''; the current most satisfying solutions
 involve examining the spatial consistency of network area relationships
-(see \emph{e.g.} Galiana \emph{et al.} 2018; Galiana \emph{et al.} 2019,
-2021), which is of course impossible in the absence of enough
-information about the network itse;f.~This suggests that an \emph{a
+(see \emph{e.g.} Galiana \emph{et al.} 2018, 2019, 2021; Fortin \emph{et
+al.} 2021), which is of course impossible in the absence of enough
+information about the network itself. This suggests that an \emph{a
 posteriori} refinement of the results may be required, based on a
@@
 nations. TP, TS, DC, and LP received funding from the Canadian Institue
-for Ecology \& Evolution. FB is funded by the Institut de Valorisation
-des Données. TS, SB, and TP are funded by a donation from the Courtois
-Foundation. CB was awarded a Mitacs Elevate Fellowship no. IT12391, in
-partnership with fRI Research, and also acknowledges funding from
-Alberta Innovates and the Forest Resources Improvement Association of
-Alberta. M-JF acknowledges funding from NSERC Discovery Grant and NSERC
-CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora Tuku
-Iho National Science Challenge, administered by New Zealand Ministry of
-Business, Innovation, and Employment. BM is funded by the NSERC
-Alexander Graham Bell Canada Graduate Scholarship and the FRQNT master's
-scholarship. LP acknowledges funding from NSERC Discovery Grant (NSERC
-RGPIN-2019-05771). TP acknowledges financial support from NSERC through
-the Discovery Grants and Discovery Accelerator Supplement programs.
+for Ecology \& Evolution. FB is funded by the Institute for Data
+Valorization (IVADO). TS, SB, and TP are funded by a donation from the
+Courtois Foundation. CB was awarded a Mitacs Elevate Fellowship no.
+IT12391, in partnership with fRI Research, and also acknowledges funding
+from Alberta Innovates and the Forest Resources Improvement Association
+of Alberta. M-JF acknowledges funding from NSERC Discovery Grant and
+NSERC CRC. RR is funded by New Zealand's Biological Heritage Ngā Koiora
+Tuku Iho National Science Challenge, administered by New Zealand
+Ministry of Business, Innovation, and Employment. BM is funded by the
+NSERC Alexander Graham Bell Canada Graduate Scholarship and the FRQNT
+master's scholarship. LP acknowledges funding from NSERC Discovery Grant
+(NSERC RGPIN-2019-05771). TP acknowledges financial support from NSERC
+through the Discovery Grants and Discovery Accelerator Supplement
+programs.
 
@@
 
+\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
+Fortin, M.-J., Dale, M.R.T. \& Brimacombe, C. (2021). Network ecology in
+dynamic landscapes. \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 288, rspb.2020.1889, 20201889.
+
 \leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
@@
 \emph{Nature Communications}, 9, 4621.
+
+\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
+McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
+M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
+of spatial multi-trophic networks. \emph{Oikos}, n/a.
 

### 2021-10-28 reviews/01_ELE/01_draft.tex

--- 2021-09-20 draft.tex
@@
 
-\begin{figure}
-\hypertarget{fig:concept}{%
-\centering
-\includegraphics{figures/figure-concept.png}
-\caption{Overview of the phylogenetic transfer learning (and prediction)
-of species interactions networks. Starting from an initial, known,
-network, we learn its representation through a graph embedding step
-(here, a truncated Singular Value Decomposition; Step 1), yielding a
-series of latent traits (vulnerability traits representing species at
-the lower trophic-level and generality traits representing species at
-higher trophic-levels; \emph{sensu} Schoener (1989)); second, for the
-destination species pool, we perform ancestral character estimation
-using a phylogeny (here, using a Brownian model for the latent traits;
-Step 2); we then sample from the reconstructed distribution of latent
-traits (Step 3) to generate a probabilistic metaweb at the destination
-(here, assuming a uniform distribution of traits), and threshold it to
-yield the final list of interactions (Step 4).}\label{fig:concept}
-}
-\end{figure}
-
 There is a plurality of measures of species similarities that can be
@@
 the t-SVD provides a first-order approximation of the network.
-
-\begin{figure}
-\hypertarget{fig:scree}{%
-\centering
-\includegraphics{figures/figure-screeplot.png}
-\caption{Left: representation of the screeplot of the singular values
-from the t-SVD on the European metaweb. The screeplot shows no obvious
-drop in the singular values that may be leveraged to automatically
-detect a minimal dimension for embedding, after \emph{e.g.} Zhu \&
-Ghodsi (2006). Right: cumulative fraction of variance explained by each
-dimension up to the rank of the European metaweb. The grey lines
-represent cutoffs at 50, 60\ldots{} 90\% of variance explained. For the
-rest of the analysis, we reverted to an arbitrary threshold of 60\% of
-variance explained, which represented a good tradeoff between accuracy
-and reduced number of features.}\label{fig:scree}
-}
-\end{figure}
 
@@
 
-\begin{figure}
-\hypertarget{fig:subspaces}{%
-\centering
-\includegraphics{figures/figure-subspaces.png}
-\caption{Visual representation of the left (green/purple) and right
-(green/brown) subspaces, alongside the adjacency matrix of the food web
-they encode (greyscale). The European metaweb is on the left, and the
-imputed Canadian metaweb (before data inflation) on the right. This
-figure illustrates how much structure the left sub-space captures. As we
-show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
-subspace are species without any prey.}\label{fig:subspaces}
-}
-\end{figure}
-
 Specifically, we have adopted the following approach. For every entry in
@@
 
-\begin{figure}
-\hypertarget{fig:inflation}{%
-\centering
-\includegraphics{figures/figure-validation.png}
-\caption{Left, comparison of the probabilities of interactions assigned
-by the model to all interactions (grey curve), the subset of
-interactions found in GLOBI (red), and in the Strong \& Leroux (2014)
-Newfoundland dataset (blue). The model recovers more interaction with a
-low probability compared to data mining, which can suggest that
-collected datasets are biased towards more common or easy to identify
-interactions. Right, distribution of the in-degree and out-degree of the
-mammals from Canada in the reconstructed metaweb. This figure describes
-a flat, relatively short food web, in which there are few predators but
-a large number of preys.}\label{fig:inflation}
-}
-\end{figure}
-
 First, we extracted the subgraph corresponding to the 17 species shared
@@
 supplementary material.
-
-\begin{figure}
-\hypertarget{fig:thresholds}{%
-\centering
-\includegraphics{figures/figure-cutoffs.png}
-\caption{Left: effect of varying the cutoff for probabilities to be
-considered non-zero on the number of unique links and on \(\hat{L}\),
-the probabilistic estimate of the number of links assuming that all
-interactions are independent. Right: effect of varying the cutoff on the
-number of disconnected species, and on network connectance. In both
-panels, the grey line indicates the cutoff
-\(P(i\rightarrow j) \approx 0.08\) that resulted in the first species
-losing all of its interactions.}\label{fig:thresholds}
-}
-\end{figure}
 
@@
 networks are required.
-
-\begin{figure}
-\hypertarget{fig:degree}{%
-\centering
-\includegraphics{figures/figure-degree.png}
-\caption{Top: biological significance of the first dimension. Left:
-there is a linear relationship between the values on the first dimension
-of the left subspace and the generality, \emph{i.e.} the relative number
-of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
-this subspace are at the bottom-most trophic level. Right: there is,
-similarly, a linear relationship between the position of a species on
-the first dimension of the right subspace and its vulnerability,
-\emph{i.e.} the relative number of predators. Taken together, these two
-figures show that the first-order representation of this network would
-capture its degree distribution. Bottom: topological consequences of the
-first dimension. Left: differences in the \(z\)-score of the actual
-configuration model for the reconstructed network, and the prediction
-based only on the first dimension. Right: distribution of the
-differences in the left panel.}\label{fig:degree}
-}
-\end{figure}
 

### 2021-10-28 reviews/01_ELE/01_draft_revised.tex

@@
 
-\begin{figure}
-\hypertarget{fig:concept}{%
-\centering
-\includegraphics{figures/figure-concept.png}
-\caption{Overview of the phylogenetic transfer learning (and prediction)
-of species interactions networks. Starting from an initial, known,
-network, we learn its representation through a graph embedding step
-(here, a truncated Singular Value Decomposition; Step 1), yielding a
-series of latent traits (latent vulnerability traits are more
-representative of species at the lower trophic-level and latent
-generality traits are more representative of species at higher
-trophic-levels; \emph{sensu} Schoener (1989)); second, for the
-destination species pool, we perform ancestral character estimation
-using a phylogeny (here, using a Brownian model for the latent traits;
-Step 2); we then sample from the reconstructed distribution of latent
-traits (Step 3) to generate a probabilistic metaweb at the destination
-(here, assuming a uniform distribution of traits), and threshold it to
-yield the final list of interactions (Step 4).}\label{fig:concept}
-}
-\end{figure}
-
 Our methodology is outlined in fig.~\ref{fig:concept}, where we provide
@@
 multiplied to yield a network.
-
-\begin{figure}
-\hypertarget{fig:scree}{%
-\centering
-\includegraphics{figures/figure-screeplot.png}
-\caption{Left: representation of the scree plot of the singular values
-from the t-SVD on the European metaweb. The scree plot shows no obvious
-drop in the singular values that may be leveraged to automatically
-detect a minimal dimension for embedding, after \emph{e.g.} Zhu \&
-Ghodsi (2006). Right: cumulative fraction of variance explained by each
-dimension up to the rank of the European metaweb. The grey lines
-represent cutoffs at 50, 60, \ldots, 90\% of variance explained. For the
-rest of the analysis, we reverted to an arbitrary threshold of 60\% of
-variance explained, which represented a good tradeoff between accuracy
-and reduced number of features.}\label{fig:scree}
-}
-\end{figure}
 
@@
 
-\begin{figure}
-\hypertarget{fig:subspaces}{%
-\centering
-\includegraphics{figures/figure-subspaces.png}
-\caption{Visual representation of the left (green/purple) and right
-(green/brown) subspaces, alongside the adjacency matrix of the food web
-they encode (greyscale). The European metaweb is on the left, and the
-imputed Canadian metaweb (before data inflation) on the right. This
-figure illustrates how much structure the left subspace captures. As we
-show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
-subspace are species without any prey.}\label{fig:subspaces}
-}
-\end{figure}
-
 Specifically, we have adopted the following approach. For every entry in
@@
 
-\begin{figure}
-\hypertarget{fig:inflation}{%
-\centering
-\includegraphics{figures/figure-validation.png}
-\caption{Left, comparison of the probabilities of interactions assigned
-by the model to all interactions (grey curve), the subset of
-interactions found in GLOBI (red), and in the Strong \& Leroux (2014)
-Newfoundland dataset (blue). The model recovers more interactions with a
-low probability compared to data mining, which can suggest that
-collected datasets are biased towards more common or easy to identify
-interactions. Right, distribution of the in-degree and out-degree of the
-mammals from Canada in the reconstructed metaweb. This figure describes
-a flat, relatively short food web, in which there are few predators but
-a large number of preys.}\label{fig:inflation}
-}
-\end{figure}
-
 First, we extracted the subgraph corresponding to the 17 species shared

### 2021-10-28 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@fc8297696fc28950cf3e4169b1fe815ccd7c9ca4 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@1d7727848dd39d1807440f2d3fca561177a3aeff 🚀

@@
 %
-\,\textsuperscript{4}, %
+\,\textsuperscript{7}, %
 \href{https://orcid.org/0000-0002-4104-9463}{Benjamin\,Mercier}%
@@
 %
-\,\textsuperscript{7}, %
+\,\textsuperscript{8}, %
 \href{https://orcid.org/0000-0002-3454-0633}{Giulio V.\,Dalla Riva}%
 %
-\,\textsuperscript{8}, %
+\,\textsuperscript{9}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
@@
 \textsuperscript{1}\,Département de Sciences Biologiques, Université de
-Montréal, Montréal, Canada; \textsuperscript{2}\,Québec Centre for
-Biodiversity Sciences, Montréal, Canada; \textsuperscript{3}\,Université
-de Sherbrooke, Sherbrooke, Canada; \textsuperscript{4}\,Department of
-Forest Resources Management, University of British Columbia, Vancouver,
+Montréal, Montréal, Canada; \textsuperscript{2}\,Quebec Centre for
+Biodiversity Science, Montréal, Canada; \textsuperscript{3}\,Département
+de Biologie, Université de Sherbrooke, Sherbrooke,
+Canada; \textsuperscript{4}\,Department of Forest Resources Management,
+University of British Columbia, Vancouver, B.C.,
 Canada; \textsuperscript{5}\,Department of Biology, McGill University,
@@
 Evolutionary Biology, University of Toronto, Toronto,
-Canada; \textsuperscript{7}\,Centre for Integrative Ecology, School of
+Canada; \textsuperscript{7}\,Department of Forest and Conservation
+Sciences, University of British Columbia, Vancouver,
+Canada; \textsuperscript{8}\,Centre for Integrative Ecology, School of
 Biological Sciences, University of Canterbury, Canterbury, New
-Zealand; \textsuperscript{8}\,School of Mathematics and Statistics,
+Zealand; \textsuperscript{9}\,School of Mathematics and Statistics,
 University of Canterbury, Canterbury, New Zealand\\
@@
 are unable to infer potential species interactions. Having a general
-solution for inferring a \emph{plausible} metaweb (despite the
+solution for inferring \emph{potential} interactions (despite the
 unavailability of interaction data) could be the catalyst for
 significant breakthroughs in our ability to start thinking about species
-interaction networks over large spatial scales.
-
-Here, we present a general method for the transfer learning of network
-representations, relying on the similarities of species in a
+interaction networks over large spatial scales. In a recent overview of
+the field of ecological network prediction, Strydom \emph{et al.}
+(2021a) identified two challenges of interest to the prediction of
+interactions at large scales. First, there is a relative scarcity of
+relevant data in most places globally -- paradoxically, this restricts
+our ability to infer interactions to locations where inference is
+perhaps the least required; second, accurate predictions often demand
+accurate predictors, and the lack of methods that can leverage small
+amount of data is a serious impediment to our predictive ability
+globally.
+
+Here, we present a general method to recommend potential trophic
+interactions, relying on the transfer learning of network
+representations, specifically by using similarities of species in a
 biologically/ecologically relevant proxy space (\emph{e.g.} shared
@@
 another species pool for which interactions are known by using
-phylogenetic structure as a medium for transfer. This allows us to
-construct a \emph{probabilistic} metaweb for a community for which we
-have \emph{no} prior trophic interaction data for the desired species
-pool. Our methodology is outlined in fig.~\ref{fig:concept}, where we
-provide an illustration based on learning the embedding of a metaweb of
-trophic interactions for European mammals (known interactions; Maiorano
-\emph{et al.} 2020b, a) and, based on phylogenetic relationships between
-mammals globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.}
-2019), infer a metaweb for the Canadian mammalian species pool
-(interactions are treated as unknown in this instance).
+phylogenetic structure as a medium for transfer. There is a plurality of
+measures of species similarities that can be used for inferring
+\emph{potential} species interactions \emph{i.e.} metaweb reconstruction
+(see \emph{e.g.} Morales-Castilla \emph{et al.} 2015); however,
+phylogenetic proximity has several desirable properties when working at
+large scales. Gerhold \emph{et al.} (2015) made the point that
+phylogenetic signal captures diversification of characters (large
+macro-evolutionary process), but not necessarily community assembly
+(fine ecological process); Dormann \emph{et al.} (2010) previously found
+very similar conclusions. Interactions tend to reflect a phylogenetic
+signal because they have a conserved pattern of evolutionary convergence
+that encompasses a wide range of ecological and evolutionary mechanisms
+(Cavender-Bares \emph{et al.} 2009; Mouquet \emph{et al.} 2012), and -
+most importantly - retain this signal even when it is not detectable at
+the community scale (Hutchinson \emph{et al.} 2017; Poisot \& Stouffer
+2018). Finally, species interactions at macro-ecological scales seem to
+respond mostly to macro-evolutionary processes (Price 2003); which is
+evidenced by the presence of conserved backbones in food webs (Dalla
+Riva \& Stouffer 2016; Mora \emph{et al.} 2018), strong evolutionary
+signature on prey choice (Stouffer \emph{et al.} 2012), and strong
+phylogenetic signature in food web intervality (Eklöf \& Stouffer 2016).
+Phylogenetic reconstruction has also previously been used within the
+context of ecological networks, namely understanding ancestral
+plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
+these considerations suggest that phylogenies can reliably be used to
+transfer knowledge on species interactions.
 
@@
 
-There is a plurality of measures of species similarities that can be
-used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla
-\emph{et al.} 2015); however, phylogenetic proximity has several
-desirable properties when working at large scales. Gerhold \emph{et al.}
-(2015) made the point that phylogenetic signal captures diversification
-of characters (large macro-evolutionary process), but not necessarily
-community assembly (fine ecological process); Dormann \emph{et al.}
-(2010) previously found very similar conclusions. Interactions tend
-reflect a phylogenetic signal because they have a conserved pattern of
-evolutionary convergence that encompasses a wide range of ecological and
-evolutionary mechanisms (Cavender-Bares \emph{et al.} 2009; Mouquet
-\emph{et al.} 2012), and - most importantly - retain this signal even
-when it is not detectable at the community scale (Hutchinson \emph{et
-al.} 2017; Poisot \& Stouffer 2018). Finally, species interactions at
-macro-ecological scales seem to respond mostly to macro-evolutionary
-processes (Price 2003); which is evidenced by the presence of conserved
-backbones in food webs (Dalla Riva \& Stouffer 2016), strong
-evolutionary signature on prey choice (Stouffer \emph{et al.} 2012), and
-strong phylogenetic signature in food web intervality (Eklöf \& Stouffer
-2016). Phylogenetic reconstruction has also previously been used within
-the context of ecological networks, namely understanding ancestral
-plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
-these considerations suggest that phylogenies can reliably be used to
-transfer knowledge on species interactions.
-
-Our case study shows that phylogenetic transfer learning is indeed an
-effective approach to predict the Canadian mammalian metaweb. This
-showcases that although the components (species) that make up the
-Canadian and European communities may be \emph{minimally} shared, if the
-medium (proxy space) selected in the transfer step is biologically
-plausible, we can still effectively learn from the known network and
-make biologically relevant predictions of interactions. It should be
-reiterated that the framework presented in fig.~\ref{fig:concept} is
-amenable to changes; notably, the measure of similarity may not be
-phylogeny, and can be replaced by information on foraging (Beckerman
-\emph{et al.} 2006), cell-level mechanisms (Boeckaerts \emph{et al.}
-2021), or a combination of traits and phylogenetic structure (Stock
-2021).
+Our methodology is outlined in fig.~\ref{fig:concept}, where we provide
+an illustration based on learning the embedding of a metaweb of trophic
+interactions for European mammals (known interactions; Maiorano \emph{et
+al.} 2020b, a) and, based on phylogenetic relationships between mammals
+globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.} 2019),
+infer a metaweb for the Canadian mammalian species pool (interactions
+are treated as unknown in this instance). Following the definition of
+Dunne (2006), a metaweb is a network analogue to the regional species
+pool; specifically, it is an inventory of all \emph{potential}
+interactions between species from a spatially delimited area (and so
+captures the \(\gamma\) diversity of interactions). The metaweb is,
+therefore, \emph{not} a prediction of the food web at a specific locale
+within the spatial area it covers, and will have a different structure
+(notably by having a larger connectance; see \emph{e.g.} Wood \emph{et
+al.} 2015). These local food webs (which captures the \(\alpha\)
+diversity of interactions) are a subset of the metaweb's species and
+interactions, and have been called ``metaweb realizations'' (Poisot
+\emph{et al.} 2015). Differences between local food web and their
+metaweb are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others.
+
+Because the metaweb represents the joint effect of functional,
+phylogenetic, and macroecological processes (Morales-Castilla \emph{et
+al.} 2015), it holds valuable ecological information. Specifically, it
+is the ``upper bounds'' on what the composition of the local networks
+can be (see \emph{e.g.} McLeod \emph{et al.} 2021). These local
+networks, in turn, can be reconstructed given appropriate knowledge of
+local species composition, providing information on structure of food
+webs at finer spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel \emph{et al.} 2018), fish trophic
+interactions (Albouy \emph{et al.} 2019), tetrapod trophic interactions
+(O'Connor \emph{et al.} 2020), and crop-pest networks (Grünig \emph{et
+al.} 2020). Whereas the original metaweb definition, and indeed most
+past uses of metawebs, was based on the presence/absence of
+interactions, we focus on \emph{probabilistic} metawebs where
+interactions are represented as the chance of success of a Bernoulli
+trial (see \emph{e.g.} Poisot \emph{et al.} 2016); therefore, not only
+does our method recommend interactions that may exist, it gives each
+interaction a score, allowing us to properly weigh them.
+
+Our case study shows that phylogenetic transfer learning is an effective
+approach to the generation of probabilistic metawebs. This showcases
+that although the components (species) that make up the Canadian and
+European communities may be \emph{minimally} shared (the overall species
+overlap is less than 4\%), if the medium (proxy space) selected in the
+transfer step is biologically plausible, we can still effectively learn
+from the known network and make biologically relevant predictions of
+interactions. Indeed, as we detail in the results, when validated
+against known but fractional data of trophic interactions between
+Canadian mammals, our model achieves a predictive accuracy of
+approximately 91\%. It should be reiterated that the framework presented
+in fig.~\ref{fig:concept} is amenable to changes; notably, the measure
+of similarity may not be phylogeny, and can be replaced by information
+on foraging (Beckerman \emph{et al.} 2006), cell-level mechanisms
+(Boeckaerts \emph{et al.} 2021), or a combination of traits and
+phylogenetic structure (Stock 2021). Most importantly, although we focus
+on a trophic system, it is an established fact that different
+(non-trophic) interactions do themselves interact with and influence the
+outcome of trophic interactions (Kéfi \emph{et al.} 2012; see
+\emph{e.g.} Kawatsu \emph{et al.} 2021). Future development of metaweb
+inference techniques should cover the prediction of multiple interaction
+types.
 
@@
 We use data from the European metaweb assembled by Maiorano \emph{et
-al.} (2020b), following the definition of the metaweb first introduced
-by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
-within species from a spatially delimited pool. Notably the metaweb is
-not a prediction of the food web at any specific locale within the
-frontiers of the species pool -- in fact, these local food webs are
-expected to have a subset of both the species and the interactions of
-their metaweb (Poisot \emph{et al.} 2012). This being said, as the
-metaweb represents the total of functional, phylogenetic, and
-macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
-thus still worthy of ecological attention. We deduced the subgraph
-corresponding to all mammals by matching species names in the original
-network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
-retaining all those who matched to mammals. This serves a dual purpose
-1) to extract only mammals from the European network and 2) to match and
-standardize species names when aggregating the different data sources
-further downstream (which is an important consideration when combining
-datasets (Grenié \emph{et al.} 2021)). All nodes had valid matches to
-GBIF at this step, and so this backbone is used for all name
-reconciliation steps as outlined below.
+al.} (2020b). This was assembled using data extracted from scientific
+literature (including published papers, books, and grey literature) from
+the last 50 years and includes all terrestrial tetrapods (mammals,
+breeding birds, reptiles and amphibians) occurring on the European
+sub-continent (and Turkey) - with the caveat that only species
+introduced in historical times and currently naturalized being included.
+This metaweb itself is a network of binary (\emph{i.e.}
+presence/absence), potential two-way interactions between species pairs.
+
+We filtered down the European metaweb to create a subgraph corresponding
+to all mammals by matching species names in the original network to the
+Global Biodiversity Information Facility (GBIF) taxonomic backbone (GBIF
+Secretariat 2021) and retaining all those who matched to mammals. This
+serves a dual purpose 1) to extract only mammals from the European
+network and 2) to match and standardize species names when aggregating
+the different data sources further downstream (which is an important
+consideration when combining datasets (Grenié \emph{et al.} 2021)). All
+nodes had valid matches to GBIF at this step, and so this backbone is
+used for all name reconciliation steps as outlined below.
 
@@
 (t-SVD; Halko \emph{et al.} 2011) to generate latent traits representing
-a low-dimensional embedding of the network; these traits give an
-unbiased estimate of the node's position in the latent feature spaces.
-Then, we map these latent traits onto a reference phylogeny (other
-distance-based measures of species proximity that allow for the
-inference of features in the latent space can be used, for example the
-dissimilarity in functional traits). Based on the reconstructed latent
-traits for species in the destination species pool, a Random Dot Product
-Graph model (hereafter RDPG; Young \& Scheinerman 2007) predicts the
-interaction between species through a function of the nodes' features
-through matrix multiplication. Thus, from latent traits and node
-position, we can infer interactions.
+a low-dimensional embedding of the network. As an aside, most ecologists
+are indirectly familiar with SVD: Principal Component Analysis is a
+special case of SVD, which is more sensitive to numerical instabilities
+(see notably Shlens 2014). The latent traits give an unbiased estimate
+of the node's position in the latent feature spaces and can be mapped
+onto a reference phylogeny (other distance-based measures of species
+proximity that allow for the inference of features in the latent space
+can be used, for example the dissimilarity in functional traits). Based
+on the reconstructed latent traits for species in the destination
+species pool, a Random Dot Product Graph model (hereafter RDPG; Young \&
+Scheinerman 2007) predicts the interaction between species through a
+function of the nodes' features through matrix multiplication. Thus,
+from latent traits and node position, we can infer interactions.
+
+The method we develop is, ecologically speaking, a ``black box,''
+\emph{i.e.} an algorithm that can be understood mathematically, but
+whose component parts are not always directly tied to ecological
+processes. There is a growing realization in machine learning that
+(unintentional) black box algorithms are not necessarily a bad thing
+(Holm 2019), as long as their constituent parts can be examined (which
+is the case with our method). But more importantly, data hold more
+information than we might think; as such, even algorithms that are
+disconnected from the model can make correct guesses most of the time
+(Halevy \emph{et al.} 2009); in fact, in an instance of ecological
+forecasting of spatio-temporal systems, model-free approaches
+(\emph{i.e.} drawing all of their information from the data)
+outperformed model-informed ones (Perretti \emph{et al.} 2013).
 
@@
 signal, and to capture the evolutionary backbone of food webs (Dalla
-Riva \& Stouffer 2016). In addition, recent advances show that the
-latent variables produced this way can be used to predict \emph{de novo}
-network edges (\emph{i.e.} interactions; Runghen \emph{et al.} 2021).
+Riva \& Stouffer 2016); in other words, the latent variables of an RDPG
+can be mapped onto a phylogenetic tree, and phylogenetically similar
+predators should share phylogenetically similar preys. In addition,
+recent advances show that the latent variables produced this way can be
+used to predict \emph{de novo} network edges. Interestingly, the latent
+variables do not need to be produced by decomposing the network itself;
+in a recent contribution, Runghen \emph{et al.} (2021) showed that deep
+artificial neural networks are able to reconstruct the left and right
+subspaces of an RDPG, in order to predict human movement networks from
+individual/location metadata. This is an exciting opportunity, as it
+opens up the possibility of using additional metadata as predictors.
 
@@
 at which we truncate the matrix) containing only non-zero \(\sigma\)
-values. Additionally, \(\mathbf{L}\) is now a \(m \times r\) semi
-unitary matrix and \(\mathbf{R}'\) a \(n \times r\) semi-unitary matrix.
+values. Additionally, \(\mathbf{U}\) is now a \(m \times r\) semi
+unitary matrix and \(\mathbf{V}'\) a \(n \times r\) semi-unitary matrix.
 
@@
 
-A RDPG estimates the probability of observing interactions between nodes
-(species) as a function of the nodes' latent variables. The latent
-variables used for the RDPG, called the left and right subspaces, are
-defined as \(\mathscr{L} = \mathbf{L}\sqrt{\mathbf{\Sigma}}\), and
-\(\mathscr{R} = \sqrt{\mathbf{\Sigma}}\mathbf{R}\) -- using the full
-rank of \(\mathbf{A}\), \(\mathscr{L}\mathscr{R}' = \mathbf{A}\), and
+An RDPG estimates the probability of observing interactions between
+nodes (species) as a function of the nodes' latent variables, and is a
+way to turn a SVD (which decompose one matrix into three) into two
+matrices that can be multiplied to provide an approximation of the
+network. The latent variables used for the RDPG, called the left and
+right subspaces, are defined as
+\(\mathscr{L} = \mathbf{U}\sqrt{\mathbf{\Sigma}}\), and
+\(\mathscr{R} = \sqrt{\mathbf{\Sigma}}\mathbf{V}'\) -- using the full
+rank of \(\mathbf{A}\), \(\mathscr{L}\mathscr{R} = \mathbf{A}\), and
 using any smaller rank results in
-\(\mathscr{L}\mathscr{R}' \approx \mathbf{A}\). Using a rank of 1 for
-the t-SVD provides a first-order approximation of the network.
+\(\mathscr{L}\mathscr{R} \approx \mathbf{A}\). Using a rank of 1 for the
+t-SVD provides a first-order approximation of the network. One advantage
+of using a RDPG rather than a SVD is that the number of components to
+estimate decreases; notably, one does not have to estimate the singular
+values of the SVD. Furthermore, the two subspaces can be directly
+multiplied to yield a network.
 
@@
 (1950)); the resulting cutoff was 0.22, and gave an accuracy above 0.99.
+In Supp. Mat. 1, we provide several lines of evidence that using the
+entire network to estimate the threshold does not lead to overfitting;
+that using a subset of species would yield the same threshold; that
+decreasing the quality of the original data by adding of removing
+interactions would minimally affect the predictive accuracy of RDPG
+applied to the European metaweb; and that the networks reconstructed
+from artificially modified data are reconstructed with the correct
+ecological properties.
 
@@
 reconstruction for all species (conceptually something akin to a
-trait-based mammalian phylogeny using generality and vulnerability
-traits) and allows us to impute the missing (latent) trait data for the
-Canadian species that are not already in the European network; as we are
-focused on predicting contemporary interactions, we only retained the
-values for the tips of the tree. We assumed that all traits (\emph{i.e.}
-the feature vectors for the left and right subspaces) were independent,
-which is a reasonable assumption as every trait/dimension added to the
-t-SVD has an \emph{additive} effect to the one before it. Note that the
-Upham \emph{et al.} (2019) tree itself has some uncertainty associated
-to inner nodes of the phylogeny. In this case study, we have decided to
-not propagate this uncertainty, as it would complexify the process. The
-Brownian motion algorithm returns the \emph{average} value of the trait,
-and its upper and lower bounds. Because we do not estimate other
-parameters of the traits' distributions, we considered that every
-species trait is represented as a uniform distribution between these
-bounds; in a situation where the algorithm would return point values for
-all simulations, one could in theory either estimate the parameters of a
-distribution for each tip, or draw randomly from the outputs. In all
-cases, the inferred left and right sub-spaces for the Canadian species
-pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have entries that
-are distributions, representing the range of values for a given species
-at a given dimension.
+trait-based mammalian phylogeny using latent generality and
+vulnerability traits) and allows us to impute the missing (latent) trait
+data for the Canadian species that are not already in the European
+network; as we are focused on predicting contemporary interactions, we
+only retained the values for the tips of the tree. We assumed that all
+traits (\emph{i.e.} the feature vectors for the left and right
+subspaces) were independent, which is a reasonable assumption as every
+trait/dimension added to the t-SVD has an \emph{additive} effect to the
+one before it. Note that the Upham \emph{et al.} (2019) tree itself has
+some uncertainty associated to inner nodes of the phylogeny. In this
+case study, we have decided to not propagate this uncertainty, as it
+would complexify the process. The Brownian motion algorithm returns the
+\emph{average} value of the trait, and its upper and lower bounds.
+Because we do not estimate other parameters of the traits'
+distributions, we considered that every species trait is represented as
+a uniform distribution between these bounds. The choice of the uniform
+distribution was made because the algorithm returns a minimum and
+maximum point estimate for the value, and given this information, the
+uniform distribution is the one with maximum entropy. Had all mean
+parameters estimates been positive, the exponential distribution would
+have been an alternative, but this is not the case for the subspaces of
+an RDPG. In order to examine the consequences of the choice of
+distribution, we estimated the variance per latent variable per node to
+use a Normal distribution; as we show in Supp. Mat. 2, this decision
+results in dramatically over-estimating the number and probability of
+interactions, and therefore we keep the discussions in the main text to
+the uniform case. The inferred left and right subspaces for the Canadian
+species pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have
+entries that are distributions, representing the range of values for a
+given species at a given dimension.
 
@@
 
+It must be noted that despite bringing in a large amount of information
+from the European species pool and interactions, the Canadian metaweb
+has distinct structural properties. Following an approach similar to
+Vermaat \emph{et al.} (2009), we show in Supp. Mat. 3 that not only can
+we observe differences in a multivariate space between the European and
+Canadian metaweb, we can also observe differences in the same space
+between random subgraphs from these networks. These results line up with
+the studies spatializing metawebs that have been discussed in the
+introduction: changes in the species pool are driving local structural
+changes in the networks.
+
 \hypertarget{data-cleanup-discovery-validation-and-thresholding}{%
@@
 Nevertheless, should the predictive model work, we would expect that a
-majority of interactions known to GLOBI would also be predicted. After
-performing this check, we set the probability of all interactions known
-to GLOBI (366 in total, 33 of which were not predicted by the model, for
-a success rate of 91\%) to 1.
+majority of interactions known to GLoBI would also be predicted. We
+retrieved 366 interactions between mammals from the Canadian species
+pool from GLoBI, 33 of which were not predicted by the model; this
+results in a success rate of 91\%. After performing this check, we set
+the probability of all interactions known to GLoBI to 1.
 
@@
 plausible based on the species' evolutionary history, however some
-interactions would not be realized due to human impact.
-
-Cirtwill \emph{et al.} (2019) previously made the point that network
-inference techniques based on Bayesian approaches would perform far
-better in the presence of an interaction-level informative prior; the
-desirable properties of such a prior would be that it is expressed as a
-probability, preferably representing a Bernoulli event, the value of
-which would be representative of relevant biological processes
+interactions would/would not be realized due to human impact.
+
+Dallas \emph{et al.} (2017) suggested that most links in ecological
+networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
+observe. This argument essentially echoes Jordano (2016b): the sampling
+of ecological interactions is difficult because it requires first the
+joint observation of two species, and then the observation of their
+interaction. In addition, it is generally expected that weak or rare
+links would be more common in networks (Csermely 2004), compared to
+strong, persistent links; this is notably the case in food chains,
+wherein many weaker links are key to the stability of a system (Neutel
+\emph{et al.} 2002). In the light of these observations, the results in
+fig.~\ref{fig:inflation} are not particularly surprising: we expect to
+see a surge in these low-probability interactions under a model that has
+a good predictive accuracy. Because the predictions we generate are by
+design probabilistic, then one can weigh these rare links appropriately.
+In a sense, that most ecological interactions are elusive can call for a
+slightly different approach to sampling: once the common interactions
+are documented, the effort required in documenting each rare interaction
+may increase exponentially. Recent proposals suggest that machine
+learning algorithms, in these situations, can act as data generators
+(Hoffmann \emph{et al.} 2019): in this perspective, high quality
+observational data can be supplemented with synthetic data coming from
+predictive models, which increases the volume of information available
+for inference. Indeed, Strydom \emph{et al.} (2021a) suggested that
+knowing the metaweb may render the prediction of local networks easier,
+because it fixes an ``upper bound'' on which interactions can exist;
+indeed, with a probabilistic metaweb, we can consider that the metaweb
+represents an aggregation of informative priors on the interactions.
+
+Related to the last point, Cirtwill \emph{et al.} (2019) showed that
+network inference techniques based on Bayesian approaches would perform
+far better in the presence of an interaction-level informative prior;
+the desirable properties of such a prior would be that it is expressed
+as a probability, preferably representing a Bernoulli event, the value
+of which would be representative of relevant biological processes
 (probability of predation in this case). We argue that the probability
@@
 of network comparison at the global scale. In this case study, we have
-embedded the original metaweb using t-SVD, because it lends itself to a
+embedded the original metaweb using t-SVD, because it lends itself to an
 RDPG reconstruction, which is known to capture the consequences of
 evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
-there are others ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
+there are other ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
 Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
@@
 As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, our approach must
-contend with two interesting problems. The first is the limit of the
-metaweb to embed and transfer. If the initial metaweb is too narrow in
-scope, notably from a taxonomic point of view, the chances of finding
-another area with enough related species to make a reliable inference
-decrease. This is notably true if the metaweb is assembled in an area
-with mostly endemic species. Conversely, the metaweb should be reliably
-filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
-species have been examined, either through literature surveys or expert
-elicitation. The second problem is to determine which area should be
-used to infer the new metaweb in, as this determines the species pool
-that must be used. In our application, we focused on the mammals of
-Canada. The upside of this approach is that information at the country
-level is likely to be required by policy makers and stakeholders for
-their biodiversity assessment, as each country tends to set goals at the
+lines around planet-wide problems''; in this regard, our approach (and
+indeed, any inference of a metaweb at large scales) must contend with
+several interesting and interwoven families of problems. The first is
+the limit of the metaweb to embed and transfer. If the initial metaweb
+is too narrow in scope, notably from a taxonomic point of view, the
+chances of finding another area with enough related species to make a
+reliable inference decreases; this would likely be indicated by large
+confidence intervals during ancestral character estimation, but the lack
+of well documented metawebs is currently preventing the development of
+more concrete guidelines. The question of phylogenetic relatedness and
+dispersal is notably true if the metaweb is assembled in an area with
+mostly endemic species, and as with every predictive algorithm, there is
+room for the application of our best ecological judgement. Conversely,
+the metaweb should be reliably filled, which assumes that the \(S^2\)
+interactions in a pool of \(S\) species have been examined, either
+through literature surveys or expert elicitation. Supp. Mat. 1 provides
+some guidance as to the type of sampling effort that should be
+prioritized. Although RDPG was able to maintain very high predictive
+power when interactions were missing, the addition of false positive
+interactions was immediately detected; this suggests that it may be
+appropriate to err on the side of ``too many'' interactions when
+constructing the initial metaweb to be transferred. The second series of
+problems are related to determining which area should be used to infer
+the new metaweb in, as this determines the species pool that must be
+used. In our application, we focused on the mammals of Canada. The
+upside of this approach is that information at the country level is
+likely to be required by policy makers and stakeholders for their
+biodiversity assessment, as each country tends to set goals at the
 national level (Buxton \emph{et al.} 2021) for which quantitative
 instruments are designed (Turak \emph{et al.} 2017), with specific
-strategies often enacted at smaller scales (Ray \emph{et al.} 2021). Yet
-these national divisions, in large parts of the world, reflect nothing
-except for the legacy of settler colonialism, and operating under them
-must be done under the clear realization that they contributed to the
-ongoing biodiversity crisis (Adam 2014), can reinforce environmental
-injustice (Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
-especially, will probably end up being replaced by Indigenous principles
-of land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
-2021).
+strategies often enacted at smaller scales (Ray \emph{et al.} 2021). And
+yet, we do not really have a satisfying answer to the question of
+``where does a food web stop?''; the current most satisfying solutions
+involve examining the spatial consistency of network area relationships
+(see \emph{e.g.} Galiana \emph{et al.} 2018, 2019, 2021; Fortin \emph{et
+al.} 2021), which is of course impossible in the absence of enough
+information about the network itself. This suggests that an \emph{a
+posteriori} refinement of the results may be required, based on a
+downscaling of the metaweb. The final family of problems relates less to
+the availability of data or quantitative tools, and more to the praxis
+of spatial ecology. Operating under the context of national divisions,
+in large parts of the world, reflects nothing more than the legacy of
+settler colonialism. Indeed, the use of ecological data is not an
+apolitical act (Nost \& Goldstein 2021), as data infrastructures tend to
+be designed to answer questions within national boundaries, and their
+use both draws upon and reinforces territorial statecraft; as per Machen
+\& Nost (2021), this is particularly true when the output of
+``algorithmic thinking'' (\emph{e.g.} relying on machine learning to
+generate knowledge) can be re-used for governance (\emph{e.g.} enacting
+conservation decisions at the national scale). We therefore recognize
+that methods such as we propose operate under the framework that
+contributed to the ongoing biodiversity crisis (Adam 2014), reinforced
+environmental injustice (Choudry 2013; Domínguez \& Luoma 2020), and on
+Turtle Island especially, should be replaced by Indigenous principles of
+land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
+2021). As we see AI/ML being increasingly mobilized to generate
+knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
+\emph{et al.} 2019; Mosebo Fernandes \emph{et al.} 2020), our discussion
+of these tools need to go beyond the technical, and into the governance
+consequences they can have.
 
@@
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, A.R., Eklf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
-A quantitative framework for investigating the reliability of empirical
+Cirtwill, A.R., Ekl, A., Roslin, T., Wootton, K. \& Gravel, D. (2019). A
+quantitative framework for investigating the reliability of empirical
 network construction. \emph{Methods in Ecology and Evolution}, 0.
@@
 125, 446--456.
+
+\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
+Dallas, T., Park, A.W. \& Drake, J.M. (2017). Predicting cryptic links
+in host-parasite networks. \emph{PLOS Computational Biology}, 13,
+e1005557.
 
@@
 
+\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
+Fortin, M.-J., Dale, M.R.T. \& Brimacombe, C. (2021). Network ecology in
+dynamic landscapes. \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 288, rspb.2020.1889, 20201889.
+
+\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
+Galiana, N., Barros, C., Braga, J., Ficetola, G.F., Maiorano, L.,
+Thuiller, W., \emph{et al.} (2021). The spatial scaling of food web
+structure across European biogeographical regions. \emph{Ecography},
+n/a.
+
+\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
+Galiana, N., Hawkins, B.A. \& Montoya, J.M. (2019). The geographical
+variation of network structure is scale dependent: Understanding the
+biotic specialization of hostparasitoid networks. \emph{Ecography}, 42,
+1175--1187.
+
+\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
+Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
+Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
+interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.
+
 \leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
@@
 Ancestral State Reconstruction. \emph{Systematic Biology}, 61, 533--538.
+
+\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
+Machen, R. \& Nost, E. (2021). Thinking algorithmically: The making of
+hegemonic knowledge in climate governance. \emph{Transactions of the
+Institute of British Geographers}, 46, 555--569.
 
@@
 
-\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
+\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
 Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
@@
 
+\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
+McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
+M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
+of spatial multi-trophic networks. \emph{Oikos}, n/a.
+
+\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
+Mora, B.B., Gravel, D., Gilarranz, L.J., Poisot, T. \& Stouffer, D.B.
+(2018). Identifying a common backbone of interactions underlying food
+webs from different ecosystems. \emph{Nature Communications}, 9, 2603.
+
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
@@
 
+\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
+Mosebo Fernandes, A.C., Quintero Gonzalez, R., Lenihan-Clarke, M.A.,
+Leslie Trotter, E.F. \& Jokar Arsanjani, J. (2020). Machine Learning for
+Conservation Planning in a Changing Climate. \emph{Sustainability}, 12,
+7657.
+
 \leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
@@
 
+\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
+Nost, E. \& Goldstein, J.E. (2021). A political ecology of data.
+\emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
@@
 Distribution. \emph{Journal of Statistical Physics}, 173, 806--844.
+
+\leavevmode\hypertarget{ref-Vermaat2009MajDim}{}%
+Vermaat, J.E., Dunne, J.A. \& Gilbert, A.J. (2009). Major dimensions in
+food-web structure properties. \emph{Ecology}, 90, 278--282.
+
+\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
+Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, 5, 3769--3782.
 

### 2021-11-03 scripts/wordcount.sh
abstract

@@ -1,0 +1,1 @@
+pandoc README.md -o _wc.docx --variable suppress-bibliography=true  --citeproc --bibliography=references.bib

### 2021-11-03 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@fc8297696fc28950cf3e4169b1fe815ccd7c9ca4 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@f43705e294b97501d82ade71305b5b18023fb583 🚀

@@
 \vfill
-Despite their importance in many ecological processes, collecting data
-and information on ecological interactions is an exceedingly challenging
-task. For this reason, large parts of the world have a data deficit when
-it comes to species interactions, and how the resulting networks are
-structured. As data collection alone is unlikely to be sufficient,
-community ecologists must adopt predictive methods. Here we develop such
-a method, relying on graph embedding and transfer learning to assemble a
-predicted list of trophic interactions between Canadian mammals. This
-interaction list is derived from the European food web, despite sharing
-only 5\% of common species with Canada. The results of the predictive
-model are compared against databases of recorded pairwise interactions,
-showing that we correctly recover over 95\% of known interactions. We
-provide guidance on how this method can be adapted by substituting some
-approaches or predictors in order to make it more generally applicable.
+
+\begin{enumerate}
+    \itemDespite their importance in many ecological processes,
+collecting data and information on ecological interactions is an
+exceedingly challenging task. For this reason, large parts of the world
+have a data deficit when it comes to species interactions, and how the
+resulting networks are structured. As data collection alone is unlikely
+to be sufficient, community ecologists must adopt predictive methods.%
+    \itemWe present a methodological framework that uses graph embedding
+and transfer learning to assemble a predicted list of trophic
+interactions of a species pool for which their interactions are unknown.
+Specifically, we `learn' the information from a known interaction
+network by inferring the latent traits of species and infer the latent
+traits of a species pool for which we have no \emph{a priori}
+interaction data based on their phylogenetic relatedness to species from
+the known network. The latent traits can then be used to predict
+interactions and construct and interaction network.%
+    \itemHere we assembled a metaweb for Canadian mammals derived from
+interactions in the European food web, despite only 4\% of common
+species being shared between the two locations. The results of the
+predictive model are compared against databases of recorded pairwise
+interactions, showing that we correctly recover 91\% of known
+interactions.%
+    \itemThe framework itself is robust even when the known network is
+incomplete or contains spurious interactions making it an ideal
+candidate as a tool for filling gaps when it comes to species
+interactions. We provide guidance on how this frameworl can be adapted
+by substituting some approaches or predictors in order to make it more
+generally applicable.%
+\end{enumerate}
 
@@
 understanding of ecological networks across space, particularly at
-macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
-2016). First, networks within a location are difficult to sample
-properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
-shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
-about inter and intra specific relationships. This first challenge has
-been, in large part, addressed by the recent emergence of a suite of
-methods aiming to predict interactions within \emph{existing} networks,
-many of which are reviewed in Strydom \emph{et al.} (2021a). Second,
-recent analyses based on collected data (Poisot \emph{et al.} 2021a) or
-metadata (Cameron \emph{et al.} 2019) highlight that ecological networks
-are currently studied in a biased subset of space and bioclimates, which
-impedes our ability to generalize any local understanding of network
-structure. Meaning that, although the framework to address
-incompleteness \emph{within} networks exists, there would still be
-regions for which, due to a \emph{lack} of local interaction data, we
-are unable to infer potential species interactions. Having a general
-solution for inferring a \emph{plausible} metaweb (despite the
-unavailability of interaction data) could be the catalyst for
+macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen,
+2016). First, ecological networks within a location are difficult to
+sample properly (Jordano, 2016a, 2016b), resulting in a widespread
+``Eltonian shortfall'' (Hortal et al., 2015), \emph{i.e.} a lack of
+knowledge about inter- and intra- specific relationships. This first
+challenge has been, in large part, addressed by the recent emergence of
+a suite of methods aiming to predict interactions within \emph{existing}
+networks, many of which are reviewed in Strydom, Catchen, et al. (2021).
+Second, recent analyses based on collected data (Poisot, Bergeron, et
+al., 2021) or metadata (Cameron et al., 2019) highlight that ecological
+networks are currently studied in a biased subset of space and
+bioclimates, which impedes our ability to generalize any local
+understanding of network structure. Meaning that, although the framework
+to address incompleteness \emph{within} networks exists, there would
+still be regions for which, due to a \emph{lack} of local interaction
+data, we are unable to infer potential species interactions. Having a
+general solution for inferring \emph{potential} interactions (despite
+the unavailability of interaction data) could be the catalyst for
 significant breakthroughs in our ability to start thinking about species
-interaction networks over large spatial scales.
-
-Here, we present a general method for the transfer learning of network
-representations, relying on the similarities of species in a
+interaction networks over large spatial scales. In a recent overview of
+the field of ecological network prediction, Strydom, Catchen, et al.
+(2021) identified two challenges of interest to the prediction of
+interactions at large scales. First, there is a relative scarcity of
+relevant data in most places globally -- paradoxically, this restricts
+our ability to infer interactions to locations where inference is
+perhaps the least required; second, accurate predictions often demand
+accurate predictors, and the lack of methods that can leverage small
+amount of data is a serious impediment to our predictive ability
+globally.
+
+Here, we present a general method to recommend potential trophic
+interactions, relying on the transfer learning of network
+representations, specifically by using similarities of species in a
 biologically/ecologically relevant proxy space (\emph{e.g.} shared
@@
 methodology that uses the knowledge gained from solving one problem and
-applying it to a related (destination) problem (Pan \& Yang 2010; Torrey
-\& Shavlik 2010). In this instance, we solve the problem of predicting
-trophic interactions between species, based on knowledge extracted from
-another species pool for which interactions are known by using
-phylogenetic structure as a medium for transfer. This allows us to
-construct a \emph{probabilistic} metaweb for a community for which we
-have \emph{no} prior trophic interaction data for the desired species
-pool. Our methodology is outlined in fig.~\ref{fig:concept}, where we
-provide an illustration based on learning the embedding of a metaweb of
-trophic interactions for European mammals (known interactions; Maiorano
-\emph{et al.} 2020b, a) and, based on phylogenetic relationships between
-mammals globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.}
-2019), infer a metaweb for the Canadian mammalian species pool
-(interactions are treated as unknown in this instance).
+applying it to a related (destination) problem (Pan \& Yang, 2010;
+Torrey \& Shavlik, 2010). In this instance, we solve the problem of
+predicting trophic interactions between species, based on knowledge
+extracted from another species pool for which interactions are known by
+using phylogenetic structure as a medium for transfer. There is a
+plurality of measures of species similarities that can be used for
+inferring \emph{potential} species interactions \emph{i.e.} metaweb
+reconstruction (see \emph{e.g.} Morales-Castilla et al., 2015); however,
+phylogenetic proximity has several desirable properties when working at
+large scales. Gerhold et al. (2015) made the point that phylogenetic
+signal captures diversification of characters (large macro-evolutionary
+process), but not necessarily community assembly (fine ecological
+process); Dormann et al. (2010) previously found very similar
+conclusions. Interactions tend to reflect a phylogenetic signal because
+they have a conserved pattern of evolutionary convergence that
+encompasses a wide range of ecological and evolutionary mechanisms
+(Cavender-Bares et al., 2009; Mouquet et al., 2012), and - most
+importantly - retain this signal even when it is not detectable at the
+community scale (Hutchinson et al., 2017; Poisot \& Stouffer, 2018).
+Finally, species interactions at macro-ecological scales seem to respond
+mostly to macro-evolutionary processes (Price, 2003); which is evidenced
+by the presence of conserved backbones in food webs (Dalla Riva \&
+Stouffer, 2016; Mora et al., 2018), strong evolutionary signature on
+prey choice (Stouffer et al., 2012), and strong phylogenetic signature
+in food web intervality (Eklöf \& Stouffer, 2016). Phylogenetic
+reconstruction has also previously been used within the context of
+ecological networks, namely understanding ancestral plant-insect
+interactions (Braga et al., 2021). Taken together, these considerations
+suggest that phylogenies can reliably be used to transfer knowledge on
+species interactions.
 
@@
 
-There is a plurality of measures of species similarities that can be
-used for metaweb reconstruction (see \emph{e.g.} Morales-Castilla
-\emph{et al.} 2015); however, phylogenetic proximity has several
-desirable properties when working at large scales. Gerhold \emph{et al.}
-(2015) made the point that phylogenetic signal captures diversification
-of characters (large macro-evolutionary process), but not necessarily
-community assembly (fine ecological process); Dormann \emph{et al.}
-(2010) previously found very similar conclusions. Interactions tend
-reflect a phylogenetic signal because they have a conserved pattern of
-evolutionary convergence that encompasses a wide range of ecological and
-evolutionary mechanisms (Cavender-Bares \emph{et al.} 2009; Mouquet
-\emph{et al.} 2012), and - most importantly - retain this signal even
-when it is not detectable at the community scale (Hutchinson \emph{et
-al.} 2017; Poisot \& Stouffer 2018). Finally, species interactions at
-macro-ecological scales seem to respond mostly to macro-evolutionary
-processes (Price 2003); which is evidenced by the presence of conserved
-backbones in food webs (Dalla Riva \& Stouffer 2016), strong
-evolutionary signature on prey choice (Stouffer \emph{et al.} 2012), and
-strong phylogenetic signature in food web intervality (Eklöf \& Stouffer
-2016). Phylogenetic reconstruction has also previously been used within
-the context of ecological networks, namely understanding ancestral
-plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
-these considerations suggest that phylogenies can reliably be used to
-transfer knowledge on species interactions.
-
-Our case study shows that phylogenetic transfer learning is indeed an
-effective approach to predict the Canadian mammalian metaweb. This
-showcases that although the components (species) that make up the
-Canadian and European communities may be \emph{minimally} shared, if the
-medium (proxy space) selected in the transfer step is biologically
-plausible, we can still effectively learn from the known network and
-make biologically relevant predictions of interactions. It should be
-reiterated that the framework presented in fig.~\ref{fig:concept} is
-amenable to changes; notably, the measure of similarity may not be
-phylogeny, and can be replaced by information on foraging (Beckerman
-\emph{et al.} 2006), cell-level mechanisms (Boeckaerts \emph{et al.}
-2021), or a combination of traits and phylogenetic structure (Stock
-2021).
+Our methodology is outlined in fig.~\ref{fig:concept}, where we provide
+an illustration based on learning the embedding of a metaweb of trophic
+interactions for European mammals (known interactions; Maiorano et al.,
+2020a, 2020b) and, based on phylogenetic relationships between mammals
+globally (\emph{i.e.}, phylogenetic tree Upham et al., 2019), infer a
+metaweb for the Canadian mammalian species pool (interactions are
+treated as unknown in this instance). Following the definition of Dunne
+(2006), a metaweb is a network analogue to the regional species pool;
+specifically, it is an inventory of all \emph{potential} interactions
+between species from a spatially delimited area (and so captures the
+\(\gamma\) diversity of interactions). The metaweb is, therefore,
+\emph{not} a prediction of the food web at a specific locale within the
+spatial area it covers, and will have a different structure (notably by
+having a larger connectance; see \emph{e.g.} Wood et al., 2015). These
+local food webs (which captures the \(\alpha\) diversity of
+interactions) are a subset of the metaweb's species and interactions,
+and have been called ``metaweb realizations'' (Poisot et al., 2015).
+Differences between local food web and their metaweb are due to chance,
+species abundance and co-occurrence, local environmental conditions, and
+local distribution of functional traits, among others.
+
+Because the metaweb represents the joint effect of functional,
+phylogenetic, and macroecological processes (Morales-Castilla et al.,
+2015), it holds valuable ecological information. Specifically, it is the
+``upper bounds'' on what the composition of the local networks can be
+(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
+can be reconstructed given appropriate knowledge of local species
+composition, providing information on structure of food webs at finer
+spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
+interactions (Albouy et al., 2019), tetrapod trophic interactions
+(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
+Whereas the original metaweb definition, and indeed most past uses of
+metawebs, was based on the presence/absence of interactions, we focus on
+\emph{probabilistic} metawebs where interactions are represented as the
+chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
+2016); therefore, not only does our method recommend interactions that
+may exist, it gives each interaction a score, allowing us to properly
+weigh them.
+
+Our case study shows that phylogenetic transfer learning is an effective
+approach to the generation of probabilistic metawebs. This showcases
+that although the components (species) that make up the Canadian and
+European communities may be \emph{minimally} shared (the overall species
+overlap is less than 4\%), if the medium (proxy space) selected in the
+transfer step is biologically plausible, we can still effectively learn
+from the known network and make biologically relevant predictions of
+interactions. Indeed, as we detail in the results, when validated
+against known but fractional data of trophic interactions between
+Canadian mammals, our model achieves a predictive accuracy of
+approximately 91\%. It should be reiterated that the framework presented
+in fig.~\ref{fig:concept} is amenable to changes; notably, the measure
+of similarity may not be phylogeny, and can be replaced by information
+on foraging (Beckerman et al., 2006), cell-level mechanisms (Boeckaerts
+et al., 2021), or a combination of traits and phylogenetic structure
+(Stock, 2021). Most importantly, although we focus on a trophic system,
+it is an established fact that different (non-trophic) interactions do
+themselves interact with and influence the outcome of trophic
+interactions (see \emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012).
+Future development of metaweb inference techniques should cover the
+prediction of multiple interaction types.
 
@@
 
-We use data from the European metaweb assembled by Maiorano \emph{et
-al.} (2020b), following the definition of the metaweb first introduced
-by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
-within species from a spatially delimited pool. Notably the metaweb is
-not a prediction of the food web at any specific locale within the
-frontiers of the species pool -- in fact, these local food webs are
-expected to have a subset of both the species and the interactions of
-their metaweb (Poisot \emph{et al.} 2012). This being said, as the
-metaweb represents the total of functional, phylogenetic, and
-macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
-thus still worthy of ecological attention. We deduced the subgraph
-corresponding to all mammals by matching species names in the original
-network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
-retaining all those who matched to mammals. This serves a dual purpose
-1) to extract only mammals from the European network and 2) to match and
-standardize species names when aggregating the different data sources
-further downstream (which is an important consideration when combining
-datasets (Grenié \emph{et al.} 2021)). All nodes had valid matches to
-GBIF at this step, and so this backbone is used for all name
-reconciliation steps as outlined below.
+We use data from the European metaweb assembled by Maiorano et al.
+(2020a). This was assembled using data extracted from scientific
+literature (including published papers, books, and grey literature) from
+the last 50 years and includes all terrestrial tetrapods (mammals,
+breeding birds, reptiles and amphibians) occurring on the European
+sub-continent (and Turkey) - with the caveat that only species
+introduced in historical times and currently naturalized being included.
+This metaweb itself is a network of binary (\emph{i.e.}
+presence/absence), potential two-way interactions between species pairs.
+
+We filtered down the European metaweb to create a subgraph corresponding
+to all mammals by matching species names in the original network to the
+Global Biodiversity Information Facility (GBIF) taxonomic backbone (GBIF
+Secretariat, 2021) and retaining all those who matched to mammals. This
+serves a dual purpose 1) to extract only mammals from the European
+network and 2) to match and standardize species names when aggregating
+the different data sources further downstream (which is an important
+consideration when combining datasets (Grenié et al., 2021)). All nodes
+had valid matches to GBIF at this step, and so this backbone is used for
+all name reconciliation steps as outlined below.
 
@@
 transfer; the phylogenetic similarity of mammals here represents the
-information for transfer. We used the mammalian consensus supertree by
-Upham \emph{et al.} (2019), for which all approximatively 6000 names
-have been similarly matched to their GBIF valid names. This step allows
-us to place each node of the mammalian European metaweb in the
-phylogeny.
+information for transfer (\emph{i.e.} the transfer medium). We used the
+mammalian consensus supertree by Upham et al. (2019), for which all
+approximatively 6000 names have been similarly matched to their GBIF
+valid names. This step allows us to place each node of the mammalian
+European metaweb in the phylogeny.
 
@@
 trophic interactions between mammals in Canada. We obtained the list of
-extant species from the IUCN checklist, and selected the terrestrial and
-semi-aquatic species (this corresponds to the same selection that was
-applied by Maiorano \emph{et al.} (2020b) in the European metaweb). The
-IUCN names were, as previously, reconciled against GBIF to have an exact
-match to the taxonomy.
+extant species from the International Union for Conservation of Nature
+(IUCN) checklist, and selected the terrestrial and semi-aquatic species
+(this corresponds to the same selection that was applied by Maiorano et
+al. (2020a) in the European metaweb). The IUCN names were, as
+previously, reconciled against GBIF to have an exact match to the
+taxonomy.
 
@@
 network in Europe, we use a truncated Singular Value Decomposition
-(t-SVD; Halko \emph{et al.} 2011) to generate latent traits representing
-a low-dimensional embedding of the network; these traits give an
-unbiased estimate of the node's position in the latent feature spaces.
-Then, we map these latent traits onto a reference phylogeny (other
-distance-based measures of species proximity that allow for the
-inference of features in the latent space can be used, for example the
-dissimilarity in functional traits). Based on the reconstructed latent
-traits for species in the destination species pool, a Random Dot Product
-Graph model (hereafter RDPG; Young \& Scheinerman 2007) predicts the
-interaction between species through a function of the nodes' features
-through matrix multiplication. Thus, from latent traits and node
-position, we can infer interactions.
+(t-SVD; Halko et al., 2011) to generate latent traits representing a
+low-dimensional embedding of the network. As an aside, most ecologists
+are indirectly familiar with SVD: Principal Component Analysis is a
+special case of SVD, which is more sensitive to numerical instabilities
+(see notably Shlens, 2014). The latent traits give an unbiased estimate
+of the node's position in the latent feature spaces and can be mapped
+onto a reference phylogeny (other distance-based measures of species
+proximity that allow for the inference of features in the latent space
+can be used, for example the dissimilarity in functional traits). Based
+on the reconstructed latent traits for species in the destination
+species pool, a Random Dot Product Graph model (hereafter RDPG; S. J.
+Young \& Scheinerman, 2007) predicts the interaction between species
+through a function of the nodes' features through matrix multiplication.
+Thus, from latent traits and node position, we can infer interactions.
+
+The method we develop is, ecologically speaking, a ``black box,''
+\emph{i.e.} an algorithm that can be understood mathematically, but
+whose component parts are not always directly tied to ecological
+processes. There is a growing realization in machine learning that
+(unintentional) black box algorithms are not necessarily a bad thing
+(Holm, 2019), as long as their constituent parts can be examined (which
+is the case with our method). But more importantly, data hold more
+information than we might think; as such, even algorithms that are
+disconnected from the model can make correct guesses most of the time
+(Halevy et al., 2009); in fact, in an instance of ecological forecasting
+of spatio-temporal systems, model-free approaches (\emph{i.e.} drawing
+all of their information from the data) outperformed model-informed ones
+(Perretti et al., 2013).
 
@@
 
-The entire pipeline is implemented in \emph{Julia} 1.6 (Bezanson
-\emph{et al.} 2017) and is available under the permissive MIT License at
+The entire pipeline is implemented in \emph{Julia} 1.6 (Bezanson et al.,
+2017) and is available under the permissive MIT License at
 \href{https://osf.io/2zwqm/}{\texttt{https://osf.io/2zwqm/}}. The
 taxonomic cleanup steps are done using \texttt{GBIF.jl} (Dansereau \&
-Poisot 2021). The network embedding and analysis is done using
-\texttt{EcologicalNetworks.jl} (Poisot \emph{et al.} 2019; Banville
-\emph{et al.} 2021). The phylogenetic simulations are done using
-\texttt{PhyloNetworks.jl} (Solís-Lemus \emph{et al.} 2017) and
-\texttt{Phylo.jl} (Reeve \emph{et al.} 2016). A complete
-\texttt{Project.toml} file specifying the full tree of dependencies is
-available alongside the code. This material also includes a fully
-annotated copy of the entire code required to run this project
-(describing both the intent of the code and discussing some technical
-implementation details), a vignette for every step of the process, and a
-series of Jupyter notebooks with the text and code. The pipeline can be
-executed on a laptop in a matter of minutes, and therefore does not
-require extensive computational power.
+Poisot, 2021). The network embedding and analysis is done using
+\texttt{EcologicalNetworks.jl} (Banville et al., 2021; Poisot et al.,
+2019). The phylogenetic simulations are done using
+\texttt{PhyloNetworks.jl} (Solís-Lemus et al., 2017) and
+\texttt{Phylo.jl} (Reeve et al., 2016). A complete \texttt{Project.toml}
+file specifying the full tree of dependencies is available alongside the
+code. This material also includes a fully annotated copy of the entire
+code required to run this project (describing both the intent of the
+code and discussing some technical implementation details), a vignette
+for every step of the process, and a series of Jupyter notebooks with
+the text and code. The pipeline can be executed on a laptop in a matter
+of minutes, and therefore does not require extensive computational
+power.
 
@@
 conceptually different from other metaweb-scale predictions (\emph{e.g.}
-Albouy \emph{et al.} 2019), in that the metaweb representation is easily
+Albouy et al., 2019), in that the metaweb representation is easily
 transferable. Specifically, we use RDPG to create a number of latent
@@
 signal, and to capture the evolutionary backbone of food webs (Dalla
-Riva \& Stouffer 2016). In addition, recent advances show that the
-latent variables produced this way can be used to predict \emph{de novo}
-network edges (\emph{i.e.} interactions; Runghen \emph{et al.} 2021).
+Riva \& Stouffer, 2016); in other words, the latent variables of an RDPG
+can be mapped onto a phylogenetic tree, and phylogenetically similar
+predators should share phylogenetically similar preys. In addition,
+recent advances show that the latent variables produced this way can be
+used to predict \emph{de novo} network edges. Interestingly, the latent
+variables do not need to be produced by decomposing the network itself;
+in a recent contribution, Runghen et al. (2021) showed that deep
+artificial neural networks are able to reconstruct the left and right
+subspaces of an RDPG, in order to predict human movement networks from
+individual/location metadata. This is an exciting opportunity, as it
+opens up the possibility of using additional metadata as predictors.
 
@@
 appropriate embedding of ecological networks, which has recently been
-shown to both capture their complex, emerging properties (Strydom
-\emph{et al.} 2021b) and to allow highly accurate prediction of the
-interactions within a single network (Poisot \emph{et al.} 2021b). Under
-SVD, an adjacency matrix \(\mathbf{A}\) (where
+shown to both capture their complex, emerging properties (Strydom, Dalla
+Riva, et al., 2021) and to allow highly accurate prediction of the
+interactions within a single network (Poisot, Ouellet, et al., 2021).
+Under SVD, an adjacency matrix \(\mathbf{A}\) (where
 \(\mathbf{A}_{m,n}\in\mathbb{B}\) where 1 indicates predation and 0 an
 absence thereof) is decomposed into three components resulting in
-\(\mathbf{A} = \mathbf{L}\mathbf{\Sigma}\mathbf{R'}.\) Here,
+\(\mathbf{A} = \mathbf{U}\mathbf{\Sigma}\mathbf{V'}.\) Here,
 \(\mathbf{\Sigma}\) is a \(m \times n\) diagonal matrix and contains
-only singular (\(\sigma\)) values along its diagonal, \(\mathbf{L}\) is
-a \(m \times m\) unitary matrix, and \(\mathbf{R}'\) a \(n \times n\)
+only singular (\(\sigma\)) values along its diagonal, \(\mathbf{U}\) is
+a \(m \times m\) unitary matrix, and \(\mathbf{V}'\) a \(n \times n\)
 unitary matrix. Truncating the SVD removes additional noise in the
@@
 \(\mathbf{\Sigma}\) can show a sharp drop at the rank where noise starts
-(Zhu \& Ghodsi 2006). Because the European metaweb is almost entirely
+(Zhu \& Ghodsi, 2006). Because the European metaweb is almost entirely
 known, the amount of noise (uncertainty) is low; this is reflected in
@@
 European metaweb are all true. Given the methodological details given in
-Maiorano \emph{et al.} (2020b) and O'Connor \emph{et al.} (2020), this
-seems like a reasonable assumption, although one that does not hold for
-all metawebs. We used the thresholding approach presented in Poisot
-\emph{et al.} (2021b), and picked a cutoff that maximized Youden's \(J\)
-statistic (a measure of the informedness (trust) of predictions; Youden
-(1950)); the resulting cutoff was 0.22, and gave an accuracy above 0.99.
+Maiorano et al. (2020a) and O'Connor et al. (2020), this seems like a
+reasonable assumption, although one that does not hold for all metawebs.
+We used the thresholding approach presented in Poisot, Ouellet, et al.
+(2021), and picked a cutoff that maximized Youden's \(J\) statistic (a
+measure of the informedness (trust) of predictions; Youden (1950)); the
+resulting cutoff was 0.22, and gave an accuracy above 0.99. In Supp.
+Mat. 1, we provide several lines of evidence that using the entire
+network to estimate the threshold does not lead to overfitting; that
+using a subset of species would yield the same threshold; that
+decreasing the quality of the original data by adding of removing
+interactions would minimally affect the predictive accuracy of RDPG
+applied to the European metaweb; and that the networks reconstructed
+from artificially modified data are reconstructed with the correct
+ecological properties.
 
@@
 of strong hypotheses about the nature of phylogenetic signal in the
-network decomposition (Litsios \& Salamin 2012). This uses the estimated
-feature vectors for the European mammals to create a state
+network decomposition (Litsios \& Salamin, 2012). This uses the
+estimated feature vectors for the European mammals to create a state
 reconstruction for all species (conceptually something akin to a
-trait-based mammalian phylogeny using generality and vulnerability
-traits) and allows us to impute the missing (latent) trait data for the
-Canadian species that are not already in the European network; as we are
-focused on predicting contemporary interactions, we only retained the
-values for the tips of the tree. We assumed that all traits (\emph{i.e.}
-the feature vectors for the left and right subspaces) were independent,
-which is a reasonable assumption as every trait/dimension added to the
-t-SVD has an \emph{additive} effect to the one before it. Note that the
-Upham \emph{et al.} (2019) tree itself has some uncertainty associated
-to inner nodes of the phylogeny. In this case study, we have decided to
-not propagate this uncertainty, as it would complexify the process. The
-Brownian motion algorithm returns the \emph{average} value of the trait,
-and its upper and lower bounds. Because we do not estimate other
-parameters of the traits' distributions, we considered that every
-species trait is represented as a uniform distribution between these
-bounds; in a situation where the algorithm would return point values for
-all simulations, one could in theory either estimate the parameters of a
-distribution for each tip, or draw randomly from the outputs. In all
-cases, the inferred left and right sub-spaces for the Canadian species
-pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have entries that
-are distributions, representing the range of values for a given species
-at a given dimension.
+trait-based mammalian phylogeny using latent generality and
+vulnerability traits) and allows us to impute the missing (latent) trait
+data for the Canadian species that are not already in the European
+network; as we are focused on predicting contemporary interactions, we
+only retained the values for the tips of the tree. We assumed that all
+traits (\emph{i.e.} the feature vectors for the left and right
+subspaces) were independent, which is a reasonable assumption as every
+trait/dimension added to the t-SVD has an \emph{additive} effect to the
+one before it. Note that the Upham et al. (2019) tree itself has some
+uncertainty associated to inner nodes of the phylogeny. In this case
+study, we have decided to not propagate this uncertainty, as it would
+complexify the process. The Brownian motion algorithm returns the
+\emph{average} value of the trait, and its upper and lower bounds.
+Because we do not estimate other parameters of the traits'
+distributions, we considered that every species trait is represented as
+a uniform distribution between these bounds. The choice of the uniform
+distribution was made because the algorithm returns a minimum and
+maximum point estimate for the value, and given this information, the
+uniform distribution is the one with maximum entropy. Had all mean
+parameters estimates been positive, the exponential distribution would
+have been an alternative, but this is not the case for the subspaces of
+an RDPG. In order to examine the consequences of the choice of
+distribution, we estimated the variance per latent variable per node to
+use a Normal distribution; as we show in Supp. Mat. 2, this decision
+results in dramatically over-estimating the number and probability of
+interactions, and therefore we keep the discussions in the main text to
+the uniform case. The inferred left and right subspaces for the Canadian
+species pool (\(\hat{\mathscr{L}}\) and \(\hat{\mathscr{R}}\)) have
+entries that are distributions, representing the range of values for a
+given species at a given dimension.
 
@@
 Therefore, we can use this information to assemble a
-\emph{probabilistic} metaweb in the sense of Poisot \emph{et al.}
-(2016), \emph{i.e.} in which every interaction is represented as a
-single, independent, Bernoulli event of probability \(p\).
+\emph{probabilistic} metaweb in the sense of Poisot et al. (2016),
+\emph{i.e.} in which every interaction is represented as a single,
+independent, Bernoulli event of probability \(p\).
 
@@
 probably broader than what they would actually be, see \emph{e.g.}
-Garland \emph{et al.} 1999), we repeat the above process
-\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
-where the probability of an interaction (here conveying our degree of
-trust that it exists given the inferred trait distributions) is given by
-the number of times where it appears across all random draws \(N\),
-divided by the number of samples. An interaction with \(P_{i,j} = 1\)
-means that these two species were predicted to interact in all
-\(2\times 10^5\) random draws.
+Garland et al., 1999), we repeat the above process \(2\times 10^5\)
+times, which results in a probabilistic metaweb \(P\), where the
+probability of an interaction (here conveying our degree of trust that
+it exists given the inferred trait distributions) is given by the number
+of times where it appears across all random draws \(N\), divided by the
+number of samples. An interaction with \(P_{i,j} = 1\) means that these
+two species were predicted to interact in all \(2\times 10^5\) random
+draws.
+
+It must be noted that despite bringing in a large amount of information
+from the European species pool and interactions, the Canadian metaweb
+has distinct structural properties. Following an approach similar to
+Vermaat et al. (2009), we show in Supp. Mat. 3 that not only can we
+observe differences in a multivariate space between the European and
+Canadian metaweb, we can also observe differences in the same space
+between random subgraphs from these networks. These results line up with
+the studies spatializing metawebs that have been discussed in the
+introduction: changes in the species pool are driving local structural
+changes in the networks.
 
@@
 Second, we looked for all species in the Canadian pool known to the
-Global Biotic Interactions (GLoBI) database (Poelen \emph{et al.} 2014),
-and extracted their known interactions. Because GLOBI aggregates
-observed interactions, it is not a \emph{networks} data source, and
-therefore the only information we can reliably extract from it is that a
-species pair \emph{was reported to interact at least once}. This last
-statement should yet be taken with caution, as some sources in GLOBI
-(\emph{e.g.} Thessen \& Parr 2014) are produced through text analysis,
-and therefore may not document direct evidence of the interaction.
-Nevertheless, should the predictive model work, we would expect that a
-majority of interactions known to GLOBI would also be predicted. After
-performing this check, we set the probability of all interactions known
-to GLOBI (366 in total, 33 of which were not predicted by the model, for
-a success rate of 91\%) to 1.
+Global Biotic Interactions (GLoBI) database (Poelen et al., 2014), and
+extracted their known interactions. Because GLoBI aggregates observed
+interactions, it is not a \emph{networks} data source, and therefore the
+only information we can reliably extract from it is that a species pair
+\emph{was reported to interact at least once}. This last statement
+should yet be taken with caution, as some sources in GLoBI (\emph{e.g.}
+Thessen \& Parr, 2014) are produced through text analysis, and therefore
+may not document direct evidence of the interaction. Nevertheless,
+should the predictive model work, we would expect that a majority of
+interactions known to GLoBI would also be predicted. We retrieved 366
+interactions between mammals from the Canadian species pool from GLoBI,
+33 of which were not predicted by the model; this results in a success
+rate of 91\%. After performing this check, we set the probability of all
+interactions known to GLoBI to 1.
 
@@
 the network. fig.~\ref{fig:degree} shows that the first rank correlates
-linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
-the number of preys and predators. Importantly, this implies that a rank
-1 approximation represents the configuration model for the metaweb,
-\emph{i.e.} a set of random networks generated from a given degree
-sequence (Park \& Newman 2004). Accounting for the probabilistic nature
-of the degrees, the rank 1 approximation also represents the \emph{soft}
-configuration model (van der Hoorn \emph{et al.} 2018). Both models are
-maximum entropy graph models (Garlaschelli \emph{et al.} 2018), with
-sharp (all network realizations satisfy the specified degree sequence)
-and soft (network realizations satisfy the degree sequence on average)
-local constraints, respectively. The (soft) configuration model is an
-unbiased random graph model widely used by ecologists in the context of
-null hypothesis significance testing of network structure (\emph{e.g.}
-Bascompte \emph{et al.} 2003) and can provide informative priors for
-Bayesian inference of network structure (\emph{e.g.} Young \emph{et al.}
-2021). It is noteworthy that for this metaweb, the relevant information
-was extracted at the first rank. Because the first rank corresponds to
-the leading singular value of the system, the results of
-fig.~\ref{fig:degree} have a straightforward interpretation:
-degree-based processes are the most important in structuring the
-mammalian food web.
+linearly with generality and vulnerability (Schoener, 1989), \emph{i.e.}
+the number of preys and predators for each species. Importantly, this
+implies that a rank 1 approximation represents the configuration model
+for the metaweb, \emph{i.e.} a set of random networks generated from a
+given degree sequence (Park \& Newman, 2004). Accounting for the
+probabilistic nature of the degrees, the rank 1 approximation also
+represents the \emph{soft} configuration model (van der Hoorn et al.,
+2018). Both models are maximum entropy graph models (Garlaschelli et
+al., 2018), with sharp (all network realizations satisfy the specified
+degree sequence) and soft (network realizations satisfy the degree
+sequence on average) local constraints, respectively. The (soft)
+configuration model is an unbiased random graph model widely used by
+ecologists in the context of null hypothesis significance testing of
+network structure (\emph{e.g.} Bascompte et al., 2003) and can provide
+informative priors for Bayesian inference of network structure
+(\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that for this
+metaweb, the relevant information was extracted at the first rank.
+Because the first rank corresponds to the leading singular value of the
+system, the results of fig.~\ref{fig:degree} have a straightforward
+interpretation: degree-based processes are the most important in
+structuring the mammalian food web.
 
@@
 comparable bioclimatic conditions) is the degree of the legacy of human
-impacts, which have been much longer in Europe. Nenzén \emph{et al.}
-(2014) showed that even at small scales (the Iberian peninsula), mammal
-food webs retain the signal of both climate change and human activity,
-even when this human activity was orders of magnitude less important
-than it is now. Similarly, Yeakel \emph{et al.} (2014) showed that
-changes in human occupation over several centuries can lead to food web
-collapse. Megafauna in particular seems to be very sensitive to human
-arrival (Pires \emph{et al.} 2015). In short, there is
-well-substantiated support for the idea that human footprint affects
-more than the risk of species extinction (Marco \emph{et al.} 2018), and
-can lead to changes in interaction structure. Yet, owing to the inherent
-plasticity of interactions, there have been documented instances of food
-webs undergoing rapid collapse/recovery cycles over short periods of
-time (Pedersen \emph{et al.} 2017). The embedding of a network, in a
-sense, embeds its macro-evolutionary history, especially as RDPG
-captures ecological signal (Dalla Riva \& Stouffer 2016); at this point,
-it is important to recall that a metaweb is intended as a catalogue of
-all possible interactions, which should then be filtered
-(Morales-Castilla \emph{et al.} 2015). In practice (and in this
-instance) the reconstructed metaweb will predict interactions that are
-plausible based on the species' evolutionary history, however some
-interactions would not be realized due to human impact.
-
-Cirtwill \emph{et al.} (2019) previously made the point that network
+impacts, which have been much longer in Europe. Nenzén et al. (2014)
+showed that even at small scales (the Iberian peninsula), mammal food
+webs retain the signal of both climate change and human activity, even
+when this human activity was orders of magnitude less important than it
+is now. Similarly, Yeakel et al. (2014) showed that changes in human
+occupation over several centuries can lead to food web collapse.
+Megafauna in particular seems to be very sensitive to human arrival
+(Pires et al., 2015). In short, there is well-substantiated support for
+the idea that human footprint affects more than the risk of species
+extinction (Marco et al., 2018), and can lead to changes in interaction
+structure. Yet, owing to the inherent plasticity of interactions, there
+have been documented instances of food webs undergoing rapid
+collapse/recovery cycles over short periods of time (Pedersen et al.,
+2017). The embedding of a network, in a sense, embeds its
+macro-evolutionary history, especially as RDPG captures ecological
+signal (Dalla Riva \& Stouffer, 2016); at this point, it is important to
+recall that a metaweb is intended as a catalogue of all potential
+interactions, which should then be filtered (Morales-Castilla et al.,
+2015). In practice (and in this instance) the reconstructed metaweb will
+predict interactions that are plausible based on the species'
+evolutionary history, however some interactions would/would not be
+realized due to human impact.
+
+Dallas et al. (2017) suggested that most links in ecological networks
+may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
+argument essentially echoes Jordano (2016b): the sampling of ecological
+interactions is difficult because it requires first the joint
+observation of two species, and then the observation of their
+interaction. In addition, it is generally expected that weak or rare
+links would be more common in networks (Csermely, 2004), compared to
+strong, persistent links; this is notably the case in food chains,
+wherein many weaker links are key to the stability of a system (Neutel
+et al., 2002). In the light of these observations, the results in
+fig.~\ref{fig:inflation} are not particularly surprising: we expect to
+see a surge in these low-probability interactions under a model that has
+a good predictive accuracy. Because the predictions we generate are by
+design probabilistic, then one can weigh these rare links appropriately.
+In a sense, that most ecological interactions are elusive can call for a
+slightly different approach to sampling: once the common interactions
+are documented, the effort required in documenting each rare interaction
+may increase exponentially. Recent proposals suggest that machine
+learning algorithms, in these situations, can act as data generators
+(Hoffmann et al., 2019): in this perspective, high quality observational
+data can be supplemented with synthetic data coming from predictive
+models, which increases the volume of information available for
+inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
+knowing the metaweb may render the prediction of local networks easier,
+because it fixes an ``upper bound'' on which interactions can exist;
+indeed, with a probabilistic metaweb, we can consider that the metaweb
+represents an aggregation of informative priors on the interactions.
+
+Related to the last point, Cirtwill et al. (2019) showed that network
 inference techniques based on Bayesian approaches would perform far
@@
 application of binary classification statistics very difficult (although
-see Strydom \emph{et al.} 2021a for a discussion of alternative
+see Strydom, Catchen, et al., 2021 for a discussion of alternative
 suggestions). The other way through which our framework can be improved
@@
 (and allometrically related variables) has been established as such a
-variable (Brose \emph{et al.} 2006); the identification of relevant
-functional traits is facilitated by recent methodological developments
-(Rosado \emph{et al.} 2013). It should be noted that Xing \& Fayle
-(2021) highlight phylogenetic relatedness as one of the core components
-of network comparison at the global scale. In this case study, we have
-embedded the original metaweb using t-SVD, because it lends itself to a
-RDPG reconstruction, which is known to capture the consequences of
-evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
-there are others ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
-Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
-alternatives.
+variable (Brose et al., 2006); the identification of relevant functional
+traits is facilitated by recent methodological developments (Rosado et
+al., 2013). It should be noted that Xing \& Fayle (2021) highlight
+phylogenetic relatedness as one of the core components of network
+comparison at the global scale. In this case study, we have embedded the
+original metaweb using t-SVD, because it lends itself to an RDPG
+reconstruction, which is known to capture the consequences of
+evolutionary processes (Dalla Riva \& Stouffer, 2016); this being said,
+there are other ways to embed graphs (Arsov \& Mirceva, 2019; Cai et
+al., 2017; Cao et al., 2019), which can be used as alternatives.
 
 As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, our approach must
-contend with two interesting problems. The first is the limit of the
-metaweb to embed and transfer. If the initial metaweb is too narrow in
-scope, notably from a taxonomic point of view, the chances of finding
-another area with enough related species to make a reliable inference
-decrease. This is notably true if the metaweb is assembled in an area
-with mostly endemic species. Conversely, the metaweb should be reliably
-filled, which assumes that the \(S^2\) interactions in a pool of \(S\)
-species have been examined, either through literature surveys or expert
-elicitation. The second problem is to determine which area should be
-used to infer the new metaweb in, as this determines the species pool
-that must be used. In our application, we focused on the mammals of
-Canada. The upside of this approach is that information at the country
-level is likely to be required by policy makers and stakeholders for
-their biodiversity assessment, as each country tends to set goals at the
-national level (Buxton \emph{et al.} 2021) for which quantitative
-instruments are designed (Turak \emph{et al.} 2017), with specific
-strategies often enacted at smaller scales (Ray \emph{et al.} 2021). Yet
-these national divisions, in large parts of the world, reflect nothing
-except for the legacy of settler colonialism, and operating under them
-must be done under the clear realization that they contributed to the
-ongoing biodiversity crisis (Adam 2014), can reinforce environmental
-injustice (Choudry 2013; Domínguez \& Luoma 2020), and on Turtle Island
-especially, will probably end up being replaced by Indigenous principles
-of land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
-2021).
+lines around planet-wide problems''; in this regard, our approach (and
+indeed, any inference of a metaweb at large scales) must contend with
+several interesting and interwoven families of problems. The first is
+the limit of the metaweb to embed and transfer. If the initial metaweb
+is too narrow in scope, notably from a taxonomic point of view, the
+chances of finding another area with enough related species to make a
+reliable inference decreases; this would likely be indicated by large
+confidence intervals during ancestral character estimation, but the lack
+of well documented metawebs is currently preventing the development of
+more concrete guidelines. The question of phylogenetic relatedness and
+dispersal is notably true if the metaweb is assembled in an area with
+mostly endemic species, and as with every predictive algorithm, there is
+room for the application of our best ecological judgement. Conversely,
+the metaweb should be reliably filled, which assumes that the \(S^2\)
+interactions in a pool of \(S\) species have been examined, either
+through literature surveys or expert elicitation. Supp. Mat. 1 provides
+some guidance as to the type of sampling effort that should be
+prioritized. Although RDPG was able to maintain very high predictive
+power when interactions were missing, the addition of false positive
+interactions was immediately detected; this suggests that it may be
+appropriate to err on the side of ``too many'' interactions when
+constructing the initial metaweb to be transferred. The second series of
+problems are related to determining which area should be used to infer
+the new metaweb in, as this determines the species pool that must be
+used. In our application, we focused on the mammals of Canada. The
+upside of this approach is that information at the country level is
+likely to be required by policy makers and stakeholders for their
+biodiversity assessment, as each country tends to set goals at the
+national level (Buxton et al., 2021) for which quantitative instruments
+are designed (Turak et al., 2017), with specific strategies often
+enacted at smaller scales (Ray et al., 2021). And yet, we do not really
+have a satisfying answer to the question of ``where does a food web
+stop?''; the current most satisfying solutions involve examining the
+spatial consistency of network area relationships (Fortin et al., 2021;
+see \emph{e.g.} Galiana et al., 2018, 2019, 2021), which is of course
+impossible in the absence of enough information about the network
+itself. This suggests that an \emph{a posteriori} refinement of the
+results may be required, based on a downscaling of the metaweb. The
+final family of problems relates less to the availability of data or
+quantitative tools, and more to the praxis of spatial ecology. Operating
+under the context of national divisions, in large parts of the world,
+reflects nothing more than the legacy of settler colonialism. Indeed,
+the use of ecological data is not an apolitical act (Nost \& Goldstein,
+2021), as data infrastructures tend to be designed to answer questions
+within national boundaries, and their use both draws upon and reinforces
+territorial statecraft; as per Machen \& Nost (2021), this is
+particularly true when the output of ``algorithmic thinking''
+(\emph{e.g.} relying on machine learning to generate knowledge) can be
+re-used for governance (\emph{e.g.} enacting conservation decisions at
+the national scale). We therefore recognize that methods such as we
+propose operate under the framework that contributed to the ongoing
+biodiversity crisis (Adam, 2014), reinforced environmental injustice
+(Choudry, 2013; Domínguez \& Luoma, 2020), and on Turtle Island
+especially, should be replaced by Indigenous principles of land
+management (Eichhorn et al., 2019; No'kmaq et al., 2021). As we see
+AI/ML being increasingly mobilized to generate knowledge that is lacking
+for conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo
+Fernandes et al., 2020), our discussion of these tools need to go beyond
+the technical, and into the governance consequences they can have.
 
@@
 \leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
-Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
-D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
-globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.
+Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
+D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
+S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
+Gravel, D. (2019). The marine fish food web is globally connected.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
+\url{https://doi.org/10.1038/s41559-019-0950-y}
 
 \leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
-Arsov, N. \& Mirceva, G. (2019). Network Embedding: An Overview.
-\emph{arXiv:1911.11726 {[}cs, stat{]}}.
+Arsov, N., \& Mirceva, G. (2019, November 26). \emph{Network Embedding:
+An Overview}. \url{http://arxiv.org/abs/1911.11726}
 
 \leavevmode\hypertarget{ref-Banville2021ManJl}{}%
-Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
+Banville, F., Vissault, S., \& Poisot, T. (2021). Mangal.jl and
 EcologicalNetworks.jl: Two complementary packages for analyzing
-ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
-2721.
+ecological networks in Julia. \emph{Journal of Open Source Software},
+\emph{6}(61), 2721. \url{https://doi.org/10.21105/joss.02721}
 
 \leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
-Bascompte, J., Jordano, P., Melian, C.J. \& Olesen, J.M. (2003). The
+Bascompte, J., Jordano, P., Melian, C. J., \& Olesen, J. M. (2003). The
 nested assembly of plant-animal mutualistic networks. \emph{Proceedings
-of the National Academy of Sciences}, 100, 9383--9387.
+of the National Academy of Sciences}, \emph{100}(16), 9383--9387.
+\url{https://doi.org/10.1073/pnas.1633576100}
 
 \leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
-Beckerman, A.P., Petchey, O.L. \& Warren, P.H. (2006). Foraging biology
-predicts food web complexity. \emph{Proceedings of the National Academy
-of Sciences}, 103, 13745--13749.
+Beckerman, A. P., Petchey, O. L., \& Warren, P. H. (2006). Foraging
+biology predicts food web complexity. \emph{Proceedings of the National
+Academy of Sciences}, \emph{103}(37), 13745--13749.
+\url{https://doi.org/10.1073/pnas.0603039103}
 
 \leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
-Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V. (2017). Julia: A
-Fresh Approach to Numerical Computing. \emph{SIAM Review}, 59, 65--98.
+Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
+Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
+65--98. \url{https://doi.org/10.1137/141000671}
 
 \leavevmode\hypertarget{ref-Boeckaerts2021PreBac}{}%
-Boeckaerts, D., Stock, M., Criel, B., Gerstmans, H., De Baets, B. \&
+Boeckaerts, D., Stock, M., Criel, B., Gerstmans, H., De Baets, B., \&
 Briers, Y. (2021). Predicting bacteriophage hosts based on sequences of
-annotated receptor-binding proteins. \emph{Scientific Reports}, 11,
-1467.
+annotated receptor-binding proteins. \emph{Scientific Reports},
+\emph{11}(1, 1), 1467. \url{https://doi.org/10.1038/s41598-021-81063-4}
 
 \leavevmode\hypertarget{ref-Braga2021PhyRec}{}%
-Braga, M.P., Janz, N., Nylin, S., Ronquist, F. \& Landis, M.J. (2021).
-Phylogenetic reconstruction of ancestral ecological networks through
-time for pierid butterflies and their host plants. \emph{Ecology
-Letters}, n/a.
+Braga, M. P., Janz, N., Nylin, S., Ronquist, F., \& Landis, M. J.
+(2021). Phylogenetic reconstruction of ancestral ecological networks
+through time for pierid butterflies and their host plants. \emph{Ecology
+Letters}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/ele.13842}
 
 \leavevmode\hypertarget{ref-Brose2006ConRes}{}%
-Brose, U., Jonsson, T., Berlow, E.L., Warren, P., Banasek-Richter, C.,
-Bersier, L.-F., \emph{et al.} (2006). ConsumerResource Body-Size
-Relationships in Natural Food Webs. \emph{Ecology}, 87, 2411--2417.
+Brose, U., Jonsson, T., Berlow, E. L., Warren, P., Banasek-Richter, C.,
+Bersier, L.-F., Blanchard, J. L., Brey, T., Carpenter, S. R.,
+Blandenier, M.-F. C., Cushing, L., Dawah, H. A., Dell, T., Edwards, F.,
+Harper-Smith, S., Jacob, U., Ledger, M. E., Martinez, N. D., Memmott,
+J., \ldots{} Cohen, J. E. (2006). ConsumerResource Body-Size
+Relationships in Natural Food Webs. \emph{Ecology}, \emph{87}(10),
+2411--2417.
+\url{https://doi.org/10.1890/0012-9658(2006)87\%5B2411:CBRINF\%5D2.0.CO;2}
 
 \leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
-Buxton, R.T., Bennett, J.R., Reid, A.J., Shulman, C., Cooke, S.J.,
-Francis, C.M., \emph{et al.} (2021). Key information needs to move from
+Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
+Francis, C. M., Nyboer, E. A., Pritchard, G., Binley, A. D., Avery-Gomm,
+S., Ban, N. C., Beazley, K. F., Bennett, E., Blight, L. K., Bortolotti,
+L. E., Camfield, A. F., Gadallah, F., Jacob, A. L., Naujokaitis-Lewis,
+I., \ldots{} Smith, P. A. (2021). Key information needs to move from
 knowledge to action for biodiversity conservation in Canada.
-\emph{Biological Conservation}, 256, 108983.
+\emph{Biological Conservation}, \emph{256}, 108983.
+\url{https://doi.org/10.1016/j.biocon.2021.108983}
 
 \leavevmode\hypertarget{ref-Cai2017ComSur}{}%
-Cai, H., Zheng, V.W. \& Chang, K.C.-C. (2017). A Comprehensive Survey of
-Graph Embedding: Problems, Techniques and Applications. \emph{arXiv
-preprint arXiv:1709.07604}.
+Cai, H., Zheng, V. W., \& Chang, K. C.-C. (2017). \emph{A Comprehensive
+Survey of Graph Embedding: Problems, Techniques and Applications}.
+\url{http://arxiv.org/abs/1709.07604}
 
 \leavevmode\hypertarget{ref-Cameron2019UneGlo}{}%
-Cameron, E.K., Sundqvist, M.K., Keith, S.A., CaraDonna, P.J., Mousing,
-E.A., Nilsson, K.A., \emph{et al.} (2019). Uneven global distribution of
-food web studies under climate change. \emph{Ecosphere}, 10, e02645.
+Cameron, E. K., Sundqvist, M. K., Keith, S. A., CaraDonna, P. J.,
+Mousing, E. A., Nilsson, K. A., Metcalfe, D. B., \& Classen, A. T.
+(2019). Uneven global distribution of food web studies under climate
+change. \emph{Ecosphere}, \emph{10}(3), e02645.
+\url{https://doi.org/10.1002/ecs2.2645}
 
 \leavevmode\hypertarget{ref-Cao2019NetEmb}{}%
-Cao, R.-M., Liu, S.-Y. \& Xu, X.-K. (2019). Network embedding for link
+Cao, R.-M., Liu, S.-Y., \& Xu, X.-K. (2019). Network embedding for link
 prediction: The pitfall and improvement. \emph{Chaos: An
-Interdisciplinary Journal of Nonlinear Science}, 29, 103102.
+Interdisciplinary Journal of Nonlinear Science}, \emph{29}(10), 103102.
+\url{https://doi.org/10.1063/1.5120724}
 
 \leavevmode\hypertarget{ref-Cavender-Bares2009MerCom}{}%
-Cavender-Bares, J., Kozak, K.H., Fine, P.V.A. \& Kembel, S.W. (2009).
-The merging of community ecology and phylogenetic biology. \emph{Ecology
-Letters}, 12, 693--715.
+Cavender-Bares, J., Kozak, K. H., Fine, P. V. A., \& Kembel, S. W.
+(2009). The merging of community ecology and phylogenetic biology.
+\emph{Ecology Letters}, \emph{12}(7), 693--715.
+\url{https://doi.org/10.1111/j.1461-0248.2009.01314.x}
 
@@
 Conservation NGOs, complicity, colonialism and conquest in an era of
-capitalist globalization. In: \emph{NGOization: Complicity,
-contradictions and prospects}. Bloomsbury Publishing, pp. 24--44.
+capitalist globalization. In \emph{NGOization: Complicity,
+contradictions and prospects} (pp. 24--44). Bloomsbury Publishing.
 
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, A.R., Eklf, A., Roslin, T., Wootton, K. \& Gravel, D. (2019).
+Cirtwill, A. R., Ekl, A., Roslin, T., Wootton, K., \& Gravel, D. (2019).
 A quantitative framework for investigating the reliability of empirical
-network construction. \emph{Methods in Ecology and Evolution}, 0.
+network construction. \emph{Methods in Ecology and Evolution}, \emph{0}.
+\url{https://doi.org/10.1111/2041-210X.13180}
 
 \leavevmode\hypertarget{ref-Cirtwill2021BuiFoo}{}%
-Cirtwill, A.R. \& Hambäck, P. (2021). Building food networks from
+Cirtwill, A. R., \& Hambäck, P. (2021). Building food networks from
 molecular data: Bayesian or fixed-number thresholds for including links.
-\emph{Basic and Applied Ecology}, 50, 67--76.
+\emph{Basic and Applied Ecology}, \emph{50}, 67--76.
+\url{https://doi.org/10.1016/j.baae.2020.11.007}
+
+\leavevmode\hypertarget{ref-Csermely2004StrLin}{}%
+Csermely, P. (2004). Strong links are important, but weak links
+stabilize them. \emph{Trends in Biochemical Sciences}, \emph{29}(7),
+331--334. \url{https://doi.org/10.1016/j.tibs.2004.05.004}
 
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
-Dalla Riva, G.V. \& Stouffer, D.B. (2016). Exploring the evolutionary
+Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
 signature of food webs' backbones using functional traits. \emph{Oikos},
-125, 446--456.
+\emph{125}(4), 446--456. \url{https://doi.org/10.1111/oik.02305}
+
+\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
+Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
+links in host-parasite networks. \emph{PLOS Computational Biology},
+\emph{13}(5), e1005557.
+\url{https://doi.org/10.1371/journal.pcbi.1005557}
 
 \leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
-Dansereau, G. \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
+Dansereau, G., \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
 Framework for Species Distribution Modeling in Julia. \emph{Journal of
-Open Source Software}, 6, 2872.
+Open Source Software}, \emph{6}(57), 2872.
+\url{https://doi.org/10.21105/joss.02872}
 
 \leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
-Domínguez, L. \& Luoma, C. (2020). Decolonising Conservation Policy: How
-Colonial Land and Conservation Ideologies Persist and Perpetuate
-Indigenous Injustices at the Expense of the Environment. \emph{Land}, 9,
-65.
+Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
+How Colonial Land and Conservation Ideologies Persist and Perpetuate
+Indigenous Injustices at the Expense of the Environment. \emph{Land},
+\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
 
 \leavevmode\hypertarget{ref-Dormann2010EvoCli}{}%
-Dormann, C.F., Gruber, B., Winter, M. \& Herrmann, D. (2010). Evolution
-of climate niches in European mammals? \emph{Biology Letters}, 6,
-229--232.
+Dormann, C. F., Gruber, B., Winter, M., \& Herrmann, D. (2010).
+Evolution of climate niches in European mammals? \emph{Biology Letters},
+\emph{6}(2), 229--232. \url{https://doi.org/10.1098/rsbl.2009.0688}
 
 \leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
-Dunne, J.A. (2006). The Network Structure of Food Webs. In:
-\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
-J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
+Dunne, J. A. (2006). The Network Structure of Food Webs. In J. A. Dunne
+\& M. Pascual (Eds.), \emph{Ecological networks: Linking structure and
+dynamics} (pp. 27--86). Oxford University Press.
 
 \leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
-Eichhorn, M.P., Baker, K. \& Griffiths, M. (2019). Steps towards
-decolonising biogeography. \emph{Frontiers of Biogeography}, 12, 1--7.
+Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
+decolonising biogeography. \emph{Frontiers of Biogeography},
+\emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
 
 \leavevmode\hypertarget{ref-Eklof2016PhyCom}{}%
-Eklöf, A. \& Stouffer, D.B. (2016). The phylogenetic component of food
-web structure and intervality. \emph{Theoretical Ecology}, 9, 107--115.
+Eklöf, A., \& Stouffer, D. B. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theoretical Ecology}, \emph{9}(1),
+107--115. \url{https://doi.org/10.1007/s12080-015-0273-9}
+
+\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
+Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
+in dynamic landscapes. \emph{Proceedings of the Royal Society B:
+Biological Sciences}, \emph{288}(1949), rspb.2020.1889, 20201889.
+\url{https://doi.org/10.1098/rspb.2020.1889}
+
+\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
+Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
+Thuiller, W., Montoya, J. M., \& Lurgi, M. (2021). The spatial scaling
+of food web structure across European biogeographical regions.
+\emph{Ecography}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/ecog.05229}
+
+\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
+Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
+variation of network structure is scale dependent: Understanding the
+biotic specialization of hostparasitoid networks. \emph{Ecography},
+\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
+
+\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
+Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
+Cazelles, K., Gravel, D., \& Montoya, J. M. (2018). The spatial scaling
+of species interaction networks. \emph{Nature Ecology \& Evolution},
+\emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
 
 \leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
-Garland, T., JR., Midford, P.E. \& Ives, A.R. (1999). An Introduction to
-Phylogenetically Based Statistical Methods, with a New Method for
+Garland, T., JR., Midford, P. E., \& Ives, A. R. (1999). An Introduction
+to Phylogenetically Based Statistical Methods, with a New Method for
 Confidence Intervals on Ancestral Values1. \emph{American Zoologist},
-39, 374--388.
+\emph{39}(2), 374--388. \url{https://doi.org/10.1093/icb/39.2.374}
 
 \leavevmode\hypertarget{ref-Garlaschelli2018CovStr}{}%
-Garlaschelli, D., Hollander, F. den \& Roccaverde, A. (2018). Covariance
-structure behind breaking of ensemble equivalence in random graphs.
-\emph{Journal of Statistical Physics}, 173, 644--662.
+Garlaschelli, D., Hollander, F. den, \& Roccaverde, A. (2018).
+Covariance structure behind breaking of ensemble equivalence in random
+graphs. \emph{Journal of Statistical Physics}, \emph{173}(3-4),
+644--662. \url{https://doi.org/10.1007/s10955-018-2114-x}
 
 \leavevmode\hypertarget{ref-GBIFSecretariat2021GbiBac}{}%
-GBIF Secretariat. (2021). GBIF Backbone Taxonomy.
+GBIF Secretariat. (2021). \emph{GBIF Backbone Taxonomy}.
+\url{https://doi.org/10.15468/39omei}
 
 \leavevmode\hypertarget{ref-Gerhold2015PhyPat}{}%
-Gerhold, P., Cahill, J.F., Winter, M., Bartish, I.V. \& Prinzing, A.
+Gerhold, P., Cahill, J. F., Winter, M., Bartish, I. V., \& Prinzing, A.
 (2015). Phylogenetic patterns are not proxies of community assembly
-mechanisms (they are far better). \emph{Functional Ecology}, 29,
-600--614.
+mechanisms (they are far better). \emph{Functional Ecology},
+\emph{29}(5), 600--614. \url{https://doi.org/10.1111/1365-2435.12425}
+
+\leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
+Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
+Nyman, T., Poisot, T., Stouffer, D. B., Tylianakis, J. M., Wood, S. A.,
+\& Roslin, T. (2018). Bringing Elton and Grinnell together: A
+quantitative framework to represent the biogeography of ecological
+interaction networks. \emph{Ecography}, \emph{0}(0).
+\url{https://doi.org/10.1111/ecog.04006}
 
 \leavevmode\hypertarget{ref-Grenie2021HarTax}{}%
-Grenié, M., Berti, E., Carvajal-Quintero, J.D., Winter, M. \& Sagouis,
-A. (2021). Harmonizing taxon names in biodiversity data: A review of
-tools, databases, and best practices.
+Grenié, M., Berti, E., Carvajal-Quintero, J. D., Winter, M., \& Sagouis,
+A. (2021). \emph{Harmonizing taxon names in biodiversity data: A review
+of tools, databases, and best practices}.
+\url{https://doi.org/10.32942/osf.io/e3qnz}
+
+\leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
+Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
+(2020). Crop and forest pest metawebs shift towards increased linkage
+and suitability overlap under climate change. \emph{Communications
+Biology}, \emph{3}(1, 1), 1--10.
+\url{https://doi.org/10.1038/s42003-020-0962-9}
+
+\leavevmode\hypertarget{ref-Halevy2009UnrEff}{}%
+Halevy, A., Norvig, P., \& Pereira, F. (2009). The Unreasonable
+Effectiveness of Data. \emph{IEEE Intelligent Systems}, \emph{24}(2),
+8--12. \url{https://doi.org/10.1109/MIS.2009.36}
 
 \leavevmode\hypertarget{ref-Halko2011FinStr}{}%
-Halko, N., Martinsson, P.G. \& Tropp, J.A. (2011). Finding Structure
+Halko, N., Martinsson, P. G., \& Tropp, J. A. (2011). Finding Structure
 with Randomness: Probabilistic Algorithms for Constructing Approximate
-Matrix Decompositions. \emph{SIAM Review}, 53, 217--288.
+Matrix Decompositions. \emph{SIAM Review}, \emph{53}(2), 217--288.
+\url{https://doi.org/10.1137/090771806}
 
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, F. (1965). \emph{Dune}. First. Chilton Book Company,
-Philadelphia.
+Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
+
+\leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
+Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
+Rubinstein, S. M., \& Rycroft, C. H. (2019). Machine learning in a
+data-limited regime: Augmenting experiments with synthetic data uncovers
+order in crumpled sheets. \emph{Science Advances}, \emph{5}(4),
+eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}
+
+\leavevmode\hypertarget{ref-Holm2019DefBla}{}%
+Holm, E. A. (2019). In defense of the black box. \emph{Science},
+\emph{364}(6435), 26--27. \url{https://doi.org/10.1126/science.aax0162}
 
 \leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
-Hortal, J., de Bello, F., Diniz-Filho, J.A.F., Lewinsohn, T.M., Lobo,
-J.M. \& Ladle, R.J. (2015). Seven Shortfalls that Beset Large-Scale
+Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
+J. M., \& Ladle, R. J. (2015). Seven Shortfalls that Beset Large-Scale
 Knowledge of Biodiversity. \emph{Annual Review of Ecology, Evolution,
-and Systematics}, 46, 523--549.
+and Systematics}, \emph{46}(1), 523--549.
+\url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}
 
 \leavevmode\hypertarget{ref-Hutchinson2017CopSig}{}%
-Hutchinson, M.C., Cagua, E.F. \& Stouffer, D.B. (2017). Cophylogenetic
-signal is detectable in pollination interactions across ecological
-scales. \emph{Ecology}, n/a--n/a.
+Hutchinson, M. C., Cagua, E. F., \& Stouffer, D. B. (2017).
+Cophylogenetic signal is detectable in pollination interactions across
+ecological scales. \emph{Ecology}, n/a--n/a.
+\url{https://doi.org/10.1002/ecy.1955}
 
@@
 Jordano, P. (2016a). Chasing Ecological Interactions. \emph{PLOS Biol},
-14, e1002559.
+\emph{14}(9), e1002559.
+\url{https://doi.org/10.1371/journal.pbio.1002559}
 
@@
 Jordano, P. (2016b). Sampling networks of ecological interactions.
-\emph{Functional Ecology}, 30, 1883--1893.
+\emph{Functional Ecology}, \emph{30}(12), 1883--1893.
+\url{https://doi.org/10.1111/1365-2435.12763}
+
+\leavevmode\hypertarget{ref-Kawatsu2021AreNet}{}%
+Kawatsu, K., Ushio, M., van Veen, F. J. F., \& Kondoh, M. (2021). Are
+networks of trophic interactions sufficient for understanding the
+dynamics of multi-trophic communities? Analysis of a tri-trophic insect
+food-web time-series. \emph{Ecology Letters}, \emph{24}(3), 543--552.
+\url{https://doi.org/10.1111/ele.13672}
+
+\leavevmode\hypertarget{ref-Kefi2012MorMea}{}%
+Kéfi, S., Berlow, E. L., Wieters, E. A., Navarrete, S. A., Petchey, O.
+L., Wood, S. A., Boit, A., Joppa, L. N., Lafferty, K. D., Williams, R.
+J., Martinez, N. D., Menge, B. A., Blanchette, C. A., Iles, A. C., \&
+Brose, U. (2012). More than a meal\ldots{} integrating non-feeding
+interactions into food webs: More than a meal \ldots. \emph{Ecology
+Letters}, \emph{15}(4), 291--300.
+\url{https://doi.org/10.1111/j.1461-0248.2011.01732.x}
+
+\leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
+Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
+learning for environmental conservation. \emph{Current Biology},
+\emph{29}(19), R977--R982.
+\url{https://doi.org/10.1016/j.cub.2019.08.016}
 
 \leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
-Litsios, G. \& Salamin, N. (2012). Effects of Phylogenetic Signal on
-Ancestral State Reconstruction. \emph{Systematic Biology}, 61, 533--538.
+Litsios, G., \& Salamin, N. (2012). Effects of Phylogenetic Signal on
+Ancestral State Reconstruction. \emph{Systematic Biology}, \emph{61}(3),
+533--538. \url{https://doi.org/10.1093/sysbio/syr124}
+
+\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
+Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
+hegemonic knowledge in climate governance. \emph{Transactions of the
+Institute of British Geographers}, \emph{46}(3), 555--569.
+\url{https://doi.org/10.1111/tran.12441}
+
+\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
+Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
+Thuiller, W. (2020a). TETRA-EU 1.0: A species-level trophic metaweb of
+European tetrapods. \emph{Global Ecology and Biogeography},
+\emph{29}(9), 1452--1457. \url{https://doi.org/10.1111/geb.13138}
 
 \leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
-Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020a). Data from: Tetra-EU 1.0: A species-level trophic
-meta-web of European tetrapods.
-
-\leavevmode\hypertarget{ref-Maiorano2020TetEu}{}%
-Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020b). TETRA-EU 1.0: A species-level trophic metaweb of
-European tetrapods. \emph{Global Ecology and Biogeography}, 29,
-1452--1457.
+Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
+Thuiller, W. (2020b). \emph{Data from: Tetra-EU 1.0: A species-level
+trophic meta-web of European tetrapods} (Version 3, pp. 16596876 bytes)
+{[}Data set{]}. Dryad. \url{https://doi.org/10.5061/DRYAD.JM63XSJ7B}
 
 \leavevmode\hypertarget{ref-Marco2018ChaHum}{}%
-Marco, M.D., Venter, O., Possingham, H.P. \& Watson, J.E.M. (2018).
+Marco, M. D., Venter, O., Possingham, H. P., \& Watson, J. E. M. (2018).
 Changes in human footprint drive changes in species extinction risk.
-\emph{Nature Communications}, 9, 4621.
+\emph{Nature Communications}, \emph{9}(1), 4621.
+\url{https://doi.org/10.1038/s41467-018-07049-5}
+
+\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
+McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
+M.-J., Galiana, N., Poisot, T., \& Wood, S. A. (2021). Sampling and
+asymptotic network properties of spatial multi-trophic networks.
+\emph{Oikos}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/oik.08650}
+
+\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
+Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
+B. (2018). Identifying a common backbone of interactions underlying food
+webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
 
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
-Morales-Castilla, I., Matias, M.G., Gravel, D. \& Araújo, M.B. (2015).
-Inferring biotic interactions from proxies. \emph{Trends in Ecology \&
-Evolution}, 30, 347--356.
+Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
+(2015). Inferring biotic interactions from proxies. \emph{Trends in
+Ecology \& Evolution}, \emph{30}(6), 347--356.
+\url{https://doi.org/10.1016/j.tree.2015.03.014}
+
+\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
+Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
+Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
+for Conservation Planning in a Changing Climate. \emph{Sustainability},
+\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
 
 \leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
-Mouquet, N., Devictor, V., Meynard, C.N., Munoz, F., Bersier, L.-F.,
-Chave, J., \emph{et al.} (2012). Ecophylogenetics: Advances and
-perspectives. \emph{Biological Reviews}, 87, 769--785.
+Mouquet, N., Devictor, V., Meynard, C. N., Munoz, F., Bersier, L.-F.,
+Chave, J., Couteron, P., Dalecky, A., Fontaine, C., Gravel, D., Hardy,
+O. J., Jabot, F., Lavergne, S., Leibold, M., Mouillot, D., Münkemüller,
+T., Pavoine, S., Prinzing, A., Rodrigues, A. S. L., \ldots{} Thuiller,
+W. (2012). Ecophylogenetics: Advances and perspectives. \emph{Biological
+Reviews}, \emph{87}(4), 769--785.
+\url{https://doi.org/10.1111/j.1469-185X.2012.00224.x}
 
 \leavevmode\hypertarget{ref-Nenzen2014Imp850}{}%
-Nenzén, H.K., Montoya, D. \& Varela, S. (2014). The Impact of 850,000
+Nenzén, H. K., Montoya, D., \& Varela, S. (2014). The Impact of 850,000
 Years of Climate Changes on the Structure and Dynamics of Mammal Food
-Webs. \emph{PLOS ONE}, 9, e106651.
+Webs. \emph{PLOS ONE}, \emph{9}(9), e106651.
+\url{https://doi.org/10.1371/journal.pone.0106651}
+
+\leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
+Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
+Stability in Real Food Webs: Weak Links in Long Loops. \emph{Science},
+\emph{296}(5570), 1120--1123.
+\url{https://doi.org/10.1126/science.1068326}
 
 \leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
-No'kmaq, M., Marshall, A., Beazley, K.F., Hum, J., joudry, shalan,
-Papadopoulos, A., \emph{et al.} (2021). {``Awakening the sleeping
-giant''}: Re-Indigenization principles for transforming biodiversity
-conservation in Canada and beyond. \emph{FACETS}, 6, 839--869.
+No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
+Papadopoulos, A., Pictou, S., Rabesca, J., Young, L., \& Zurba, M.
+(2021). {``Awakening the sleeping giant''}: Re-Indigenization principles
+for transforming biodiversity conservation in Canada and beyond.
+\emph{FACETS}, \emph{6}(1), 839--869.
+
+\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
+Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
+\emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+\url{https://doi.org/10.1177/25148486211043503}
 
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
-O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
-of tetrapods across Europe through the prism of the Eltonian niche.
-\emph{Journal of Biogeography}, 47, 181--192.
+O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
+Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
+through the prism of the Eltonian niche. \emph{Journal of Biogeography},
+\emph{47}(1), 181--192. \url{https://doi.org/10.1111/jbi.13773}
 
 \leavevmode\hypertarget{ref-Pan2010SurTra}{}%
-Pan, S.J. \& Yang, Q. (2010). A Survey on Transfer Learning. \emph{IEEE
-Transactions on Knowledge and Data Engineering}, 22, 1345--1359.
+Pan, S. J., \& Yang, Q. (2010). A Survey on Transfer Learning.
+\emph{IEEE Transactions on Knowledge and Data Engineering},
+\emph{22}(10), 1345--1359. \url{https://doi.org/10.1109/TKDE.2009.191}
 
 \leavevmode\hypertarget{ref-Park2004StaMec}{}%
-Park, J. \& Newman, M.E.J. (2004). Statistical mechanics of networks.
-\emph{Physical Review E}, 70, 066117.
+Park, J., \& Newman, M. E. J. (2004). Statistical mechanics of networks.
+\emph{Physical Review E}, \emph{70}(6), 066117.
+\url{https://doi.org/10.1103/PhysRevE.70.066117}
 
 \leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
-Pedersen, E.J., Thompson, P.L., Ball, R.A., Fortin, M.-J., Gouhier,
-T.C., Link, H., \emph{et al.} (2017). Signatures of the collapse and
-incipient recovery of an overexploited marine ecosystem. \emph{Royal
-Society Open Science}, 4, 170215.
+Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
+T. C., Link, H., Moritz, C., Nenzen, H., Stanley, R. R. E., Taranu, Z.
+E., Gonzalez, A., Guichard, F., \& Pepin, P. (2017). Signatures of the
+collapse and incipient recovery of an overexploited marine ecosystem.
+\emph{Royal Society Open Science}, \emph{4}(7), 170215.
+\url{https://doi.org/10.1098/rsos.170215}
+
+\leavevmode\hypertarget{ref-Perretti2013ModFor}{}%
+Perretti, C. T., Munch, S. B., \& Sugihara, G. (2013). Model-free
+forecasting outperforms the correct mechanistic model for simulated and
+experimental data. \emph{Proceedings of the National Academy of
+Sciences}, \emph{110}(13), 5253--5257.
+\url{https://doi.org/10.1073/pnas.1216076110}
 
 \leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
-Pires, M.M., Koch, P.L., Fariña, R.A., de Aguiar, M.A.M., dos Reis, S.F.
-\& Guimarães, P.R. (2015). Pleistocene megafaunal interaction networks
-became more vulnerable after human arrival. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, 282, 20151367.
+Pires, M. M., Koch, P. L., Fariña, R. A., de Aguiar, M. A. M., dos Reis,
+S. F., \& Guimarães, P. R. (2015). Pleistocene megafaunal interaction
+networks became more vulnerable after human arrival. \emph{Proceedings
+of the Royal Society B: Biological Sciences}, \emph{282}(1814),
+20151367. \url{https://doi.org/10.1098/rspb.2015.1367}
 
 \leavevmode\hypertarget{ref-Poelen2014GloBio}{}%
-Poelen, J.H., Simons, J.D. \& Mungall, C.J. (2014). Global biotic
+Poelen, J. H., Simons, J. D., \& Mungall, C. J. (2014). Global biotic
 interactions: An open infrastructure to share and analyze
-species-interaction datasets. \emph{Ecological Informatics}, 24,
-148--159.
+species-interaction datasets. \emph{Ecological Informatics}, \emph{24},
+148--159. \url{https://doi.org/10.1016/j.ecoinf.2014.08.005}
 
 \leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
-Poisot, T., Belisle, Z., Hoebeke, L., Stock, M. \& Szefer, P. (2019).
+Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
 EcologicalNetworks.jl - analysing ecological networks. \emph{Ecography}.
+\url{https://doi.org/10.1111/ecog.04310}
 
@@
 Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
-MacDonald, A., \emph{et al.} (2021a). Global knowledge gaps in species
-interaction networks data. \emph{Journal of Biogeography}, n/a.
-
-\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
-Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
-The dissimilarity of species interaction networks. \emph{Ecology
-Letters}, 15, 1353--1361.
+MacDonald, A., Mercier, B., Violet, C., \& Vissault, S. (2021). Global
+knowledge gaps in species interaction networks data. \emph{Journal of
+Biogeography}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/jbi.14127}
 
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
-Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
-Stouffer, D.B. (2016). The structure of probabilistic networks.
-\emph{Methods in Ecology and Evolution}, 7, 303--312.
+Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
+Stouffer, D. B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, \emph{7}(3), 303--312.
+\url{https://doi.org/10.1111/2041-210X.12468}
 
 \leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
-Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
-Albery, G.F., \emph{et al.} (2021b). Imputing the mammalian virome with
-linear filtering and singular value decomposition.
-\emph{arXiv:2105.14973 {[}q-bio{]}}.
+Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
+J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J. (2021,
+May 31). \emph{Imputing the mammalian virome with linear filtering and
+singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
 
 \leavevmode\hypertarget{ref-Poisot2018IntRet}{}%
-Poisot, T. \& Stouffer, D.B. (2018). Interactions retain the
-co-phylogenetic matching that communities lost. \emph{Oikos}, 127,
-230--238.
+Poisot, T., \& Stouffer, D. B. (2018). Interactions retain the
+co-phylogenetic matching that communities lost. \emph{Oikos},
+\emph{127}(2), 230--238. \url{https://doi.org/10.1111/oik.03788}
+
+\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, \emph{124}(3), 243--251.
+\url{https://doi.org/10.1111/oik.01719}
 
 \leavevmode\hypertarget{ref-Price2003MacThe}{}%
-Price, P.W. (2003). \emph{Macroevolutionary theory on macroecological
+Price, P. W. (2003). \emph{Macroevolutionary theory on macroecological
 patterns}. Cambridge University Press.
@@
 \leavevmode\hypertarget{ref-Ray2021BioCri}{}%
-Ray, J.C., Grimm, J. \& Olive, A. (2021). The biodiversity crisis in
+Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
 Canada: Failures and challenges of federal and sub-national strategic
-and legal frameworks. \emph{FACETS}, 6, 1044--1068.
+and legal frameworks. \emph{FACETS}, \emph{6}, 1044--1068.
+\url{https://doi.org/10.1139/facets-2020-0075}
 
 \leavevmode\hypertarget{ref-Reeve2016HowPar}{}%
-Reeve, R., Leinster, T., Cobbold, C.A., Thompson, J., Brummitt, N.,
-Mitchell, S.N., \emph{et al.} (2016). How to partition diversity.
-\emph{arXiv:1404.6520 {[}q-bio{]}}.
+Reeve, R., Leinster, T., Cobbold, C. A., Thompson, J., Brummitt, N.,
+Mitchell, S. N., \& Matthews, L. (2016, December 8). \emph{How to
+partition diversity}. \url{http://arxiv.org/abs/1404.6520}
 
 \leavevmode\hypertarget{ref-Rosado2013GoiBac}{}%
-Rosado, B.H.P., Dias, A. \& de Mattos, E. (2013). Going Back to Basics:
-Importance of Ecophysiology when Choosing Functional Traits for Studying
-Communities and Ecosystems. \emph{Natureza \&
-conservaç\textasciitilde ao revista brasileira de
-conservaç\textasciitilde ao da natureza}, 11, 15--22.
+Rosado, B. H. P., Dias, A., \& de Mattos, E. (2013). Going Back to
+Basics: Importance of Ecophysiology when Choosing Functional Traits for
+Studying Communities and Ecosystems. \emph{Natureza \&
+Conservaç\textasciitilde ao Revista Brasileira de
+Conservaç\textasciitilde ao Da Natureza}, \emph{11}, 15--22.
+\url{https://doi.org/10.4322/natcon.2013.002}
 
 \leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
-Runghen, R., Stouffer, D.B. \& Dalla Riva, G.V. (2021). Exploiting node
-metadata to predict interactions in large networks using graph embedding
-and neural networks.
+Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
+\emph{Exploiting node metadata to predict interactions in large networks
+using graph embedding and neural networks}.
+\url{https://doi.org/10.1101/2021.06.10.447991}
 
 \leavevmode\hypertarget{ref-Schoener1989FooWeb}{}%
-Schoener, T.W. (1989). Food webs from the small to the large.
-\emph{Ecology}, 70, 1559--1589.
+Schoener, T. W. (1989). Food webs from the small to the large.
+\emph{Ecology}, \emph{70}(6), 1559--1589.
+
+\leavevmode\hypertarget{ref-Shlens2014TutPri}{}%
+Shlens, J. (2014, April 3). \emph{A Tutorial on Principal Component
+Analysis}. \url{http://arxiv.org/abs/1404.1100}
 
 \leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
-Solís-Lemus, C., Bastide, P. \& Ané, C. (2017). PhyloNetworks: A Package
-for Phylogenetic Networks. \emph{Molecular Biology and Evolution}, 34,
-3292--3298.
+Solís-Lemus, C., Bastide, P., \& Ané, C. (2017). PhyloNetworks: A
+Package for Phylogenetic Networks. \emph{Molecular Biology and
+Evolution}, \emph{34}(12), 3292--3298.
+\url{https://doi.org/10.1093/molbev/msx235}
 
@@
 \leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
-Stouffer, D.B., Sales-Pardo, M., Sirer, M.I. \& Bascompte, J. (2012).
+Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
 Evolutionary Conservation of Species' Roles in Food Webs.
-\emph{Science}, 335, 1489--1492.
+\emph{Science}, \emph{335}(6075), 1489--1492.
+\url{https://doi.org/10.1126/science.1216556}
 
 \leavevmode\hypertarget{ref-Strong2014ImpNon}{}%
-Strong, J.S. \& Leroux, S.J. (2014). Impact of Non-Native Terrestrial
+Strong, J. S., \& Leroux, S. J. (2014). Impact of Non-Native Terrestrial
 Mammals on the Structure of the Terrestrial Mammal Food Web of
-Newfoundland, Canada. \emph{PLOS ONE}, 9, e106264.
+Newfoundland, Canada. \emph{PLOS ONE}, \emph{9}(8), e106264.
+\url{https://doi.org/10.1371/journal.pone.0106264}
 
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
-Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021a). \emph{A Roadmap Toward
-Predicting Species Interaction Networks (Across Space and Time)}
-(Preprint). EcoEvoRxiv.
+Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
+Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
+towards predicting species interaction networks (across space and time).
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, \emph{376}(1837), 20210063.
+\url{https://doi.org/10.1098/rstb.2021.0063}
 
 \leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
-Strydom, T., Dalla Riva, G.V. \& Poisot, T. (2021b). SVD Entropy Reveals
-the High Complexity of Ecological Networks. \emph{Frontiers in Ecology
-and Evolution}, 9.
+Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). SVD Entropy
+Reveals the High Complexity of Ecological Networks. \emph{Frontiers in
+Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.623141}
 
 \leavevmode\hypertarget{ref-Thessen2014KnoExt}{}%
-Thessen, A.E. \& Parr, C.S. (2014). Knowledge extraction and semantic
-annotation of text from the encyclopedia of life. \emph{PloS one}, 9,
-e89550.
+Thessen, A. E., \& Parr, C. S. (2014). Knowledge extraction and semantic
+annotation of text from the encyclopedia of life. \emph{PloS One},
+\emph{9}(3), e89550.
 
 \leavevmode\hypertarget{ref-Torrey2010TraLea}{}%
-Torrey, L. \& Shavlik, J. (2010). Transfer learning. In: \emph{Handbook
+Torrey, L., \& Shavlik, J. (2010). Transfer learning. In \emph{Handbook
 of research on machine learning applications and trends: Algorithms,
-methods, and techniques}. IGI global, pp. 242--264.
+methods, and techniques} (pp. 242--264). IGI global.
 
 \leavevmode\hypertarget{ref-Trojelsgaard2016EcoNet}{}%
-Trøjelsgaard, K. \& Olesen, J.M. (2016). Ecological networks in motion:
-Micro- and macroscopic variability across scales. \emph{Functional
-Ecology}, 30, 1926--1935.
+Trøjelsgaard, K., \& Olesen, J. M. (2016). Ecological networks in
+motion: Micro- and macroscopic variability across scales.
+\emph{Functional Ecology}, \emph{30}(12), 1926--1935.
+\url{https://doi.org/10.1111/1365-2435.12710}
 
@@
 Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
-Dunkerley, G., \emph{et al.} (2017). Using the essential biodiversity
-variables framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, SI:Measures of biodiversity, 213,
-264--271.
+Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
+T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
+Williams, K. (2017). Using the essential biodiversity variables
+framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, \emph{213}, 264--271.
+\url{https://doi.org/10.1016/j.biocon.2016.08.019}
 
 \leavevmode\hypertarget{ref-Upham2019InfMam}{}%
-Upham, N.S., Esselstyn, J.A. \& Jetz, W. (2019). Inferring the mammal
+Upham, N. S., Esselstyn, J. A., \& Jetz, W. (2019). Inferring the mammal
 tree: Species-level sets of phylogenies for questions in ecology,
-evolution, and conservation. \emph{PLOS Biology}, 17, e3000494.
+evolution, and conservation. \emph{PLOS Biology}, \emph{17}(12),
+e3000494. \url{https://doi.org/10.1371/journal.pbio.3000494}
 
 \leavevmode\hypertarget{ref-vanderHoorn2018SpaMax}{}%
-van der Hoorn, P., Lippner, G. \& Krioukov, D. (2018). Sparse
+van der Hoorn, P., Lippner, G., \& Krioukov, D. (2018). Sparse
 Maximum-Entropy Random Graphs with a Given Power-Law Degree
-Distribution. \emph{Journal of Statistical Physics}, 173, 806--844.
+Distribution. \emph{Journal of Statistical Physics}, \emph{173}(3-4),
+806--844. \url{https://doi.org/10.1007/s10955-017-1887-7}
+
+\leavevmode\hypertarget{ref-Vermaat2009MajDim}{}%
+Vermaat, J. E., Dunne, J. A., \& Gilbert, A. J. (2009). Major dimensions
+in food-web structure properties. \emph{Ecology}, \emph{90}(1),
+278--282. \url{http://www.ncbi.nlm.nih.gov/pubmed/19294932}
+
+\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
+Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
+\url{https://doi.org/10.1002/ece3.1640}
 
 \leavevmode\hypertarget{ref-Xing2021RisEco}{}%
-Xing, S. \& Fayle, T.M. (2021). The rise of ecological network
+Xing, S., \& Fayle, T. M. (2021). The rise of ecological network
 meta-analyses: Problems and prospects. \emph{Global Ecology and
-Conservation}, 30, e01805.
+Conservation}, \emph{30}, e01805.
+\url{https://doi.org/10.1016/j.gecco.2021.e01805}
 
 \leavevmode\hypertarget{ref-Yeakel2014ColEco}{}%
-Yeakel, J.D., Pires, M.M., Rudolf, L., Dominy, N.J., Koch, P.L.,
-Guimarães, P.R., \emph{et al.} (2014). Collapse of an ecological network
-in Ancient Egypt. \emph{PNAS}, 111, 14472--14477.
+Yeakel, J. D., Pires, M. M., Rudolf, L., Dominy, N. J., Koch, P. L.,
+Guimarães, P. R., \& Gross, T. (2014). Collapse of an ecological network
+in Ancient Egypt. \emph{PNAS}, \emph{111}(40), 14472--14477.
+\url{https://doi.org/10.1073/pnas.1408471111}
 
 \leavevmode\hypertarget{ref-Youden1950IndRat}{}%
-Youden, W.J. (1950). Index for rating diagnostic tests. \emph{Cancer},
-3, 32--35.
+Youden, W. J. (1950). Index for rating diagnostic tests. \emph{Cancer},
+\emph{3}(1), 32--35.
+\url{https://doi.org/10.1002/1097-0142(1950)3:1\%3C32::AID-CNCR2820030106\%3E3.0.CO;2-3}
 
 \leavevmode\hypertarget{ref-Young2021BayInf}{}%
-Young, J.-G., Cantwell, G.T. \& Newman, M.E.J. (2021). Bayesian
+Young, J.-G., Cantwell, G. T., \& Newman, M. E. J. (2021). Bayesian
 inference of network structure from unreliable data. \emph{Journal of
-Complex Networks}, 8.
+Complex Networks}, \emph{8}(6).
+\url{https://doi.org/10.1093/comnet/cnaa046}
 
 \leavevmode\hypertarget{ref-Young2007RanDot}{}%
-Young, S.J. \& Scheinerman, E.R. (2007). Random Dot Product Graph Models
-for Social Networks. In: \emph{Algorithms and Models for the Web-Graph},
-Lecture Notes in Computer Science (eds. Bonato, A. \& Chung, F.R.K.).
-Springer, Berlin, Heidelberg, pp. 138--149.
+Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
+Models for Social Networks. In A. Bonato \& F. R. K. Chung (Eds.),
+\emph{Algorithms and Models for the Web-Graph} (pp. 138--149). Springer.
+\url{https://doi.org/10.1007/978-3-540-77004-6_11}
 
 \leavevmode\hypertarget{ref-Zhu2006AutDim}{}%
-Zhu, M. \& Ghodsi, A. (2006). Automatic dimensionality selection from
+Zhu, M., \& Ghodsi, A. (2006). Automatic dimensionality selection from
 the scree plot via the use of profile likelihood. \emph{Computational
-Statistics \& Data Analysis}, 51, 918--930.
+Statistics \& Data Analysis}, \emph{51}(2), 918--930.
+\url{https://doi.org/10.1016/j.csda.2005.09.010}
 

### 2021-11-03 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@f43705e294b97501d82ade71305b5b18023fb583 🚀

@@
             letterpaper,
-            top=1.0in,
-            bottom=2.510cm,
-            left=0.35in,
-            right=0.35in,
-            marginparwidth=2.0in,
-            marginparsep=0.35in}
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
 
 \usepackage[singlelinecheck=off]{caption}
+
 \captionsetup{
@@
 
-Despite their importance in many ecological processes, collecting data
-and information on ecological interactions is an exceedingly challenging
-task. For this reason, large parts of the world have a data deficit when
-it comes to species interactions, and how the resulting networks are
-structured. As data collection alone is unlikely to be sufficient,
-community ecologists must adopt predictive methods. Here, we develop
-such a method relying on graph embedding and transfer learning to
-assemble a predicted list of trophic interactions between Canadian
-mammals. This interaction list is derived from the European food web,
-despite sharing 4\% of common species with Canada. The results of the
+\begin{enumerate}
+    \itemDespite their importance in many ecological processes,
+collecting data and information on ecological interactions is an
+exceedingly challenging task. For this reason, large parts of the world
+have a data deficit when it comes to species interactions, and how the
+resulting networks are structured. As data collection alone is unlikely
+to be sufficient, community ecologists must adopt predictive methods.%
+    \itemWe present a methodological framework that uses graph embedding
+and transfer learning to assemble a predicted list of trophic
+interactions of a species pool for which their interactions are unknown.
+Specifically, we `learn' the information from a known interaction
+network by inferring the latent traits of species and infer the latent
+traits of a species pool for which we have no \emph{a priori}
+interaction data based on their phylogenetic relatedness to species from
+the known network. The latent traits can then be used to predict
+interactions and construct and interaction network.%
+    \itemHere we assembled a metaweb for Canadian mammals derived from
+interactions in the European food web, despite only 4\% of common
+species being shared between the two locations. The results of the
 predictive model are compared against databases of recorded pairwise
 interactions, showing that we correctly recover 91\% of known
-interactions. We provide guidance on how this method can be adapted by
-substituting some approaches or predictors in order to make it more
-generally applicable.
+interactions.%
+    \itemThe framework itself is robust even when the known network is
+incomplete or contains spurious interactions making it an ideal
+candidate as a tool for filling gaps when it comes to species
+interactions. We provide guidance on how this frameworl can be adapted
+by substituting some approaches or predictors in order to make it more
+generally applicable.%
+\end{enumerate}
 
@@
 understanding of ecological networks across space, particularly at
-macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
+macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen,
 2016). First, ecological networks within a location are difficult to
-sample properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
-shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
-about inter- and intra- specific relationships. This first challenge has
-been, in large part, addressed by the recent emergence of a suite of
-methods aiming to predict interactions within \emph{existing} networks,
-many of which are reviewed in Strydom \emph{et al.} (2021a). Second,
-recent analyses based on collected data (Poisot \emph{et al.} 2021a) or
-metadata (Cameron \emph{et al.} 2019) highlight that ecological networks
-are currently studied in a biased subset of space and bioclimates, which
-impedes our ability to generalize any local understanding of network
-structure. Meaning that, although the framework to address
-incompleteness \emph{within} networks exists, there would still be
-regions for which, due to a \emph{lack} of local interaction data, we
-are unable to infer potential species interactions. Having a general
-solution for inferring \emph{potential} interactions (despite the
-unavailability of interaction data) could be the catalyst for
+sample properly (Jordano, 2016a, 2016b), resulting in a widespread
+``Eltonian shortfall'' (Hortal et al., 2015), \emph{i.e.} a lack of
+knowledge about inter- and intra- specific relationships. This first
+challenge has been, in large part, addressed by the recent emergence of
+a suite of methods aiming to predict interactions within \emph{existing}
+networks, many of which are reviewed in Strydom, Catchen, et al. (2021).
+Second, recent analyses based on collected data (Poisot, Bergeron, et
+al., 2021) or metadata (Cameron et al., 2019) highlight that ecological
+networks are currently studied in a biased subset of space and
+bioclimates, which impedes our ability to generalize any local
+understanding of network structure. Meaning that, although the framework
+to address incompleteness \emph{within} networks exists, there would
+still be regions for which, due to a \emph{lack} of local interaction
+data, we are unable to infer potential species interactions. Having a
+general solution for inferring \emph{potential} interactions (despite
+the unavailability of interaction data) could be the catalyst for
 significant breakthroughs in our ability to start thinking about species
 interaction networks over large spatial scales. In a recent overview of
-the field of ecological network prediction, Strydom \emph{et al.}
-(2021a) identified two challenges of interest to the prediction of
+the field of ecological network prediction, Strydom, Catchen, et al.
+(2021) identified two challenges of interest to the prediction of
 interactions at large scales. First, there is a relative scarcity of
@@
 methodology that uses the knowledge gained from solving one problem and
-applying it to a related (destination) problem (Pan \& Yang 2010; Torrey
-\& Shavlik 2010). In this instance, we solve the problem of predicting
-trophic interactions between species, based on knowledge extracted from
-another species pool for which interactions are known by using
-phylogenetic structure as a medium for transfer. There is a plurality of
-measures of species similarities that can be used for inferring
-\emph{potential} species interactions \emph{i.e.} metaweb reconstruction
-(see \emph{e.g.} Morales-Castilla \emph{et al.} 2015); however,
+applying it to a related (destination) problem (Pan \& Yang, 2010;
+Torrey \& Shavlik, 2010). In this instance, we solve the problem of
+predicting trophic interactions between species, based on knowledge
+extracted from another species pool for which interactions are known by
+using phylogenetic structure as a medium for transfer. There is a
+plurality of measures of species similarities that can be used for
+inferring \emph{potential} species interactions \emph{i.e.} metaweb
+reconstruction (see \emph{e.g.} Morales-Castilla et al., 2015); however,
 phylogenetic proximity has several desirable properties when working at
-large scales. Gerhold \emph{et al.} (2015) made the point that
-phylogenetic signal captures diversification of characters (large
-macro-evolutionary process), but not necessarily community assembly
-(fine ecological process); Dormann \emph{et al.} (2010) previously found
-very similar conclusions. Interactions tend to reflect a phylogenetic
-signal because they have a conserved pattern of evolutionary convergence
-that encompasses a wide range of ecological and evolutionary mechanisms
-(Cavender-Bares \emph{et al.} 2009; Mouquet \emph{et al.} 2012), and -
-most importantly - retain this signal even when it is not detectable at
-the community scale (Hutchinson \emph{et al.} 2017; Poisot \& Stouffer
-2018). Finally, species interactions at macro-ecological scales seem to
-respond mostly to macro-evolutionary processes (Price 2003); which is
-evidenced by the presence of conserved backbones in food webs (Dalla
-Riva \& Stouffer 2016; Mora \emph{et al.} 2018), strong evolutionary
-signature on prey choice (Stouffer \emph{et al.} 2012), and strong
-phylogenetic signature in food web intervality (Eklöf \& Stouffer 2016).
-Phylogenetic reconstruction has also previously been used within the
-context of ecological networks, namely understanding ancestral
-plant-insect interactions (Braga \emph{et al.} 2021). Taken together,
-these considerations suggest that phylogenies can reliably be used to
-transfer knowledge on species interactions.
+large scales. Gerhold et al. (2015) made the point that phylogenetic
+signal captures diversification of characters (large macro-evolutionary
+process), but not necessarily community assembly (fine ecological
+process); Dormann et al. (2010) previously found very similar
+conclusions. Interactions tend to reflect a phylogenetic signal because
+they have a conserved pattern of evolutionary convergence that
+encompasses a wide range of ecological and evolutionary mechanisms
+(Cavender-Bares et al., 2009; Mouquet et al., 2012), and - most
+importantly - retain this signal even when it is not detectable at the
+community scale (Hutchinson et al., 2017; Poisot \& Stouffer, 2018).
+Finally, species interactions at macro-ecological scales seem to respond
+mostly to macro-evolutionary processes (Price, 2003); which is evidenced
+by the presence of conserved backbones in food webs (Dalla Riva \&
+Stouffer, 2016; Mora et al., 2018), strong evolutionary signature on
+prey choice (Stouffer et al., 2012), and strong phylogenetic signature
+in food web intervality (Eklöf \& Stouffer, 2016). Phylogenetic
+reconstruction has also previously been used within the context of
+ecological networks, namely understanding ancestral plant-insect
+interactions (Braga et al., 2021). Taken together, these considerations
+suggest that phylogenies can reliably be used to transfer knowledge on
+species interactions.
 
@@
 an illustration based on learning the embedding of a metaweb of trophic
-interactions for European mammals (known interactions; Maiorano \emph{et
-al.} 2020b, a) and, based on phylogenetic relationships between mammals
-globally (\emph{i.e.}, phylogenetic tree Upham \emph{et al.} 2019),
-infer a metaweb for the Canadian mammalian species pool (interactions
-are treated as unknown in this instance). Following the definition of
-Dunne (2006), a metaweb is a network analogue to the regional species
-pool; specifically, it is an inventory of all \emph{potential}
-interactions between species from a spatially delimited area (and so
-captures the \(\gamma\) diversity of interactions). The metaweb is,
-therefore, \emph{not} a prediction of the food web at a specific locale
-within the spatial area it covers, and will have a different structure
-(notably by having a larger connectance; see \emph{e.g.} Wood \emph{et
-al.} 2015). These local food webs (which captures the \(\alpha\)
-diversity of interactions) are a subset of the metaweb's species and
-interactions, and have been called ``metaweb realizations'' (Poisot
-\emph{et al.} 2015). Differences between local food web and their
-metaweb are due to chance, species abundance and co-occurrence, local
-environmental conditions, and local distribution of functional traits,
-among others.
+interactions for European mammals (known interactions; Maiorano et al.,
+2020a, 2020b) and, based on phylogenetic relationships between mammals
+globally (\emph{i.e.}, phylogenetic tree Upham et al., 2019), infer a
+metaweb for the Canadian mammalian species pool (interactions are
+treated as unknown in this instance). Following the definition of Dunne
+(2006), a metaweb is a network analogue to the regional species pool;
+specifically, it is an inventory of all \emph{potential} interactions
+between species from a spatially delimited area (and so captures the
+\(\gamma\) diversity of interactions). The metaweb is, therefore,
+\emph{not} a prediction of the food web at a specific locale within the
+spatial area it covers, and will have a different structure (notably by
+having a larger connectance; see \emph{e.g.} Wood et al., 2015). These
+local food webs (which captures the \(\alpha\) diversity of
+interactions) are a subset of the metaweb's species and interactions,
+and have been called ``metaweb realizations'' (Poisot et al., 2015).
+Differences between local food web and their metaweb are due to chance,
+species abundance and co-occurrence, local environmental conditions, and
+local distribution of functional traits, among others.
 
 Because the metaweb represents the joint effect of functional,
-phylogenetic, and macroecological processes (Morales-Castilla \emph{et
-al.} 2015), it holds valuable ecological information. Specifically, it
-is the ``upper bounds'' on what the composition of the local networks
-can be (see \emph{e.g.} McLeod \emph{et al.} 2021). These local
-networks, in turn, can be reconstructed given appropriate knowledge of
-local species composition, providing information on structure of food
-webs at finer spatial scales. This has been done for example for
-tree-galler-parasitoid systems (Gravel \emph{et al.} 2018), fish trophic
-interactions (Albouy \emph{et al.} 2019), tetrapod trophic interactions
-(O'Connor \emph{et al.} 2020), and crop-pest networks (Grünig \emph{et
-al.} 2020). Whereas the original metaweb definition, and indeed most
-past uses of metawebs, was based on the presence/absence of
-interactions, we focus on \emph{probabilistic} metawebs where
-interactions are represented as the chance of success of a Bernoulli
-trial (see \emph{e.g.} Poisot \emph{et al.} 2016); therefore, not only
-does our method recommend interactions that may exist, it gives each
-interaction a score, allowing us to properly weigh them.
+phylogenetic, and macroecological processes (Morales-Castilla et al.,
+2015), it holds valuable ecological information. Specifically, it is the
+``upper bounds'' on what the composition of the local networks can be
+(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
+can be reconstructed given appropriate knowledge of local species
+composition, providing information on structure of food webs at finer
+spatial scales. This has been done for example for
+tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
+interactions (Albouy et al., 2019), tetrapod trophic interactions
+(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
+Whereas the original metaweb definition, and indeed most past uses of
+metawebs, was based on the presence/absence of interactions, we focus on
+\emph{probabilistic} metawebs where interactions are represented as the
+chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
+2016); therefore, not only does our method recommend interactions that
+may exist, it gives each interaction a score, allowing us to properly
+weigh them.
 
@@
 of similarity may not be phylogeny, and can be replaced by information
-on foraging (Beckerman \emph{et al.} 2006), cell-level mechanisms
-(Boeckaerts \emph{et al.} 2021), or a combination of traits and
-phylogenetic structure (Stock 2021). Most importantly, although we focus
-on a trophic system, it is an established fact that different
-(non-trophic) interactions do themselves interact with and influence the
-outcome of trophic interactions (Kéfi \emph{et al.} 2012; see
-\emph{e.g.} Kawatsu \emph{et al.} 2021). Future development of metaweb
-inference techniques should cover the prediction of multiple interaction
-types.
+on foraging (Beckerman et al., 2006), cell-level mechanisms (Boeckaerts
+et al., 2021), or a combination of traits and phylogenetic structure
+(Stock, 2021). Most importantly, although we focus on a trophic system,
+it is an established fact that different (non-trophic) interactions do
+themselves interact with and influence the outcome of trophic
+interactions (see \emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012).
+Future development of metaweb inference techniques should cover the
+prediction of multiple interaction types.
 
@@
 
-We use data from the European metaweb assembled by Maiorano \emph{et
-al.} (2020b). This was assembled using data extracted from scientific
+We use data from the European metaweb assembled by Maiorano et al.
+(2020a). This was assembled using data extracted from scientific
 literature (including published papers, books, and grey literature) from
@@
 Global Biodiversity Information Facility (GBIF) taxonomic backbone (GBIF
-Secretariat 2021) and retaining all those who matched to mammals. This
+Secretariat, 2021) and retaining all those who matched to mammals. This
 serves a dual purpose 1) to extract only mammals from the European
@@
 the different data sources further downstream (which is an important
-consideration when combining datasets (Grenié \emph{et al.} 2021)). All
-nodes had valid matches to GBIF at this step, and so this backbone is
-used for all name reconciliation steps as outlined below.
+consideration when combining datasets (Grenié et al., 2021)). All nodes
+had valid matches to GBIF at this step, and so this backbone is used for
+all name reconciliation steps as outlined below.
 
@@
 information for transfer (\emph{i.e.} the transfer medium). We used the
-mammalian consensus supertree by Upham \emph{et al.} (2019), for which
-all approximatively 6000 names have been similarly matched to their GBIF
+mammalian consensus supertree by Upham et al. (2019), for which all
+approximatively 6000 names have been similarly matched to their GBIF
 valid names. This step allows us to place each node of the mammalian
@@
 (IUCN) checklist, and selected the terrestrial and semi-aquatic species
-(this corresponds to the same selection that was applied by Maiorano
-\emph{et al.} (2020b) in the European metaweb). The IUCN names were, as
+(this corresponds to the same selection that was applied by Maiorano et
+al. (2020a) in the European metaweb). The IUCN names were, as
 previously, reconciled against GBIF to have an exact match to the
@@
 network in Europe, we use a truncated Singular Value Decomposition
-(t-SVD; Halko \emph{et al.} 2011) to generate latent traits representing
-a low-dimensional embedding of the network. As an aside, most ecologists
+(t-SVD; Halko et al., 2011) to generate latent traits representing a
+low-dimensional embedding of the network. As an aside, most ecologists
 are indirectly familiar with SVD: Principal Component Analysis is a
 special case of SVD, which is more sensitive to numerical instabilities
-(see notably Shlens 2014). The latent traits give an unbiased estimate
+(see notably Shlens, 2014). The latent traits give an unbiased estimate
 of the node's position in the latent feature spaces and can be mapped
@@
 on the reconstructed latent traits for species in the destination
-species pool, a Random Dot Product Graph model (hereafter RDPG; Young \&
-Scheinerman 2007) predicts the interaction between species through a
-function of the nodes' features through matrix multiplication. Thus,
-from latent traits and node position, we can infer interactions.
+species pool, a Random Dot Product Graph model (hereafter RDPG; S. J.
+Young \& Scheinerman, 2007) predicts the interaction between species
+through a function of the nodes' features through matrix multiplication.
+Thus, from latent traits and node position, we can infer interactions.
 
@@
 (unintentional) black box algorithms are not necessarily a bad thing
-(Holm 2019), as long as their constituent parts can be examined (which
+(Holm, 2019), as long as their constituent parts can be examined (which
 is the case with our method). But more importantly, data hold more
@@
 disconnected from the model can make correct guesses most of the time
-(Halevy \emph{et al.} 2009); in fact, in an instance of ecological
-forecasting of spatio-temporal systems, model-free approaches
-(\emph{i.e.} drawing all of their information from the data)
-outperformed model-informed ones (Perretti \emph{et al.} 2013).
+(Halevy et al., 2009); in fact, in an instance of ecological forecasting
+of spatio-temporal systems, model-free approaches (\emph{i.e.} drawing
+all of their information from the data) outperformed model-informed ones
+(Perretti et al., 2013).
 
@@
 signal, and to capture the evolutionary backbone of food webs (Dalla
-Riva \& Stouffer 2016); in other words, the latent variables of an RDPG
+Riva \& Stouffer, 2016); in other words, the latent variables of an RDPG
 can be mapped onto a phylogenetic tree, and phylogenetically similar
@@
 variables do not need to be produced by decomposing the network itself;
-in a recent contribution, Runghen \emph{et al.} (2021) showed that deep
+in a recent contribution, Runghen et al. (2021) showed that deep
 artificial neural networks are able to reconstruct the left and right
@@
 appropriate embedding of ecological networks, which has recently been
-shown to both capture their complex, emerging properties (Strydom
-\emph{et al.} 2021b) and to allow highly accurate prediction of the
-interactions within a single network (Poisot \emph{et al.} 2021b). Under
-SVD, an adjacency matrix \(\mathbf{A}\) (where
+shown to both capture their complex, emerging properties (Strydom, Dalla
+Riva, et al., 2021) and to allow highly accurate prediction of the
+interactions within a single network (Poisot, Ouellet, et al., 2021).
+Under SVD, an adjacency matrix \(\mathbf{A}\) (where
 \(\mathbf{A}_{m,n}\in\mathbb{B}\) where 1 indicates predation and 0 an
@@
 European metaweb are all true. Given the methodological details given in
-Maiorano \emph{et al.} (2020b) and O'Connor \emph{et al.} (2020), this
-seems like a reasonable assumption, although one that does not hold for
-all metawebs. We used the thresholding approach presented in Poisot
-\emph{et al.} (2021b), and picked a cutoff that maximized Youden's \(J\)
-statistic (a measure of the informedness (trust) of predictions; Youden
-(1950)); the resulting cutoff was 0.22, and gave an accuracy above 0.99.
-In Supp. Mat. 1, we provide several lines of evidence that using the
-entire network to estimate the threshold does not lead to overfitting;
-that using a subset of species would yield the same threshold; that
+Maiorano et al. (2020a) and O'Connor et al. (2020), this seems like a
+reasonable assumption, although one that does not hold for all metawebs.
+We used the thresholding approach presented in Poisot, Ouellet, et al.
+(2021), and picked a cutoff that maximized Youden's \(J\) statistic (a
+measure of the informedness (trust) of predictions; Youden (1950)); the
+resulting cutoff was 0.22, and gave an accuracy above 0.99. In Supp.
+Mat. 1, we provide several lines of evidence that using the entire
+network to estimate the threshold does not lead to overfitting; that
+using a subset of species would yield the same threshold; that
 decreasing the quality of the original data by adding of removing
@@
 of strong hypotheses about the nature of phylogenetic signal in the
-network decomposition (Litsios \& Salamin 2012). This uses the estimated
-feature vectors for the European mammals to create a state
+network decomposition (Litsios \& Salamin, 2012). This uses the
+estimated feature vectors for the European mammals to create a state
 reconstruction for all species (conceptually something akin to a
@@
 trait/dimension added to the t-SVD has an \emph{additive} effect to the
-one before it. Note that the Upham \emph{et al.} (2019) tree itself has
-some uncertainty associated to inner nodes of the phylogeny. In this
-case study, we have decided to not propagate this uncertainty, as it
-would complexify the process. The Brownian motion algorithm returns the
+one before it. Note that the Upham et al. (2019) tree itself has some
+uncertainty associated to inner nodes of the phylogeny. In this case
+study, we have decided to not propagate this uncertainty, as it would
+complexify the process. The Brownian motion algorithm returns the
 \emph{average} value of the trait, and its upper and lower bounds.
@@
 probably broader than what they would actually be, see \emph{e.g.}
-Garland \emph{et al.} 1999), we repeat the above process
-\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
-where the probability of an interaction (here conveying our degree of
-trust that it exists given the inferred trait distributions) is given by
-the number of times where it appears across all random draws \(N\),
-divided by the number of samples. An interaction with \(P_{i,j} = 1\)
-means that these two species were predicted to interact in all
-\(2\times 10^5\) random draws.
+Garland et al., 1999), we repeat the above process \(2\times 10^5\)
+times, which results in a probabilistic metaweb \(P\), where the
+probability of an interaction (here conveying our degree of trust that
+it exists given the inferred trait distributions) is given by the number
+of times where it appears across all random draws \(N\), divided by the
+number of samples. An interaction with \(P_{i,j} = 1\) means that these
+two species were predicted to interact in all \(2\times 10^5\) random
+draws.
 
@@
 has distinct structural properties. Following an approach similar to
-Vermaat \emph{et al.} (2009), we show in Supp. Mat. 3 that not only can
-we observe differences in a multivariate space between the European and
+Vermaat et al. (2009), we show in Supp. Mat. 3 that not only can we
+observe differences in a multivariate space between the European and
 Canadian metaweb, we can also observe differences in the same space
@@
 Second, we looked for all species in the Canadian pool known to the
-Global Biotic Interactions (GLoBI) database (Poelen \emph{et al.} 2014),
-and extracted their known interactions. Because GLoBI aggregates
-observed interactions, it is not a \emph{networks} data source, and
-therefore the only information we can reliably extract from it is that a
-species pair \emph{was reported to interact at least once}. This last
-statement should yet be taken with caution, as some sources in GLoBI
-(\emph{e.g.} Thessen \& Parr 2014) are produced through text analysis,
-and therefore may not document direct evidence of the interaction.
-Nevertheless, should the predictive model work, we would expect that a
-majority of interactions known to GLoBI would also be predicted. We
-retrieved 366 interactions between mammals from the Canadian species
-pool from GLoBI, 33 of which were not predicted by the model; this
-results in a success rate of 91\%. After performing this check, we set
-the probability of all interactions known to GLoBI to 1.
+Global Biotic Interactions (GLoBI) database (Poelen et al., 2014), and
+extracted their known interactions. Because GLoBI aggregates observed
+interactions, it is not a \emph{networks} data source, and therefore the
+only information we can reliably extract from it is that a species pair
+\emph{was reported to interact at least once}. This last statement
+should yet be taken with caution, as some sources in GLoBI (\emph{e.g.}
+Thessen \& Parr, 2014) are produced through text analysis, and therefore
+may not document direct evidence of the interaction. Nevertheless,
+should the predictive model work, we would expect that a majority of
+interactions known to GLoBI would also be predicted. We retrieved 366
+interactions between mammals from the Canadian species pool from GLoBI,
+33 of which were not predicted by the model; this results in a success
+rate of 91\%. After performing this check, we set the probability of all
+interactions known to GLoBI to 1.
 
@@
 the network. fig.~\ref{fig:degree} shows that the first rank correlates
-linearly with generality and vulnerability (Schoener 1989), \emph{i.e.}
+linearly with generality and vulnerability (Schoener, 1989), \emph{i.e.}
 the number of preys and predators for each species. Importantly, this
@@
 for the metaweb, \emph{i.e.} a set of random networks generated from a
-given degree sequence (Park \& Newman 2004). Accounting for the
+given degree sequence (Park \& Newman, 2004). Accounting for the
 probabilistic nature of the degrees, the rank 1 approximation also
-represents the \emph{soft} configuration model (van der Hoorn \emph{et
-al.} 2018). Both models are maximum entropy graph models (Garlaschelli
-\emph{et al.} 2018), with sharp (all network realizations satisfy the
-specified degree sequence) and soft (network realizations satisfy the
-degree sequence on average) local constraints, respectively. The (soft)
+represents the \emph{soft} configuration model (van der Hoorn et al.,
+2018). Both models are maximum entropy graph models (Garlaschelli et
+al., 2018), with sharp (all network realizations satisfy the specified
+degree sequence) and soft (network realizations satisfy the degree
+sequence on average) local constraints, respectively. The (soft)
 configuration model is an unbiased random graph model widely used by
 ecologists in the context of null hypothesis significance testing of
-network structure (\emph{e.g.} Bascompte \emph{et al.} 2003) and can
-provide informative priors for Bayesian inference of network structure
-(\emph{e.g.} Young \emph{et al.} 2021). It is noteworthy that for this
+network structure (\emph{e.g.} Bascompte et al., 2003) and can provide
+informative priors for Bayesian inference of network structure
+(\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that for this
 metaweb, the relevant information was extracted at the first rank.
@@
 comparable bioclimatic conditions) is the degree of the legacy of human
-impacts, which have been much longer in Europe. Nenzén \emph{et al.}
-(2014) showed that even at small scales (the Iberian peninsula), mammal
-food webs retain the signal of both climate change and human activity,
-even when this human activity was orders of magnitude less important
-than it is now. Similarly, Yeakel \emph{et al.} (2014) showed that
-changes in human occupation over several centuries can lead to food web
-collapse. Megafauna in particular seems to be very sensitive to human
-arrival (Pires \emph{et al.} 2015). In short, there is
-well-substantiated support for the idea that human footprint affects
-more than the risk of species extinction (Marco \emph{et al.} 2018), and
-can lead to changes in interaction structure. Yet, owing to the inherent
-plasticity of interactions, there have been documented instances of food
-webs undergoing rapid collapse/recovery cycles over short periods of
-time (Pedersen \emph{et al.} 2017). The embedding of a network, in a
-sense, embeds its macro-evolutionary history, especially as RDPG
-captures ecological signal (Dalla Riva \& Stouffer 2016); at this point,
-it is important to recall that a metaweb is intended as a catalogue of
-all potential interactions, which should then be filtered
-(Morales-Castilla \emph{et al.} 2015). In practice (and in this
-instance) the reconstructed metaweb will predict interactions that are
-plausible based on the species' evolutionary history, however some
-interactions would/would not be realized due to human impact.
-
-Dallas \emph{et al.} (2017) suggested that most links in ecological
-networks may be cryptic, \emph{i.e.} uncommon or otherwise hard to
-observe. This argument essentially echoes Jordano (2016b): the sampling
-of ecological interactions is difficult because it requires first the
-joint observation of two species, and then the observation of their
+impacts, which have been much longer in Europe. Nenzén et al. (2014)
+showed that even at small scales (the Iberian peninsula), mammal food
+webs retain the signal of both climate change and human activity, even
+when this human activity was orders of magnitude less important than it
+is now. Similarly, Yeakel et al. (2014) showed that changes in human
+occupation over several centuries can lead to food web collapse.
+Megafauna in particular seems to be very sensitive to human arrival
+(Pires et al., 2015). In short, there is well-substantiated support for
+the idea that human footprint affects more than the risk of species
+extinction (Marco et al., 2018), and can lead to changes in interaction
+structure. Yet, owing to the inherent plasticity of interactions, there
+have been documented instances of food webs undergoing rapid
+collapse/recovery cycles over short periods of time (Pedersen et al.,
+2017). The embedding of a network, in a sense, embeds its
+macro-evolutionary history, especially as RDPG captures ecological
+signal (Dalla Riva \& Stouffer, 2016); at this point, it is important to
+recall that a metaweb is intended as a catalogue of all potential
+interactions, which should then be filtered (Morales-Castilla et al.,
+2015). In practice (and in this instance) the reconstructed metaweb will
+predict interactions that are plausible based on the species'
+evolutionary history, however some interactions would/would not be
+realized due to human impact.
+
+Dallas et al. (2017) suggested that most links in ecological networks
+may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
+argument essentially echoes Jordano (2016b): the sampling of ecological
+interactions is difficult because it requires first the joint
+observation of two species, and then the observation of their
 interaction. In addition, it is generally expected that weak or rare
-links would be more common in networks (Csermely 2004), compared to
+links would be more common in networks (Csermely, 2004), compared to
 strong, persistent links; this is notably the case in food chains,
 wherein many weaker links are key to the stability of a system (Neutel
-\emph{et al.} 2002). In the light of these observations, the results in
+et al., 2002). In the light of these observations, the results in
 fig.~\ref{fig:inflation} are not particularly surprising: we expect to
@@
 learning algorithms, in these situations, can act as data generators
-(Hoffmann \emph{et al.} 2019): in this perspective, high quality
-observational data can be supplemented with synthetic data coming from
-predictive models, which increases the volume of information available
-for inference. Indeed, Strydom \emph{et al.} (2021a) suggested that
+(Hoffmann et al., 2019): in this perspective, high quality observational
+data can be supplemented with synthetic data coming from predictive
+models, which increases the volume of information available for
+inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
 knowing the metaweb may render the prediction of local networks easier,
@@
 
-Related to the last point, Cirtwill \emph{et al.} (2019) showed that
-network inference techniques based on Bayesian approaches would perform
-far better in the presence of an interaction-level informative prior;
-the desirable properties of such a prior would be that it is expressed
-as a probability, preferably representing a Bernoulli event, the value
-of which would be representative of relevant biological processes
+Related to the last point, Cirtwill et al. (2019) showed that network
+inference techniques based on Bayesian approaches would perform far
+better in the presence of an interaction-level informative prior; the
+desirable properties of such a prior would be that it is expressed as a
+probability, preferably representing a Bernoulli event, the value of
+which would be representative of relevant biological processes
 (probability of predation in this case). We argue that the probability
@@
 (and allometrically related variables) has been established as such a
-variable (Brose \emph{et al.} 2006); the identification of relevant
-functional traits is facilitated by recent methodological developments
-(Rosado \emph{et al.} 2013). It should be noted that Xing \& Fayle
-(2021) highlight phylogenetic relatedness as one of the core components
-of network comparison at the global scale. In this case study, we have
-embedded the original metaweb using t-SVD, because it lends itself to an
-RDPG reconstruction, which is known to capture the consequences of
-evolutionary processes (Dalla Riva \& Stouffer 2016); this being said,
-there are other ways to embed graphs (Cai \emph{et al.} 2017; Arsov \&
-Mirceva 2019; Cao \emph{et al.} 2019), which can be used as
-alternatives.
+variable (Brose et al., 2006); the identification of relevant functional
+traits is facilitated by recent methodological developments (Rosado et
+al., 2013). It should be noted that Xing \& Fayle (2021) highlight
+phylogenetic relatedness as one of the core components of network
+comparison at the global scale. In this case study, we have embedded the
+original metaweb using t-SVD, because it lends itself to an RDPG
+reconstruction, which is known to capture the consequences of
+evolutionary processes (Dalla Riva \& Stouffer, 2016); this being said,
+there are other ways to embed graphs (Arsov \& Mirceva, 2019; Cai et
+al., 2017; Cao et al., 2019), which can be used as alternatives.
 
@@
 biodiversity assessment, as each country tends to set goals at the
-national level (Buxton \emph{et al.} 2021) for which quantitative
-instruments are designed (Turak \emph{et al.} 2017), with specific
-strategies often enacted at smaller scales (Ray \emph{et al.} 2021). And
-yet, we do not really have a satisfying answer to the question of
-``where does a food web stop?''; the current most satisfying solutions
-involve examining the spatial consistency of network area relationships
-(see \emph{e.g.} Galiana \emph{et al.} 2018, 2019, 2021; Fortin \emph{et
-al.} 2021), which is of course impossible in the absence of enough
-information about the network itself. This suggests that an \emph{a
-posteriori} refinement of the results may be required, based on a
-downscaling of the metaweb. The final family of problems relates less to
-the availability of data or quantitative tools, and more to the praxis
-of spatial ecology. Operating under the context of national divisions,
-in large parts of the world, reflects nothing more than the legacy of
-settler colonialism. Indeed, the use of ecological data is not an
-apolitical act (Nost \& Goldstein 2021), as data infrastructures tend to
-be designed to answer questions within national boundaries, and their
-use both draws upon and reinforces territorial statecraft; as per Machen
-\& Nost (2021), this is particularly true when the output of
-``algorithmic thinking'' (\emph{e.g.} relying on machine learning to
-generate knowledge) can be re-used for governance (\emph{e.g.} enacting
-conservation decisions at the national scale). We therefore recognize
-that methods such as we propose operate under the framework that
-contributed to the ongoing biodiversity crisis (Adam 2014), reinforced
-environmental injustice (Choudry 2013; Domínguez \& Luoma 2020), and on
-Turtle Island especially, should be replaced by Indigenous principles of
-land management (Eichhorn \emph{et al.} 2019; No'kmaq \emph{et al.}
-2021). As we see AI/ML being increasingly mobilized to generate
-knowledge that is lacking for conservation decisions (\emph{e.g.} Lamba
-\emph{et al.} 2019; Mosebo Fernandes \emph{et al.} 2020), our discussion
-of these tools need to go beyond the technical, and into the governance
-consequences they can have.
+national level (Buxton et al., 2021) for which quantitative instruments
+are designed (Turak et al., 2017), with specific strategies often
+enacted at smaller scales (Ray et al., 2021). And yet, we do not really
+have a satisfying answer to the question of ``where does a food web
+stop?''; the current most satisfying solutions involve examining the
+spatial consistency of network area relationships (Fortin et al., 2021;
+see \emph{e.g.} Galiana et al., 2018, 2019, 2021), which is of course
+impossible in the absence of enough information about the network
+itself. This suggests that an \emph{a posteriori} refinement of the
+results may be required, based on a downscaling of the metaweb. The
+final family of problems relates less to the availability of data or
+quantitative tools, and more to the praxis of spatial ecology. Operating
+under the context of national divisions, in large parts of the world,
+reflects nothing more than the legacy of settler colonialism. Indeed,
+the use of ecological data is not an apolitical act (Nost \& Goldstein,
+2021), as data infrastructures tend to be designed to answer questions
+within national boundaries, and their use both draws upon and reinforces
+territorial statecraft; as per Machen \& Nost (2021), this is
+particularly true when the output of ``algorithmic thinking''
+(\emph{e.g.} relying on machine learning to generate knowledge) can be
+re-used for governance (\emph{e.g.} enacting conservation decisions at
+the national scale). We therefore recognize that methods such as we
+propose operate under the framework that contributed to the ongoing
+biodiversity crisis (Adam, 2014), reinforced environmental injustice
+(Choudry, 2013; Domínguez \& Luoma, 2020), and on Turtle Island
+especially, should be replaced by Indigenous principles of land
+management (Eichhorn et al., 2019; No'kmaq et al., 2021). As we see
+AI/ML being increasingly mobilized to generate knowledge that is lacking
+for conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo
+Fernandes et al., 2020), our discussion of these tools need to go beyond
+the technical, and into the governance consequences they can have.
 
@@
 \leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
-Albouy, C., Archambault, P., Appeltans, W., Araújo, M.B., Beauchesne,
-D., Cazelles, K., \emph{et al.} (2019). The marine fish food web is
-globally connected. \emph{Nature Ecology \& Evolution}, 3, 1153--1161.
+Albouy, C., Archambault, P., Appeltans, W., Araújo, M. B., Beauchesne,
+D., Cazelles, K., Cirtwill, A. R., Fortin, M.-J., Galiana, N., Leroux,
+S. J., Pellissier, L., Poisot, T., Stouffer, D. B., Wood, S. A., \&
+Gravel, D. (2019). The marine fish food web is globally connected.
+\emph{Nature Ecology \& Evolution}, \emph{3}(8, 8), 1153--1161.
+\url{https://doi.org/10.1038/s41559-019-0950-y}
 
 \leavevmode\hypertarget{ref-Arsov2019NetEmb}{}%
-Arsov, N. \& Mirceva, G. (2019). \emph{Network Embedding: An Overview}.
-Available at: \url{http://arxiv.org/abs/1911.11726}. Last accessed.
+Arsov, N., \& Mirceva, G. (2019, November 26). \emph{Network Embedding:
+An Overview}. \url{http://arxiv.org/abs/1911.11726}
 
 \leavevmode\hypertarget{ref-Banville2021ManJl}{}%
-Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
+Banville, F., Vissault, S., \& Poisot, T. (2021). Mangal.jl and
 EcologicalNetworks.jl: Two complementary packages for analyzing
-ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
-2721.
+ecological networks in Julia. \emph{Journal of Open Source Software},
+\emph{6}(61), 2721. \url{https://doi.org/10.21105/joss.02721}
 
 \leavevmode\hypertarget{ref-Bascompte2003NesAss}{}%
-Bascompte, J., Jordano, P., Melian, C.J. \& Olesen, J.M. (2003). The
+Bascompte, J., Jordano, P., Melian, C. J., \& Olesen, J. M. (2003). The
 nested assembly of plant-animal mutualistic networks. \emph{Proceedings
-of the National Academy of Sciences}, 100, 9383--9387.
+of the National Academy of Sciences}, \emph{100}(16), 9383--9387.
+\url{https://doi.org/10.1073/pnas.1633576100}
 
 \leavevmode\hypertarget{ref-Beckerman2006ForBio}{}%
-Beckerman, A.P., Petchey, O.L. \& Warren, P.H. (2006). Foraging biology
-predicts food web complexity. \emph{Proceedings of the National Academy
-of Sciences}, 103, 13745--13749.
+Beckerman, A. P., Petchey, O. L., \& Warren, P. H. (2006). Foraging
+biology predicts food web complexity. \emph{Proceedings of the National
+Academy of Sciences}, \emph{103}(37), 13745--13749.
+\url{https://doi.org/10.1073/pnas.0603039103}
 
 \leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
-Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V. (2017). Julia: A
-Fresh Approach to Numerical Computing. \emph{SIAM Review}, 59, 65--98.
+Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
+Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
+65--98. \url{https://doi.org/10.1137/141000671}
 
 \leavevmode\hypertarget{ref-Boeckaerts2021PreBac}{}%
-Boeckaerts, D., Stock, M., Criel, B., Gerstmans, H., De Baets, B. \&
+Boeckaerts, D., Stock, M., Criel, B., Gerstmans, H., De Baets, B., \&
 Briers, Y. (2021). Predicting bacteriophage hosts based on sequences of
-annotated receptor-binding proteins. \emph{Scientific Reports}, 11,
-1467.
+annotated receptor-binding proteins. \emph{Scientific Reports},
+\emph{11}(1, 1), 1467. \url{https://doi.org/10.1038/s41598-021-81063-4}
 
 \leavevmode\hypertarget{ref-Braga2021PhyRec}{}%
-Braga, M.P., Janz, N., Nylin, S., Ronquist, F. \& Landis, M.J. (2021).
-Phylogenetic reconstruction of ancestral ecological networks through
-time for pierid butterflies and their host plants. \emph{Ecology
-Letters}, n/a.
+Braga, M. P., Janz, N., Nylin, S., Ronquist, F., \& Landis, M. J.
+(2021). Phylogenetic reconstruction of ancestral ecological networks
+through time for pierid butterflies and their host plants. \emph{Ecology
+Letters}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/ele.13842}
 
 \leavevmode\hypertarget{ref-Brose2006ConRes}{}%
-Brose, U., Jonsson, T., Berlow, E.L., Warren, P., Banasek-Richter, C.,
-Bersier, L.-F., \emph{et al.} (2006). ConsumerResource Body-Size
-Relationships in Natural Food Webs. \emph{Ecology}, 87, 2411--2417.
+Brose, U., Jonsson, T., Berlow, E. L., Warren, P., Banasek-Richter, C.,
+Bersier, L.-F., Blanchard, J. L., Brey, T., Carpenter, S. R.,
+Blandenier, M.-F. C., Cushing, L., Dawah, H. A., Dell, T., Edwards, F.,
+Harper-Smith, S., Jacob, U., Ledger, M. E., Martinez, N. D., Memmott,
+J., \ldots{} Cohen, J. E. (2006). ConsumerResource Body-Size
+Relationships in Natural Food Webs. \emph{Ecology}, \emph{87}(10),
+2411--2417.
+\url{https://doi.org/10.1890/0012-9658(2006)87\%5B2411:CBRINF\%5D2.0.CO;2}
 
 \leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
-Buxton, R.T., Bennett, J.R., Reid, A.J., Shulman, C., Cooke, S.J.,
-Francis, C.M., \emph{et al.} (2021). Key information needs to move from
+Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
+Francis, C. M., Nyboer, E. A., Pritchard, G., Binley, A. D., Avery-Gomm,
+S., Ban, N. C., Beazley, K. F., Bennett, E., Blight, L. K., Bortolotti,
+L. E., Camfield, A. F., Gadallah, F., Jacob, A. L., Naujokaitis-Lewis,
+I., \ldots{} Smith, P. A. (2021). Key information needs to move from
 knowledge to action for biodiversity conservation in Canada.
-\emph{Biological Conservation}, 256, 108983.
+\emph{Biological Conservation}, \emph{256}, 108983.
+\url{https://doi.org/10.1016/j.biocon.2021.108983}
 
 \leavevmode\hypertarget{ref-Cai2017ComSur}{}%
-Cai, H., Zheng, V.W. \& Chang, K.C.-C. (2017). \emph{A Comprehensive
+Cai, H., Zheng, V. W., \& Chang, K. C.-C. (2017). \emph{A Comprehensive
 Survey of Graph Embedding: Problems, Techniques and Applications}.
-Available at: \url{http://arxiv.org/abs/1709.07604}. Last accessed.
+\url{http://arxiv.org/abs/1709.07604}
 
 \leavevmode\hypertarget{ref-Cameron2019UneGlo}{}%
-Cameron, E.K., Sundqvist, M.K., Keith, S.A., CaraDonna, P.J., Mousing,
-E.A., Nilsson, K.A., \emph{et al.} (2019). Uneven global distribution of
-food web studies under climate change. \emph{Ecosphere}, 10, e02645.
+Cameron, E. K., Sundqvist, M. K., Keith, S. A., CaraDonna, P. J.,
+Mousing, E. A., Nilsson, K. A., Metcalfe, D. B., \& Classen, A. T.
+(2019). Uneven global distribution of food web studies under climate
+change. \emph{Ecosphere}, \emph{10}(3), e02645.
+\url{https://doi.org/10.1002/ecs2.2645}
 
 \leavevmode\hypertarget{ref-Cao2019NetEmb}{}%
-Cao, R.-M., Liu, S.-Y. \& Xu, X.-K. (2019). Network embedding for link
+Cao, R.-M., Liu, S.-Y., \& Xu, X.-K. (2019). Network embedding for link
 prediction: The pitfall and improvement. \emph{Chaos: An
-Interdisciplinary Journal of Nonlinear Science}, 29, 103102.
+Interdisciplinary Journal of Nonlinear Science}, \emph{29}(10), 103102.
+\url{https://doi.org/10.1063/1.5120724}
 
 \leavevmode\hypertarget{ref-Cavender-Bares2009MerCom}{}%
-Cavender-Bares, J., Kozak, K.H., Fine, P.V.A. \& Kembel, S.W. (2009).
-The merging of community ecology and phylogenetic biology. \emph{Ecology
-Letters}, 12, 693--715.
+Cavender-Bares, J., Kozak, K. H., Fine, P. V. A., \& Kembel, S. W.
+(2009). The merging of community ecology and phylogenetic biology.
+\emph{Ecology Letters}, \emph{12}(7), 693--715.
+\url{https://doi.org/10.1111/j.1461-0248.2009.01314.x}
 
@@
 Conservation NGOs, complicity, colonialism and conquest in an era of
-capitalist globalization. In: \emph{NGOization: Complicity,
-contradictions and prospects}. Bloomsbury Publishing, pp. 24--44.
+capitalist globalization. In \emph{NGOization: Complicity,
+contradictions and prospects} (pp. 24--44). Bloomsbury Publishing.
 
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
-Cirtwill, A.R., Ekl, A., Roslin, T., Wootton, K. \& Gravel, D. (2019). A
-quantitative framework for investigating the reliability of empirical
-network construction. \emph{Methods in Ecology and Evolution}, 0.
+Cirtwill, A. R., Ekl, A., Roslin, T., Wootton, K., \& Gravel, D. (2019).
+A quantitative framework for investigating the reliability of empirical
+network construction. \emph{Methods in Ecology and Evolution}, \emph{0}.
+\url{https://doi.org/10.1111/2041-210X.13180}
 
 \leavevmode\hypertarget{ref-Cirtwill2021BuiFoo}{}%
-Cirtwill, A.R. \& Hambäck, P. (2021). Building food networks from
+Cirtwill, A. R., \& Hambäck, P. (2021). Building food networks from
 molecular data: Bayesian or fixed-number thresholds for including links.
-\emph{Basic and Applied Ecology}, 50, 67--76.
+\emph{Basic and Applied Ecology}, \emph{50}, 67--76.
+\url{https://doi.org/10.1016/j.baae.2020.11.007}
 
@@
 Csermely, P. (2004). Strong links are important, but weak links
-stabilize them. \emph{Trends in Biochemical Sciences}, 29, 331--334.
+stabilize them. \emph{Trends in Biochemical Sciences}, \emph{29}(7),
+331--334. \url{https://doi.org/10.1016/j.tibs.2004.05.004}
 
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
-Dalla Riva, G.V. \& Stouffer, D.B. (2016). Exploring the evolutionary
+Dalla Riva, G. V., \& Stouffer, D. B. (2016). Exploring the evolutionary
 signature of food webs' backbones using functional traits. \emph{Oikos},
-125, 446--456.
+\emph{125}(4), 446--456. \url{https://doi.org/10.1111/oik.02305}
 
 \leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
-Dallas, T., Park, A.W. \& Drake, J.M. (2017). Predicting cryptic links
-in host-parasite networks. \emph{PLOS Computational Biology}, 13,
-e1005557.
+Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
+links in host-parasite networks. \emph{PLOS Computational Biology},
+\emph{13}(5), e1005557.
+\url{https://doi.org/10.1371/journal.pcbi.1005557}
 
 \leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
-Dansereau, G. \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
+Dansereau, G., \& Poisot, T. (2021). SimpleSDMLayers.jl and GBIF.jl: A
 Framework for Species Distribution Modeling in Julia. \emph{Journal of
-Open Source Software}, 6, 2872.
+Open Source Software}, \emph{6}(57), 2872.
+\url{https://doi.org/10.21105/joss.02872}
 
 \leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
-Domínguez, L. \& Luoma, C. (2020). Decolonising Conservation Policy: How
-Colonial Land and Conservation Ideologies Persist and Perpetuate
-Indigenous Injustices at the Expense of the Environment. \emph{Land}, 9,
-65.
+Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
+How Colonial Land and Conservation Ideologies Persist and Perpetuate
+Indigenous Injustices at the Expense of the Environment. \emph{Land},
+\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
 
 \leavevmode\hypertarget{ref-Dormann2010EvoCli}{}%
-Dormann, C.F., Gruber, B., Winter, M. \& Herrmann, D. (2010). Evolution
-of climate niches in European mammals? \emph{Biology Letters}, 6,
-229--232.
+Dormann, C. F., Gruber, B., Winter, M., \& Herrmann, D. (2010).
+Evolution of climate niches in European mammals? \emph{Biology Letters},
+\emph{6}(2), 229--232. \url{https://doi.org/10.1098/rsbl.2009.0688}
 
 \leavevmode\hypertarget{ref-Dunne2006NetStr}{}%
-Dunne, J.A. (2006). The Network Structure of Food Webs. In:
-\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
-J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
+Dunne, J. A. (2006). The Network Structure of Food Webs. In J. A. Dunne
+\& M. Pascual (Eds.), \emph{Ecological networks: Linking structure and
+dynamics} (pp. 27--86). Oxford University Press.
 
 \leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
-Eichhorn, M.P., Baker, K. \& Griffiths, M. (2019). Steps towards
-decolonising biogeography. \emph{Frontiers of Biogeography}, 12, 1--7.
+Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
+decolonising biogeography. \emph{Frontiers of Biogeography},
+\emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
 
 \leavevmode\hypertarget{ref-Eklof2016PhyCom}{}%
-Eklöf, A. \& Stouffer, D.B. (2016). The phylogenetic component of food
-web structure and intervality. \emph{Theoretical Ecology}, 9, 107--115.
+Eklöf, A., \& Stouffer, D. B. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theoretical Ecology}, \emph{9}(1),
+107--115. \url{https://doi.org/10.1007/s12080-015-0273-9}
 
 \leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
-Fortin, M.-J., Dale, M.R.T. \& Brimacombe, C. (2021). Network ecology in
-dynamic landscapes. \emph{Proceedings of the Royal Society B: Biological
-Sciences}, 288, rspb.2020.1889, 20201889.
+Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
+in dynamic landscapes. \emph{Proceedings of the Royal Society B:
+Biological Sciences}, \emph{288}(1949), rspb.2020.1889, 20201889.
+\url{https://doi.org/10.1098/rspb.2020.1889}
 
 \leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
-Galiana, N., Barros, C., Braga, J., Ficetola, G.F., Maiorano, L.,
-Thuiller, W., \emph{et al.} (2021). The spatial scaling of food web
-structure across European biogeographical regions. \emph{Ecography},
-n/a.
+Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
+Thuiller, W., Montoya, J. M., \& Lurgi, M. (2021). The spatial scaling
+of food web structure across European biogeographical regions.
+\emph{Ecography}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/ecog.05229}
 
 \leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
-Galiana, N., Hawkins, B.A. \& Montoya, J.M. (2019). The geographical
+Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
 variation of network structure is scale dependent: Understanding the
-biotic specialization of hostparasitoid networks. \emph{Ecography}, 42,
-1175--1187.
+biotic specialization of hostparasitoid networks. \emph{Ecography},
+\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
 
@@
 Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
-Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
-interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.
+Cazelles, K., Gravel, D., \& Montoya, J. M. (2018). The spatial scaling
+of species interaction networks. \emph{Nature Ecology \& Evolution},
+\emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
 
 \leavevmode\hypertarget{ref-Garland1999IntPhy}{}%
-Garland, T., JR., Midford, P.E. \& Ives, A.R. (1999). An Introduction to
-Phylogenetically Based Statistical Methods, with a New Method for
+Garland, T., JR., Midford, P. E., \& Ives, A. R. (1999). An Introduction
+to Phylogenetically Based Statistical Methods, with a New Method for
 Confidence Intervals on Ancestral Values1. \emph{American Zoologist},
-39, 374--388.
+\emph{39}(2), 374--388. \url{https://doi.org/10.1093/icb/39.2.374}
 
 \leavevmode\hypertarget{ref-Garlaschelli2018CovStr}{}%
-Garlaschelli, D., Hollander, F. den \& Roccaverde, A. (2018). Covariance
-structure behind breaking of ensemble equivalence in random graphs.
-\emph{Journal of Statistical Physics}, 173, 644--662.
+Garlaschelli, D., Hollander, F. den, \& Roccaverde, A. (2018).
+Covariance structure behind breaking of ensemble equivalence in random
+graphs. \emph{Journal of Statistical Physics}, \emph{173}(3-4),
+644--662. \url{https://doi.org/10.1007/s10955-018-2114-x}
 
 \leavevmode\hypertarget{ref-GBIFSecretariat2021GbiBac}{}%
-GBIF Secretariat. (2021). GBIF Backbone Taxonomy.
+GBIF Secretariat. (2021). \emph{GBIF Backbone Taxonomy}.
+\url{https://doi.org/10.15468/39omei}
 
 \leavevmode\hypertarget{ref-Gerhold2015PhyPat}{}%
-Gerhold, P., Cahill, J.F., Winter, M., Bartish, I.V. \& Prinzing, A.
+Gerhold, P., Cahill, J. F., Winter, M., Bartish, I. V., \& Prinzing, A.
 (2015). Phylogenetic patterns are not proxies of community assembly
-mechanisms (they are far better). \emph{Functional Ecology}, 29,
-600--614.
+mechanisms (they are far better). \emph{Functional Ecology},
+\emph{29}(5), 600--614. \url{https://doi.org/10.1111/1365-2435.12425}
 
 \leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
-Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
-Nyman, T., \emph{et al.} (2018). Bringing Elton and Grinnell together: A
+Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
+Nyman, T., Poisot, T., Stouffer, D. B., Tylianakis, J. M., Wood, S. A.,
+\& Roslin, T. (2018). Bringing Elton and Grinnell together: A
 quantitative framework to represent the biogeography of ecological
-interaction networks. \emph{Ecography}, 0.
+interaction networks. \emph{Ecography}, \emph{0}(0).
+\url{https://doi.org/10.1111/ecog.04006}
 
 \leavevmode\hypertarget{ref-Grenie2021HarTax}{}%
-Grenié, M., Berti, E., Carvajal-Quintero, J.D., Winter, M. \& Sagouis,
-A. (2021). Harmonizing taxon names in biodiversity data: A review of
-tools, databases, and best practices.
+Grenié, M., Berti, E., Carvajal-Quintero, J. D., Winter, M., \& Sagouis,
+A. (2021). \emph{Harmonizing taxon names in biodiversity data: A review
+of tools, databases, and best practices}.
+\url{https://doi.org/10.32942/osf.io/e3qnz}
 
 \leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
-Grünig, M., Mazzi, D., Calanca, P., Karger, D.N. \& Pellissier, L.
+Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
 (2020). Crop and forest pest metawebs shift towards increased linkage
 and suitability overlap under climate change. \emph{Communications
-Biology}, 3, 1--10.
+Biology}, \emph{3}(1, 1), 1--10.
+\url{https://doi.org/10.1038/s42003-020-0962-9}
 
 \leavevmode\hypertarget{ref-Halevy2009UnrEff}{}%
-Halevy, A., Norvig, P. \& Pereira, F. (2009). The Unreasonable
-Effectiveness of Data. \emph{IEEE Intelligent Systems}, 24, 8--12.
+Halevy, A., Norvig, P., \& Pereira, F. (2009). The Unreasonable
+Effectiveness of Data. \emph{IEEE Intelligent Systems}, \emph{24}(2),
+8--12. \url{https://doi.org/10.1109/MIS.2009.36}
 
 \leavevmode\hypertarget{ref-Halko2011FinStr}{}%
-Halko, N., Martinsson, P.G. \& Tropp, J.A. (2011). Finding Structure
+Halko, N., Martinsson, P. G., \& Tropp, J. A. (2011). Finding Structure
 with Randomness: Probabilistic Algorithms for Constructing Approximate
-Matrix Decompositions. \emph{SIAM Review}, 53, 217--288.
+Matrix Decompositions. \emph{SIAM Review}, \emph{53}(2), 217--288.
+\url{https://doi.org/10.1137/090771806}
 
 \leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, F. (1965). \emph{Dune}. 1st edn. Chilton Book Company,
-Philadelphia.
+Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
 
 \leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
-Hoffmann, J., Bar-Sinai, Y., Lee, L.M., Andrejevic, J., Mishra, S.,
-Rubinstein, S.M., \emph{et al.} (2019). Machine learning in a
+Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
+Rubinstein, S. M., \& Rycroft, C. H. (2019). Machine learning in a
 data-limited regime: Augmenting experiments with synthetic data uncovers
-order in crumpled sheets. \emph{Science Advances}, 5, eaau6792.
+order in crumpled sheets. \emph{Science Advances}, \emph{5}(4),
+eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}
 
 \leavevmode\hypertarget{ref-Holm2019DefBla}{}%
-Holm, E.A. (2019). In defense of the black box. \emph{Science}, 364,
-26--27.
+Holm, E. A. (2019). In defense of the black box. \emph{Science},
+\emph{364}(6435), 26--27. \url{https://doi.org/10.1126/science.aax0162}
 
 \leavevmode\hypertarget{ref-Hortal2015SevSho}{}%
-Hortal, J., de Bello, F., Diniz-Filho, J.A.F., Lewinsohn, T.M., Lobo,
-J.M. \& Ladle, R.J. (2015). Seven Shortfalls that Beset Large-Scale
+Hortal, J., de Bello, F., Diniz-Filho, J. A. F., Lewinsohn, T. M., Lobo,
+J. M., \& Ladle, R. J. (2015). Seven Shortfalls that Beset Large-Scale
 Knowledge of Biodiversity. \emph{Annual Review of Ecology, Evolution,
-and Systematics}, 46, 523--549.
+and Systematics}, \emph{46}(1), 523--549.
+\url{https://doi.org/10.1146/annurev-ecolsys-112414-054400}
 
 \leavevmode\hypertarget{ref-Hutchinson2017CopSig}{}%
-Hutchinson, M.C., Cagua, E.F. \& Stouffer, D.B. (2017). Cophylogenetic
-signal is detectable in pollination interactions across ecological
-scales. \emph{Ecology}, n/a--n/a.
+Hutchinson, M. C., Cagua, E. F., \& Stouffer, D. B. (2017).
+Cophylogenetic signal is detectable in pollination interactions across
+ecological scales. \emph{Ecology}, n/a--n/a.
+\url{https://doi.org/10.1002/ecy.1955}
 
@@
 Jordano, P. (2016b). Sampling networks of ecological interactions.
-\emph{Functional Ecology}, 30, 1883--1893.
+\emph{Functional Ecology}, \emph{30}(12), 1883--1893.
+\url{https://doi.org/10.1111/1365-2435.12763}
 
 \leavevmode\hypertarget{ref-Kawatsu2021AreNet}{}%
-Kawatsu, K., Ushio, M., van Veen, F.J.F. \& Kondoh, M. (2021). Are
+Kawatsu, K., Ushio, M., van Veen, F. J. F., \& Kondoh, M. (2021). Are
 networks of trophic interactions sufficient for understanding the
 dynamics of multi-trophic communities? Analysis of a tri-trophic insect
-food-web time-series. \emph{Ecology Letters}, 24, 543--552.
+food-web time-series. \emph{Ecology Letters}, \emph{24}(3), 543--552.
+\url{https://doi.org/10.1111/ele.13672}
 
 \leavevmode\hypertarget{ref-Kefi2012MorMea}{}%
-Kéfi, S., Berlow, E.L., Wieters, E.A., Navarrete, S.A., Petchey, O.L.,
-Wood, S.A., \emph{et al.} (2012). More than a meal\ldots{} integrating
-non-feeding interactions into food webs: More than a meal \ldots.
-\emph{Ecology Letters}, 15, 291--300.
+Kéfi, S., Berlow, E. L., Wieters, E. A., Navarrete, S. A., Petchey, O.
+L., Wood, S. A., Boit, A., Joppa, L. N., Lafferty, K. D., Williams, R.
+J., Martinez, N. D., Menge, B. A., Blanchette, C. A., Iles, A. C., \&
+Brose, U. (2012). More than a meal\ldots{} integrating non-feeding
+interactions into food webs: More than a meal \ldots. \emph{Ecology
+Letters}, \emph{15}(4), 291--300.
+\url{https://doi.org/10.1111/j.1461-0248.2011.01732.x}
 
 \leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
-Lamba, A., Cassey, P., Segaran, R.R. \& Koh, L.P. (2019). Deep learning
-for environmental conservation. \emph{Current Biology}, 29, R977--R982.
+Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
+learning for environmental conservation. \emph{Current Biology},
+\emph{29}(19), R977--R982.
+\url{https://doi.org/10.1016/j.cub.2019.08.016}
 
 \leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
-Litsios, G. \& Salamin, N. (2012). Effects of Phylogenetic Signal on
-Ancestral State Reconstruction. \emph{Systematic Biology}, 61, 533--538.
+Litsios, G., \& Salamin, N. (2012). Effects of Phylogenetic Signal on
+Ancestral State Reconstruction. \emph{Systematic Biology}, \emph{61}(3),
+533--538. \url{https://doi.org/10.1093/sysbio/syr124}
 
 \leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
-Machen, R. \& Nost, E. (2021). Thinking algorithmically: The making of
+Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
 hegemonic knowledge in climate governance. \emph{Transactions of the
-Institute of British Geographers}, 46, 555--569.
+Institute of British Geographers}, \emph{46}(3), 555--569.
+\url{https://doi.org/10.1111/tran.12441}
+
+\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
+Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
+Thuiller, W. (2020a). TETRA-EU 1.0: A species-level trophic metaweb of
+European tetrapods. \emph{Global Ecology and Biogeography},
+\emph{29}(9), 1452--1457. \url{https://doi.org/10.1111/geb.13138}
 
 \leavevmode\hypertarget{ref-Maiorano2020DatTet}{}%
-Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020a). Data from: Tetra-EU 1.0: A species-level trophic
-meta-web of European tetrapods.
-
-\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
-Maiorano, L., Montemaggiori, A., Ficetola, G.F., O'Connor, L. \&
-Thuiller, W. (2020b). TETRA-EU 1.0: A species-level trophic metaweb of
-European tetrapods. \emph{Global Ecology and Biogeography}, 29,
-1452--1457.
+Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
+Thuiller, W. (2020b). \emph{Data from: Tetra-EU 1.0: A species-level
+trophic meta-web of European tetrapods} (Version 3, pp. 16596876 bytes)
+{[}Data set{]}. Dryad. \url{https://doi.org/10.5061/DRYAD.JM63XSJ7B}
 
 \leavevmode\hypertarget{ref-Marco2018ChaHum}{}%
-Marco, M.D., Venter, O., Possingham, H.P. \& Watson, J.E.M. (2018).
+Marco, M. D., Venter, O., Possingham, H. P., \& Watson, J. E. M. (2018).
 Changes in human footprint drive changes in species extinction risk.
-\emph{Nature Communications}, 9, 4621.
+\emph{Nature Communications}, \emph{9}(1), 4621.
+\url{https://doi.org/10.1038/s41467-018-07049-5}
 
 \leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
-McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
-M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
-of spatial multi-trophic networks. \emph{Oikos}, n/a.
+McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
+M.-J., Galiana, N., Poisot, T., \& Wood, S. A. (2021). Sampling and
+asymptotic network properties of spatial multi-trophic networks.
+\emph{Oikos}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/oik.08650}
 
 \leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
-Mora, B.B., Gravel, D., Gilarranz, L.J., Poisot, T. \& Stouffer, D.B.
-(2018). Identifying a common backbone of interactions underlying food
-webs from different ecosystems. \emph{Nature Communications}, 9, 2603.
+Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
+B. (2018). Identifying a common backbone of interactions underlying food
+webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
 
 \leavevmode\hypertarget{ref-Morales-Castilla2015InfBio}{}%
-Morales-Castilla, I., Matias, M.G., Gravel, D. \& Araújo, M.B. (2015).
-Inferring biotic interactions from proxies. \emph{Trends in Ecology \&
-Evolution}, 30, 347--356.
+Morales-Castilla, I., Matias, M. G., Gravel, D., \& Araújo, M. B.
+(2015). Inferring biotic interactions from proxies. \emph{Trends in
+Ecology \& Evolution}, \emph{30}(6), 347--356.
+\url{https://doi.org/10.1016/j.tree.2015.03.014}
 
 \leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
-Mosebo Fernandes, A.C., Quintero Gonzalez, R., Lenihan-Clarke, M.A.,
-Leslie Trotter, E.F. \& Jokar Arsanjani, J. (2020). Machine Learning for
-Conservation Planning in a Changing Climate. \emph{Sustainability}, 12,
-7657.
+Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
+Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
+for Conservation Planning in a Changing Climate. \emph{Sustainability},
+\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
 
 \leavevmode\hypertarget{ref-Mouquet2012EcoAdv}{}%
-Mouquet, N., Devictor, V., Meynard, C.N., Munoz, F., Bersier, L.-F.,
-Chave, J., \emph{et al.} (2012). Ecophylogenetics: Advances and
-perspectives. \emph{Biological Reviews}, 87, 769--785.
+Mouquet, N., Devictor, V., Meynard, C. N., Munoz, F., Bersier, L.-F.,
+Chave, J., Couteron, P., Dalecky, A., Fontaine, C., Gravel, D., Hardy,
+O. J., Jabot, F., Lavergne, S., Leibold, M., Mouillot, D., Münkemüller,
+T., Pavoine, S., Prinzing, A., Rodrigues, A. S. L., \ldots{} Thuiller,
+W. (2012). Ecophylogenetics: Advances and perspectives. \emph{Biological
+Reviews}, \emph{87}(4), 769--785.
+\url{https://doi.org/10.1111/j.1469-185X.2012.00224.x}
 
 \leavevmode\hypertarget{ref-Nenzen2014Imp850}{}%
-Nenzén, H.K., Montoya, D. \& Varela, S. (2014). The Impact of 850,000
+Nenzén, H. K., Montoya, D., \& Varela, S. (2014). The Impact of 850,000
 Years of Climate Changes on the Structure and Dynamics of Mammal Food
-Webs. \emph{PLOS ONE}, 9, e106651.
+Webs. \emph{PLOS ONE}, \emph{9}(9), e106651.
+\url{https://doi.org/10.1371/journal.pone.0106651}
 
 \leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
-Neutel, A.-M., Heesterbeek, J.A.P. \& de Ruiter, P.C. (2002). Stability
-in Real Food Webs: Weak Links in Long Loops. \emph{Science}, 296,
-1120--1123.
+Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
+Stability in Real Food Webs: Weak Links in Long Loops. \emph{Science},
+\emph{296}(5570), 1120--1123.
+\url{https://doi.org/10.1126/science.1068326}
 
 \leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
-No'kmaq, M., Marshall, A., Beazley, K.F., Hum, J., joudry, shalan,
-Papadopoulos, A., \emph{et al.} (2021). {``Awakening the sleeping
-giant''}: Re-Indigenization principles for transforming biodiversity
-conservation in Canada and beyond. \emph{FACETS}, 6, 839--869.
+No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
+Papadopoulos, A., Pictou, S., Rabesca, J., Young, L., \& Zurba, M.
+(2021). {``Awakening the sleeping giant''}: Re-Indigenization principles
+for transforming biodiversity conservation in Canada and beyond.
+\emph{FACETS}, \emph{6}(1), 839--869.
 
 \leavevmode\hypertarget{ref-Nost2021PolEco}{}%
-Nost, E. \& Goldstein, J.E. (2021). A political ecology of data.
+Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
 \emph{Environment and Planning E: Nature and Space}, 25148486211043503.
+\url{https://doi.org/10.1177/25148486211043503}
 
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
-O'Connor, L.M.J., Pollock, L.J., Braga, J., Ficetola, G.F., Maiorano,
-L., Martinez-Almoyna, C., \emph{et al.} (2020). Unveiling the food webs
-of tetrapods across Europe through the prism of the Eltonian niche.
-\emph{Journal of Biogeography}, 47, 181--192.
+O'Connor, L. M. J., Pollock, L. J., Braga, J., Ficetola, G. F.,
+Maiorano, L., Martinez-Almoyna, C., Montemaggiori, A., Ohlmann, M., \&
+Thuiller, W. (2020). Unveiling the food webs of tetrapods across Europe
+through the prism of the Eltonian niche. \emph{Journal of Biogeography},
+\emph{47}(1), 181--192. \url{https://doi.org/10.1111/jbi.13773}
 
 \leavevmode\hypertarget{ref-Pan2010SurTra}{}%
-Pan, S.J. \& Yang, Q. (2010). A Survey on Transfer Learning. \emph{IEEE
-Transactions on Knowledge and Data Engineering}, 22, 1345--1359.
+Pan, S. J., \& Yang, Q. (2010). A Survey on Transfer Learning.
+\emph{IEEE Transactions on Knowledge and Data Engineering},
+\emph{22}(10), 1345--1359. \url{https://doi.org/10.1109/TKDE.2009.191}
 
 \leavevmode\hypertarget{ref-Park2004StaMec}{}%
-Park, J. \& Newman, M.E.J. (2004). Statistical mechanics of networks.
-\emph{Physical Review E}, 70, 066117.
+Park, J., \& Newman, M. E. J. (2004). Statistical mechanics of networks.
+\emph{Physical Review E}, \emph{70}(6), 066117.
+\url{https://doi.org/10.1103/PhysRevE.70.066117}
 
 \leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
-Pedersen, E.J., Thompson, P.L., Ball, R.A., Fortin, M.-J., Gouhier,
-T.C., Link, H., \emph{et al.} (2017). Signatures of the collapse and
-incipient recovery of an overexploited marine ecosystem. \emph{Royal
-Society Open Science}, 4, 170215.
+Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
+T. C., Link, H., Moritz, C., Nenzen, H., Stanley, R. R. E., Taranu, Z.
+E., Gonzalez, A., Guichard, F., \& Pepin, P. (2017). Signatures of the
+collapse and incipient recovery of an overexploited marine ecosystem.
+\emph{Royal Society Open Science}, \emph{4}(7), 170215.
+\url{https://doi.org/10.1098/rsos.170215}
 
 \leavevmode\hypertarget{ref-Perretti2013ModFor}{}%
-Perretti, C.T., Munch, S.B. \& Sugihara, G. (2013). Model-free
+Perretti, C. T., Munch, S. B., \& Sugihara, G. (2013). Model-free
 forecasting outperforms the correct mechanistic model for simulated and
 experimental data. \emph{Proceedings of the National Academy of
-Sciences}, 110, 5253--5257.
+Sciences}, \emph{110}(13), 5253--5257.
+\url{https://doi.org/10.1073/pnas.1216076110}
 
 \leavevmode\hypertarget{ref-Pires2015PleMeg}{}%
-Pires, M.M., Koch, P.L., Fariña, R.A., de Aguiar, M.A.M., dos Reis, S.F.
-\& Guimarães, P.R. (2015). Pleistocene megafaunal interaction networks
-became more vulnerable after human arrival. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, 282, 20151367.
+Pires, M. M., Koch, P. L., Fariña, R. A., de Aguiar, M. A. M., dos Reis,
+S. F., \& Guimarães, P. R. (2015). Pleistocene megafaunal interaction
+networks became more vulnerable after human arrival. \emph{Proceedings
+of the Royal Society B: Biological Sciences}, \emph{282}(1814),
+20151367. \url{https://doi.org/10.1098/rspb.2015.1367}
 
 \leavevmode\hypertarget{ref-Poelen2014GloBio}{}%
-Poelen, J.H., Simons, J.D. \& Mungall, C.J. (2014). Global biotic
+Poelen, J. H., Simons, J. D., \& Mungall, C. J. (2014). Global biotic
 interactions: An open infrastructure to share and analyze
-species-interaction datasets. \emph{Ecological Informatics}, 24,
-148--159.
+species-interaction datasets. \emph{Ecological Informatics}, \emph{24},
+148--159. \url{https://doi.org/10.1016/j.ecoinf.2014.08.005}
 
 \leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
-Poisot, T., Belisle, Z., Hoebeke, L., Stock, M. \& Szefer, P. (2019).
+Poisot, T., Belisle, Z., Hoebeke, L., Stock, M., \& Szefer, P. (2019).
 EcologicalNetworks.jl - analysing ecological networks. \emph{Ecography}.
+\url{https://doi.org/10.1111/ecog.04310}
 
@@
 Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
-MacDonald, A., \emph{et al.} (2021a). Global knowledge gaps in species
-interaction networks data. \emph{Journal of Biogeography}, n/a.
+MacDonald, A., Mercier, B., Violet, C., \& Vissault, S. (2021). Global
+knowledge gaps in species interaction networks data. \emph{Journal of
+Biogeography}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/jbi.14127}
 
 \leavevmode\hypertarget{ref-Poisot2016StrPro}{}%
-Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
-Stouffer, D.B. (2016). The structure of probabilistic networks.
-\emph{Methods in Ecology and Evolution}, 7, 303--312.
+Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., \&
+Stouffer, D. B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, \emph{7}(3), 303--312.
+\url{https://doi.org/10.1111/2041-210X.12468}
 
 \leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
-Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
-Albery, G.F., \emph{et al.} (2021b). \emph{Imputing the mammalian virome
-with linear filtering and singular value decomposition}. Available at:
-\url{http://arxiv.org/abs/2105.14973}. Last accessed.
+Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
+J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J. (2021,
+May 31). \emph{Imputing the mammalian virome with linear filtering and
+singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}
 
 \leavevmode\hypertarget{ref-Poisot2018IntRet}{}%
-Poisot, T. \& Stouffer, D.B. (2018). Interactions retain the
-co-phylogenetic matching that communities lost. \emph{Oikos}, 127,
-230--238.
+Poisot, T., \& Stouffer, D. B. (2018). Interactions retain the
+co-phylogenetic matching that communities lost. \emph{Oikos},
+\emph{127}(2), 230--238. \url{https://doi.org/10.1111/oik.03788}
 
 \leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
-Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
 ecological interaction networks vary through space and time.
-\emph{Oikos}, 124, 243--251.
+\emph{Oikos}, \emph{124}(3), 243--251.
+\url{https://doi.org/10.1111/oik.01719}
 
 \leavevmode\hypertarget{ref-Price2003MacThe}{}%
-Price, P.W. (2003). \emph{Macroevolutionary theory on macroecological
+Price, P. W. (2003). \emph{Macroevolutionary theory on macroecological
 patterns}. Cambridge University Press.
@@
 \leavevmode\hypertarget{ref-Ray2021BioCri}{}%
-Ray, J.C., Grimm, J. \& Olive, A. (2021). The biodiversity crisis in
+Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
 Canada: Failures and challenges of federal and sub-national strategic
-and legal frameworks. \emph{FACETS}, 6, 1044--1068.
+and legal frameworks. \emph{FACETS}, \emph{6}, 1044--1068.
+\url{https://doi.org/10.1139/facets-2020-0075}
 
 \leavevmode\hypertarget{ref-Reeve2016HowPar}{}%
-Reeve, R., Leinster, T., Cobbold, C.A., Thompson, J., Brummitt, N.,
-Mitchell, S.N., \emph{et al.} (2016). \emph{How to partition diversity}.
-Available at: \url{http://arxiv.org/abs/1404.6520}. Last accessed.
+Reeve, R., Leinster, T., Cobbold, C. A., Thompson, J., Brummitt, N.,
+Mitchell, S. N., \& Matthews, L. (2016, December 8). \emph{How to
+partition diversity}. \url{http://arxiv.org/abs/1404.6520}
 
 \leavevmode\hypertarget{ref-Rosado2013GoiBac}{}%
-Rosado, B.H.P., Dias, A. \& de Mattos, E. (2013). Going Back to Basics:
-Importance of Ecophysiology when Choosing Functional Traits for Studying
-Communities and Ecosystems. \emph{Natureza \&
-conservaç\textasciitilde ao revista brasileira de
-conservaç\textasciitilde ao da natureza}, 11, 15--22.
+Rosado, B. H. P., Dias, A., \& de Mattos, E. (2013). Going Back to
+Basics: Importance of Ecophysiology when Choosing Functional Traits for
+Studying Communities and Ecosystems. \emph{Natureza \&
+Conservaç\textasciitilde ao Revista Brasileira de
+Conservaç\textasciitilde ao Da Natureza}, \emph{11}, 15--22.
+\url{https://doi.org/10.4322/natcon.2013.002}
 
 \leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
-Runghen, R., Stouffer, D.B. \& Dalla Riva, G.V. (2021). Exploiting node
-metadata to predict interactions in large networks using graph embedding
-and neural networks.
+Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
+\emph{Exploiting node metadata to predict interactions in large networks
+using graph embedding and neural networks}.
+\url{https://doi.org/10.1101/2021.06.10.447991}
 
 \leavevmode\hypertarget{ref-Schoener1989FooWeb}{}%
-Schoener, T.W. (1989). Food webs from the small to the large.
-\emph{Ecology}, 70, 1559--1589.
+Schoener, T. W. (1989). Food webs from the small to the large.
+\emph{Ecology}, \emph{70}(6), 1559--1589.
 
 \leavevmode\hypertarget{ref-Shlens2014TutPri}{}%
-Shlens, J. (2014). \emph{A Tutorial on Principal Component Analysis}.
-Available at: \url{http://arxiv.org/abs/1404.1100}. Last accessed.
+Shlens, J. (2014, April 3). \emph{A Tutorial on Principal Component
+Analysis}. \url{http://arxiv.org/abs/1404.1100}
 
 \leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%
-Solís-Lemus, C., Bastide, P. \& Ané, C. (2017). PhyloNetworks: A Package
-for Phylogenetic Networks. \emph{Molecular Biology and Evolution}, 34,
-3292--3298.
+Solís-Lemus, C., Bastide, P., \& Ané, C. (2017). PhyloNetworks: A
+Package for Phylogenetic Networks. \emph{Molecular Biology and
+Evolution}, \emph{34}(12), 3292--3298.
+\url{https://doi.org/10.1093/molbev/msx235}
 
@@
 \leavevmode\hypertarget{ref-Stouffer2012EvoCon}{}%
-Stouffer, D.B., Sales-Pardo, M., Sirer, M.I. \& Bascompte, J. (2012).
+Stouffer, D. B., Sales-Pardo, M., Sirer, M. I., \& Bascompte, J. (2012).
 Evolutionary Conservation of Species' Roles in Food Webs.
-\emph{Science}, 335, 1489--1492.
+\emph{Science}, \emph{335}(6075), 1489--1492.
+\url{https://doi.org/10.1126/science.1216556}
 
 \leavevmode\hypertarget{ref-Strong2014ImpNon}{}%
-Strong, J.S. \& Leroux, S.J. (2014). Impact of Non-Native Terrestrial
+Strong, J. S., \& Leroux, S. J. (2014). Impact of Non-Native Terrestrial
 Mammals on the Structure of the Terrestrial Mammal Food Web of
-Newfoundland, Canada. \emph{PLOS ONE}, 9, e106264.
+Newfoundland, Canada. \emph{PLOS ONE}, \emph{9}(8), e106264.
+\url{https://doi.org/10.1371/journal.pone.0106264}
 
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
-Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021a). A roadmap towards
-predicting species interaction networks (across space and time).
+Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
+Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
+towards predicting species interaction networks (across space and time).
 \emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences}, 376, 20210063.
+Sciences}, \emph{376}(1837), 20210063.
+\url{https://doi.org/10.1098/rstb.2021.0063}
 
 \leavevmode\hypertarget{ref-Strydom2021SvdEnt}{}%
-Strydom, T., Dalla Riva, G.V. \& Poisot, T. (2021b). SVD Entropy Reveals
-the High Complexity of Ecological Networks. \emph{Frontiers in Ecology
-and Evolution}, 9.
+Strydom, T., Dalla Riva, G. V., \& Poisot, T. (2021). SVD Entropy
+Reveals the High Complexity of Ecological Networks. \emph{Frontiers in
+Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.623141}
 
 \leavevmode\hypertarget{ref-Thessen2014KnoExt}{}%
-Thessen, A.E. \& Parr, C.S. (2014). Knowledge extraction and semantic
-annotation of text from the encyclopedia of life. \emph{PloS one}, 9,
-e89550.
+Thessen, A. E., \& Parr, C. S. (2014). Knowledge extraction and semantic
+annotation of text from the encyclopedia of life. \emph{PloS One},
+\emph{9}(3), e89550.
 
 \leavevmode\hypertarget{ref-Torrey2010TraLea}{}%
-Torrey, L. \& Shavlik, J. (2010). Transfer learning. In: \emph{Handbook
+Torrey, L., \& Shavlik, J. (2010). Transfer learning. In \emph{Handbook
 of research on machine learning applications and trends: Algorithms,
-methods, and techniques}. IGI global, pp. 242--264.
+methods, and techniques} (pp. 242--264). IGI global.
 
 \leavevmode\hypertarget{ref-Trojelsgaard2016EcoNet}{}%
-Trøjelsgaard, K. \& Olesen, J.M. (2016). Ecological networks in motion:
-Micro- and macroscopic variability across scales. \emph{Functional
-Ecology}, 30, 1926--1935.
+Trøjelsgaard, K., \& Olesen, J. M. (2016). Ecological networks in
+motion: Micro- and macroscopic variability across scales.
+\emph{Functional Ecology}, \emph{30}(12), 1926--1935.
+\url{https://doi.org/10.1111/1365-2435.12710}
 
@@
 Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
-Dunkerley, G., \emph{et al.} (2017). Using the essential biodiversity
-variables framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, SI:measures of biodiversity, 213,
-264--271.
+Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
+T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
+Williams, K. (2017). Using the essential biodiversity variables
+framework to measure biodiversity change at national scale.
+\emph{Biological Conservation}, \emph{213}, 264--271.
+\url{https://doi.org/10.1016/j.biocon.2016.08.019}
 
 \leavevmode\hypertarget{ref-Upham2019InfMam}{}%
-Upham, N.S., Esselstyn, J.A. \& Jetz, W. (2019). Inferring the mammal
+Upham, N. S., Esselstyn, J. A., \& Jetz, W. (2019). Inferring the mammal
 tree: Species-level sets of phylogenies for questions in ecology,
-evolution, and conservation. \emph{PLOS Biology}, 17, e3000494.
+evolution, and conservation. \emph{PLOS Biology}, \emph{17}(12),
+e3000494. \url{https://doi.org/10.1371/journal.pbio.3000494}
 
 \leavevmode\hypertarget{ref-vanderHoorn2018SpaMax}{}%
-van der Hoorn, P., Lippner, G. \& Krioukov, D. (2018). Sparse
+van der Hoorn, P., Lippner, G., \& Krioukov, D. (2018). Sparse
 Maximum-Entropy Random Graphs with a Given Power-Law Degree
-Distribution. \emph{Journal of Statistical Physics}, 173, 806--844.
+Distribution. \emph{Journal of Statistical Physics}, \emph{173}(3-4),
+806--844. \url{https://doi.org/10.1007/s10955-017-1887-7}
 
 \leavevmode\hypertarget{ref-Vermaat2009MajDim}{}%
-Vermaat, J.E., Dunne, J.A. \& Gilbert, A.J. (2009). Major dimensions in
-food-web structure properties. \emph{Ecology}, 90, 278--282.
+Vermaat, J. E., Dunne, J. A., \& Gilbert, A. J. (2009). Major dimensions
+in food-web structure properties. \emph{Ecology}, \emph{90}(1),
+278--282. \url{http://www.ncbi.nlm.nih.gov/pubmed/19294932}
 
 \leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
-Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
 (2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, 5, 3769--3782.
+\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
+\url{https://doi.org/10.1002/ece3.1640}
 
 \leavevmode\hypertarget{ref-Xing2021RisEco}{}%
-Xing, S. \& Fayle, T.M. (2021). The rise of ecological network
+Xing, S., \& Fayle, T. M. (2021). The rise of ecological network
 meta-analyses: Problems and prospects. \emph{Global Ecology and
-Conservation}, 30, e01805.
+Conservation}, \emph{30}, e01805.
+\url{https://doi.org/10.1016/j.gecco.2021.e01805}
 
 \leavevmode\hypertarget{ref-Yeakel2014ColEco}{}%
-Yeakel, J.D., Pires, M.M., Rudolf, L., Dominy, N.J., Koch, P.L.,
-Guimarães, P.R., \emph{et al.} (2014). Collapse of an ecological network
-in Ancient Egypt. \emph{PNAS}, 111, 14472--14477.
+Yeakel, J. D., Pires, M. M., Rudolf, L., Dominy, N. J., Koch, P. L.,
+Guimarães, P. R., \& Gross, T. (2014). Collapse of an ecological network
+in Ancient Egypt. \emph{PNAS}, \emph{111}(40), 14472--14477.
+\url{https://doi.org/10.1073/pnas.1408471111}
 
 \leavevmode\hypertarget{ref-Youden1950IndRat}{}%
-Youden, W.J. (1950). Index for rating diagnostic tests. \emph{Cancer},
-3, 32--35.
+Youden, W. J. (1950). Index for rating diagnostic tests. \emph{Cancer},
+\emph{3}(1), 32--35.
+\url{https://doi.org/10.1002/1097-0142(1950)3:1\%3C32::AID-CNCR2820030106\%3E3.0.CO;2-3}
 
 \leavevmode\hypertarget{ref-Young2021BayInf}{}%
-Young, J.-G., Cantwell, G.T. \& Newman, M.E.J. (2021). Bayesian
+Young, J.-G., Cantwell, G. T., \& Newman, M. E. J. (2021). Bayesian
 inference of network structure from unreliable data. \emph{Journal of
-Complex Networks}, 8.
+Complex Networks}, \emph{8}(6).
+\url{https://doi.org/10.1093/comnet/cnaa046}
 
 \leavevmode\hypertarget{ref-Young2007RanDot}{}%
-Young, S.J. \& Scheinerman, E.R. (2007). Random Dot Product Graph Models
-for Social Networks. In: \emph{Algorithms and Models for the Web-Graph},
-Lecture Notes in Computer Science (eds. Bonato, A. \& Chung, F.R.K.).
-Springer, Berlin, Heidelberg, pp. 138--149.
+Young, S. J., \& Scheinerman, E. R. (2007). Random Dot Product Graph
+Models for Social Networks. In A. Bonato \& F. R. K. Chung (Eds.),
+\emph{Algorithms and Models for the Web-Graph} (pp. 138--149). Springer.
+\url{https://doi.org/10.1007/978-3-540-77004-6_11}
 
 \leavevmode\hypertarget{ref-Zhu2006AutDim}{}%
-Zhu, M. \& Ghodsi, A. (2006). Automatic dimensionality selection from
+Zhu, M., \& Ghodsi, A. (2006). Automatic dimensionality selection from
 the scree plot via the use of profile likelihood. \emph{Computational
-Statistics \& Data Analysis}, 51, 918--930.
+Statistics \& Data Analysis}, \emph{51}(2), 918--930.
+\url{https://doi.org/10.1016/j.csda.2005.09.010}
 

### 2021-11-03 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@40a6ba0ece7ab414b8f3153607c43069d1b9edb6 🚀

@@
 \begin{enumerate}
-    \itemDespite their importance in many ecological processes,
+    \item Despite their importance in many ecological processes,
 collecting data and information on ecological interactions is an
@@
 to be sufficient, community ecologists must adopt predictive methods.%
-    \itemWe present a methodological framework that uses graph embedding
-and transfer learning to assemble a predicted list of trophic
+    \item We present a methodological framework that uses graph
+embedding and transfer learning to assemble a predicted list of trophic
 interactions of a species pool for which their interactions are unknown.
@@
 interactions and construct and interaction network.%
-    \itemHere we assembled a metaweb for Canadian mammals derived from
+    \item Here we assembled a metaweb for Canadian mammals derived from
 interactions in the European food web, despite only 4\% of common
@@
 interactions.%
-    \itemThe framework itself is robust even when the known network is
+    \item The framework itself is robust even when the known network is
 incomplete or contains spurious interactions making it an ideal

### 2021-11-03 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@c4b04a3fe4b39edfe72220031c65df498f0238a1 🚀

@@
 
+\textbf{Conflict of interest:} The authors have no conflict interests to
+disclose
+
+\textbf{Authors' contributions:} TS, SB, and TP designed the study and
+performed the analysis; GVDR, MF, and RR provided additional feedback on
+the analyses. DC, BM, and FB helped with data collection. All editors
+contributed to writing and editing the manuscript.
+
+\textbf{Data availability:} All code and data used in this manuscript is
+publicly available and archived on OSF \url{https://osf.io/2zwqm/} and
+is currently referenced in the manuscript.
+
 \hypertarget{references}{%

### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@cf723b26cf48b6350d857f651e5d72035bb526cd 🚀

@@
 the known network. The latent traits can then be used to predict
-interactions and construct and interaction network.%
+interactions and construct an interaction network.%
     \item Here we assembled a metaweb for Canadian mammals derived from
@@
 candidate as a tool for filling gaps when it comes to species
-interactions. We provide guidance on how this frameworl can be adapted
+interactions. We provide guidance on how this framework can be adapted
 by substituting some approaches or predictors in order to make it more
@@
 
-Here, we present a general method to recommend potential trophic
+Here, we present a general method to infer potential trophic
 interactions, relying on the transfer learning of network
@@
 (Cavender-Bares et al., 2009; Mouquet et al., 2012), and - most
-importantly - retain this signal even when it is not detectable at the
-community scale (Hutchinson et al., 2017; Poisot \& Stouffer, 2018).
-Finally, species interactions at macro-ecological scales seem to respond
-mostly to macro-evolutionary processes (Price, 2003); which is evidenced
-by the presence of conserved backbones in food webs (Dalla Riva \&
-Stouffer, 2016; Mora et al., 2018), strong evolutionary signature on
-prey choice (Stouffer et al., 2012), and strong phylogenetic signature
-in food web intervality (Eklöf \& Stouffer, 2016). Phylogenetic
-reconstruction has also previously been used within the context of
-ecological networks, namely understanding ancestral plant-insect
-interactions (Braga et al., 2021). Taken together, these considerations
-suggest that phylogenies can reliably be used to transfer knowledge on
-species interactions.
+importantly - retain this signal even if it is obscured at the community
+scale due to \emph{e.g.} local conditions (Hutchinson et al., 2017;
+Poisot \& Stouffer, 2018). Finally, species interactions at
+macro-ecological scales seem to respond mostly to macro-evolutionary
+processes (Price, 2003); which is evidenced by the presence of conserved
+backbones in food webs (Dalla Riva \& Stouffer, 2016; Mora et al.,
+2018), strong evolutionary signature on prey choice (Stouffer et al.,
+2012), and strong phylogenetic signature in food web intervality (Eklöf
+\& Stouffer, 2016). Phylogenetic reconstruction has also previously been
+used within the context of ecological networks, namely understanding
+ancestral plant-insect interactions (Braga et al., 2021). Taken
+together, these considerations suggest that phylogenies can reliably be
+used to transfer knowledge on species interactions.
 
@@
 \centering
-\includegraphics{figures/figure-concept.png}
+\includegraphics{figures/figure-concept_v2.png}
 \caption{Overview of the phylogenetic transfer learning (and prediction)
@@
 
-Our methodology is outlined in fig.~\ref{fig:concept}, where we provide
-an illustration based on learning the embedding of a metaweb of trophic
-interactions for European mammals (known interactions; Maiorano et al.,
-2020a, 2020b) and, based on phylogenetic relationships between mammals
-globally (\emph{i.e.}, phylogenetic tree Upham et al., 2019), infer a
-metaweb for the Canadian mammalian species pool (interactions are
-treated as unknown in this instance). Following the definition of Dunne
-(2006), a metaweb is a network analogue to the regional species pool;
-specifically, it is an inventory of all \emph{potential} interactions
-between species from a spatially delimited area (and so captures the
-\(\gamma\) diversity of interactions). The metaweb is, therefore,
-\emph{not} a prediction of the food web at a specific locale within the
-spatial area it covers, and will have a different structure (notably by
-having a larger connectance; see \emph{e.g.} Wood et al., 2015). These
-local food webs (which captures the \(\alpha\) diversity of
-interactions) are a subset of the metaweb's species and interactions,
-and have been called ``metaweb realizations'' (Poisot et al., 2015).
-Differences between local food web and their metaweb are due to chance,
-species abundance and co-occurrence, local environmental conditions, and
-local distribution of functional traits, among others.
+In fig.~\ref{fig:concept}, where we provide a methodological overview
+based on learning the embedding of a metaweb of trophic interactions for
+European mammals (known interactions; Maiorano et al., 2020a, 2020b)
+and, based on phylogenetic relationships between mammals globally
+(\emph{i.e.}, phylogenetic tree Upham et al., 2019), infer a metaweb for
+the Canadian mammalian species pool (using only a species list
+\emph{i.e.} interactions are `unknown' in this instance). Following the
+definition of Dunne (2006), a metaweb is a network analogue to the
+regional species pool; specifically, it is an inventory of all
+\emph{potential} interactions between species from a spatially delimited
+area (and so captures the \(\gamma\) diversity of interactions). The
+metaweb is, therefore, \emph{not} a prediction of the food web at a
+specific locale within the spatial area it covers, and will have a
+different structure (notably by having a larger connectance; see
+\emph{e.g.} Wood et al., 2015). These local food webs (which captures
+the \(\alpha\) diversity of interactions) are a subset of the metaweb's
+species and interactions, and have been called ``metaweb realizations''
+(Poisot et al., 2015). Differences between local food web and their
+metaweb are due to chance, species abundance and co-occurrence, local
+environmental conditions, and local distribution of functional traits,
+among others.
 
@@
 approximately 91\%. It should be reiterated that the framework presented
-in fig.~\ref{fig:concept} is amenable to changes; notably, the measure
-of similarity may not be phylogeny, and can be replaced by information
-on foraging (Beckerman et al., 2006), cell-level mechanisms (Boeckaerts
-et al., 2021), or a combination of traits and phylogenetic structure
-(Stock, 2021). Most importantly, although we focus on a trophic system,
-it is an established fact that different (non-trophic) interactions do
-themselves interact with and influence the outcome of trophic
-interactions (see \emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012).
-Future development of metaweb inference techniques should cover the
-prediction of multiple interaction types.
+in fig.~\ref{fig:concept} is amenable to changes \emph{e.g.} it is
+possible to use distinct trees if working with distinct clades (such as
+pollination networks) or, alternatively, the measure of similarity may
+not be phylogeny, and can be replaced by information on foraging
+(Beckerman et al., 2006), cell-level mechanisms (Boeckaerts et al.,
+2021), or a combination of traits and phylogenetic structure (Stock,
+2021). Most importantly, although we focus on a trophic system, it is an
+established fact that different (non-trophic) interactions do themselves
+interact with and influence the outcome of trophic interactions (see
+\emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012). Future development
+of metaweb inference techniques should cover the prediction of multiple
+interaction types.
 
@@
 introduced in historical times and currently naturalized being included.
-This metaweb itself is a network of binary (\emph{i.e.}
-presence/absence), potential two-way interactions between species pairs.
-
-We filtered down the European metaweb to create a subgraph corresponding
-to all mammals by matching species names in the original network to the
-Global Biodiversity Information Facility (GBIF) taxonomic backbone (GBIF
-Secretariat, 2021) and retaining all those who matched to mammals. This
-serves a dual purpose 1) to extract only mammals from the European
-network and 2) to match and standardize species names when aggregating
-the different data sources further downstream (which is an important
-consideration when combining datasets (Grenié et al., 2021)). All nodes
-had valid matches to GBIF at this step, and so this backbone is used for
-all name reconciliation steps as outlined below.
-
-The European metaweb represents the knowledge we want to learn and
-transfer; the phylogenetic similarity of mammals here represents the
-information for transfer (\emph{i.e.} the transfer medium). We used the
-mammalian consensus supertree by Upham et al. (2019), for which all
-approximatively 6000 names have been similarly matched to their GBIF
-valid names. This step allows us to place each node of the mammalian
-European metaweb in the phylogeny.
-
-The destination problem to which we want to transfer knowledge is the
-trophic interactions between mammals in Canada. We obtained the list of
-extant species from the International Union for Conservation of Nature
-(IUCN) checklist, and selected the terrestrial and semi-aquatic species
-(this corresponds to the same selection that was applied by Maiorano et
-al. (2020a) in the European metaweb). The IUCN names were, as
-previously, reconciled against GBIF to have an exact match to the
-taxonomy.
-
-After taxonomic cleaning and reconciliation as outlined in the following
-sections, the mammalian European metaweb has 260 species, and the
-Canadian species pool has 163; of these, 17 (about 4\% of the total) are
-shared, and 89 species from Canada (54\%) had at least one congeneric
-species in Europe. The similarity for both species pools predictably
-increases with higher taxonomic order, with 19\% of shared genera, 47\%
-of shared families, and 75\% of shared orders; for the last point,
-Canada and Europe each had a single unique order (\emph{Didelphimorphia}
-for Canada, \emph{Erinaceomorpha} for Europe).
-
-In the following sections, we describe the representational learning
-step applied to European data, the transfer step through phylogenetic
-similarity, and the generation of a probabilistic metaweb for the
-destination species pool.
+The European metaweb was filtered using the Global Biodiversity
+Information Facility (GBIF) taxonomic backbone (GBIF Secretariat, 2021)
+so as to contain only terrestrial and semi-aquatic mammals. As all
+species had valid matches to the GBIF taxonomy it was used as the
+backbone for the remaining reconciliation steps namely, the mammalian
+consensus supertree by Upham et al. (2019) (which is used for the
+knowledge transfer step) and for the Canadian species list---which was
+extracted from the International Union for Conservation of Nature (IUCN)
+checklist, and corresponds to the same selection criteria that was
+applied by Maiorano et al. (2020a) in the European metaweb.
+
+After taxonomic cleaning and reconciliation the mammalian European
+metaweb has 260 species, and the Canadian species pool 163; of these, 17
+(about 4\% of the total) are shared, and 89 species from Canada (54\%)
+had at least one congeneric species in Europe. The similarity for both
+species pools predictably increases with higher taxonomic order, with
+19\% of shared genera, 47\% of shared families, and 75\% of shared
+orders; for the last point, Canada and Europe each had a single unique
+order (\emph{Didelphimorphia} for Canada, \emph{Erinaceomorpha} for
+Europe).
 
@@
 ecological network, in order to predict interactions between species
-from another location at which the network is unknown (or partially
-known). In fig.~\ref{fig:concept}, we give a high-level overview of the
-approach; in the example around which this manuscript is built
-(leveraging detailed knowledge about binary trophic interactions between
-Mammalia in Europe to predict the less known trophic interactions
-between closely phylogenetically related Mammalia in Canada), we use a
-series of specific steps for network embedding, trait inference, network
-prediction and thresholding.
-
-Specifically, our approach can be summarized as follows: from the known
-network in Europe, we use a truncated Singular Value Decomposition
-(t-SVD; Halko et al., 2011) to generate latent traits representing a
-low-dimensional embedding of the network. As an aside, most ecologists
-are indirectly familiar with SVD: Principal Component Analysis is a
-special case of SVD, which is more sensitive to numerical instabilities
-(see notably Shlens, 2014). The latent traits give an unbiased estimate
-of the node's position in the latent feature spaces and can be mapped
-onto a reference phylogeny (other distance-based measures of species
-proximity that allow for the inference of features in the latent space
-can be used, for example the dissimilarity in functional traits). Based
-on the reconstructed latent traits for species in the destination
-species pool, a Random Dot Product Graph model (hereafter RDPG; S. J.
-Young \& Scheinerman, 2007) predicts the interaction between species
-through a function of the nodes' features through matrix multiplication.
-Thus, from latent traits and node position, we can infer interactions.
-
-The method we develop is, ecologically speaking, a ``black box,''
+from another location for which the network is unknown (or partially
+known). In fig.~\ref{fig:concept} the grey text boxes give a high-level
+overview of the approach; in the example around which this manuscript is
+built The method we develop is, ecologically speaking, a ``black box,''
 \emph{i.e.} an algorithm that can be understood mathematically, but
@@
 information than we might think; as such, even algorithms that are
-disconnected from the model can make correct guesses most of the time
+disconnected from a model can make correct guesses most of the time
 (Halevy et al., 2009); in fact, in an instance of ecological forecasting
@@
 Albouy et al., 2019), in that the metaweb representation is easily
-transferable. Specifically, we use RDPG to create a number of latent
-variables that can be combined into an approximation of the network
-adjacency matrix. RDPG results are known to have strong phylogenetic
-signal, and to capture the evolutionary backbone of food webs (Dalla
-Riva \& Stouffer, 2016); in other words, the latent variables of an RDPG
-can be mapped onto a phylogenetic tree, and phylogenetically similar
-predators should share phylogenetically similar preys. In addition,
-recent advances show that the latent variables produced this way can be
-used to predict \emph{de novo} network edges. Interestingly, the latent
-variables do not need to be produced by decomposing the network itself;
-in a recent contribution, Runghen et al. (2021) showed that deep
-artificial neural networks are able to reconstruct the left and right
-subspaces of an RDPG, in order to predict human movement networks from
-individual/location metadata. This is an exciting opportunity, as it
-opens up the possibility of using additional metadata as predictors.
+transferable. Specifically, we use Random Dot Product Graph model
+(hereafter RDPG; S. J. Young \& Scheinerman, 2007) to create a number of
+latent variables that can be combined into an approximation of the
+network adjacency matrix. RDPG is known to capture the evolutionary
+backbone of food webs (Dalla Riva \& Stouffer, 2016), resulting in
+strong phylogenetic signal in RDPG results; in other words, the latent
+variables of an RDPG can be mapped onto a phylogenetic tree, and
+phylogenetically similar predators should share phylogenetically similar
+preys. In addition, recent advances show that the latent variables
+produced this way can be used to predict \emph{de novo} interactions.
+Interestingly, the latent variables do not need to be produced by
+decomposing the network itself; in a recent contribution, Runghen et al.
+(2021) showed that deep artificial neural networks are able to
+reconstruct the left and right subspaces of an RDPG, in order to predict
+human movement networks from individual/location metadata and opens up
+the possibility of using additional metadata as predictors.
 
 The latent variables are created by performing a truncated Singular
-Value Decomposition (t-SVD) on the adjacency matrix. SVD is an
-appropriate embedding of ecological networks, which has recently been
-shown to both capture their complex, emerging properties (Strydom, Dalla
-Riva, et al., 2021) and to allow highly accurate prediction of the
-interactions within a single network (Poisot, Ouellet, et al., 2021).
-Under SVD, an adjacency matrix \(\mathbf{A}\) (where
+Value Decomposition (t-SVD; Halko et al., 2011) on the adjacency matrix.
+SVD is an appropriate embedding of ecological networks, which has
+recently been shown to both capture their complex, emerging properties
+(Strydom, Dalla Riva, et al., 2021) and to allow highly accurate
+prediction of the interactions within a single network (Poisot, Ouellet,
+et al., 2021). Under SVD, an adjacency matrix \(\mathbf{A}\) (where
 \(\mathbf{A}_{m,n}\in\mathbb{B}\) where 1 indicates predation and 0 an
@@
 \(\mathbf{A}_{m,n}\) is decomposed so that \(\mathbf{\Sigma}\) is a
-square \(r \times r\) diagonal matrix (whith \(1 \le r \le r_{full}\)
+square \(r \times r\) diagonal matrix (with \(1 \le r \le r_{full}\)
 where \(r_{full}\) is the full rank of \(\mathbf{A}\) and \(r\) the rank
@@
 nodes (species) as a function of the nodes' latent variables, and is a
-way to turn a SVD (which decompose one matrix into three) into two
+way to turn an SVD (which decompose one matrix into three) into two
 matrices that can be multiplied to provide an approximation of the
@@
 t-SVD provides a first-order approximation of the network. One advantage
-of using a RDPG rather than a SVD is that the number of components to
+of using an RDPG rather than an SVD is that the number of components to
 estimate decreases; notably, one does not have to estimate the singular
@@
 using a subset of species would yield the same threshold; that
-decreasing the quality of the original data by adding of removing
+decreasing the quality of the original data by adding or removing
 interactions would minimally affect the predictive accuracy of RDPG
@@
 probably over-estimates, we decided to apply a thresholding step to the
-interactions after the data inflation (fig.~\ref{fig:thresholds}).
+interactions after the data inflation (see fig.~\ref{fig:thresholds}
+showing the effect of varying the cutoff on \(P(i \rightarrow j)\)).
 Cirtwill \& Hambäck (2021) proposed a number of strategies to threshold
@@
 study}\label{results-and-discussion-of-the-case-study}}
-
-In fig.~\ref{fig:thresholds}, we examine the effect of varying the
-cutoff on \(P(i \rightarrow j)\) on the number of links, species, and
-connectance. Determining a cutoff using the maximum curvature, or
-central difference approximation of the second order partial derivative,
-as suggested by \emph{e.g.} Cirtwill \& Hambäck (2021), results in
-species being lost, or almost all links being kept. We therefore settled
-on the value that allowed all species to remain with at least one
-interaction. This result, in and of itself, suggests that additional
-methodological developments for the thresholding of probabilistic
-networks are required.
 
@@
 showed that even at small scales (the Iberian peninsula), mammal food
-webs retain the signal of both climate change and human activity, even
-when this human activity was orders of magnitude less important than it
-is now. Similarly, Yeakel et al. (2014) showed that changes in human
-occupation over several centuries can lead to food web collapse.
+webs retain the signal of both past climate change and human activity,
+even when this human activity was orders of magnitude less important
+than it is now. Similarly, Yeakel et al. (2014) showed that changes in
+human occupation over several centuries can lead to food web collapse.
 Megafauna in particular seems to be very sensitive to human arrival
@@
 some guidance as to the type of sampling effort that should be
-prioritized. Although RDPG was able to maintain very high predictive
-power when interactions were missing, the addition of false positive
+prioritized. While RDPG was able to maintain very high predictive power
+when interactions were missing, the addition of false positive
 interactions was immediately detected; this suggests that it may be
@@
 performed the analysis; GVDR, MF, and RR provided additional feedback on
-the analyses. DC, BM, and FB helped with data collection. All editors
+the analyses. DC, BM, and FB helped with data collection. All authors
 contributed to writing and editing the manuscript.
@@
 
-\leavevmode\hypertarget{ref-Grenie2021HarTax}{}%
-Grenié, M., Berti, E., Carvajal-Quintero, J. D., Winter, M., \& Sagouis,
-A. (2021). \emph{Harmonizing taxon names in biodiversity data: A review
-of tools, databases, and best practices}.
-\url{https://doi.org/10.32942/osf.io/e3qnz}
-
 \leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
@@
 
-\leavevmode\hypertarget{ref-Shlens2014TutPri}{}%
-Shlens, J. (2014, April 3). \emph{A Tutorial on Principal Component
-Analysis}. \url{http://arxiv.org/abs/1404.1100}
-
 \leavevmode\hypertarget{ref-Solis-Lemus2017PhyPac}{}%

### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@8ddafbb3de0b99e96ee7fb253b6d3505e2c1f382 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@296421f2fd91597c6d2c5332a653469ae1a20b64 🚀

@@
 still be regions for which, due to a \emph{lack} of local interaction
-data, we are unable to infer potential species interactions. Having a
-general solution for inferring \emph{potential} interactions (despite
-the unavailability of interaction data) could be the catalyst for
-significant breakthroughs in our ability to start thinking about species
-interaction networks over large spatial scales. In a recent overview of
-the field of ecological network prediction, Strydom, Catchen, et al.
-(2021) identified two challenges of interest to the prediction of
-interactions at large scales. First, there is a relative scarcity of
-relevant data in most places globally -- paradoxically, this restricts
-our ability to infer interactions to locations where inference is
-perhaps the least required; second, accurate predictions often demand
-accurate predictors, and the lack of methods that can leverage small
-amount of data is a serious impediment to our predictive ability
-globally.
+data, we are unable to infer potential species interactions.
 
@@
 
-In fig.~\ref{fig:concept}, where we provide a methodological overview
-based on learning the embedding of a metaweb of trophic interactions for
-European mammals (known interactions; Maiorano et al., 2020a, 2020b)
-and, based on phylogenetic relationships between mammals globally
-(\emph{i.e.}, phylogenetic tree Upham et al., 2019), infer a metaweb for
-the Canadian mammalian species pool (using only a species list
-\emph{i.e.} interactions are `unknown' in this instance). Following the
-definition of Dunne (2006), a metaweb is a network analogue to the
-regional species pool; specifically, it is an inventory of all
-\emph{potential} interactions between species from a spatially delimited
-area (and so captures the \(\gamma\) diversity of interactions). The
-metaweb is, therefore, \emph{not} a prediction of the food web at a
-specific locale within the spatial area it covers, and will have a
-different structure (notably by having a larger connectance; see
-\emph{e.g.} Wood et al., 2015). These local food webs (which captures
-the \(\alpha\) diversity of interactions) are a subset of the metaweb's
-species and interactions, and have been called ``metaweb realizations''
-(Poisot et al., 2015). Differences between local food web and their
-metaweb are due to chance, species abundance and co-occurrence, local
-environmental conditions, and local distribution of functional traits,
-among others.
-
-Because the metaweb represents the joint effect of functional,
-phylogenetic, and macroecological processes (Morales-Castilla et al.,
-2015), it holds valuable ecological information. Specifically, it is the
-``upper bounds'' on what the composition of the local networks can be
-(see \emph{e.g.} McLeod et al., 2021). These local networks, in turn,
-can be reconstructed given appropriate knowledge of local species
-composition, providing information on structure of food webs at finer
-spatial scales. This has been done for example for
-tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
-interactions (Albouy et al., 2019), tetrapod trophic interactions
-(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
-Whereas the original metaweb definition, and indeed most past uses of
-metawebs, was based on the presence/absence of interactions, we focus on
-\emph{probabilistic} metawebs where interactions are represented as the
-chance of success of a Bernoulli trial (see \emph{e.g.} Poisot et al.,
-2016); therefore, not only does our method recommend interactions that
-may exist, it gives each interaction a score, allowing us to properly
-weigh them.
-
-Our case study shows that phylogenetic transfer learning is an effective
-approach to the generation of probabilistic metawebs. This showcases
-that although the components (species) that make up the Canadian and
-European communities may be \emph{minimally} shared (the overall species
-overlap is less than 4\%), if the medium (proxy space) selected in the
-transfer step is biologically plausible, we can still effectively learn
-from the known network and make biologically relevant predictions of
+In fig.~\ref{fig:concept}, we provide a methodological overview based on
+learning the embedding of a metaweb of trophic interactions for European
+mammals (known interactions; Maiorano et al., 2020a, 2020b) and, based
+on phylogenetic relationships between mammals globally (\emph{i.e.},
+phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
+mammalian species pool (using only a species list \emph{i.e.}
+interactions are treated as unknown in this instance). Our case study
+shows that phylogenetic transfer learning is an effective approach to
+the generation of probabilistic metawebs. This showcases that although
+the components (species) that make up the Canadian and European
+communities may be \emph{minimally} shared (the overall species overlap
+is less than 4\%), if the medium (proxy space) selected in the transfer
+step is biologically plausible, we can still effectively learn from the
+known network and make biologically relevant predictions of
 interactions. Indeed, as we detail in the results, when validated
@@
 Canadian mammals, our model achieves a predictive accuracy of
-approximately 91\%. It should be reiterated that the framework presented
-in fig.~\ref{fig:concept} is amenable to changes \emph{e.g.} it is
-possible to use distinct trees if working with distinct clades (such as
-pollination networks) or, alternatively, the measure of similarity may
-not be phylogeny, and can be replaced by information on foraging
-(Beckerman et al., 2006), cell-level mechanisms (Boeckaerts et al.,
-2021), or a combination of traits and phylogenetic structure (Stock,
-2021). Most importantly, although we focus on a trophic system, it is an
-established fact that different (non-trophic) interactions do themselves
-interact with and influence the outcome of trophic interactions (see
-\emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012). Future development
-of metaweb inference techniques should cover the prediction of multiple
-interaction types.
+approximately 91\%.
+
+\hypertarget{method-description}{%
+\section{Method description}\label{method-description}}
+
+The core point of our method is the transfer of knowledge of a known
+ecological network to predict interactions between species for another
+location for which the network is unknown (or partially known) and is
+summarized in the grey text boxes in fig.~\ref{fig:concept}. The method
+we develop is, ecologically speaking, a ``black box,'' \emph{i.e.} an
+algorithm that can be understood mathematically, but whose component
+parts are not always directly tied to ecological processes. There is a
+growing realization in machine learning that (unintentional) black box
+algorithms are not necessarily a bad thing (Holm, 2019), as long as
+their constituent parts can be examined (which is the case with our
+method). But more importantly, data hold more information than we might
+think; as such, even algorithms that are disconnected from a model can
+make correct guesses most of the time (Halevy et al., 2009); in fact, in
+an instance of ecological forecasting of spatio-temporal systems,
+model-free approaches (\emph{i.e.} drawing all of their information from
+the data) outperformed model-informed ones (Perretti et al., 2013).
 
 \hypertarget{data-used-for-the-case-study}{%
-\section{Data used for the case
+\subsection{Data used for the case
 study}\label{data-used-for-the-case-study}}
@@
 checklist, and corresponds to the same selection criteria that was
-applied by Maiorano et al. (2020a) in the European metaweb.
-
-After taxonomic cleaning and reconciliation the mammalian European
-metaweb has 260 species, and the Canadian species pool 163; of these, 17
-(about 4\% of the total) are shared, and 89 species from Canada (54\%)
-had at least one congeneric species in Europe. The similarity for both
-species pools predictably increases with higher taxonomic order, with
-19\% of shared genera, 47\% of shared families, and 75\% of shared
-orders; for the last point, Canada and Europe each had a single unique
-order (\emph{Didelphimorphia} for Canada, \emph{Erinaceomorpha} for
-Europe).
-
-\hypertarget{method-description}{%
-\section{Method description}\label{method-description}}
-
-The core point of our method is the transfer of knowledge of a known
-ecological network, in order to predict interactions between species
-from another location for which the network is unknown (or partially
-known). In fig.~\ref{fig:concept} the grey text boxes give a high-level
-overview of the approach; in the example around which this manuscript is
-built The method we develop is, ecologically speaking, a ``black box,''
-\emph{i.e.} an algorithm that can be understood mathematically, but
-whose component parts are not always directly tied to ecological
-processes. There is a growing realization in machine learning that
-(unintentional) black box algorithms are not necessarily a bad thing
-(Holm, 2019), as long as their constituent parts can be examined (which
-is the case with our method). But more importantly, data hold more
-information than we might think; as such, even algorithms that are
-disconnected from a model can make correct guesses most of the time
-(Halevy et al., 2009); in fact, in an instance of ecological forecasting
-of spatio-temporal systems, model-free approaches (\emph{i.e.} drawing
-all of their information from the data) outperformed model-informed ones
-(Perretti et al., 2013).
+applied by Maiorano et al. (2020a) in the European metaweb. After
+taxonomic cleaning and reconciliation the European metaweb has 260
+species, and the Canadian species pool 163; of these, 17 (about 4\% of
+the total) are shared, and 89 species from Canada (54\%) had at least
+one congeneric species in Europe. The similarity for both species pools
+predictably increases with higher taxonomic order, with 19\% of shared
+genera, 47\% of shared families, and 75\% of shared orders; for the last
+point, Canada and Europe each had a single unique order
+(\emph{Didelphimorphia} for Canada, \emph{Erinaceomorpha} for Europe).
 
@@
 Albouy et al., 2019), in that the metaweb representation is easily
-transferable. Specifically, we use Random Dot Product Graph model
+transferable. Specifically, we use a Random Dot Product Graph model
 (hereafter RDPG; S. J. Young \& Scheinerman, 2007) to create a number of
@@
 uncertainty associated to inner nodes of the phylogeny. In this case
-study, we have decided to not propagate this uncertainty, as it would
+study we have decided to not propagate this uncertainty as it would
 complexify the process. The Brownian motion algorithm returns the
@@
 entries that are distributions, representing the range of values for a
-given species at a given dimension.
-
-These objects represent the transferred knowledge, which we can use for
-prediction of the Canadian metaweb.
+given species at a given dimension. These objects represent the
+transferred knowledge, which we can use for prediction of the Canadian
+metaweb.
 
@@
 
-First, we extracted the subgraph corresponding to the 17 species shared
+First, we extracted the network corresponding to the 17 species shared
 between the European and Canadian pools and replaced these interactions
@@
 probably over-estimates, we decided to apply a thresholding step to the
-interactions after the data inflation (see fig.~\ref{fig:thresholds}
-showing the effect of varying the cutoff on \(P(i \rightarrow j)\)).
-Cirtwill \& Hambäck (2021) proposed a number of strategies to threshold
+interactions after data inflation (see fig.~\ref{fig:thresholds} showing
+the effect of varying the cutoff on \(P(i \rightarrow j)\)). Cirtwill \&
+Hambäck (2021) proposed a number of strategies to threshold
 probabilistic networks. Their methods assume the underlying data to be
@@
 
-The t-SVD embedding is able to learn relevant ecological features for
-the network. fig.~\ref{fig:degree} shows that the first rank correlates
-linearly with generality and vulnerability (Schoener, 1989), \emph{i.e.}
-the number of preys and predators for each species. Importantly, this
-implies that a rank 1 approximation represents the configuration model
-for the metaweb, \emph{i.e.} a set of random networks generated from a
-given degree sequence (Park \& Newman, 2004). Accounting for the
-probabilistic nature of the degrees, the rank 1 approximation also
-represents the \emph{soft} configuration model (van der Hoorn et al.,
-2018). Both models are maximum entropy graph models (Garlaschelli et
-al., 2018), with sharp (all network realizations satisfy the specified
-degree sequence) and soft (network realizations satisfy the degree
-sequence on average) local constraints, respectively. The (soft)
-configuration model is an unbiased random graph model widely used by
-ecologists in the context of null hypothesis significance testing of
-network structure (\emph{e.g.} Bascompte et al., 2003) and can provide
-informative priors for Bayesian inference of network structure
-(\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that for this
-metaweb, the relevant information was extracted at the first rank.
-Because the first rank corresponds to the leading singular value of the
-system, the results of fig.~\ref{fig:degree} have a straightforward
-interpretation: degree-based processes are the most important in
-structuring the mammalian food web.
+Using a transfer learning framework we were able to construct a
+probabilistic metaweb and (as as per Dunne, 2006) it is a list of
+potential interactions and does not mean that they will exist wherever
+the two species co-occur. The t-SVD embedding is able to learn relevant
+ecological features for the network. fig.~\ref{fig:degree} shows that
+the first rank correlates linearly with generality and vulnerability
+(Schoener, 1989), \emph{i.e.} the number of preys and predators for each
+species. Importantly, this implies that a rank 1 approximation
+represents the configuration model for the metaweb, \emph{i.e.} a set of
+random networks generated from a given degree sequence (Park \& Newman,
+2004). Accounting for the probabilistic nature of the degrees, the rank
+1 approximation also represents the \emph{soft} configuration model (van
+der Hoorn et al., 2018). Both models are maximum entropy graph models
+(Garlaschelli et al., 2018), with sharp (all network realizations
+satisfy the specified degree sequence) and soft (network realizations
+satisfy the degree sequence on average) local constraints, respectively.
+The (soft) configuration model is an unbiased random graph model widely
+used by ecologists in the context of null hypothesis significance
+testing of network structure (\emph{e.g.} Bascompte et al., 2003) and
+can provide informative priors for Bayesian inference of network
+structure (\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that
+for this metaweb, the relevant information was extracted at the first
+rank. Because the first rank corresponds to the leading singular value
+of the system, the results of fig.~\ref{fig:degree} have a
+straightforward interpretation: degree-based processes are the most
+important in structuring the mammalian food web.
 
@@
 extinction (Marco et al., 2018), and can lead to changes in interaction
-structure. Yet, owing to the inherent plasticity of interactions, there
-have been documented instances of food webs undergoing rapid
-collapse/recovery cycles over short periods of time (Pedersen et al.,
-2017). The embedding of a network, in a sense, embeds its
-macro-evolutionary history, especially as RDPG captures ecological
-signal (Dalla Riva \& Stouffer, 2016); at this point, it is important to
-recall that a metaweb is intended as a catalogue of all potential
-interactions, which should then be filtered (Morales-Castilla et al.,
-2015). In practice (and in this instance) the reconstructed metaweb will
-predict interactions that are plausible based on the species'
-evolutionary history, however some interactions would/would not be
-realized due to human impact.
-
-Dallas et al. (2017) suggested that most links in ecological networks
-may be cryptic, \emph{i.e.} uncommon or otherwise hard to observe. This
-argument essentially echoes Jordano (2016b): the sampling of ecological
-interactions is difficult because it requires first the joint
-observation of two species, and then the observation of their
-interaction. In addition, it is generally expected that weak or rare
-links would be more common in networks (Csermely, 2004), compared to
-strong, persistent links; this is notably the case in food chains,
-wherein many weaker links are key to the stability of a system (Neutel
-et al., 2002). In the light of these observations, the results in
-fig.~\ref{fig:inflation} are not particularly surprising: we expect to
-see a surge in these low-probability interactions under a model that has
-a good predictive accuracy. Because the predictions we generate are by
-design probabilistic, then one can weigh these rare links appropriately.
-In a sense, that most ecological interactions are elusive can call for a
-slightly different approach to sampling: once the common interactions
-are documented, the effort required in documenting each rare interaction
-may increase exponentially. Recent proposals suggest that machine
-learning algorithms, in these situations, can act as data generators
-(Hoffmann et al., 2019): in this perspective, high quality observational
-data can be supplemented with synthetic data coming from predictive
-models, which increases the volume of information available for
-inference. Indeed, Strydom, Catchen, et al. (2021) suggested that
-knowing the metaweb may render the prediction of local networks easier,
-because it fixes an ``upper bound'' on which interactions can exist;
-indeed, with a probabilistic metaweb, we can consider that the metaweb
-represents an aggregation of informative priors on the interactions.
-
-Related to the last point, Cirtwill et al. (2019) showed that network
-inference techniques based on Bayesian approaches would perform far
-better in the presence of an interaction-level informative prior; the
-desirable properties of such a prior would be that it is expressed as a
-probability, preferably representing a Bernoulli event, the value of
-which would be representative of relevant biological processes
-(probability of predation in this case). We argue that the probability
-returned at the very last step of our framework may serve as this
-informative prior; indeed, the output of our analysis can be used in
-subsequent steps, also possibly involving expert elicitation to validate
-some of the most strongly recommended interactions. One important
-\emph{caveat} to keep in mind when working with interaction inference is
-that interactions can never really be true negatives (in the current
-state of our methodological framework and data collection limitations);
-this renders the task of validating a model through the usual
-application of binary classification statistics very difficult (although
-see Strydom, Catchen, et al., 2021 for a discussion of alternative
-suggestions). The other way through which our framework can be improved
-is by substituting the predictors that are used for transfer. For
-example, in the presence of information on species traits that are known
-to be predictive of species interactions, one might want to rely on
-functional rather than phylogenetic distances -- in food webs, body size
-(and allometrically related variables) has been established as such a
-variable (Brose et al., 2006); the identification of relevant functional
-traits is facilitated by recent methodological developments (Rosado et
-al., 2013). It should be noted that Xing \& Fayle (2021) highlight
-phylogenetic relatedness as one of the core components of network
-comparison at the global scale. In this case study, we have embedded the
+structure.
+
+Cirtwill et al. (2019) showed that network inference techniques based on
+Bayesian approaches would perform far better in the presence of an
+interaction-level informative prior; the desirable properties of such a
+prior would be that it is expressed as a probability, preferably
+representing a Bernoulli event, the value of which would be
+representative of relevant biological processes (probability of
+predation in this case). We argue that the probability returned at the
+very last step of our framework may serve as this informative prior;
+indeed, the output of our analysis can be used in subsequent steps, also
+possibly involving expert elicitation to validate some of the most
+strongly recommended interactions. One important \emph{caveat} to keep
+in mind when working with interaction inference is that interactions can
+never really be true negatives (in the current state of our
+methodological framework and data collection limitations); this renders
+the task of validating a model through the usual application of binary
+classification statistics very difficult (although see Strydom, Catchen,
+et al., 2021 for a discussion of alternative suggestions). The other way
+through which our framework can be improved is by substituting the
+predictors that are used for transfer. For example, in the presence of
+information on species traits that are known to be predictive of species
+interactions, one might want to rely on functional rather than
+phylogenetic distances -- in food webs, body size (and allometrically
+related variables) has been established as such a variable (Brose et
+al., 2006); the identification of relevant functional traits is
+facilitated by recent methodological developments (Rosado et al., 2013).
+
+Finally, it should be noted that the framework we have presented is
+amenable to changes lending to applicability to a broad range of
+potential scenarios. For example in this case study we have embedded the
 original metaweb using t-SVD, because it lends itself to an RDPG
@@
 al., 2017; Cao et al., 2019), which can be used as alternatives.
-
-As Herbert (1965) rightfully pointed out, ``{[}y{]}ou can't draw neat
-lines around planet-wide problems''; in this regard, our approach (and
-indeed, any inference of a metaweb at large scales) must contend with
-several interesting and interwoven families of problems. The first is
-the limit of the metaweb to embed and transfer. If the initial metaweb
-is too narrow in scope, notably from a taxonomic point of view, the
-chances of finding another area with enough related species to make a
-reliable inference decreases; this would likely be indicated by large
-confidence intervals during ancestral character estimation, but the lack
-of well documented metawebs is currently preventing the development of
-more concrete guidelines. The question of phylogenetic relatedness and
-dispersal is notably true if the metaweb is assembled in an area with
-mostly endemic species, and as with every predictive algorithm, there is
-room for the application of our best ecological judgement. Conversely,
-the metaweb should be reliably filled, which assumes that the \(S^2\)
-interactions in a pool of \(S\) species have been examined, either
-through literature surveys or expert elicitation. Supp. Mat. 1 provides
-some guidance as to the type of sampling effort that should be
-prioritized. While RDPG was able to maintain very high predictive power
-when interactions were missing, the addition of false positive
-interactions was immediately detected; this suggests that it may be
-appropriate to err on the side of ``too many'' interactions when
-constructing the initial metaweb to be transferred. The second series of
-problems are related to determining which area should be used to infer
-the new metaweb in, as this determines the species pool that must be
-used. In our application, we focused on the mammals of Canada. The
-upside of this approach is that information at the country level is
-likely to be required by policy makers and stakeholders for their
-biodiversity assessment, as each country tends to set goals at the
-national level (Buxton et al., 2021) for which quantitative instruments
-are designed (Turak et al., 2017), with specific strategies often
-enacted at smaller scales (Ray et al., 2021). And yet, we do not really
-have a satisfying answer to the question of ``where does a food web
-stop?''; the current most satisfying solutions involve examining the
-spatial consistency of network area relationships (Fortin et al., 2021;
-see \emph{e.g.} Galiana et al., 2018, 2019, 2021), which is of course
-impossible in the absence of enough information about the network
-itself. This suggests that an \emph{a posteriori} refinement of the
-results may be required, based on a downscaling of the metaweb. The
-final family of problems relates less to the availability of data or
-quantitative tools, and more to the praxis of spatial ecology. Operating
-under the context of national divisions, in large parts of the world,
-reflects nothing more than the legacy of settler colonialism. Indeed,
-the use of ecological data is not an apolitical act (Nost \& Goldstein,
-2021), as data infrastructures tend to be designed to answer questions
-within national boundaries, and their use both draws upon and reinforces
-territorial statecraft; as per Machen \& Nost (2021), this is
-particularly true when the output of ``algorithmic thinking''
-(\emph{e.g.} relying on machine learning to generate knowledge) can be
-re-used for governance (\emph{e.g.} enacting conservation decisions at
-the national scale). We therefore recognize that methods such as we
-propose operate under the framework that contributed to the ongoing
-biodiversity crisis (Adam, 2014), reinforced environmental injustice
-(Choudry, 2013; Domínguez \& Luoma, 2020), and on Turtle Island
-especially, should be replaced by Indigenous principles of land
-management (Eichhorn et al., 2019; No'kmaq et al., 2021). As we see
-AI/ML being increasingly mobilized to generate knowledge that is lacking
-for conservation decisions (\emph{e.g.} Lamba et al., 2019; Mosebo
-Fernandes et al., 2020), our discussion of these tools need to go beyond
-the technical, and into the governance consequences they can have.
+Regarding the transfer step it is possible to use distinct trees if
+working with distinct clades (such as pollination networks) or an
+alternative measure of similarity (transfer medium) such as information
+on foraging (Beckerman et al., 2006), cell-level mechanisms (Boeckaerts
+et al., 2021), or a combination of traits and phylogenetic structure
+(Stock, 2021). Most importantly, although we focus on a trophic system,
+it is an established fact that different (non-trophic) interactions do
+themselves interact with and influence the outcome of trophic
+interactions (see \emph{e.g.} Kawatsu et al., 2021; Kéfi et al., 2012).
+Future development of metaweb inference techniques should cover the
+prediction of multiple interaction types.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Adam2014EleTre}{}%
-Adam, R. (2014). \emph{Elephant treaties: The Colonial legacy of the
-biodiversity crisis}. UPNE.
-
 \leavevmode\hypertarget{ref-Albouy2019MarFis}{}%
@@
 
-\leavevmode\hypertarget{ref-Buxton2021KeyInf}{}%
-Buxton, R. T., Bennett, J. R., Reid, A. J., Shulman, C., Cooke, S. J.,
-Francis, C. M., Nyboer, E. A., Pritchard, G., Binley, A. D., Avery-Gomm,
-S., Ban, N. C., Beazley, K. F., Bennett, E., Blight, L. K., Bortolotti,
-L. E., Camfield, A. F., Gadallah, F., Jacob, A. L., Naujokaitis-Lewis,
-I., \ldots{} Smith, P. A. (2021). Key information needs to move from
-knowledge to action for biodiversity conservation in Canada.
-\emph{Biological Conservation}, \emph{256}, 108983.
-\url{https://doi.org/10.1016/j.biocon.2021.108983}
-
 \leavevmode\hypertarget{ref-Cai2017ComSur}{}%
@@
 
-\leavevmode\hypertarget{ref-Choudry2013SavBio}{}%
-Choudry, A. (2013). Saving biodiversity, for whom and for what?
-Conservation NGOs, complicity, colonialism and conquest in an era of
-capitalist globalization. In \emph{NGOization: Complicity,
-contradictions and prospects} (pp. 24--44). Bloomsbury Publishing.
-
 \leavevmode\hypertarget{ref-Cirtwill2019QuaFra}{}%
@@
 
-\leavevmode\hypertarget{ref-Csermely2004StrLin}{}%
-Csermely, P. (2004). Strong links are important, but weak links
-stabilize them. \emph{Trends in Biochemical Sciences}, \emph{29}(7),
-331--334. \url{https://doi.org/10.1016/j.tibs.2004.05.004}
-
 \leavevmode\hypertarget{ref-DallaRiva2016ExpEvo}{}%
@@
 \emph{125}(4), 446--456. \url{https://doi.org/10.1111/oik.02305}
-
-\leavevmode\hypertarget{ref-Dallas2017PreCry}{}%
-Dallas, T., Park, A. W., \& Drake, J. M. (2017). Predicting cryptic
-links in host-parasite networks. \emph{PLOS Computational Biology},
-\emph{13}(5), e1005557.
-\url{https://doi.org/10.1371/journal.pcbi.1005557}
 
@@
 
-\leavevmode\hypertarget{ref-Dominguez2020DecCon}{}%
-Domínguez, L., \& Luoma, C. (2020). Decolonising Conservation Policy:
-How Colonial Land and Conservation Ideologies Persist and Perpetuate
-Indigenous Injustices at the Expense of the Environment. \emph{Land},
-\emph{9}(3, 3), 65. \url{https://doi.org/10.3390/land9030065}
-
 \leavevmode\hypertarget{ref-Dormann2010EvoCli}{}%
@@
 
-\leavevmode\hypertarget{ref-Eichhorn2019SteDec}{}%
-Eichhorn, M. P., Baker, K., \& Griffiths, M. (2019). Steps towards
-decolonising biogeography. \emph{Frontiers of Biogeography},
-\emph{12}(1), 1--7. \url{https://doi.org/10.21425/F5FBG44795}
-
 \leavevmode\hypertarget{ref-Eklof2016PhyCom}{}%
@@
 107--115. \url{https://doi.org/10.1007/s12080-015-0273-9}
-
-\leavevmode\hypertarget{ref-Fortin2021NetEco}{}%
-Fortin, M.-J., Dale, M. R. T., \& Brimacombe, C. (2021). Network ecology
-in dynamic landscapes. \emph{Proceedings of the Royal Society B:
-Biological Sciences}, \emph{288}(1949), rspb.2020.1889, 20201889.
-\url{https://doi.org/10.1098/rspb.2020.1889}
-
-\leavevmode\hypertarget{ref-Galiana2021SpaSca}{}%
-Galiana, N., Barros, C., Braga, J., Ficetola, G. F., Maiorano, L.,
-Thuiller, W., Montoya, J. M., \& Lurgi, M. (2021). The spatial scaling
-of food web structure across European biogeographical regions.
-\emph{Ecography}, \emph{n/a}(n/a).
-\url{https://doi.org/10.1111/ecog.05229}
-
-\leavevmode\hypertarget{ref-Galiana2019GeoVar}{}%
-Galiana, N., Hawkins, B. A., \& Montoya, J. M. (2019). The geographical
-variation of network structure is scale dependent: Understanding the
-biotic specialization of hostparasitoid networks. \emph{Ecography},
-\emph{42}(6), 1175--1187. \url{https://doi.org/10.1111/ecog.03684}
-
-\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
-Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
-Cazelles, K., Gravel, D., \& Montoya, J. M. (2018). The spatial scaling
-of species interaction networks. \emph{Nature Ecology \& Evolution},
-\emph{2}(5), 782--790. \url{https://doi.org/10.1038/s41559-018-0517-3}
 
@@
 
-\leavevmode\hypertarget{ref-Gravel2018BriElt}{}%
-Gravel, D., Baiser, B., Dunne, J. A., Kopelke, J.-P., Martinez, N. D.,
-Nyman, T., Poisot, T., Stouffer, D. B., Tylianakis, J. M., Wood, S. A.,
-\& Roslin, T. (2018). Bringing Elton and Grinnell together: A
-quantitative framework to represent the biogeography of ecological
-interaction networks. \emph{Ecography}, \emph{0}(0).
-\url{https://doi.org/10.1111/ecog.04006}
-
-\leavevmode\hypertarget{ref-Grunig2020CroFor}{}%
-Grünig, M., Mazzi, D., Calanca, P., Karger, D. N., \& Pellissier, L.
-(2020). Crop and forest pest metawebs shift towards increased linkage
-and suitability overlap under climate change. \emph{Communications
-Biology}, \emph{3}(1, 1), 1--10.
-\url{https://doi.org/10.1038/s42003-020-0962-9}
-
 \leavevmode\hypertarget{ref-Halevy2009UnrEff}{}%
@@
 \url{https://doi.org/10.1137/090771806}
-
-\leavevmode\hypertarget{ref-Herbert1965Dun}{}%
-Herbert, F. (1965). \emph{Dune} (1st ed.). Chilton Book Company.
-
-\leavevmode\hypertarget{ref-Hoffmann2019MacLea}{}%
-Hoffmann, J., Bar-Sinai, Y., Lee, L. M., Andrejevic, J., Mishra, S.,
-Rubinstein, S. M., \& Rycroft, C. H. (2019). Machine learning in a
-data-limited regime: Augmenting experiments with synthetic data uncovers
-order in crumpled sheets. \emph{Science Advances}, \emph{5}(4),
-eaau6792. \url{https://doi.org/10.1126/sciadv.aau6792}
 
@@
 
-\leavevmode\hypertarget{ref-Lamba2019DeeLea}{}%
-Lamba, A., Cassey, P., Segaran, R. R., \& Koh, L. P. (2019). Deep
-learning for environmental conservation. \emph{Current Biology},
-\emph{29}(19), R977--R982.
-\url{https://doi.org/10.1016/j.cub.2019.08.016}
-
 \leavevmode\hypertarget{ref-Litsios2012EffPhy}{}%
@@
 533--538. \url{https://doi.org/10.1093/sysbio/syr124}
-
-\leavevmode\hypertarget{ref-Machen2021ThiAlg}{}%
-Machen, R., \& Nost, E. (2021). Thinking algorithmically: The making of
-hegemonic knowledge in climate governance. \emph{Transactions of the
-Institute of British Geographers}, \emph{46}(3), 555--569.
-\url{https://doi.org/10.1111/tran.12441}
 
@@
 
-\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
-McLeod, A., Leroux, S. J., Gravel, D., Chu, C., Cirtwill, A. R., Fortin,
-M.-J., Galiana, N., Poisot, T., \& Wood, S. A. (2021). Sampling and
-asymptotic network properties of spatial multi-trophic networks.
-\emph{Oikos}, \emph{n/a}(n/a). \url{https://doi.org/10.1111/oik.08650}
-
 \leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
@@
 \url{https://doi.org/10.1016/j.tree.2015.03.014}
-
-\leavevmode\hypertarget{ref-MoseboFernandes2020MacLea}{}%
-Mosebo Fernandes, A. C., Quintero Gonzalez, R., Lenihan-Clarke, M. A.,
-Leslie Trotter, E. F., \& Jokar Arsanjani, J. (2020). Machine Learning
-for Conservation Planning in a Changing Climate. \emph{Sustainability},
-\emph{12}(18, 18), 7657. \url{https://doi.org/10.3390/su12187657}
 
@@
 
-\leavevmode\hypertarget{ref-Neutel2002StaRea}{}%
-Neutel, A.-M., Heesterbeek, J. A. P., \& de Ruiter, P. C. (2002).
-Stability in Real Food Webs: Weak Links in Long Loops. \emph{Science},
-\emph{296}(5570), 1120--1123.
-\url{https://doi.org/10.1126/science.1068326}
-
-\leavevmode\hypertarget{ref-Nokmaq2021AwaSle}{}%
-No'kmaq, M., Marshall, A., Beazley, K. F., Hum, J., joudry, shalan,
-Papadopoulos, A., Pictou, S., Rabesca, J., Young, L., \& Zurba, M.
-(2021). {``Awakening the sleeping giant''}: Re-Indigenization principles
-for transforming biodiversity conservation in Canada and beyond.
-\emph{FACETS}, \emph{6}(1), 839--869.
-
-\leavevmode\hypertarget{ref-Nost2021PolEco}{}%
-Nost, E., \& Goldstein, J. E. (2021). A political ecology of data.
-\emph{Environment and Planning E: Nature and Space}, 25148486211043503.
-\url{https://doi.org/10.1177/25148486211043503}
-
 \leavevmode\hypertarget{ref-OConnor2020UnvFoo}{}%
@@
 
-\leavevmode\hypertarget{ref-Pedersen2017SigCol}{}%
-Pedersen, E. J., Thompson, P. L., Ball, R. A., Fortin, M.-J., Gouhier,
-T. C., Link, H., Moritz, C., Nenzen, H., Stanley, R. R. E., Taranu, Z.
-E., Gonzalez, A., Guichard, F., \& Pepin, P. (2017). Signatures of the
-collapse and incipient recovery of an overexploited marine ecosystem.
-\emph{Royal Society Open Science}, \emph{4}(7), 170215.
-\url{https://doi.org/10.1098/rsos.170215}
-
 \leavevmode\hypertarget{ref-Perretti2013ModFor}{}%
@@
 
-\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
-Poisot, T., Stouffer, D. B., \& Gravel, D. (2015). Beyond species: Why
-ecological interaction networks vary through space and time.
-\emph{Oikos}, \emph{124}(3), 243--251.
-\url{https://doi.org/10.1111/oik.01719}
-
 \leavevmode\hypertarget{ref-Price2003MacThe}{}%
@@
 patterns}. Cambridge University Press.
-
-\leavevmode\hypertarget{ref-Ray2021BioCri}{}%
-Ray, J. C., Grimm, J., \& Olive, A. (2021). The biodiversity crisis in
-Canada: Failures and challenges of federal and sub-national strategic
-and legal frameworks. \emph{FACETS}, \emph{6}, 1044--1068.
-\url{https://doi.org/10.1139/facets-2020-0075}
 
@@
 
-\leavevmode\hypertarget{ref-Turak2017UsiEss}{}%
-Turak, E., Brazill-Boast, J., Cooney, T., Drielsma, M., DelaCruz, J.,
-Dunkerley, G., Fernandez, M., Ferrier, S., Gill, M., Jones, H., Koen,
-T., Leys, J., McGeoch, M., Mihoub, J.-B., Scanes, P., Schmeller, D., \&
-Williams, K. (2017). Using the essential biodiversity variables
-framework to measure biodiversity change at national scale.
-\emph{Biological Conservation}, \emph{213}, 264--271.
-\url{https://doi.org/10.1016/j.biocon.2016.08.019}
-
 \leavevmode\hypertarget{ref-Upham2019InfMam}{}%
@@
 
-\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
-Wood, S. A., Russell, R., Hanson, D., Williams, R. J., \& Dunne, J. A.
-(2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, \emph{5}(17), 3769--3782.
-\url{https://doi.org/10.1002/ece3.1640}
-
-\leavevmode\hypertarget{ref-Xing2021RisEco}{}%
-Xing, S., \& Fayle, T. M. (2021). The rise of ecological network
-meta-analyses: Problems and prospects. \emph{Global Ecology and
-Conservation}, \emph{30}, e01805.
-\url{https://doi.org/10.1016/j.gecco.2021.e01805}
-
 \leavevmode\hypertarget{ref-Yeakel2014ColEco}{}%

### 2022-01-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@667f48eb27acd2dd82781f05f5b932dfddb8526e 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@ac7854fa5de6288a3f05d20a567f0a4b5f77d7e3 🚀

@@
 
-\hypertarget{results-and-discussion-of-the-case-study}{%
-\section{Results and discussion of the case
-study}\label{results-and-discussion-of-the-case-study}}
+\hypertarget{results-and-discussion}{%
+\section{Results and discussion}\label{results-and-discussion}}
 
@@
 Using a transfer learning framework we were able to construct a
-probabilistic metaweb and (as as per Dunne, 2006) it is a list of
-potential interactions and does not mean that they will exist wherever
-the two species co-occur. The t-SVD embedding is able to learn relevant
+probabilistic metaweb and (as per Dunne, 2006) is a list of potential
+interactions, meaning that they will not necessarily exist wherever the
+two species co-occur. The t-SVD embedding is able to learn relevant
 ecological features for the network. fig.~\ref{fig:degree} shows that
@@
 important in structuring the mammalian food web.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
 

### 2022-01-25 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@452e53e0b3d1fcd3d390982f752d836b2efed7ec 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@abd848de24d19518dcde87822d941a473bad53d5 🚀

@@
 interactions of a species pool for which their interactions are unknown.
-Specifically, we `learn' the information from a known interaction
-network by inferring the latent traits of species and infer the latent
-traits of a species pool for which we have no \emph{a priori}
-interaction data based on their phylogenetic relatedness to species from
-the known network. The latent traits can then be used to predict
-interactions and construct an interaction network.%
+Specifically, we `learn' the information (latent traits) of species from
+a known interaction network and infer the latent traits of another
+species pool for which we have no \emph{a priori} interaction data based
+on their phylogenetic relatedness to species from the known network. The
+latent traits can then be used to predict interactions and construct an
+interaction network.%
     \item Here we assembled a metaweb for Canadian mammals derived from
@@
 at which we truncate the matrix) containing only non-zero \(\sigma\)
-values. Additionally, \(\mathbf{U}\) is now a \(m \times r\) semi
-unitary matrix and \(\mathbf{V}'\) a \(n \times r\) semi-unitary matrix.
+values. Additionally, \(\mathbf{U}\) is now an \(m \times r\) semi
+unitary matrix and \(\mathbf{V}'\) an \(r \times n\) semi-unitary
+matrix.
 
@@
 question. The purpose of SVD is to remove the noise (expressed at high
-dimensions) and to focus on the signal, (expressed at low dimensions).
-In datasets with a clear signal/noise demarcation, a scree plot of
+dimensions) and to focus on the signal (expressed at low dimensions). In
+datasets with a clear signal/noise demarcation, a scree plot of
 \(\mathbf{\Sigma}\) can show a sharp drop at the rank where noise starts
@@
 t-SVD provides a first-order approximation of the network. One advantage
-of using an RDPG rather than an SVD is that the number of components to
-estimate decreases; notably, one does not have to estimate the singular
-values of the SVD. Furthermore, the two subspaces can be directly
-multiplied to yield a network.
+of using an RDPG for the network reconstruction rather than an SVD is
+that the number of components to estimate decreases; notably, one does
+not have to estimate the singular values of the SVD. Furthermore, the
+two subspaces can be directly multiplied to yield a network.
 
@@
 Vermaat et al. (2009), we show in Supp. Mat. 3 that not only can we
-observe differences in a multivariate space between the European and
-Canadian metaweb, we can also observe differences in the same space
+observe differences in the multivariate space between the European and
+Canadian metawebs, we can also observe differences in the same space
 between random subgraphs from these networks. These results line up with
@@
 \includegraphics{figures/figure-validation.png}
-\caption{Left, comparison of the probabilities of interactions assigned
+\caption{Left: comparison of the probabilities of interactions assigned
 by the model to all interactions (grey curve), the subset of
-interactions found in GLOBI (red), and in the Strong \& Leroux (2014)
+interactions found in GloBI (red), and in the Strong \& Leroux (2014)
 Newfoundland dataset (blue). The model recovers more interactions with a
@@
 collected datasets are biased towards more common or easy to identify
-interactions. Right, distribution of the in-degree and out-degree of the
+interactions. Right: distribution of the in-degree and out-degree of the
 mammals from Canada in the reconstructed metaweb. This figure describes
@@
 Second, we looked for all species in the Canadian pool known to the
-Global Biotic Interactions (GLoBI) database (Poelen et al., 2014), and
-extracted their known interactions. Because GLoBI aggregates observed
+Global Biotic Interactions (GloBI) database (Poelen et al., 2014), and
+extracted their known interactions. Because GloBI aggregates observed
 interactions, it is not a \emph{networks} data source, and therefore the
@@
 \emph{was reported to interact at least once}. This last statement
-should yet be taken with caution, as some sources in GLoBI (\emph{e.g.}
+should yet be taken with caution, as some sources in GloBI (\emph{e.g.}
 Thessen \& Parr, 2014) are produced through text analysis, and therefore
@@
 should the predictive model work, we would expect that a majority of
-interactions known to GLoBI would also be predicted. We retrieved 366
-interactions between mammals from the Canadian species pool from GLoBI,
+interactions known to GloBI would also be predicted. We retrieved 366
+interactions between mammals from the Canadian species pool from GloBI,
 33 of which were not predicted by the model; this results in a success
 rate of 91\%. After performing this check, we set the probability of all
-interactions known to GLoBI to 1.
+interactions known to GloBI to 1.
 
@@
 resulting in a success rate of 92\%. These two interactions were added
-to our predicted metaweb with a probability of 1. A table listing all
-interactions in the predicted Canadian metaweb can be found in the
+to our predicted metaweb with a probability of 1. A comparison of
+interaction densities for the inferred metaweb, and the Globi and
+Newfoundland is shown in fig.~\ref{fig:inflation} and a table listing
+all interactions in the predicted Canadian metaweb can be found in the
 supplementary material.
@@
 Hambäck (2021) proposed a number of strategies to threshold
-probabilistic networks. Their methods assume the underlying data to be
-tag-based sequencing, which represents interactions as co-occurrences of
-predator and prey within the same tags; this is conceptually identical
-to our Bernoulli-trial based reconstruction of a probabilistic network.
-We performed a full analysis of the effect of various cutoffs, and as
-they either resulted in removing too few interactions, or removing
-enough interactions that species started to be disconnected from the
-network, we set this threshold for a probability equivalent to 0 to the
-largest possible value that still allowed all species to have at least
-one interaction with a non-zero probability. The need for this slight
-deviation from the Cirtwill \& Hambäck (2021) method highlights the need
-for additional development on network thresholding.
+probabilistic networks. Their methodology assumes the underlying data to
+be tag-based sequencing, which represents interactions as co-occurrences
+of predator and prey within the same tags; this is conceptually
+identical to our Bernoulli-trial based reconstruction of a probabilistic
+network. We performed a full analysis of the effect of various cutoffs,
+and as they either resulted in removing too few interactions, or
+removing enough interactions that species started to be disconnected
+from the network, we set this threshold for a probability equivalent to
+0 to the largest possible value that still allowed all species to have
+at least one interaction with a non-zero probability. The need for this
+slight deviation from the Cirtwill \& Hambäck (2021) methodology
+highlights the need for additional development on network thresholding.
 
@@
 probabilistic metaweb and (as per Dunne, 2006) is a list of potential
-interactions, meaning that they will not necessarily exist wherever the
-two species co-occur. The t-SVD embedding is able to learn relevant
-ecological features for the network. fig.~\ref{fig:degree} shows that
-the first rank correlates linearly with generality and vulnerability
-(Schoener, 1989), \emph{i.e.} the number of preys and predators for each
-species. Importantly, this implies that a rank 1 approximation
-represents the configuration model for the metaweb, \emph{i.e.} a set of
-random networks generated from a given degree sequence (Park \& Newman,
-2004). Accounting for the probabilistic nature of the degrees, the rank
-1 approximation also represents the \emph{soft} configuration model (van
-der Hoorn et al., 2018). Both models are maximum entropy graph models
-(Garlaschelli et al., 2018), with sharp (all network realizations
-satisfy the specified degree sequence) and soft (network realizations
-satisfy the degree sequence on average) local constraints, respectively.
-The (soft) configuration model is an unbiased random graph model widely
-used by ecologists in the context of null hypothesis significance
-testing of network structure (\emph{e.g.} Bascompte et al., 2003) and
-can provide informative priors for Bayesian inference of network
-structure (\emph{e.g.} J.-G. Young et al., 2021). It is noteworthy that
-for this metaweb, the relevant information was extracted at the first
-rank. Because the first rank corresponds to the leading singular value
-of the system, the results of fig.~\ref{fig:degree} have a
-straightforward interpretation: degree-based processes are the most
-important in structuring the mammalian food web.
+interactions, meaning that they will not necessarily be realized
+wherever the two species co-occur. The t-SVD embedding is able to learn
+relevant ecological features for the network. fig.~\ref{fig:degree}
+shows that the first rank correlates linearly with generality and
+vulnerability (Schoener, 1989), \emph{i.e.} the number of preys and
+predators for each species. Importantly, this implies that a rank 1
+approximation represents the configuration model for the metaweb,
+\emph{i.e.} a set of random networks generated from a given degree
+sequence (Park \& Newman, 2004). Accounting for the probabilistic nature
+of the degrees, the rank 1 approximation also represents the \emph{soft}
+configuration model (van der Hoorn et al., 2018). Both models are
+maximum entropy graph models (Garlaschelli et al., 2018), with sharp
+(all network realizations satisfy the specified degree sequence) and
+soft (network realizations satisfy the degree sequence on average) local
+constraints, respectively. The (soft) configuration model is an unbiased
+random graph model widely used by ecologists in the context of null
+hypothesis significance testing of network structure (\emph{e.g.}
+Bascompte et al., 2003) and can provide informative priors for Bayesian
+inference of network structure (\emph{e.g.} J.-G. Young et al., 2021).
+It is noteworthy that for this metaweb, the relevant information was
+extracted at the first rank. Because the first rank corresponds to the
+leading singular value of the system, the results of
+fig.~\ref{fig:degree} have a straightforward interpretation:
+degree-based processes are the most important in structuring the
+mammalian food web.
 
@@
 Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
-nations. TP, TS, DC, and LP received funding from the Canadian Institue
+nations. TP, TS, DC, and LP received funding from the Canadian Institute
 for Ecology \& Evolution. FB is funded by the Institute for Data

### 2022-01-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@cab3bae55623b235e20fe3edb3a8d5cc5bc5c82a 🚀

@@
 interactions. Indeed, as we detail in the results, when validated
-against known but fractional data of trophic interactions between
-Canadian mammals, our model achieves a predictive accuracy of
+against the known (but fractional) data of trophic interactions present
+between Canadian mammals, our model achieves a predictive accuracy of
 approximately 91\%.

### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@6b0bf45bcca3c5087278c6e20f4b0df04edcef44 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@3cbf9a2f9d29a07718d0e876dab9484dcc411514 🚀

@@
 \includegraphics{figures/figure-subspaces.png}
-\caption{Visual representation of the left (green/purple) and right
-(green/brown) subspaces, alongside the adjacency matrix of the food web
-they encode (greyscale). The European metaweb is on the left, and the
-imputed Canadian metaweb (before data inflation) on the right. This
-figure illustrates how much structure the left subspace captures. As we
-show in fig.~\ref{fig:degree}, the species with a value of 0 in the left
-subspace are species without any prey.}\label{fig:subspaces}
+\caption{Visual representation of the left (green/purple; left side
+matrix) and right (green/brown; top matrix) subspaces, alongside the
+adjacency matrix of the food web they encode (greyscale). The European
+metaweb is on the left, and the imputed Canadian metaweb (before data
+inflation) on the right. This figure illustrates how much structure the
+left subspace captures. As we show in fig.~\ref{fig:degree}, the species
+with a value of 0 in the left subspace are species without any
+prey.}\label{fig:subspaces}
 }
@@
 through the Discovery Grants and Discovery Accelerator Supplement
-programs.
+programs. MJF is supported by an NSERC PDF and an RBC Post-Doctoral
+Fellowship
 

### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@3c227d502c51d6af7120b629e55d2607747bcc7f 🚀

@@
 \includegraphics{figures/figure-subspaces.png}
-\caption{Visual representation of the left (green/purple; left side
+\caption{Visual representation of the left (green/purple; left-side
 matrix) and right (green/brown; top matrix) subspaces, alongside the
@@
 capture its degree distribution. Bottom: topological consequences of the
-first dimension. Left: differences in the \(z\)-score of the actual
+first dimension. Left: differences in the \(z\)-scores of the actual
 configuration model for the reconstructed network, and the prediction

### 2022-02-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@ac3aadc9dd93816520066c49d8cb7bcecbb6ad8a 🚀

@@
 processes (Price, 2003); which is evidenced by the presence of conserved
-backbones in food webs (Dalla Riva \& Stouffer, 2016; Mora et al.,
-2018), strong evolutionary signature on prey choice (Stouffer et al.,
-2012), and strong phylogenetic signature in food web intervality (Eklöf
-\& Stouffer, 2016). Phylogenetic reconstruction has also previously been
-used within the context of ecological networks, namely understanding
-ancestral plant-insect interactions (Braga et al., 2021). Taken
-together, these considerations suggest that phylogenies can reliably be
-used to transfer knowledge on species interactions.
+backbones in food webs (Bramon Mora et al., 2018; Dalla Riva \&
+Stouffer, 2016), strong evolutionary signature on prey choice (Stouffer
+et al., 2012), and strong phylogenetic signature in food web intervality
+(Eklöf \& Stouffer, 2016). Phylogenetic reconstruction has also
+previously been used within the context of ecological networks, namely
+understanding ancestral plant-insect interactions (Braga et al., 2021).
+Taken together, these considerations suggest that phylogenies can
+reliably be used to transfer knowledge on species interactions.
 
@@
 
+\leavevmode\hypertarget{ref-BramonMora2018IdeCom}{}%
+Bramon Mora, B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer,
+D. B. (2018). Identifying a common backbone of interactions underlying
+food webs from different ecosystems. \emph{Nature Communications},
+\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
+
 \leavevmode\hypertarget{ref-Brose2006ConRes}{}%
@@
 
-\leavevmode\hypertarget{ref-Maiorano2020Tet10}{}%
+\leavevmode\hypertarget{ref-Maiorano2020TetSpe}{}%
 Maiorano, L., Montemaggiori, A., Ficetola, G. F., O'Connor, L., \&
@@
 \url{https://doi.org/10.1038/s41467-018-07049-5}
-
-\leavevmode\hypertarget{ref-Mora2018IdeCom}{}%
-Mora, B. B., Gravel, D., Gilarranz, L. J., Poisot, T., \& Stouffer, D.
-B. (2018). Identifying a common backbone of interactions underlying food
-webs from different ecosystems. \emph{Nature Communications},
-\emph{9}(1), 2603. \url{https://doi.org/10.1038/s41467-018-05056-0}
 

### 2022-02-18 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@4521b6e6879c8d9b86f4b4ba38f826f373b680b7 🚀

@@
 phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
-mammalian species pool (using only a species list \emph{i.e.}
-interactions are treated as unknown in this instance). Our case study
-shows that phylogenetic transfer learning is an effective approach to
-the generation of probabilistic metawebs. This showcases that although
-the components (species) that make up the Canadian and European
-communities may be \emph{minimally} shared (the overall species overlap
-is less than 4\%), if the medium (proxy space) selected in the transfer
-step is biologically plausible, we can still effectively learn from the
-known network and make biologically relevant predictions of
+mammalian species pool (using only a species list \emph{i.e.} we have no
+prior data on species interaction data for Canada in this instance). Our
+case study shows that phylogenetic transfer learning is an effective
+approach to the generation of probabilistic metawebs. This showcases
+that although the components (species) that make up the Canadian and
+European communities may be \emph{minimally} shared (the overall species
+overlap is less than 4\%), if the medium (proxy space) selected in the
+transfer step is biologically plausible, we can still effectively learn
+from the known network and make biologically relevant predictions of
 interactions. Indeed, as we detail in the results, when validated
@@
 matrix) and right (green/brown; top matrix) subspaces, alongside the
-adjacency matrix of the food web they encode (greyscale). The European
-metaweb is on the left, and the imputed Canadian metaweb (before data
-inflation) on the right. This figure illustrates how much structure the
-left subspace captures. As we show in fig.~\ref{fig:degree}, the species
-with a value of 0 in the left subspace are species without any
-prey.}\label{fig:subspaces}
+adjacency matrix of the food web they encode (greyscale). Where the
+color saturation is the magnitude of the latent trait value. The
+European metaweb is on the left, and the imputed Canadian metaweb
+(before data inflation) on the right. This figure illustrates how much
+structure the left subspace captures. As we show in
+fig.~\ref{fig:degree}, the species with a value of 0 in the left
+subspace are species without any prey.}\label{fig:subspaces}
 }
@@
 interactions. Right: distribution of the in-degree and out-degree of the
-mammals from Canada in the reconstructed metaweb. This figure describes
-a flat, relatively short food web, in which there are few predators but
-a large number of preys.}\label{fig:inflation}
+mammals from Canada in the reconstructed metaweb, where the rank is the
+maximal number of linearly independent columns (interactions) in the
+metaweb. This figure describes a flat, relatively short food web, in
+which there are few predators but a large number of
+preys.}\label{fig:inflation}
 }
@@
 first dimension. Left: differences in the \(z\)-scores of the actual
-configuration model for the reconstructed network, and the prediction
-based only on the first dimension. Right: distribution of the
-differences in the left panel.}\label{fig:degree}
+configuration model for the reconstructed network and the prediction
+based only on the first dimension (with a deeper saturation indicating a
+bigger difference in scores). Right: distribution of the differences in
+the left panel.}\label{fig:degree}
 }
